### 2016-03-31 main.tex
Initial ShareLaTeX Import

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand{\sii}{S~{\textsc II}\ } 
\newcommand{\oiii}{O~{\textsc III}\ } 
\newcommand{\hi}{H~{\textsc I}\ }

\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

%\defcitealias{Hossein12}{T12}

\begin{document}
% TITLE
\defcitealias{Hossein12}{T12}

\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: data mining approach}
\author{rahmani.sahar }
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
\maketitle

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%abstract
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\begin{abstract} 
In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.

\end{abstract}
\begin{keywords} 
 galaxies: star formation, galaxies: stellar content, galaxies: ISM, methods: observational, methods: statistical, data mining, methods:data analysis
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{sections/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{sections/}{data0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\import{sections/}{method0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{sections/}{results0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

%\import{sections/}{diss0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}
1) we used SOM blah blah balh.
\newline
2) with this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
\newline
3) This method can help us to find outliers or new categories of galaxies very easily  and fast.

\section*{ACKNOWLEDGMENTS}
S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining_h.bib}

\import{sections/}{apps0.0.tex}
\end{document}

### 2016-03-31 sections/data0.0.tex
Initial ShareLaTeX Import

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{DATA}
\label{sec: data}
%Basically these are 2012 data
As mentioned in Sec.~\ref{sec: intro}, for training neural networks, we used SED templates from K96.
Moreover, to test our networks, we obtained SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
 \subsection{Kinney spectral model}
    K96 produced a template of UV-optical spectra of 70 star forming and quiescent galaxies which can be used to classify the SED of the high redshift galaxies.
    They introduced 12 types of spectra based on their morphological type or colour excess for quiescent and star burst galaxies, respectively (~\ref{fig: k96}).
    %I know it is exactly as Hossein's plot, but I can see any other choice to put here.
    \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../images/k96.jpg}
        \caption{K96 spectra template for 12 types of galaxies.Type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belongs to early type galaxies. Star burst galaxies spectra are indicated with SB 1 to 6. Higher numbers represents more inartistic colour extinction.}
        \label{fig: k96}
    \end{figure}
    The quiescent group of galaxies includes Elliptical (E), Bulge (B), S0, Sa, Sb, and Sc galaxies.
    Bulge groups represents galaxies similar to M31 and M81, which their UV and optical spectroscopy dominated by the stellar population in their bulges.

    The star burst galaxies are divided in six groups (SB1 - SB6) based on their inartistic colour extinctions ($E(B-V)$). 
    As it is clear in the Fig.~\ref{fig: k96}, SB1 galaxies have lower internal colour excess ($E(B-V) \simeq 0.05$) while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among star burst galaxies.

    K96 spectra spans from $\sim1200-1000$\AA.
    However, we only used data between $\sim1200-1000$\AA~in Fig.~\ref{fig: k96}, over availability of flux information in those wavelength for all 12 groups.
    In early type galaxies spectrum (B-Sb), spectra is redder and strong absorption lines, and 4000\AA~break is distinguishable. 
    While SEDs of star burst galaxies are more flatter than early type one and show strong emission lines.
    For more details on each spectra type, we encourage readers to see K96 and references therein.

 \subsection{SED and Properties of the sample galaxies}
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field, which have a photometry data from the Good-MUSIC catalogue. 
    The photometry data contains data in 10 - 13 filters with wavelength range of $\sim 0.4-24 \mu$m. 
    They used these photometry data as inputs for Code Investigating GALaxy Emission (CIGALE code;~\citep{Noll09}) to generate the best fitted SED for each galaxy as well as some of the physical properties of the galaxies.

    CIGALE is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
    This code were successfully tested with data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match for each galaxies.
    For testing the created networks, we only used part of the spectra that have the same wavelength as K96 SEDs.
    Then, they used an exponentially decreasing SFR, visual attenuation ($\tau$) model and derived physical properties of galaxies such as age, and stellar mass.
    They assumed the Salpeter initial mass function~\citep{Salpeter55} and old stellar population age of $\sim 10$~Gyr.More details on creating SEDs and extracting information about galaxies properties using CIGALE can be found in N09 and T12.

### 2016-03-31 sections/intro0.0.tex
Initial ShareLaTeX Import

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}
\label{sec: intro}
% categorizing galaxies based on their SED
The light from galaxies is all the information we could get from them. 
All the observable phenomena inside galaxies leave footprint on galaxies' spectral energy distributions (SEDs).
With proper modeling of various features on their SEDs, some of the galaxies' physical properties can be determined.
Beside the physical properties of galaxies, SEDs of galaxies can be used as an identifier of the morphological type of the galaxies.
In the first attempt the morphological features of galaxies can be categorized to three main groups: elliptical, spiral or irregular galaxies.
Each of these groups have their own characteristic features and the first two groups can be divided to many branches.

Advances in imaging techniques, and photometry and spectroscopy devises help to have higher resolution data and more detailed SED. 
Thus, the variations between SEDs become more clear and the classification of galaxies became more complicated.
Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney94}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00}.%and more references
These templates are mostly restricted to wavelengths from near-IR to ultraviolet (UV), so they contain main features from physical properties of galaxies i.e. age, star formation rate (SFR), stellar mass, wide range of the stellar population, interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.

One of the main usage of the SED templates is finding the morphological type of high redshift galaxies. 
However, since not two galaxies, even with same morphology, are exactly the same, classifying the SED of the galaxies are a challenge.
Many fitting methods are developed and used to find the best matches of template for each SED.
$\chi^2$ minimizing method is the most commonly used method to do so. 
Artificial neural networks (ANNs) are the other method to find the morphological type of the galaxies based on their SED.

%ANNs
ANNs are very powerful tools to used in data processing and pattern recognitions problems.
Their information process method inspired by the way neurons in human brains work.
An ANN contains many interconnected units (neurons) which process data and work together to solve problems.
It uses sets of trainings method to learn about a nonlinear and complex relations between input and output data and how to apply it on new sets of data.
Studies shows that ANNs provides better fitting than minimizing chi square and would be an alternative choice for fitting data \citep[e.g.][]{Marquez91,Moayed09}

%SOMs and its advantages over supervised methods
Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by~\citep{Kohonen82}.
The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
%Both advantage and disadvantage of the unsupervised method is that there are no previous predictions about the outcome.
In supervised method, a neural network would be trained using input data based on desired outcome.
This method is very useful for classification of data with specific target values (i.e. classifying SED of galaxies from a SED template).
On the other hand, in unsupervised method there is no prediction of output data.
This method classifies data based on their underlying structures and hidden variables.
The unsupervised method is a very helpful method to knowledge discovery of your data, or when the underlying structure of data is not well established (i.e. producing a template of SED of galaxies) %eh

%What is this paper about
We obtained SED of a 142 galaxies with 0.5 < $z$ < 1 from~\citet[][hereafter T12]{Hossein12} paper.
T12 classified SED of a sample of galaxies using supervised neural network method, based on the spectral model presented by K96.
They classified SED of the 105 out of 142 galaxies using K96 template. 
The SED of the 37 galaxies from their samples could not be matched with any of those in the template. 
They found that the unclassified galaxies can be matched with a combined spectrum of the K96 model. 
They also showed that there are tight correlations between physical properties of galaxies and this correlations might be different based on the types of the galaxies.

In this paper, we used data from K96 template to train an unsupervised neural network.
The network clustered the SEDs and mapped those clusters and their relative relations.
We compared our results with K96 galaxies classification.
Then we classify the SED of the sample of 142 galaxies using the constructed SOM.
 In Section $\S$~\ref{sec: data}, we present the data. We describe the SOM in Section $\S$~\ref{sec: method}. The results of the SED classifications are shown in Section $\S$~\ref{sec: result} and discussed in Section $\S$~\ref{sec: diss}. In Section $\S$~\ref{sec: summary}, we present the summary of our conclusion and the future works in this subject.

### 2016-03-31 sections/method0.0.tex
Initial ShareLaTeX Import

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{METHOD}
\label{sec: method}
 \subsection{Self Organizing Maps}
 \label{sec: som}

 %Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by~\citep{Kohonen82}. 
% The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
 The SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
 Results of SOM contains nodes (usually hexagonal ones) that arranged in 1D or 2D arrays.

 Each nodes may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
 In the way that similar data are closer together in the array and the further nodes go from each other, the more dissimilarity appears between their samples.
 %Sahar_self_notes: maybe "some" is better instead of one or more
 Moreover,a weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be change during the process and has a key factor in a position of nodes in the map.

 \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail. In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results. %PB20160218: contrast SOM with principal component analysis (PCA), which may be more familiar?

 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on a map's topology provided by user.
     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
     The process of creating SOM, happens over series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration:
     \begin{enumerate}
        \item Choose a random vector from our data set.
        \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$". This neuron is the winner node and is calling Best Matching Unit (BMU). 
        \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item Change the weight vectors of the BMU and all the nodes within r(t) as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
        \item  Repeat these steps for $N$ times.
     \end{enumerate}

\subsection{Creating SOM}
\label{sec: create_som}
     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     SOM in {\tiny NNT} can be created by {\tiny newsom} library which works in two phases. 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.

     The second phase is the ``tuning phase".
     In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
     This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. 
     We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.

     To show our results, we combine two of the {\tiny NNT}'s built-in plots. 
     A Hits map, which shows number of hits for each neurons, and a distances map, which shows the same neurons as the hits map and the distance between them. 
     To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
     The neurons with zero hit, left empty.
     In distance maps, the grey hexagonal shape areas represent the neurons.
     The red lines between neurons, show the immediate neighbours.
     The distances in a distance map are showing by colours.
     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.

    %Although size of the SOM could be anything \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size.
     Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of maps. 
     Users usually must choose the size of grids based on their data set and their usages of the results.
     For our 10 regions we created maps with sizes from $1\times2$ to $50\times50$ to choose the sufficient size for our maps.
     varying grids of the maps helps us to monitor whether grouping regions in smaller maps is real or its because of the shortage of the neurons.
     Based on size of our data and our results, we chose max of the grid size to be 1$\times$10 and 10$\times$10 in 1D and 2D maps, respectively.

     Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
     Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
     %All the other parameters are default values in {\tiny newsom} library and cannot be changed by the users.

 %using self organizing maps instead of the newsom

### 2016-03-31 sections/results0.0.tex
Initial ShareLaTeX Import

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{RESULTS and DISCUSSION}
\label{sec: result}
    In this section we are showing the results of trained neural networks, using K96 data. 
    To have a realistic model of the input data we created SOMs with various sizes in both 1D and 2D.
    We start our analysing by creating 1D SOMs. 
    First, we created SOMs with only two neurons (1$\times$2 map) and then we increased number of neurons one at a time in 1D case (~\ref{sec: 1D}).
    Then we generated 2D networks (~\ref{sec: 2D}), and once again we start with smallest number of neuron possible (4 neurons in 2$\times$2 map) and then increased the number of neurons to 144 in 12$\times$12 map.

    For each generated network, we compare the results with K96 categorization.
    We also used these networks to classify the T12 galaxies samples, and compare them with classifications from supervised network.
    \subsection{1D SOMs}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            We assumed that galaxies can be divided only in two types; quiescent and star burst, and then generated a network with only two neurons.
            Then we increased size of the maps gradually till we separated the input 12 sample galaxies into the 12 neurons.

            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by3T} show results of training network.
            Upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance $D_j$ between the neurons and the darker is the colour the more $D_j$ is between them.
            The lower part shows how many galaxies from K96 template places in each neurons.

            In upper side of the Fig.~\ref{fig: 1by2T}, the red colour between two neurons indicate that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups.
            In the lower part of the Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc galaxies have been categorized as star burst galaxy due to their high amount of the emission lines.

            %add more about why Sc is acting differently
            %\import{~/images/texes/}{1by2_t.tex}
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/dist_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by2T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/hit_t_1_by_2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by2Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts. Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            Fig.~\ref{fig: 1by3T} shows results of the training in a 1$\times$3 network.
            In these plots we forced the galaxies to categorized themselves in maximum 3 groups. 
            If the galaxies in Fig.~\ref{fig: 1by2T} are very similar to each other or are exactly the same, they still want to be divided in two groups and left the middle node empty. 
            However, in the lower part of the Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
            These two galaxies, which are separated from group of star bust galaxies in the lower part of Fig.~\ref{fig: 1by2T},are types SB5 and SB6 galaxies.
            In upper plot of the Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is yellow. 
            The black colours indicates that the left neuron is completely different from the other two groups, while the yellow colour shows the two neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided to two groups. 
            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are star burst galaxies and have strong emission lines.
            However, these two groups have the most internal colour extinctions, so they intend to move more towards the early type galaxies.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/dist_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/hit_t_1_by_3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts. However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes when with increasing the size of map, program pays more attention to small differences between each groups.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together, respectively. 
            The SB3 and SB4 grouping breaks when we increased the size of the map to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E does not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{Results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

            In Fig.~\ref{fig: 1by22T}, although in lower plot we can see twelve different groups, but in upper plot 5 groups are in the left side neurons and there is a black colour between them and then the rest of the galaxies. 
            It shows that although we separated the galaxies in twelve groups but they are still divided by two main groups.
            The closest occupied neurons in the star burst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies have the most extinction and its SED has similarity to early type galaxies more than other star burst types.

            The fact that the galaxies had to have 22 different neurons till be divided to 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
            These small differences might be very hard to distinguish in normal classification methods and might lead to wrong classifications.

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the SEDs galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.55\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96. Up: Numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.

             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network ( Fig.~\ref{fig: 1by2T}). 
             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to star burst galaxies. 
             29 of the galaxies are more similar to star burst ones but, not with all of their features. 
             These group of galaxies have strong emission lines and the ascending slop towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of the Fig.~\ref{fig: 1by2V}).

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.55\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times3$ to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size we could see, the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of the Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_22.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times22$ to classify the sample galaxies.}
                \label{fig: 1by22V}
            \end{figure*}
            And the lower plot of the figure represents the average SED of the galaxies in each neurons.
            However, this time, since galaxies had more space to separated some of the neurons left empty. 
            Thus instead of having 22 average SED plots in the lower part of the Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of the Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
            If a groups of the T12 galaxies fills the same neurons as a K96 galaxies, we can conclude that this group of the galaxies have SEDs very similar to the SED of one of K96 galaxies.
            Whereas, we can conclude that a group of the galaxies have properties between the two groups if they fill a neuron which is empty and places between two categories of galaxies in the Fig.~\ref{fig: 1by22T}.
            However, the colours between these neurons in the upper side of the Fig.~\ref{fig: 1by22T}, establishes that the group of galaxies are more similar to which group.

            In the first two neurons of the upper plot in the Fig.~\ref{fig: 1by22V}, there is no galaxies, while in galaxies B and E are in the same neurons in the trained network.
            So we can conclude that there is no galaxies with similar
            There are 3 galaxies in the third neurons which shows these 3 galaxies are very much similar to the S0 type. 
            18 of the galaxies are on the fifth neurons and similar to the Sa type of the galaxies, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are in the edge of the early type and star burst galaxies.
            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
            The far right of the network, galaxies with SED comparable to type SB1 and SB2.

            In general from the 142 galaxies in T12, we categorized them as following; three of the galaxies belongs to SO galaxies, fifteen are Sa, one is Sb, four are SB6, two are SB5, and 21 have a similar SED to SB2.
            The rest of the galaxies have SEDs in between of the initial 12 suggestions.
            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model were constructed from co-adding 12 spectra of the 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model, perfectly and the original classifications have high uncertainty.

            On the other hand, all the other methods (i.e. $\chi^2$ fitting, trained neural network) of matching SEDs limit themselves to models, and if they could not find the best match, report the results as an uncertain ones.
            However, with SOM, galaxies have this freedom to be categorized in the intermediate groups.
            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.

        \subsubsection{1D NETWORKS results and Properties of galaxies}

    \subsection{2D SOMs}
    \label{sec: 2D}
    Although the 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category, each neurons in these networks is limited to be connected to on other neurons in each direction.
    Since each neuron can have more than two immediate neighbours in the 2D networks, they provide more complete pictures of the relation between each SED type.
    For analysing 2D networks, we consider two approaches; at first we assumed that all the galac

    \subsection{Caveat}
    There is no established method to find the best SOM initial values. Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new result.
    Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.

### 2016-03-31 main.tex
End of Draft 0.0

@@
 
-\begin{abstract} 
+\begin{abstract} %Most of this abstract is just a filler
 In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
@@
 We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
+We obtain physical properties of the sample galaxies measured using {\em CIGALE} code to study and compare the properties of each cluster.
 In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
+%%%%%%From this point it is just repeated%%%%%%%%%
 We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
@@
 
-\import{sections/}{intro0.0.tex}
+\import{sections0.0/}{intro0.0.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections/}{data0.0.tex}
+\import{sections0.0/}{data0.0.tex}
 
@@
 
-\import{sections/}{method0.0.tex}
+\import{sections0.0/}{method0.0.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections/}{results0.0.tex}
+\import{sections0.0/}{results0.0.tex}
 %----------------------------------------------------------------------------------------
@@
 
-%\import{sections/}{diss0.0.tex}
+%\import{sections0.0/}{diss0.0.tex}
 
@@
 \label{sec: summary}
-1) we used SOM blah blah balh.
+1) We introduced the self organizing maps to be used to categorizing the SED of galaxies.
 \newline
-2) with this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
+2) Using this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
 \newline
@@
 
+4) ...
 \section*{ACKNOWLEDGMENTS}
@@
 
-\import{sections/}{apps0.0.tex}
+\import{sections0.0/}{apps0.0.tex}
 \end{document}

### 2016-03-31 sections0.0/apps0.0.tex
End of Draft 0.0

\newpage
\appendix
\section{Results of the 1D training and validagtion}
\label{app: 1d}
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_4.png}
            %\caption{$1\times4$ weight map}
             %\label{fig: 1by4T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_4.png}
             %\caption{$1\times4$ hits map}
             %\label{fig: 1by4Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times4$~grid.}
         \label{fig: 1by4T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_5.png}
            %\caption{$1\times5$ weight map}
             %\label{fig: 1by5T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_5.png}
             %\caption{$1\times5$ hits map}
             %\label{fig: 1by5Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times5$~grid.}
         \label{fig: 1by5T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_6.png}
            %\caption{$1\times6$ weight map}
             %\label{fig: 1by6T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_6.png}
             %\caption{$1\times6$ hits map}
             %\label{fig: 1by6Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times6$~grid.}
         \label{fig: 1by6T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_7.png}
            %\caption{$1\times7$ weight map}
             %\label{fig: 1by7T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_7.png}
             %\caption{$1\times7$ hits map}
             %\label{fig: 1by7Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times7$~grid.}
         \label{fig: 1by7T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_8.png}
            %\caption{$1\times8$ weight map}
             %\label{fig: 1by8T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_8.png}
             %\caption{$1\times8$ hits map}
             %\label{fig: 1by8Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times8$~grid.}
         \label{fig: 1by8T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_9.png}
            %\caption{$1\times9$ weight map}
             %\label{fig: 1by9T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_9.png}
             %\caption{$1\times9$ hits map}
             %\label{fig: 1by9Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times9$~grid.}
         \label{fig: 1by9T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_10.png}
            %\caption{$1\times10$ weight map}
             %\label{fig: 1by10T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_10.png}
             %\caption{$1\times10$ hits map}
             %\label{fig: 1by10Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times10$~grid.}
         \label{fig: 1by10T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_11.png}
            %\caption{$1\times11$ weight map}
             %\label{fig: 1by11T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_11.png}
             %\caption{$1\times11$ hits map}
             %\label{fig: 1by11Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times11$~grid.}
         \label{fig: 1by11T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_12.png}
            %\caption{$1\times12$ weight map}
             %\label{fig: 1by12T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_12.png}
             %\caption{$1\times12$ hits map}
             %\label{fig: 1by12Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times12$~grid.}
         \label{fig: 1by12T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_15.png}
            %\caption{$1\times15$ weight map}
             %\label{fig: 1by15T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_15.png}
             %\caption{$1\times15$ hits map}
             %\label{fig: 1by15Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times15$~grid.}
         \label{fig: 1by15T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_20.png}
            %\caption{$1\times20$ weight map}
             %\label{fig: 1by20T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_20.png}
             %\caption{$1\times20$ hits map}
             %\label{fig: 1by20Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times20$~grid.}
         \label{fig: 1by20T}
    \end{figure}

### 2016-03-31 sections0.0/data0.0.tex
End of Draft 0.0

--- 2016-03-31 sections/data0.0.tex
@@
     The photometry data contains data in 10 - 13 filters with wavelength range of $\sim 0.4-24 \mu$m. 
-    They used these photometry data as inputs for Code Investigating GALaxy Emission (CIGALE code;~\citep{Noll09}) to generate the best fitted SED for each galaxy as well as some of the physical properties of the galaxies.
+    They used these photometry data as inputs for Code Investigating GALaxy Emission ({\em CIGALE} code;~\citep{Noll09}) to generate the best fitted SED for each galaxy as well as some of the physical properties of the galaxies.
 
-    CIGALE is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
+    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
     It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
@@
     Then, they used an exponentially decreasing SFR, visual attenuation ($\tau$) model and derived physical properties of galaxies such as age, and stellar mass.
-    They assumed the Salpeter initial mass function~\citep{Salpeter55} and old stellar population age of $\sim 10$~Gyr.More details on creating SEDs and extracting information about galaxies properties using CIGALE can be found in N09 and T12.
+    Some of these properties are shown in Tab~\ref{tab: props}.
+    In the Sec.~\ref{sec: 1D}, we studied these properties for each categorization.
+    They assumed the Salpeter initial mass function~\citep{Salpeter55} and old stellar population age of $\sim 10$~Gyr.
+    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.
+
+    \begin{table}
+\caption[]{Description of the properties of T12 galaxies; the output result of {\em CIGALE}}     
+\label{tab: props}
+\centering
+\begin{tabular}{l l l}
+\hline\hline
+\noalign{\smallskip}
+Par. & Unit & Description\\
+\noalign{\smallskip}
+\hline
+\noalign{\smallskip}
+$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
+$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
+$f_\mathrm{burst}$ & --- & mass fraction of \\
+& & young SP model \\
+\noalign{\smallskip}
+$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age. \\
+\noalign{\smallskip}
+$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
+SFR & M$_\odot$/yr & instantaneous SFR  \\
+\noalign{\smallskip}
+\hline
+\end{tabular}
+\end{table}

### 2016-03-31 sections0.0/method0.0.tex
End of Draft 0.0

--- 2016-03-31 sections/method0.0.tex
@@
 In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results.
-%PB20160218: contrast SOM with principal component analysis (PCA), which may be more familiar?
-
  \subsubsection{Algorithm of SOM} 
@@
      In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     SOM in {\tiny NNT} can be created by {\tiny newsom} library which works in two phases. 
+     SOM in {\tiny NNT} can be created by {\tiny newsom} or {\tiny selforgmap} library which both work in two phases. 
      Phase one is the ``ordering phase". 
@@
      Users usually must choose the size of grids based on their data set and their usages of the results.
-     For our 10 regions we created maps with sizes from $1\times2$ to $50\times50$ to choose the sufficient size for our maps.
-     varying grids of the maps helps us to monitor whether grouping regions in smaller maps is real or its because of the shortage of the neurons.
-     Based on size of our data and our results, we chose max of the grid size to be 1$\times$10 and 10$\times$10 in 1D and 2D maps, respectively.
+     For training networks using 12 galaxies from K96, we created maps with sizes from $1\times2$ to $50\times50$ to choose the sufficient size.
+     varying grids of the maps helps us to monitor whether grouping galaxies in smaller maps is because they have similar SEDs or its because of the shortage of the neurons.
+     Based on size of our data and our results, we chose max of the grid size to be 1$\times$22 and 12$\times$12 in 1D and 2D maps, respectively.
 

### 2016-03-31 sections0.0/results0.0.tex
End of Draft 0.0

--- 2016-03-31 sections/results0.0.tex
@@
         \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
+         \label{sec: 1Dv}
             We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
@@
         \subsubsection{1D NETWORKS results and Properties of galaxies}
+        In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, we plot the some physical properties listed in the Tab.~\ref{tab: props} of galaxies in each neurons in the networks.
+
+        \begin{figure}
+            \centering
+            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_2.png}
+            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by2V}}
+            \label{fig: prop1by2}
+        \end{figure}
+
+                \begin{figure}
+            \centering
+            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
+            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
+            \label{fig: prop1by3}
+        \end{figure}
+
+                \begin{figure}
+            \centering
+            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
+            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
+            \label{fig: prop1by22}
+        \end{figure}
+
+        Figs.~\ref{fig: prop1by2} to ~\ref{fig: prop1by22} show the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
+        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.
+
+        In Fig.~\ref{fig: prop1by2}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases. 
+        The same trend is noticeable in both Fig.~\ref{fig: prop1by3} and Fig.~\ref{fig: prop1by22}. 
+        The gaps in the Fig.~\ref{fig: prop1by22} is due to the empty neurons in Fig.~\ref{fig: 1by22V}.
+These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.
 
@@
     Since each neuron can have more than two immediate neighbours in the 2D networks, they provide more complete pictures of the relation between each SED type.
-    For analysing 2D networks, we consider two approaches; at first we assumed that all the galac
+    As described in the Sec.\ref{sec: method}, one of the main advantages of the SOM method is when weight of one neurons is adjusted after finding the BMU, weight of the whole map will be changed.
+    This quality of the SOMs provide us an opportunity to analysing 2D networks in two approaches. 
+    At first, as we had in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 models in Fig.~\ref{fig: k96}.
+    For the second path, we trained networks assuming that there might be some other and completely different types of the galaxies that we never encountered with before.
+    Second approach could be used to trace the outliers as well.
+
+    %maybe I should move the following paragraph to method section?! I am not sure, yet.
+    For getting the best result from both of these ways, we should have SOMs with high ``enough"  neurons to give any new sets of galaxies a chance to find their best place in the map.
+    The  high ``enough"  neurons is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and what kind of the information you need from the SOMs.
+    Since the training data (K96 ones) have 12 galaxies, we assumed a SOM with size of $8\times8$~would be a good start.
+    We then increased the size of SOM to find the highest size suitable for the training sample.
+    We noticed that SOMs with size of $12\times12$~are the maximum possible choice.
+    With increasing from $12\times12$~neurons, the SOMs would be repeat the same shapes just in bigger grids.
+
+    \begin{figure}
+        \begin{subfigure}[b]{0.5\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_12.png}
+            %\caption{$1\times22$ weight map}
+             %\label{fig: 1by22T}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_12.png}
+             %\caption{$1\times22$ hits map}
+             %\label{fig: 1by22Thits}
+        \end{subfigure}
+        \caption{Results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
+        \label{fig: 12by12T_newsom}
+    \end{figure}
+    Fig.~\ref{fig: 12by12T_newsom} shows the SOM results for the first approach. 
+    Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
+    Using this network to categorize any set of SEDs, forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
+    However, all the K96 galaxies are in small side of the map in Fig.~\ref{fig: 12by12T_selforg}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 samples.
+    \begin{figure}
+        \begin{subfigure}[b]{0.5\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_self_org_res12.png}
+            %\caption{$1\times22$ weight map}
+             %\label{fig: 1by22T}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_self_org_res12.png}
+             %\caption{$1\times22$ hits map}
+             %\label{fig: 1by22Thits}
+        \end{subfigure}
+        \caption{Results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
+        \label{fig: 12by12T_selforg}
+    \end{figure}
+
+    In the upper map in Fig.~\ref{fig: 12by12T_newsom}, there is a strip of the red, dark red and in some case black colours is distinguishable. 
+    This strip is separating early type galaxies with star burst ones.
+    The lower map shows that 5 of the neurons on left side of the strip are full. 
+    These 5s are the same ones in the left hand side of the Fig.~\ref{fig: 1by2T} (early type galaxies).
+    The only difference is that here, in this map they have more space to be separated from each other.
+    When we use this network to categorized the SED of galaxies any galaxy places on the left hand side of the strip is an early type galaxy and any one placed in the right side of the strip is a star burst one.
+    Decision about what type of the early type or star burst galaxy is it, is based upon its relative position to each type in the neurons.
+
+    The border between the early type galaxies and the star burst ones,in the Fig.~\ref{fig: 12by12T_selforg}, is the black strips in the middle of the upper map, which end up with bright red colour at the bottom of the map in the fifth neuron.
+    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the star burst ones.
+    In case of the categorizing a new set of SEDs, if the new SEDs are similar to K96 sample all of them will place in the bottom of the map, but if there are different type of the galaxies, they would sit in any other neurons in the map.
+
+    We used the both 2D networks to categorized the T12 galaxies and showed the results in Fig.~\ref{fig: 12by12V}.
+    In the lower plot, we used the network from Fig.~\ref{fig: 12by12T_selforg}.
+    Since all the galaxies placed in the bottom part of the map, we can conclude that there in no outlier or very different type of the SED in from K96 models in T12 samples.
+    The upper plot of the Fig.~\ref{fig: 12by12V} represents the T12 galaxies categorization based on the network in the Fig.~\ref{fig: 12by12T_newsom}. 
+    In both maps in the Fig.~\ref{fig: 12by12V}, majority of the galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.
+
+       \begin{figure}
+        \begin{subfigure}[b]{0.5\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_12.png}
+            %\caption{$1\times22$ weight map}
+             %\label{fig: 1by22T}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_self_org_res12.png}
+             %\caption{$1\times22$ hits map}
+             %\label{fig: 1by22Thits}
+        \end{subfigure}
+        \caption{Results of categorizing T12 galaxies using $12\times12$~network.
+Up: categorizing with network shown in Fig.~\ref{fig: 12by12T_newsom}.
+Down: using network in Fig.~\ref{fig: 12by12T_selforg}.}
+        \label{fig: 12by12V}
+    \end{figure}
+
+    Although because of the fluency of the paper, we first talked about 1D networks and continued to 2D networks we suggest that in case of using the SOMs to categorize the SED of the galaxies or to explore any related data, first step to be checking data using networks similar to the Fig.~\ref{fig: 12by12T_selforg} ones.
+    In this case, all the outlier or specific cases would be identified and removed from the sample.
 
@@
     Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
+    %no quantitative way to analyse the data?!

### 2016-04-12 sections0.0/intro0.0.tex
Adding new lines about usage of SOM in astronomy

--- 2016-03-31 sections/intro0.0.tex
@@
 Thus, the variations between SEDs become more clear and the classification of galaxies became more complicated.
-Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney94}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00}.%and more references
+Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00}.%and more references
 These templates are mostly restricted to wavelengths from near-IR to ultraviolet (UV), so they contain main features from physical properties of galaxies i.e.
@@
 $\chi^2$ minimizing method is the most commonly used method to do so. 
-Artificial neural networks (ANNs) are the other method to find the morphological type of the galaxies based on their SED.
+Artificial neural networks (ANNs), K-mean clustering, and principle component analysis are the other methods to cluster and classifying the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
 
@@
 
+%SOM in Astronomy
+The utilization of the SOM in astronomy dates back to 1990s. 
+\citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} were among the first studies in astronomy that used SOM for their studies.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classificationf of light curves, this method have been used in various aspects in astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
+\citet{Geach12} used COSMOS data to demonstrate two of main application of SOMs; object classification and clustering, and photometric redshift estimation. 
+The later one were subject of many studies \citep[e.g.][]{Kind14a}
+\citet{In12} introduced a new clustering tool which is based on SOM method to analysing large data of spectra.
+They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09}
+to test their tool, and created very large SOMs to analyse the type of spectra/objects.
+They also generated SOMs from quasar spectra in order to find unusual types of quasars spectra.
+Later \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys and found a new class of quasars.
+The other application of the SOM is to find outliers or errors in the data.
+\citet{Fustes13} used this method to produced a package to classify results from GAIA surveys and find the outlier or errors in the instruments or pipelines.
+
 %What is this paper about
@@
 Then we classify the SED of the sample of 142 galaxies using the constructed SOM.
+
  In Section $\S$~\ref{sec: data}, we present the data.
 We describe the SOM in Section $\S$~\ref{sec: method}.
-The results of the SED classifications are shown in Section $\S$~\ref{sec: result} and discussed in Section $\S$~\ref{sec: diss}.
+The results of the SED classifications and comparing them with previous studoes are shown in Section $\S$~\ref{sec: result}.
 In Section $\S$~\ref{sec: summary}, we present the summary of our conclusion and the future works in this subject.

### 2016-04-19 sections0.0/apps0.0.tex
Updates from ShareLaTeX

@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_4.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/apps/dist_1_by_4.png}
             %\caption{$1\times4$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_4.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_4.png}
              %\caption{$1\times4$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_5.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/apps/dist_1_by_5.png}
             %\caption{$1\times5$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_5.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_5.png}
              %\caption{$1\times5$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_6.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/apps/dist_1_by_6.png}
             %\caption{$1\times6$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_6.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_6.png}
              %\caption{$1\times6$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_7.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/apps/dist_1_by_7.png}
             %\caption{$1\times7$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_7.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_7.png}
              %\caption{$1\times7$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_8.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/apps/dist_1_by_8.png}
             %\caption{$1\times8$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_8.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_8.png}
              %\caption{$1\times8$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_9.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/apps/dist_1_by_9.png}
             %\caption{$1\times9$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_9.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_9.png}
              %\caption{$1\times9$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_10.png}
+            \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/dist_1_by_10.png}
             %\caption{$1\times10$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_10.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_10.png}
              %\caption{$1\times10$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_11.png}
+            \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/dist_1_by_11.png}
             %\caption{$1\times11$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_11.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_11.png}
              %\caption{$1\times11$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_12.png}
+            \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/dist_1_by_12.png}
             %\caption{$1\times12$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_12.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_12.png}
              %\caption{$1\times12$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_15.png}
+            \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/dist_1_by_15.png}
             %\caption{$1\times15$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_15.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_15.png}
              %\caption{$1\times15$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_20.png}
+            \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/dist_1_by_20.png}
             %\caption{$1\times20$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_20.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_20.png}
              %\caption{$1\times20$ hits map}

### 2016-04-19 sections0.0/data0.0.tex
Updates from ShareLaTeX

@@
 $f_\mathrm{burst}$ & --- & mass fraction of \\
-& & young SP model \\
+& & young single population (SP) model \\
 \noalign{\smallskip}

### 2016-04-19 sections0.0/results0.0.tex
Updates from ShareLaTeX

@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images/1d/dist_1_by_2.png}
+                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
                     %\caption{$1\times2$ weight map}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images/1d/hit_t_1_by_2.png}
+                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
                      %\caption{$1\times2$ hits map}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images/1d/dist_1_by_3.png}
+                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
                     %\caption{$1\times2$ weight map}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images/1d/hit_t_1_by_3.png}
+                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
                      %\caption{$1\times2$ hits map}
@@
                 \centering
-                \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_22.png}
+                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
             %\caption{$1\times22$ weight map}
@@
             \begin{subfigure}[b]{\textwidth}
-                \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_22.png}
+                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
              %\caption{$1\times22$ hits map}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_2.png}
+                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
                     %\caption{$1\times2$ weight map}
@@
                 \hfill
-                \begin{subfigure}[b]{0.55\textwidth}
+                \begin{subfigure}[b]{0.5\textwidth}
                      \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_3.png}
+                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_3.png}
                     %\caption{$1\times2$ weight map}
@@
                 \hfill
-                \begin{subfigure}[b]{0.55\textwidth}
-                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by3.png}
+                \begin{subfigure}[b]{0.5\textwidth}
+                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by3.png}
                      %\caption{$1\times2$ hits map}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_22.png}
+                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22.png}
                     %\caption{$1\times2$ weight map}
@@
                 \begin{subfigure}[b]{0.9\textwidth}
-                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by22.png}
+                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
                      %\caption{$1\times2$ hits map}
@@
 
-        \begin{figure}
+        \begin{figure*}
             \centering
-            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_2.png}
-            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by2V}}
-            \label{fig: prop1by2}
-        \end{figure}
+            \includegraphics[width=\textwidth]{../images0.01/1d/props3.png}
+            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
+            \label{fig: props}
+        \end{figure*}
 
-                \begin{figure}
-            \centering
-            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
-            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
-            \label{fig: prop1by3}
-        \end{figure}
+        %         \begin{figure}
+        %     \centering
+        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
+        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
+        %     \label{fig: prop1by3}
+        % \end{figure}
 
-                \begin{figure}
-            \centering
-            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
-            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
-            \label{fig: prop1by22}
-        \end{figure}
+        %         \begin{figure}
+        %     \centering
+        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
+        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
+        %     \label{fig: prop1by22}
+        % \end{figure}
 
-        Figs.~\ref{fig: prop1by2} to ~\ref{fig: prop1by22} show the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
+        Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
         In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.
 
-        In Fig.~\ref{fig: prop1by2}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases. 
-        The same trend is noticeable in both Fig.~\ref{fig: prop1by3} and Fig.~\ref{fig: prop1by22}. 
-        The gaps in the Fig.~\ref{fig: prop1by22} is due to the empty neurons in Fig.~\ref{fig: 1by22V}.
+        In Fig.~\ref{fig: props}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases, in all three lines. 
         These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_12.png}
+            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_12.png}
             %\caption{$1\times22$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_12.png}
+            \includegraphics[width=\textwidth]{../images0.01/2d/hit_t_12_by_12.png}
              %\caption{$1\times22$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_self_org_res12.png}
+            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_self_org_res12.png}
             %\caption{$1\times22$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_self_org_res12.png}
+            \includegraphics[width=\textwidth]{../images0.01/2d/hit_t_12_by_self_org_res12.png}
              %\caption{$1\times22$ hits map}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_12.png}
+            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_12.png}
             %\caption{$1\times22$ weight map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_self_org_res12.png}
+            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_self_org_res12.png}
              %\caption{$1\times22$ hits map}

### 2016-04-19 sections0.01/method0.01.tex
Updates from ShareLaTeX

--- 2016-03-31 sections0.0/method0.0.tex
@@
      A Hits map, which shows number of hits for each neurons, and a distances map, which shows the same neurons as the hits map and the distance between them. 
-     To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
-     The neurons with zero hit, left empty.
-     In distance maps, the grey hexagonal shape areas represent the neurons.
-     The red lines between neurons, show the immediate neighbours.
+     %To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
+     In the maps, the purple hexagonal shape areas represent the neurons.
+     %The red lines between neurons, show the immediate neighbours.
      The distances in a distance map are showing by colours.
      The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.
+     In hit maps, neurons with zero hit left empty.
 
@@
 
- %using self organizing maps instead of the newsom
+\subsection{Mock sample}
+
+         \begin{figure}
+            \begin{subfigure}[b]{0.5\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{../images0.01/sample/sample2_dist.png}
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}[b]{0.5\textwidth}
+                \includegraphics[width=\textwidth]{../images0.01/sample/sample2_hits.png}
+            \end{subfigure}
+            \caption{SOM of the mock sample.
+In both plots axis shows the position of the neurones.
+Hexagonal shapes represent the neurons.
+The upper plot is a distance map.
+The gray cycle colours shows the differences between weight of each neuron with withe is the minimum differences and black has the maximum one.
+The lower plot is a hit plot.
+It represents number of samples in each neurons, while the empty with neurons means zero hit.
+In this sample the 27 galaxies clustered in 4 groups of 8, 7, 6 and 6 galaxies.}
+            \label{fig: sample}
+        \end{figure}
+
+ We created  a mock sample of 27 galaxies to illustrate the results of SOMs and how they can be analyzed, and to show how this method works.
+ The mock sample contains two information from each galaxy; first type of galaxies: type 1 or type 2, and either they are high or low star forming galaxies.
+ We generated a SOM with size of $10 \times 10$ using the same initial values mentioned in the Section ~\ref{sec: create_som}.
+
+ Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
+ The upper plot is a distance map. 
+ The axis show the position of the neurons in a $10 \times 10$ network. 
+ The purple hexagons are illustration of the neurons, and the colours of the area between neighbours are showing the differences between weight of each two neurons.
+ In distance maps colour white between neurons represents the minimum value of the differences between weights of neurons and the colour black shows the maximum values. 
+ The gray cycle colour between white and black shows values between minimum and maximum with darker colour means more differences.
+
+ The lower plot in the Fig.~\ref{fig: sample} shows a hit map.
+ In this map similar to the distance map the axis shows the position of the neurons where the hexagonal shapes are neurons.
+ %White neurons show the empty neurons.
+ The purple neurons with a number on them shows the number of galaxy in that neurons.
+ Colour coverage of neurons is different and depends on the number of the hits on the sample.
+ The neuron with the maximum number of hits is completely coloured while the empty neurons are white.
+
+Using this method, as we predicted, we were able to divide the mock sample galaxies in 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
+The upper plot in the Fig.~\ref{fig: sample}, clearly shows this division.
+The upper part of the plot are high star forming galaxies, while the lower part of it belongs to the low star forming galaxies.
+The left part of the plots is where type 1 galaxies belong to and the right side is for type 2 galaxies.
+Grey to black colours shows the border between regions.
+The lower plot in Fig.~\ref{fig: sample} shows only 4 neurons out of 100 were occupied. 
+8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
+The reason of that there are only 4 filled neurons in the network is the simplicity of the input data, and the fact that each entry only could get either 0 or 1 as for type of galaxy and 0 or 0.5 as an indicator of SFR.
+It shows us although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed in only four groups.
+
+As we see in the following sections, In the real world with the real data, we never have two galaxies with exactly the same information.
+Therefore, if we gave them enough space they would eventually separate from each other to smaller and smaller groups. 
+However, if the  the number of neurons are maaaaauch higher than number of input samples, it shows the input data are pretty similar to each other.

### 2016-04-19 sections0.01/method0.01.tex
finishing the mock sample section 0.01

@@
 The upper plot is a distance map.
-The gray cycle colours shows the differences between weight of each neuron with withe is the minimum differences and black has the maximum one.
+The gray cycle colours shows the differences between weight of each neuron with white is the minimum differences and black has the maximum one.
 The lower plot is a hit plot.
@@
 
-As we see in the following sections, In the real world with the real data, we never have two galaxies with exactly the same information.
-Therefore, if we gave them enough space they would eventually separate from each other to smaller and smaller groups. 
-However, if the  the number of neurons are maaaaauch higher than number of input samples, it shows the input data are pretty similar to each other.
+As we show in the following sections, in the real world with the real data, we never have two galaxies with exactly the same information.
+Therefore, if the network has high enough neurons, the input data would eventually separate from each other and cluster into the smaller and smaller groups. 
+However, if the information of the input data are pretty similar to each other, the number of neurons are going to be much higher than number of input samples. 
+In similar cases, one can decide that the amount of similarity or dissimilarity between the input samples.

### 2016-04-20 main.tex
Adding new lines about usage of SOM in astronomy
Updates from ShareLaTeX
adding props_vs_props plot and writing about it. Add more comparison with T12

@@
 \newcommand \kpc        {\,{\rm kpc}}
-\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
-\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
-\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
-\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
-\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
-\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
-\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
 \newcommand \halpha    {H$\alpha $\ }
@@
 
-\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: data mining approach}
+\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach}
 \author{rahmani.sahar }
@@
 
-\import{sections0.0/}{method0.0.tex}
+\import{sections0.01/}{method0.01.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.0/}{results0.0.tex}
+\import{sections0.01/}{results0.01.tex}
 %----------------------------------------------------------------------------------------
@@
 
-4) ...
+4) We plot the properties of the galaxies using new classification and see the correlation between age and SSFR and stellar mass of the galaxies.
+
 \section*{ACKNOWLEDGMENTS}

### 2016-04-20 sections0.0/data0.0.tex
adding props_vs_props plot and writing about it. Add more comparison with T12

@@
  \subsection{Kinney spectral model}
-    K96 produced a template of UV-optical spectra of 70 star forming and quiescent galaxies which can be used to classify the SED of the high redshift galaxies.
-    They introduced 12 types of spectra based on their morphological type or colour excess for quiescent and star burst galaxies, respectively (~\ref{fig: k96}).
-    %I know it is exactly as Hossein's plot, but I can see any other choice to put here.
      \begin{figure}
@@
         \includegraphics[width=0.5\textwidth]{../images/k96.jpg}
-        \caption{K96 spectra template for 12 types of galaxies.Type of each template is shown in each frame.
+        \caption{K96 spectra template for 12 types of galaxies from T12 paper.Type of each template is shown in each frame.
 Plots B, E, S0, Sa, Sb and SC show spectra that belongs to early type galaxies.
@@
     \end{figure}
+    K96 produced a template of UV-optical spectra of 70 star forming and quiescent galaxies which can be used to classify the SED of the high redshift galaxies.
+    They introduced 12 types of spectra based on their morphological type or colour excess for quiescent and star burst galaxies, respectively (~\ref{fig: k96}).
+    %I know it is exactly as Hossein's plot, but I can see any other choice to put here.
+
     The quiescent group of galaxies includes Elliptical (E), Bulge (B), S0, Sa, Sb, and Sc galaxies.

### 2016-04-20 sections0.01/results0.01.tex
adding props_vs_props plot and writing about it. Add more comparison with T12

--- 2016-04-19 sections0.0/results0.0.tex
@@
             The lower part shows how many galaxies from K96 template places in each neurons. 
+            \begin{figure}
+                \begin{subfigure}[b]{0.5\textwidth}
+                    \centering
+                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.5\textwidth}
+                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
+                \end{subfigure}
+                \caption{Results of training network in $1\times2$~grid.
+Similar to the Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map.
+In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts.
+Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
+                 \label{fig: 1by2T}
+            \end{figure}
 
@@
             %add more about why Sc is acting differently
-            %\import{~/images/texes/}{1by2_t.tex}
-            \begin{figure}
-                \begin{subfigure}[b]{0.5\textwidth}
-                    \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
-                    %\caption{$1\times2$ weight map}
-                     %\label{fig: 1by2T}
-                \end{subfigure}
-                \hfill
-                \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by2Thits}
-                \end{subfigure}
-                \caption{Results of training network in $1\times2$~grid.
-In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts.
-Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
-                 \label{fig: 1by2T}
-            \end{figure}
 
@@
                     \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
-                    %\caption{$1\times2$ weight map}
-                     %\label{fig: 1by3T}
                 \end{subfigure}
@@
                      \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by3Thits}
                 \end{subfigure}
-                \caption{Results of training network in $1\times3$~grid.
+                \caption{The same as the Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid.
 In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts.
@@
             \end{subfigure}
-            \caption{Results of training network in $1\times22$~grid.}
+            \caption{The same as the Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
             \label{fig: 1by22T}
@@
                 \end{subfigure}
-                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96.
-Up: Numbers in each node represents the number of galaxies that belong to that group.
+                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in the Fig.~\ref{fig: 1by2T}.
+Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group.
 In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies.
@@
                 \end{subfigure}
-                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times3$ to classify the sample galaxies.}
+                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                 \label{fig: 1by3V}
@@
                 \end{subfigure}
-                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times22$ to classify the sample galaxies.}
+                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
+In the average SED of each neurons we can clearly see the changes from early type galaxies to the star burst ones.
+4000\AA~ breaks reduces from left to right and emission lines increases.}
                 \label{fig: 1by22V}
@@
 
-        \subsubsection{1D NETWORKS results and Properties of galaxies}
+        \subsubsection{1D NETWORKS results and Properties of clustered galaxies}
+
         In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, we plot the some physical properties listed in the Tab.~\ref{tab: props} of galaxies in each neurons in the networks.
 
-        \begin{figure*}
+        \begin{figure}
             \centering
-            \includegraphics[width=\textwidth]{../images0.01/1d/props3.png}
+            \includegraphics[width=0.5\textwidth]{../images0.01/1d/props4.png}
             \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
             \label{fig: props}
-        \end{figure*}
-
-        %         \begin{figure}
-        %     \centering
-        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
-        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
-        %     \label{fig: prop1by3}
-        % \end{figure}
-
-        %         \begin{figure}
-        %     \centering
-        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
-        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
-        %     \label{fig: prop1by22}
-        % \end{figure}
+        \end{figure}
 
         Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
-        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.
+        In all the plots $x$-axis shows the normalized number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.
+
+                \begin{figure*}
+        \begin{subfigure}[b]{\textwidth}
+            \centering
+            \includegraphics[width=\textwidth,height=6cm]{../images0.01/1d/age_vs_ssfr.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{\textwidth}
+            \includegraphics[width=\textwidth,height=6cm]{../images0.01/1d/ssfr_vs_stellar_mass.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{\textwidth}
+            \includegraphics[width=\textwidth,height=6cm]{../images0.01/1d/age_vs_stellar_mass.png}
+        \end{subfigure}
+        \caption{From up to down: Correlation between age ($^tD4000$) and SSFR, SSFR and stellar mass, and  age ($^tD4000$) and stellar mass.
+Points show the mean values of these properties from galaxies in $1\times22$ network.
+colours shows the type of the galaxies in the new classification.
+The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies.
+The other colours depends on how much they are close to red or blue show that the galaxies are early type or star burst.}
+        \label{fig: props_vs_props}
+    \end{figure*}
 
@@
         These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.
+
+        In order to compare our classifications with other works, we ploted some properties of the galaxies against each other for each network.%reproduced figure 16 in T12 using properties of galaxies in each networks.
+        All the plots shows the similar trend as plots in the Fig.~\ref{fig: props_vs_props} which shows the plots from $1\times22$ network. 
+        Points are mean values of the properties of the galaxies from T12 sample, with the standard deviation of those properties.
+        colours show the galaxy types where B type galaxies are shown with red and SB1 ones are shown with blue colours.
+        The spectrum from the red to blue shows the type of the galaxies in the new classifications. 
+        The redder the colour the more similarity with early type galaxies, while the purple to blue colours show more similarity to star burst galaxies.
+        Since in this method we allow galaxies to stay in the classes between the original 12 types of the galaxies, we have more than 12 colours in the Fig.~\ref{fig: props_vs_props}.
+
+        Both N09 and T12 have the similar plots with the same properties.
+        However, since in both of these papers they considered only 12 types for the galaxies, those plots have a different colours than ours.
+        Our results shows the same relation between parameters with tighter correlation in all three plots.
+        galaxies with SED similar to type Sc having bright purple colour but as expected from the shape of the SED they are young galaxies with high SSFR.
+        Therefore, in all three plots of the Fig.~\ref{fig: props_vs_props}, there is a purple point in the middle of the blue points.
 
@@
         \end{subfigure}
-        \caption{Results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
+        \caption{Same as Fig.~\ref{fig: 1by2V}, but this figure shows results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
         \label{fig: 12by12T_newsom}
     \end{figure}
+
     Fig.~\ref{fig: 12by12T_newsom} shows the SOM results for the first approach. 
@@
     However, all the K96 galaxies are in small side of the map in Fig.~\ref{fig: 12by12T_selforg}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 samples.
+
     \begin{figure}
@@
         \end{subfigure}
-        \caption{Results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
+        \caption{Same as Fig.~\ref{fig: 1by2V}, but this figure shows results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
         \label{fig: 12by12T_selforg}
@@
     \subsection{Caveat}
-    There is no established method to find the best SOM initial values. Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new result.
+    There is no established method to find the best SOM initial values. 
+    Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new results.
     Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.

### 2016-04-22 main.tex
Finishing comparing with pre. works. Need to add more details about Sc type galaxies and english check

@@
 In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
+We used an unsupervised self organizing map (SOM)method, to create a network based in SED models of galaxies and used sample of galaxies to test the networks. 
+We classify galaxies in different groups and studied the correlation between properties of the galaxies.
+we conclude that the SOM is a very useful and accurate method to be used in classifying galaxies base on their morphology.
+
 %%%%%%From this point it is just repeated%%%%%%%%%
-We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
-We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
-We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
-We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
 
@@
 \newline
-2) Using this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
+2) Using this method we not only can categorized the galaxies with more precision but also we can see the relative similarity or dissimilarity between each type of galaxies.  
 \newline
-3) This method can help us to find outliers or new categories of galaxies very easily and fast.
-
-4) We plot the properties of the galaxies using new classification and see the correlation between age and SSFR and stellar mass of the galaxies.
+3) We show that using SOM, we could recognize the galaxies have similarity to two or more morphological types of galaxies.
+\newline
+4) We trained networks using sample of SEDs and test them with sample of galaxies with SEDs in the similar badpasses.
+\newline
+5) We plot the properties of the galaxies using new classification and see the correlation between age and SSFR and stellar mass of the galaxies.
+\newline
+6) We show that the properties of the galaxies in each groups is in good agreement between their morphological types.
+\newline
+7) We show that SOM can help us to easily identified new type of the galaxies, in large surveys very easy. 
+\newline
+8) This method can be used to find outliers very fast.
+\newline
 

### 2016-04-22 sections0.01/results0.01.tex
Finishing comparing with pre. works. Need to add more details about Sc type galaxies and english check

@@
 
-        In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, we plot the some physical properties listed in the Tab.~\ref{tab: props} of galaxies in each neurons in the networks.
+        In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, in this section we are going to show the relatins between properties of the galaxies in each neurons.
 
-        \begin{figure}
+        \begin{figure*}
             \centering
-            \includegraphics[width=0.5\textwidth]{../images0.01/1d/props4.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/props4.png}
             \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
             \label{fig: props}
-        \end{figure}
+        \end{figure*}
 
-        Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
+        Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neurons in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
         In all the plots $x$-axis shows the normalized number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.
@@
        \begin{figure*}
-        \begin{subfigure}[b]{\textwidth}
-            \centering
-            \includegraphics[width=\textwidth,height=6cm]{../images0.01/1d/age_vs_ssfr.png}
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f1.png}
         \end{subfigure}
         \hfill
-        \begin{subfigure}[b]{\textwidth}
-            \includegraphics[width=\textwidth,height=6cm]{../images0.01/1d/ssfr_vs_stellar_mass.png}
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f2.png}
         \end{subfigure}
         \hfill
-        \begin{subfigure}[b]{\textwidth}
-            \includegraphics[width=\textwidth,height=6cm]{../images0.01/1d/age_vs_stellar_mass.png}
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f3.png}
         \end{subfigure}
-        \caption{From up to down: Correlation between age ($^tD4000$) and SSFR, SSFR and stellar mass, and  age ($^tD4000$) and stellar mass.
+        \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f4.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f5.png}
+        \end{subfigure}
+       \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f6.png}
+        \end{subfigure}
+        \caption{From up to down: Correlation between age (t$_{\rm {D4000}}$) and SSFR, SSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with SSFR, age (t$_{\rm {D4000}}$) and stellar mass.
 Points show the mean values of these properties from galaxies in $1\times22$ network.
@@
 
-        In order to compare our classifications with other works, we ploted some properties of the galaxies against each other for each network.%reproduced figure 16 in T12 using properties of galaxies in each networks.
-        All the plots shows the similar trend as plots in the Fig.~\ref{fig: props_vs_props} which shows the plots from $1\times22$ network. 
-        Points are mean values of the properties of the galaxies from T12 sample, with the standard deviation of those properties.
+        %maybe rephrase this part later
+        N09 used various models to derive galaxies properties.
+        Through these models, some of the properties are already known to be correlated with each others, i.e. stellar mass and star formation rate.
+        They, however, studied other relations between properties of sample of SINGS galaxies which didn't have a direct correlation in the models.
+        They found a tight correlation between SSFR and t$_{\rm {D4000}}$, which suggested that younger stellar population correlate with high SFR.
+        They also found correlation between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
+        Since in {\em CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar mass related correlation must be astrophysically meaningful. 
+        They also studied relation between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and SSFR, age, and stellar mass and did not find any correlation.
+        T12 replicated the same plots and found tighter correlation than N09 results.
+
+        In order to compare our classifications with previous works, we produced the similar plots as the ones in both N09 and T12 (Fig.~\ref{fig: props_vs_props}).
+        In Fig.~\ref{fig: props_vs_props}, points are mean values of the properties of the galaxies in the Fig.~\ref{fig: 1by22V},and error bars show the standard deviation of those properties.
         colours show the galaxy types where B type galaxies are shown with red and SB1 ones are shown with blue colours.
@@
         Since in this method we allow galaxies to stay in the classes between the original 12 types of the galaxies, we have more than 12 colours in the Fig.~\ref{fig: props_vs_props}.
+        Galaxies with SED similar to type Sc having bright purple colour but as expected from the shape of the SED they are old galaxies with high SSFR.
+        Therefore, in all three plots of the Fig.~\ref{fig: props_vs_props}, there is a purple point in the middle of the blue points.
 
-        Both N09 and T12 have the similar plots with the same properties.
-        However, since in both of these papers they considered only 12 types for the galaxies, those plots have a different colours than ours.
-        Our results shows the same relation between parameters with tighter correlation in all three plots.
-        galaxies with SED similar to type Sc having bright purple colour but as expected from the shape of the SED they are young galaxies with high SSFR.
-        Therefore, in all three plots of the Fig.~\ref{fig: props_vs_props}, there is a purple point in the middle of the blue points.
+        The upper plots in the Fig..~\ref{fig: props_vs_props} show the same relation between parameters with tighter correlation in all three plots.
+        As mentioned in both N09 and T12, galaxies with smaller mass tend to be more younger and more active galaxies.
+        In Fig.~\ref{fig: props}, we saw the same results, younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
+        It is clearly noticeable that from older galaxies to younger galaxies, colour of the points changes from red to blue  which shows a good correlation with the morphological type.
+        %for more details discussion on these correlations, we encourage readers to read N09 and T12.
+
+        The lower plots in the Fig.~\ref{fig: props_vs_props} show the relations between A$_{\rm {FUV}}$ and SSFR, age, and stellar mass.
+        Unless N09, we found a correlation between A$_{\rm {FUV}}$ and these three parameters.
+        N09 used SINGS galaxies as their test sample and concluded that the attenuation is independent of the star formation, age or stellar mass.
+        They found a very weak correlation between A$_{\rm {FUV}}$ and morphological types of galaxies, which was much weaker than previous studies~\citep[e.g.][]{Dale07}.
+        In the Fig.~\ref{fig: props_vs_props}, there is a more clear and stanger correlation between the A$_{\rm {FUV}}$ and the other parameters.
+        Considering the morphology of the galaxies, early type galaxies have more A$_{\rm {FUV}}$.
+        Therefore, we could conclude that the classification of the SED of galaxies using SOM, separates galaxies based on their morphological type and the characteristic of each of these groups are in agreement with general picture of the galaxy evolution.%%%%%I should find better wording for the last sentence%%%%%
 
@@
 
-    \subsection{Caveat}
-    There is no established method to find the best SOM initial values. 
-    Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new results.
-    Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
+    % \subsection{Caveat}
+    % There is no established method to find the best SOM initial values. 
+    % Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new results.
+    % Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
     %no quantitative way to analyse the data?!

### 2016-05-07 main.tex
Applied Pauline's and Hossein's result. Result0.01 is grammatically corrected (~ish)

@@
 
-\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach}
+\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
 \author{rahmani.sahar }
@@
 
-\begin{abstract} %Most of this abstract is just a filler
-In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
+\begin{abstract} %Most of this abstract is just a filler % PB160426: OK, no comments on it for now.
+In this paper we introduce a new method of clustering high red shift galaxies, based on their SED.
 We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
 We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using {\em CIGALE} code to study and compare the properties of each cluster.
-In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
-We used an unsupervised self organizing map (SOM)method, to create a network based in SED models of galaxies and used sample of galaxies to test the networks. 
+We used physical properties of the sample galaxies measured using {\em CIGALE} code to study and compare the properties of each cluster.
+In this paper we used an unsupervised self organizing map (SOM)method, to create a network based in SED models of galaxies and used sample of galaxies to test the networks. 
 We classify galaxies in different groups and studied the correlation between properties of the galaxies.
@@
 
-\import{sections0.0/}{intro0.0.tex}
+\import{sections0.01/}{intro0.01.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.0/}{data0.0.tex}
+\import{sections0.01/}{data0.01.tex}
 
@@
 \section{SUMMARY}
-\label{sec: summary}
+\label{sec: summary} %PB160427: not so sure I like the numbering of every sentence, or starting almost all of them with "We". But this is a style thing that we can discuss later.
 1) We introduced the self organizing maps to be used to categorizing the SED of galaxies.
@@
 \newline
+%PB160427: Um, I'm not so sure you really demonstrated numbers 7 and 8. Those are interesting and it could be that a little more work on this and addition to the results section would be a good idea.
 

### 2016-05-07 sections0.01/data0.01.tex
Applied Pauline's and Hossein's result. Result0.01 is grammatically corrected (~ish)

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{DATA}
\label{sec: data}
We used SED templates from K96, to train neural networks.
To test the train networks, we used SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
Following of T12 work, we chose these two sets of data to not only show the application of SOMs in clustering SEDs, but also to easily compare both supervised and unsupervised methods.

 \subsection{Kinney spectral model}
     \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../images/k96.jpg}
        \caption{K96 spectra template for 12 types of galaxies from T12 paper (Fig. 1 in T12).Type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belongs to early type galaxies. Star burst galaxies spectra are indicated with SB 1 to 6. Higher numbers represents more intrinsic colour extinction.}
        \label{fig: k96}
    \end{figure}
     % PB160426: Also, I think you need some stronger arguments for why K96 is a good set of templates to use. Nothing better developed in the last 20 years? 
     %Do they span the whole range of properties you expect the 0.5<z<1.0 galaxies to have?
     %SR: I looked around lots of ppl still using Kinney 96 as a template!
     %SR: In K96 paper they briefly talked about that you an use these templates to identify the morphological type of galaxies.

    K96 used UV-optical spectra of 70 star forming and quiescent nearby galaxies to produce a template that contains 12 types of SEDs.
    These template can be used to classify the SED of the high redshift galaxies. 
    The 12 types of spectra are divided based on their morphological types for early type galaxies or their extinction for star burst galaxies (Fig.~\ref{fig: k96}).

     % PB160426: I think that's OK, but you will need to look up the journal rules for reproducing a figure from another paper.

    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    Bulge groups represents galaxies similar to M31 and M81, which their UV and optical spectroscopy dominated by the stellar population in their bulges.

    The star burst galaxies are divided in six groups (SB1 - SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As it is clear in the Fig.~\ref{fig: k96}, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among star burst galaxies.

    K96 spectra spans from $\sim1200-10000$\AA.
    However, we only used data between $\sim1200-8000$\AA~to train our networks. 
    These wavelength range were chosen due to availability of flux information in those wavelength for all 12 types of galaxies.
    In early type galaxies spectrum (B-Sb), spectra is redder and strong absorption lines, and 4000\AA~break is distinguishable. 
    While SEDs of star burst galaxies are more flatter on the optical and NIR part than early type one and show strong emission lines.
    For more details on each spectra type, we encourage readers to see K96 and references therein.

 \subsection{SED and Properties of the sample galaxies}
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field, which have a photometry data from the Good-MUSIC catalogue.
    These 142 galaxies were selected due to availability of data from HST/ACS; VLA/ISAAC; and \Spitzer/MIPS and IRAC. 
    Data from these instruments were necessary in order to have a complete picture of stellar population and SFR.
    The photometry data contains data in 10 - 13 filters with wavelength range of $\sim 0.4-24 \mu$m, in the observed frame. % PB160426: I assume these galaxies have spectroscopic redshifts, or were redshifts derived from photometry? from spectroscopic. 
    They used these photometry data as inputs for Code Investigating GALaxy Emission ({\em CIGALE} code;~\citep[][hereafter N09]{Noll09}) to generate the best fitted SED for each galaxy as well as some of the physical properties of the galaxies.

    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
    This code were successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match for each galaxies.
    Then, they used an exponentially decreasing SFR, visual attenuation ($\tau$) model and derived physical properties of galaxies such as age, and stellar mass.
    Some of these properties are shown in Tab~\ref{tab: props}.
    They assumed the Salpeter initial mass function~\citep{Salpeter55} and old stellar population age of $\sim 10$~Gyr.
    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.

     For testing the created networks, we used SED produced by T12. 
     However, we only used part of the spectra that have the same wavelengths as K96 SEDs. %PB160427: need to be more explicit here about exactly what the spectra being analyzed are. Is the data vector for each object a list of fluxes (flux densities) as a function of (rest) wavelength? Same wavelengths for every object? What is the spectral resolution? Do the spectra include the whole galaxy or just the central part?
     %%%%%SR160428: Hossein will write about it.
     In the Sec.~\ref{sec: 1D}, we studied these properties for each categorization.

    \begin{table}
\caption[]{Description of the properties of T12 galaxies; the output result of {\em CIGALE}}     
\label{tab: props}
\centering
\begin{tabular}{l l l}
\hline\hline
\noalign{\smallskip}
Par. & Unit & Description\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
$f_\mathrm{burst}$ & --- & mass fraction of \\
& & young single population (SP) model \\
\noalign{\smallskip}
$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age \\
\noalign{\smallskip}
$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
SFR & M$_\odot$/yr & instantaneous SFR  \\
$A_\mathrm{FUV}$ & mag & attenuation at 1500\,\AA{} \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{table}

### 2016-05-07 sections0.01/intro0.01.tex
Applied Pauline's and Hossein's result. Result0.01 is grammatically corrected (~ish)

--- 2016-04-12 sections0.0/intro0.0.tex
@@
 
-Advances in imaging techniques, and photometry and spectroscopy devises help to have higher resolution data and more detailed SED. 
+Advances in imaging techniques, and photometry and spectroscopy devises help to have higher resolution data and more detailed SEDs. 
 Thus, the variations between SEDs become more clear and the classification of galaxies became more complicated.
-Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00}.%and more references
-These templates are mostly restricted to wavelengths from near-IR to ultraviolet (UV), so they contain main features from physical properties of galaxies i.e.
-age, star formation rate (SFR), stellar mass, wide range of the stellar population, interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.
+Many groups used data from nearby galaxies in order to composite a thorough template for categorizing the spectral type of the galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00,Mannucci01}.
+Based on the usage of the templates, these templates could be restricted to various wavelengths.
+In case of near-IR to ultraviolet (UV) wavelengths (which is pick output of stars), SED contains information about main features of physical properties of galaxies i.e.
+age, star formation rate (SFR), stellar mass, wide range of the stellar population, some information on interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.
 
-One of the main usage of the SED templates is finding the morphological type of high redshift galaxies. 
-However, since not two galaxies, even with same morphology, are exactly the same, classifying the SED of the galaxies are a challenge.
+SEDs of galaxies can be used to derive physical properties of galaxies, and from those one can find information about morphological type  galaxies.
+Since not two galaxies, even with the same morphology, are exactly the same, classifying the SED of the galaxies are a challenge.
 Many fitting methods are developed and used to find the best matches of template for each SED.
@@
 ANNs are very powerful tools to used in data processing and pattern recognitions problems.
-Their information process method inspired by the way neurons in human brains work.
-An ANN contains many interconnected units (neurons) which process data and work together to solve problems.
-It uses sets of trainings method to learn about a nonlinear and complex relations between input and output data and how to apply it on new sets of data.
-Studies shows that ANNs provides better fitting than minimizing chi square and would be an alternative choice for fitting data \citep[e.g.][]{Marquez91,Moayed09}
+Their information process method were inspired by the way neurons in human brains work.
+An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
+It uses sets of trainings method to learn about a non-linear and complex relations between input and output data and how to apply it on new sets of data.
+Studies shows that ANNs provides better fitting than minimizing chi square and would be an alternative choice for fitting data \citep[e.g.][]{Marquez91,Moayed09}.
+In cases that both methods show the same correlation, ANNs still are better method of fitting due their faster results in large data bases \citep[][]{Gulati97}.
 
-%SOMs and its advantages over supervised methods
-Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by~\citep{Kohonen82}.
-The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
-%Both advantage and disadvantage of the unsupervised method is that there are no previous predictions about the outcome.
+Neural networks can be trained in two methods; supervised and unsupervised.
 In supervised method, a neural network would be trained using input data based on desired outcome.
-This method is very useful for classification of data with specific target values (i.e. classifying SED of galaxies from a SED template).
+This method is very useful for classification of data with specific target values (i.e. any pattern recognition with known templates).
 On the other hand, in unsupervised method there is no prediction of output data.
 This method classifies data based on their underlying structures and hidden variables.
-The unsupervised method is a very helpful method to knowledge discovery of your data, or when the underlying structure of data is not well established (i.e.
-producing a template of SED of galaxies) %eh
+The unsupervised method is a very helpful method to knowledge discovery of your data, or when the underlying structure of data is not well established (i.e. producing a template of SED of galaxies).
 
+Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non-linear high dimension data introduced by~\citep{Kohonen82}.
+The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
 %SOM in Astronomy
@@
 The other application of the SOM is to find outliers or errors in the data.
-\citet{Fustes13} used this method to produced a package to classify results from GAIA surveys and find the outlier or errors in the instruments or pipelines.
+\citet{Fustes13} produced a package based on SOM to classify spectra from GAIA survey that were previously classified as "unknown" by SDSS pipeline.
+The package recognizes an astronomical object from an artificial errors, and then classifies the object based on its spectra.
 
 %What is this paper about
-We obtained SED of a 142 galaxies with 0.5 < $z$ < 1 from~\citet[][hereafter T12]{Hossein12} paper.
-T12 classified SED of a sample of galaxies using supervised neural network method, based on the spectral model presented by K96.
-They classified SED of the 105 out of 142 galaxies using K96 template. 
-The SED of the 37 galaxies from their samples could not be matched with any of those in the template. 
-They found that the unclassified galaxies can be matched with a combined spectrum of the K96 model. 
-They also showed that there are tight correlations between physical properties of galaxies and this correlations might be different based on the types of the galaxies.
-
-In this paper, we used data from K96 template to train an unsupervised neural network.
+In order to compare supervised and unsupervised method, in this paper, we used data from K96 template to train unsupervised neural networks. 
 The network clustered the SEDs and mapped those clusters and their relative relations.
 We compared our results with K96 galaxies classification.
-Then we classify the SED of the sample of 142 galaxies using the constructed SOM.
+Then we classify the SED of a sample of galaxies using the constructed SOM.
 
- In Section $\S$~\ref{sec: data}, we present the data.
+We used SED of a 142 galaxies with 0.5 < $z$ < 1 from~\citet[][hereafter T12]{Hossein12} paper.
+T12 classified SED of a sample of galaxies using supervised neural network method, based on the spectral model presented by K96.
+With supervised method, they could only classify SED of the 105 out of 142 galaxies.
+The SED of the 37 galaxies from their samples could not be matched with any of those in the K96 templates. 
+In order to classify the remaining 37 galaxies, they combined spectrum of the K96 templates.
+The latter shows that, not a single type of galaxies in K96 template could describe the SED of the 37 galaxies.
+The unsupervised methods on the other hand, have the freedom of classifying object between known classes, which can be used in this data to find a best SED class for the 37 galaxies.
+T12 also showed that there are tight correlations between physical properties of galaxies and this correlations might be different based on the types of the galaxies.
+
+ In Section $\S$~\ref{sec: data}, we present the data that we used to train and test our networks.
 We describe the SOM in Section $\S$~\ref{sec: method}.
-The results of the SED classifications and comparing them with previous studoes are shown in Section $\S$~\ref{sec: result}.
-In Section $\S$~\ref{sec: summary}, we present the summary of our conclusion and the future works in this subject.
+The results of the SED classifications and comparing them with previous studies are shown in Section $\S$~\ref{sec: result}.
+In Section $\S$~\ref{sec: summary}, we present the summary of our results and the future works in this subject.

### 2016-05-07 sections0.01/method0.01.tex
Applied Pauline's and Hossein's result. Result0.01 is grammatically corrected (~ish)

@@
 
- %Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non linear high dimension data introduced by~\citep{Kohonen82}. 
-% The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
  The SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
- Results of SOM contains nodes (usually hexagonal ones) that arranged in 1D or 2D arrays.
+ Results of SOM contains nodes (neurons) that arranged in 1D or 2D arrays \citep{Kohonen98}.
 
@@
  %Sahar_self_notes: maybe "some" is better instead of one or more
- Moreover,a weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be change during the process and has a key factor in a position of nodes in the map.
+ A weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be change during the process and has a key factor in a position of nodes in the map.
 
@@
  \label{sec: algorithm}
-     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
+     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on S1 by S2 map. 
      We start by creating S1 $\times$ S2 empty neurons. 
      The initial arrangement of these neurons depends on a map's topology provided by user.
-     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
-     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
+     In the case of the 1D maps, since each neurons have two immediate neighbours the topology of the map does not have any affect on the final result and we can choose any topology.
+     However, in 2D maps, the shape of the neurons specifies the number of the immediate neighbours for each neurons and it is up to user that which shape is more suitable for their data.
+     In this paper, we chose hexagonal topology which gives each neuron six neighbours, and causes more interactions between neurons.
+     Then, a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
      The process of creating SOM, happens over series of $N$ iterations. 
      During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
-      In each iteration:
+      In each iteration SOM code:
      \begin{enumerate}
-        \item Choose a random vector from our data set.
-        \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$".
+        \item Chooses a random vector from our data set ($V_i$).
+        \item Calculates the euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
 This neuron is the winner node and is calling Best Matching Unit (BMU).
-        \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius.
+        \item  Computes the radius of the neighbourhood of the BMU to find nodes within this radius.
 The weight vectors of these nodes will be affected in the next steps.
@@
 $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively.
-        \item Change the weight vectors of the BMU and all the nodes within r(t) as:
+        \item Changes the weight vectors of the BMU and all the nodes within r(t) as:
         \begin{equation}
@@
         \end{equation}
-        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
+        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
 $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
-        \item  Repeat these steps for $N$ times.
+        \item  Repeats these steps for $N$ times.
      \end{enumerate}
@@
      This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
-     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.
+     The ordering phase continues for requested number of iterations.
+     During the iterations, the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to tuning phase neighbourhood distance which both of the numbers set by the user.
+     In the ordering phase, the changes in the learning factor and the neighbourhood distance adjust with the number of the iterations, in the way that at the last iteration, these two values reach to the initial values for the second phase.
 
@@
      This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
-     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. 
+     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. %cite kohenen book?!
      We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.
 
-     To show our results, we combine two of the {\tiny NNT}'s built-in plots. 
-     A Hits map, which shows number of hits for each neurons, and a distances map, which shows the same neurons as the hits map and the distance between them. 
-     %To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
+     To show our results, we used two of the {\tiny NNT}'s built-in plots. 
+     A Hits map, which shows number of the times each neurons become the winner (hits), and a distances map, which shows the same neurons as the hits map and the distance between them.
      In the maps, the purple hexagonal shape areas represent the neurons.
-     %The red lines between neurons, show the immediate neighbours.
-     The distances in a distance map are showing by colours.
+     The distances in a distance map are showing by the grey cycle colours.
      The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.
@@
 
-    %Although size of the SOM could be anything \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size.
     Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of maps. 
-     Users usually must choose the size of grids based on their data set and their usages of the results.
-     For training networks using 12 galaxies from K96, we created maps with sizes from $1\times2$ to $50\times50$ to choose the sufficient size.
-     varying grids of the maps helps us to monitor whether grouping galaxies in smaller maps is because they have similar SEDs or its because of the shortage of the neurons.
-     Based on size of our data and our results, we chose max of the grid size to be 1$\times$22 and 12$\times$12 in 1D and 2D maps, respectively.
-
-     Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
-     Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
-     %All the other parameters are default values in {\tiny newsom} library and cannot be changed by the users.
+    Although \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size, users usually choose the size of grids based on their data set and their usages of the results.
 
@@
 
- We created  a mock sample of 27 galaxies to illustrate the results of SOMs and how they can be analyzed, and to show how this method works.
+ We created  a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analyzed.
  The mock sample contains two information from each galaxy; first type of galaxies: type 1 or type 2, and either they are high or low star forming galaxies. 
@@
  The axis show the position of the neurons in a $10 \times 10$ network.
- The purple hexagons are illustration of the neurons, and the colours of the area between neighbours are showing the differences between weight of each two neurons.
- In distance maps colour white between neurons represents the minimum value of the differences between weights of neurons and the colour black shows the maximum values. 
- The gray cycle colour between white and black shows values between minimum and maximum with darker colour means more differences.
-
  The lower plot in the Fig.~\ref{fig: sample} shows a hit map.
  In this map similar to the distance map the axis shows the position of the neurons where the hexagonal shapes are neurons.
- %White neurons show the empty neurons.
  The purple neurons with a number on them shows the number of galaxy in that neurons.
@@
 The upper plot in the Fig.~\ref{fig: sample}, clearly shows this division.
-The upper part of the plot are high star forming galaxies, while the lower part of it belongs to the low star forming galaxies.
+In that plot, the upper part belongs to high star forming galaxies, while the lower part belongs to the low star forming galaxies.
 The left part of the plots is where type 1 galaxies belong to and the right side is for type 2 galaxies.
@@
 8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
-The reason of that there are only 4 filled neurons in the network is the simplicity of the input data, and the fact that each entry only could get either 0 or 1 as for type of galaxy and 0 or 0.5 as an indicator of SFR.
-It shows us although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed in only four groups.
+Since the input data are so simple, each entry only could get either 0 or 1 as type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
+%The reason of that there are only 4 filled neurons in the network is the simplicity of the input data, and the fact that each entry only could get either 0 or 1 as for type of galaxy and 0 or 0.5 as an indicator of SFR.
+We can concludes that although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed only in four groups.
+This network is considered as a train network, and if there is any data set with similar entries, we can use this network to cluster the new data set.
 
-As we show in the following sections, in the real world with the real data, we never have two galaxies with exactly the same information.
+As we show in the following sections, in the real world with the real data, we never have two galaxies with exactly the same information, we have more than 2 dimensions, and more galaxy types. 
 Therefore, if the network has high enough neurons, the input data would eventually separate from each other and cluster into the smaller and smaller groups. 
-However, if the information of the input data are pretty similar to each other, the number of neurons are going to be much higher than number of input samples. 
-In similar cases, one can decide that the amount of similarity or dissimilarity between the input samples.
+However, if the information of the input data are pretty similar to each other, the number of neurons are going to be much higher than number of input samples, to be able to separate the groups from each other.
+In those cases, one can decide that the amount of similarity or dissimilarity between the input samples.

### 2016-05-07 sections0.01/results0.01.tex
Applied Pauline's and Hossein's result. Result0.01 is grammatically corrected (~ish)

--- 2016-04-19 sections0.0/results0.0.tex
@@
 \label{sec: result}
+
     In this section we are showing the results of trained neural networks, using K96 data.
-    To have a realistic model of the input data we created SOMs with various sizes in both 1D and 2D.
-    We start our analysing by creating 1D SOMs. 
-    First, we created SOMs with only two neurons (1$\times$2 map) and then we increased number of neurons one at a time in 1D case (~\ref{sec: 1D}).
-    Then we generated 2D networks (~\ref{sec: 2D}), and once again we start with smallest number of neuron possible (4 neurons in 2$\times$2 map) and then increased the number of neurons to 144 in 12$\times$12 map.
+    Training networks with K96 templates, provides us networks that have regions with known morphological types. The trained networks can be used to categorize other galaxies.
+    %In following we show how we trained data and used galaxies from T12 to show how the clustering using trained networks works.
 
-    For each generated network, we compare the results with K96 categorization.
-    We also used these networks to classify the T12 galaxies samples, and compare them with classifications from supervised network.
+    %%% should I move this paragraph to method section?!
+    In order to find sufficient size for the trained networks, we created maps with sizes from $1\times2$ to $50\times50$.
+    Varying grid of the maps helps us to monitor whether grouping galaxies in smaller maps is based on their similar SEDs or its for the shortage of the neurons.
+    Based on size the data and SOM results, we chose maximum of the grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
+    For each grid we created different SOMs with different learning factors, neighbourhood distances, and iteration numbers to find the optimum result for our sample.
+    We created the final SOMs with following initial values: number of iterations in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
+
+    We started our analysis by creating 1D SOMs. 
+    First, we created SOMs with only two neurons ($1\times2$ map), and then we increased number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
+    We generated 2D networks (Sec.~\ref{sec: 2D}), and once again we start with the smallest number of neuron possible (4 neurons in $2\times2$ map), and then increased the number of neurons to 144 in $12\times12$ map.
+
+    For each generated network, we compared the results with K96 categorization.
+    We also used these networks to classify the T12 galaxies samples, and compared them with classifications from supervised networks in T12.
     \subsection{1D SOMs}
@@
         \label{sec: 1Dt}
-            We assumed that galaxies can be divided only in two types; quiescent and star burst, and then generated a network with only two neurons.
-            Then we increased size of the maps gradually till we separated the input 12 sample galaxies into the 12 neurons.
+            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and star burst.
+            In this case, we generated a network with only two neurons.
+            We increased the size of the map gradually till we separated the input 12 sample galaxies into the 12 neurons.
 
-            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by3T} show results of training network.
-            Upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
-            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance $D_j$ between the neurons and the darker is the colour the more $D_j$ is between them.
-            The lower part shows how many galaxies from K96 template places in each neurons.
-
-            In upper side of the Fig.~\ref{fig: 1by2T}, the red colour between two neurons indicate that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups.
-            In the lower part of the Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
-            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
-            In this method, the Sc galaxies have been categorized as star burst galaxy due to their high amount of the emission lines.
-
-            %add more about why Sc is acting differently
-            %\import{~/images/texes/}{1by2_t.tex}
+            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of training networks.
+            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
+            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance, $D_j$, between the neurons and the darker is the colour the more $D_j$ is between them.
+            The lower part shows how many galaxies from K96 template places in each neuron. 
             \begin{figure}
@@
                     \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
-                    %\caption{$1\times2$ weight map}
-                     %\label{fig: 1by2T}
                 \end{subfigure}
@@
                      \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by2Thits}
                 \end{subfigure}
                 \caption{Results of training network in $1\times2$~grid.
+Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map.
 In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts.
@@
 
-            Fig.~\ref{fig: 1by3T} shows results of the training in a 1$\times$3 network.
-            In these plots we forced the galaxies to categorized themselves in maximum 3 groups. 
-            If the galaxies in Fig.~\ref{fig: 1by2T} are very similar to each other or are exactly the same, they still want to be divided in two groups and left the middle node empty. 
-            However, in the lower part of the Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
-            These two galaxies, which are separated from group of star bust galaxies in the lower part of Fig.~\ref{fig: 1by2T},are types SB5 and SB6 galaxies.
-            In upper plot of the Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is yellow. 
-            The black colours indicates that the left neuron is completely different from the other two groups, while the yellow colour shows the two neurons are very similar to one another.
+            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups.
+            In the lower part of Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
+            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
+            In this method, the Sc galaxies have been categorized as star burst galaxy due to the relatively higher amount of the disk stellar population relative to the bulge ones. 
+            According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.
 
-            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided to two groups. 
+            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
+            In these plots we forced the galaxies to categorize themselves in maximum 3 groups. 
+            If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty. 
+            However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
+            These two galaxies, which are separated from group of star burst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
+            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
+            The black colour indicates that the left neuron is completely different from the other two groups.
+            While the white colour shows the two neurons are very similar to one another.
+
+            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided into two groups. 
             Based on the colours between these two groups, we conclude that they are very similar groups; both groups are star burst galaxies and have strong emission lines.
-            However, these two groups have the most internal colour extinctions, so they intend to move more towards the early type galaxies.
+            However, SB5 and SB6 types have the most internal extinctions.
+            The high amount of extinction causes SED become more flat in the lower wavelength regions.
+            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies than other star burst ones.
+            So in the networks, SB5 and SB6 types intend to move more towards the early type galaxies.
 
@@
                      \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by3Thits}
                 \end{subfigure}
-                \caption{Results of training network in $1\times3$~grid.
+                \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid.
 In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts.
@@
             We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
-            Since there are more nodes when with increasing the size of map, program pays more attention to small differences between each groups.
+            Since there are more nodes in higher grid SOMs, the program pays more attention to small differences between each group.
             Higher the size of the maps means that even considering the smallest differences between galaxies.
-            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 each node).
+            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 at each node).
             However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
-            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together, respectively. 
-            The SB3 and SB4 grouping breaks when we increased the size of the map to $1\times15$~(Fig.~\ref{fig: 1by15T}).
-            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E does not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
+            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together. 
+            The SB3 and SB4 grouping breaks when we increased the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
+            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E had not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
         \begin{figure*}
@@
             \end{subfigure}
-            \caption{Results of training network in $1\times22$~grid.}
+            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
             \label{fig: 1by22T}
-        \end{figure*}
+        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.
 
-            In Fig.~\ref{fig: 1by22T}, although in lower plot we can see twelve different groups, but in upper plot 5 groups are in the left side neurons and there is a black colour between them and then the rest of the galaxies.
-            It shows that although we separated the galaxies in twelve groups but they are still divided by two main groups.
+            In Fig.~\ref{fig: 1by22T}, in lower plot we can see twelve different groups. 
+            In upper plot 5 groups are in the left side neurons, and there are two dark grey colours between them and then the rest of the galaxies. 
+            It shows that although we separated the galaxies in twelve groups, but they are still divided in two main groups.
             The closest occupied neurons in the star burst side of the SOM, belongs to the SB6 type. 
-            This type of the galaxies have the most extinction and its SED has similarity to early type galaxies more than other star burst types.
+            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other star burst types.
 
-            The fact that the galaxies had to have 22 different neurons till be divided to 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
-            These small differences might be very hard to distinguish in normal classification methods and might lead to wrong classifications.
-
+            The fact that the galaxies had to have 22 different neurons till be divided into 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
+            These small differences might be very small.
+            Therefore, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.
+           % For using SOM method, one should be careful about these small differences and consider that how much details do we need to pay attention to, to consider two groups are separate from each other.
+           %%%% (I'm not sure if it is good to be here or not)
         \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
@@
             We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
-            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
+            Upper plot in Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
             It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
-            The lower plot shows the average SED of the SEDs galaxies in each node. 
+            The lower plot shows the average SED of the galaxies in each node. 
             The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
-            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
-            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
-            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
-            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies.
+            These galaxies are similar to the ones in the left node in the upper plot in Fig.~\ref{fig: 1by2T}.
+            The plots clearly show the 4000\AA~break in the SEDs, which is one of the signatures of the early type galaxies.
+            The strong emission lines in that figure could be from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
+            The right plot in the lower part of Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies.
             \begin{figure}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
+                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by2.png}
                      %\caption{$1\times2$ hits map}
@@
                 \end{subfigure}
-                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96.
-Up: Numbers in each node represents the number of galaxies that belong to that group.
+                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in Fig.~\ref{fig: 1by2T}.
+Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group.
 In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies.
 Down: Average SED of the SEDs of the galaxies in each group.
-the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
+The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the star burst ones).}
                 \label{fig: 1by2V}
             \end{figure}            
-            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
+            Since in this network galaxies forced to be divided into maximum two groups, for any SED between these two groups the SOM must decide that each galaxy belongs to which group based on strongest features of its SED.
             The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
-            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.
+            Increasing the size of the SOM helps to solve the problem of the galaxies which have features of both groups.
 
-             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network ( Fig.~\ref{fig: 1by2T}). 
+             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
              In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to star burst galaxies. 
-             29 of the galaxies are more similar to star burst ones but, not with all of their features. 
-             These group of galaxies have strong emission lines and the ascending slop towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of the Fig.~\ref{fig: 1by2V}).
+             29 of the galaxies are more similar to star burst ones, but not with all of their features. 
+             These groups of galaxies have strong emission lines and the ascending slope towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).
 
@@
 
-            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the the sample galaxies.
-            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size we could see, the K96 galaxies separated in 12 different neurons.
+            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the sample galaxies.
+            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size that we could see the K96 galaxies separated in 12 different neurons.
             B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
-            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of the Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
+            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
             \begin{figure*}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22.png}
+                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22_n.png}
                     %\caption{$1\times2$ weight map}
@@
                 \end{subfigure}
-                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times22$ to classify the sample galaxies.}
+                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
+In the average SED of each neuron, we can clearly see the changes from early type galaxies in the star burst ones.
+4000\AA~ break reduces from left to right and emission lines increase.}
                 \label{fig: 1by22V}
             \end{figure*}
-            And the lower plot of the figure represents the average SED of the galaxies in each neurons.
-            However, this time, since galaxies had more space to separated some of the neurons left empty. 
-            Thus instead of having 22 average SED plots in the lower part of the Fig.~\ref{fig: 1by22V}, we have 12 SEDs.
+            The lower plot of the figure represents the average SED of the galaxies in each neuron.
+            However, this time, since galaxies had more space to separate some of the neurons left empty. 
+            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, we have 12 SEDs.
 
-            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of the Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
-            If a groups of the T12 galaxies fills the same neurons as a K96 galaxies, we can conclude that this group of the galaxies have SEDs very similar to the SED of one of K96 galaxies.
-            Whereas, we can conclude that a group of the galaxies have properties between the two groups if they fill a neuron which is empty and places between two categories of galaxies in the Fig.~\ref{fig: 1by22T}.
-            However, the colours between these neurons in the upper side of the Fig.~\ref{fig: 1by22T}, establishes that the group of galaxies are more similar to which group.
+            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
+            If a group of the T12 galaxies fills the same neurons as the K96 galaxies, we can conclude that these galaxies have SEDs very similar to the SED of one of K96 galaxies.
+            Whereas, we can conclude that a group of the galaxies has properties between the two groups if they fill a neuron which is empty and places between two categories of galaxies in Fig.~\ref{fig: 1by22T}.
+            However, the colours between these neurons in the upper side of Fig.~\ref{fig: 1by22T}, establishes that those galaxies are more similar to which group.
 
-            In the first two neurons of the upper plot in the Fig.~\ref{fig: 1by22V}, there is no galaxies, while in galaxies B and E are in the same neurons in the trained network.
-            So we can conclude that there is no galaxies with similar
-            There are 3 galaxies in the third neurons which shows these 3 galaxies are very much similar to the S0 type. 
+            In the first two neurons of the upper plot in Fig.~\ref{fig: 1by22V}, there is no galaxy, while in galaxies B and E are in the same neurons in the trained network.
+            So we can conclude that there is no galaxy with similar specification of type B or E in the T12 sample.
+            There are 3 galaxies in the third neuron, which shows these 3 galaxies are very much similar to the S0 type. 
             18 of the galaxies are on the fifth neurons and similar to the Sa type of the galaxies, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
             There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
-            The following two neurons (eighth and ninth neurons from the left) are in the edge of the early type and star burst galaxies.
+            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and star burst galaxies.
             In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
@@
 
-            In general from the 142 galaxies in T12, we categorized them as following; three of the galaxies belongs to SO galaxies, fifteen are Sa, one is Sb, four are SB6, two are SB5, and 21 have a similar SED to SB2.
-            The rest of the galaxies have SEDs in between of the initial 12 suggestions.
+            In general, 56 galaxies correspond exactly to K96 types and the other 86 are in between of the initial 12 suggestions.
             As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model were constructed from co-adding 12 spectra of the 70 galaxies.
@@
             On the other hand, all the other methods (i.e.
-$\chi^2$ fitting, trained neural network) of matching SEDs limit themselves to models, and if they could not find the best match, report the results as an uncertain ones.
+$\chi^2$ fitting, trained neural network) of matching SEDs limit themselves to models, and if they could not find the best match, report the results as uncertain ones.
             However, with SOM, galaxies have this freedom to be categorized in the intermediate groups.
@@
 
-        \subsubsection{1D NETWORKS results and Properties of galaxies}
-        In order to check weather our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, we plot the some physical properties listed in the Tab.~\ref{tab: props} of galaxies in each neurons in the networks.
+        \subsubsection{1D NETWORKS results and Properties of clustered galaxies}
+
+        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~is meaningful and correct, in this section we are going to show the relations between properties of the galaxies in each neuron.
 
@@
             \centering
-            \includegraphics[width=\textwidth]{../images0.01/1d/props3.png}
+            \includegraphics[width=\textwidth]{../images0.01/1d/props5.png}
             \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
@@
 
-        %         \begin{figure}
-        %     \centering
-        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
-        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
-        %     \label{fig: prop1by3}
-        % \end{figure}
+        Fig.~\ref{fig: props} shows the results of the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in $1\times2$, $1\times4$, and $1\times8$ networks.
+        In all the plots $x$-axis shows the number of the neurons divided by the size of the network, and $y$-axis shows one of the mentioned properties.
 
-        %         \begin{figure}
-        %     \centering
-        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
-        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
-        %     \label{fig: prop1by22}
-        % \end{figure}
+        In Fig.~\ref{fig: props}, from early type galaxies to star burst ones, stellar mass and age decreases while sSFR and $f_\mathrm{burst}$ increases, in all three lines. 
+        These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties.
 
-        Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
-        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.
+        N09 used various models to derive galaxies' properties.
+        Through these models, some of the properties are already known to be correlated with each others, i.e. stellar mass and star formation rate.
+        They, however, studied other relations between properties of a sample of SINGS galaxies which didn't have a direct correlation in the models.
+        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggested that younger stellar population correlate with high SFR.
+        They also found the correlation between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
+        Since in {\em CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar mass related correlation must be astrophysically meaningful. 
+        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
+        T12 replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than N09 results.
 
-        In Fig.~\ref{fig: props}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases, in all three lines. 
-        These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.
+               \begin{figure*}
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f1.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f2.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f3.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f4.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f5.png}
+        \end{subfigure}
+       \hfill
+        \begin{subfigure}[b]{0.3\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/1d/f6.png}
+        \end{subfigure}
+        \caption{From up to down: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
+Points show the mean values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the mean values.
+colours shows the type of the galaxies in the new classification.
+The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies.
+The other colours depend on how much they are close to red or blue show that the galaxies are early type or star burst.}
+        \label{fig: props_vs_props}
+    \end{figure*}
+
+        In order to compare our classifications with previous works, we produced the similar plots as the ones in both N09 and T12 (Fig.~\ref{fig: props_vs_props}).
+        In Fig.~\ref{fig: props_vs_props}, points are mean values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
+        The colours show the galaxy types where B type galaxies are shown with red and SB1 ones are shown with blue colours.
+        The redder the colour shows the more similarity with early type galaxies, while the purple to blue colours show more similarity to star burst galaxies.
+        Since in this method we allow galaxies to stay in the classes between the original 12 types of the galaxies, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
+        Galaxies with SEDs more similar to type Sc having bright purple colour, but as expected from the shape of the SED they are old galaxies with high sSFR.
+        Therefore, in all three plots of Fig.~\ref{fig: props_vs_props}, there is a purple point in the middle of the blue points.
+
+        The upper plots in Fig.~\ref{fig: props_vs_props} show the same relation between parameters as N09 and T12 with tighter correlation than those two, in all three plots.
+        As mentioned in both N09 and T12, galaxies with smaller mass tend to be younger and more active galaxies.
+        In Fig.~\ref{fig: props}, we saw the same results, younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
+        It is clearly noticeable that from older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
+        %for more details discussion on these correlations, we encourage readers to read N09 and T12.
+
+        The lower plots in Fig.~\ref{fig: props_vs_props} show the relations between A$_{\rm {FUV}}$ and sSFR, age, and stellar mass.
+        Unlike N09, we found a correlation between A$_{\rm {FUV}}$ and these three parameters.
+        N09 used SINGS galaxies as their test sample and concluded that the attenuation is independent of the star formation, age or stellar mass.
+        They found a very weak correlation between A$_{\rm {FUV}}$ and morphological types of galaxies, which was much weaker than previous studies~\citep[e.g.][]{Dale07}.
+        In Fig.~\ref{fig: props_vs_props}, there is a more clear and stronger correlation between the A$_{\rm {FUV}}$ and the other parameters.
+        The only exception is data from S0 type galaxies.
+        They tend to have a very low A$_{\rm {FUV}}$, which is out of the general trend in all three lower plots of Fig.~\ref{fig: props_vs_props}.
+        However, this value and position is very similar to N09 results.
+        Otherwise, considering the morphology of the galaxies, early type galaxies have more A$_{\rm {FUV}}$.
+        Therefore, we could conclude that the classification of the SED of galaxies using SOM, separates galaxies based on their morphological type and the characteristic of each of these groups are in agreement with the general picture of the galaxy evolution.
 
@@
     \label{sec: 2D}
-    Although the 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category, each neurons in these networks is limited to be connected to on other neurons in each direction.
-    Since each neuron can have more than two immediate neighbours in the 2D networks, they provide more complete pictures of the relation between each SED type.
-    As described in the Sec.\ref{sec: method}, one of the main advantages of the SOM method is when weight of one neurons is adjusted after finding the BMU, weight of the whole map will be changed.
-    This quality of the SOMs provide us an opportunity to analysing 2D networks in two approaches. 
-    At first, as we had in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 models in Fig.~\ref{fig: k96}.
-    For the second path, we trained networks assuming that there might be some other and completely different types of the galaxies that we never encountered with before.
-    Second approach could be used to trace the outliers as well.
+    The 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category.
+    However, each neuron in these networks is limited to be connected to one another neuron in each direction.
+    In 2D network, each neuron can have more than two immediate neighbours, therefore, they provide more complete pictures of relations between each SED type.
+    As described in the Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the BMU, the weight of the whole map will be changed.
+    This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
+    At first, as we had in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
+    In this case, we can categorize SEDs of other galaxies based on those 12 types.
 
-    %maybe I should move the following paragraph to method section?! I am not sure, yet.
-    For getting the best result from both of these ways, we should have SOMs with high ``enough"  neurons to give any new sets of galaxies a chance to find their best place in the map.
-    The  high ``enough"  neurons is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and what kind of the information you need from the SOMs.
+    In the second approach, we trained networks with an assumption of there might be some completely different types of galaxies that we never encountered with before.
+    This approach could be used to trace and recognize the outliers.
+    To be able to execute the second approach, we used or {\tiny selforgmap} library in {\tiny MATLAB}.
+    Using {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together.
+    The latter case, can be used to identify outliers.
+
+    For getting the best result from both of these ways, we should have SOMs with high ``enough"  neurons to give any new sets of galaxies a chance to find their place in the map.
+    The  ``high enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and what kind of the information you need from the SOMs.
+%PB160427: this is a feature of clustering methods in general.
+Maybe in the methods section where you talk about the size of maps, you could give some examples of what "what kind of information" might mean.
     Since the training data (K96 ones) have 12 galaxies, we assumed a SOM with size of $8\times8$~would be a good start.
@@
     We noticed that SOMs with size of $12\times12$~are the maximum possible choice.
-    With increasing from $12\times12$~neurons, the SOMs would be repeat the same shapes just in bigger grids.
+    With increasing from $12\times12$~neurons, the SOMs wouldn't change much.
 
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
+    \begin{figure*}
+        \begin{subfigure}[b]{0.45\textwidth}
             \centering
             \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_12.png}
-            %\caption{$1\times22$ weight map}
-             %\label{fig: 1by22T}
         \end{subfigure}
         \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/2d/hit_t_12_by_12.png}
-             %\caption{$1\times22$ hits map}
-             %\label{fig: 1by22Thits}
+        \begin{subfigure}[b]{0.45\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_self_org_res12.png}
         \end{subfigure}
-        \caption{Results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
-        \label{fig: 12by12T_newsom}
-    \end{figure}
-    Fig.~\ref{fig: 12by12T_newsom} shows the SOM results for the first approach. 
+        \hfill
+        \begin{subfigure}[b]{0.45\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_12.png}
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.45\textwidth}
+            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_self_org_res12.png}
+        \end{subfigure}
+        \caption{$12\times12$~2D SOM results.
+Up: Trained SOMs using K96.
+For training 2D SOMs two different approaches were considered; Either only 12 types of galaxies are existed (left) or not (right).
+Down: classifying the galaxies from T12, using the trained networks above them.
+From the right side one, we can see that there is no outlier in the galaxies from T12, and we can use the left side map as a final clustering results for the T12 galaxies.}
+        \label{fig: 12by12}
+    \end{figure*}
+
+    The upper left part of Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
     Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
     Using this network to categorize any set of SEDs, forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
-    However, all the K96 galaxies are in small side of the map in Fig.~\ref{fig: 12by12T_selforg}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 samples.
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_self_org_res12.png}
-            %\caption{$1\times22$ weight map}
-             %\label{fig: 1by22T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/2d/hit_t_12_by_self_org_res12.png}
-             %\caption{$1\times22$ hits map}
-             %\label{fig: 1by22Thits}
-        \end{subfigure}
-        \caption{Results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
-        \label{fig: 12by12T_selforg}
-    \end{figure}
+    However, all the K96 galaxies are in small side of the map in the upper right map in Fig.~\ref{fig: 12by12}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 templates.
 
-    In the upper map in Fig.~\ref{fig: 12by12T_newsom}, there is a strip of the red, dark red and in some case black colours is distinguishable. 
+    In the upper left part of the map in Fig.~\ref{fig: 12by12}, there is a strip of the grey, dark grey and in some cases black colour is distinguishable.
     This strip is separating early type galaxies with star burst ones.
-    The lower map shows that 5 of the neurons on left side of the strip are full. 
-    These 5s are the same ones in the left hand side of the Fig.~\ref{fig: 1by2T} (early type galaxies).
+    The lower map shows that 5 of the neurons on the left side of the strip are full. 
+    These five neurons are the same ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies).
     The only difference is that here, in this map they have more space to be separated from each other.
-    When we use this network to categorized the SED of galaxies any galaxy places on the left hand side of the strip is an early type galaxy and any one placed in the right side of the strip is a star burst one.
-    Decision about what type of the early type or star burst galaxy is it, is based upon its relative position to each type in the neurons.
+    When we use this network to categorize the SED of galaxies, any galaxy places on the left hand side of the strip is an early type galaxy and anyone placed on the right side of the strip is a star burst one.
+    The decision about what type of early type or star burst galaxy, is based upon its relative position to each type in the SOM.
 
-    The border between the early type galaxies and the star burst ones,in the Fig.~\ref{fig: 12by12T_selforg}, is the black strips in the middle of the upper map, which end up with bright red colour at the bottom of the map in the fifth neuron.
+    The border between the early type galaxies and the star burst ones, in the upper right map in Fig.~\ref{fig: 12by12}, is the black strips in the middle of the upper map, which end up with bright grey colour at the bottom of the map in the fifth neuron.
     In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the star burst ones. 
@@
 
-    We used the both 2D networks to categorized the T12 galaxies and showed the results in Fig.~\ref{fig: 12by12V}.
-    In the lower plot, we used the network from Fig.~\ref{fig: 12by12T_selforg}.
-    Since all the galaxies placed in the bottom part of the map, we can conclude that there in no outlier or very different type of the SED in from K96 models in T12 samples.
-    The upper plot of the Fig.~\ref{fig: 12by12V} represents the T12 galaxies categorization based on the network in the Fig.~\ref{fig: 12by12T_newsom}. 
-    In both maps in the Fig.~\ref{fig: 12by12V}, majority of the galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.
+    We used the both 2D networks to categorize the T12 galaxies and showed the results in lower maps in Fig.~\ref{fig: 12by12}.
+    Since in the lower right map in Fig.~\ref{fig: 12by12} all the galaxies placed in the bottom part of the map, we can conclude that there is no outlier or very different type of the SED from K96 templates in T12 samples.
+    The lower left map of Fig.~\ref{fig: 12by12} represents the T12 galaxies categorization based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
+    Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see here, only 23 galaxies correspond exactly to K96 types.
+    Using 2D maps, we categorized galaxies in more intermediate type than 1D ones.
+    In both lower maps in Fig.~\ref{fig: 12by12}, most the galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.
 
-       \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_12.png}
-            %\caption{$1\times22$ weight map}
-             %\label{fig: 1by22T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_self_org_res12.png}
-             %\caption{$1\times22$ hits map}
-             %\label{fig: 1by22Thits}
-        \end{subfigure}
-        \caption{Results of categorizing T12 galaxies using $12\times12$~network.
-Up: categorizing with network shown in Fig.~\ref{fig: 12by12T_newsom}.
-Down: using network in Fig.~\ref{fig: 12by12T_selforg}.}
-        \label{fig: 12by12V}
-    \end{figure}
-
-    Although because of the fluency of the paper, we first talked about 1D networks and continued to 2D networks we suggest that in case of using the SOMs to categorize the SED of the galaxies or to explore any related data, first step to be checking data using networks similar to the Fig.~\ref{fig: 12by12T_selforg} ones.
+    Although because of the fluency of the paper, we first talked about 1D networks and continued to 2D networks we suggest that in case of using the SOMs to categorize the SED of the galaxies or to explore any related data, first step to be checking data using networks similar to the upper left map in Fig.~\ref{fig: 12by12}.
     In this case, all the outlier or specific cases would be identified and removed from the sample.
 
-    \subsection{Caveat}
-    There is no established method to find the best SOM initial values. Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new result.
-    Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
+    % \subsection{Caveat}
+    % There is no established method to find the best SOM initial values. 
+    % Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new results.
+    % Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
     %no quantitative way to analyse the data?!

### 2016-05-13 main.tex
Draft 0.02

--- 2016-04-20 main.tex
@@
 
-\begin{abstract} %Most of this abstract is just a filler
-In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
-We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
-We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using {\em CIGALE} code to study and compare the properties of each cluster.
-In this paper we introduce a new method of classifying high red shift galaxies, based on their SED.
-%%%%%%From this point it is just repeated%%%%%%%%%
-We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
-We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
-We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
-We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We obtain physical properties of the sample galaxies measured using CIGALE code to study and compare the properties of each cluster.
+\begin{abstract}%% (Must be 250 Words)
+% In this paper, we introduce a new method of clustering of high red-shift galaxies, based on their spectral energy distributions (SED)s.
+We use unsupervised self organizing map(SOM) to train an artificial neural network to categorize SEDs of galaxies.
+We utilize as spectral template as a training set, and trained networks to be able to clustered galaxies based on the template.
+We cluster a sample of 142 galaxies with 0.5< z <1 using the trained network.
+We train networks with various sizes and properties to investigate the nature of the 142 sample galaxies.
+For each network, we cluster the sample of 142 galaxies and visualise their properties.
+In order to test new classifications,we compare physical properties of the galaxies in each cluster.
+We compare our results with  clustering  results  from  other  artificial  neural  networks,  and  with  the  original template classification.
+We conclude that SOM is a very useful method to be used in classifying galaxies based on their SEDs.
+It can be used to find morphology of the high red-shift galaxies, and find a new class of SEDs.
+In this paper, we introduce a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
+Artificial neural networks provide us a reliable method to cluster SEDs of galaxies.
+We use an unsupervised self organizing map(SOM) as a training method to train networks with a sample of galaxies with SEDs between FUV to NIR wavelengths, which their morphological types are known.
+Since information that can be extracted from each network depends on the size and dimension of the trained networks, in this project we train networks with different grids in 1D or 2D.
+We visualise each trained network using a new version of SOM plots.
+To test trained networks, we cluster a sample of 142 galaxies with 0.5 < $z$ < 1 using each of the trained networks.
+We plot average SED of SEDs of galaxies in each neurons in 1D networks, to investigate the nature galaxies in new clusters.
+For each network, we visualise the properties of galaxies in each neurons. 
+We compare mean physical properties of the galaxies such as age, specific star formation rate, stellar mass, and FUV extinction, with each other and found a tight correlations between them.
+Comparing our results with clustering results from supervised artificial neural networks, show us using SOM we can classify galaxies in between types of original spectral types.
+As a result we have a power tool to classify morphological type of galaxies based on their SEDs which also can  identify galaxies with a new shape of SEDs.
+
+%%%% SR20160512: I do not like it! But I do not know how to fix it. I already wrote at least 4 version of it. I need help with this one:((
 
@@
 \begin{keywords} 
- galaxies: star formation, galaxies: stellar content, galaxies: ISM, methods: observational, methods: statistical, data mining, methods:data analysis
+ galaxies: high red shifts, galaxies: spectral energy distribution, methods: observational, methods: statistical, data mining, methods:data analysis
 \end{keywords}
@@
 
-\import{sections0.0/}{intro0.0.tex}
+\import{sections0.02/}{intro0.02.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.0/}{data0.0.tex}
+\import{sections0.02/}{data0.02.tex}
 
@@
 
-\import{sections0.01/}{method0.01.tex}
+\import{sections0.02/}{method0.02.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.01/}{results0.01.tex}
+\import{sections0.02/}{results0.02.tex}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\section{SUMMARY}
+\section{SUMMARY AND FUTURE APPLICATIONS}
 \label{sec: summary}
-1) We introduced the self organizing maps to be used to categorizing the SED of galaxies.
-\newline
-2) Using this method we not only can categorized the galaxies with more precision but also we could recognize the galaxies have similarity to two or more groups of galaxies.
-\newline
-3) This method can help us to find outliers or new categories of galaxies very easily and fast.
 
-4) We plot the properties of the galaxies using new classification and see the correlation between age and SSFR and stellar mass of the galaxies.
+Self organizing maps can be used to classify celestial objects (i.e. stars, quasars, spectra of galaxies, light curves, etc.).
+We showed that we can create various networks with different sizes/dimensions based on information we need from the data. 
+If a broad and general classification is required, networks can have one dimension with few number of neurons.
+While if we need classifications based on differences in more details, we can use a higher number of neurons.
+Since the SOM codes does not work with uncertainty of input parameter, sometimes too much attention to details can cause problems in classifications. 
+Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
+for using SOM method, one should be careful about these small differences and consider in order to separate two groups from each other, how much details do they need to pay attention to.
+
+We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
+By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
+since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
+We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.
+
+The sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
+The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
+A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
+T12  have used a supervised training method, and trained networks with K96 SED template.
+Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
+However, they could not classify 37 out of 142 galaxies in the sample.
+The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or between those types. 
+Therefore, we classified all 142 galaxies of our test sample.
+We plotted the properties of the galaxies in test sample using new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
+We also showed he properties of the galaxies in each groups is in good agreement between their morphological types.
 
 \section*{ACKNOWLEDGMENTS}
-S.R.
-and P.B.
-acknowledge research support from the Natural Sciences and Engineering Research Council of Canada.
-This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
+S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
 %----------------------------------------------------------------------------------------

### 2016-05-13 sections0.02/intro0.02.tex
Draft 0.02

--- 2016-05-07 sections0.01/intro0.01.tex
@@
 The light from galaxies is all the information we could get from them. 
-All the observable phenomena inside galaxies leave footprint on galaxies' spectral energy distributions (SEDs).
-With proper modeling of various features on their SEDs, some of the galaxies' physical properties can be determined.
-Beside the physical properties of galaxies, SEDs of galaxies can be used as an identifier of the morphological type of the galaxies.
+All the observable phenomena inside a galaxy leave footprints on spectral energy distribution (SED) of the galaxy.
+With proper modelling of various features on their SEDs, some of the galaxies' physical properties can be determined.
+The general shape of the SEDs can be used as an identifier of the morphological type of the galaxies.
 In the first attempt the morphological features of galaxies can be categorized to three main groups: elliptical, spiral or irregular galaxies.
-Each of these groups have their own characteristic features and the first two groups can be divided to many branches.
+Each of these groups has their own characteristic features and the first two groups can be divided into many branches.
 
@@
 Based on the usage of the templates, these templates could be restricted to various wavelengths.
-In case of near-IR to ultraviolet (UV) wavelengths (which is pick output of stars), SED contains information about main features of physical properties of galaxies i.e.
+In case of near-IR to ultraviolet (UV) wavelengths (which is pick output of stars), SED contains information about the main features of physical properties of galaxies i.e.
 age, star formation rate (SFR), stellar mass, wide range of the stellar population, some information on interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.
 
-SEDs of galaxies can be used to derive physical properties of galaxies, and from those one can find information about morphological type  galaxies.
-Since not two galaxies, even with the same morphology, are exactly the same, classifying the SED of the galaxies are a challenge.
+SEDs of galaxies can be used to derive physical properties of galaxies, and morphological type galaxies.
+Since not two galaxies, even with the same morphology, have exactly the same properties, classifying the SED of the galaxies are a challenge.
 Many fitting methods are developed and used to find the best matches of template for each SED.
 $\chi^2$ minimizing method is the most commonly used method to do so. 
-Artificial neural networks (ANNs), K-mean clustering, and principle component analysis are the other methods to cluster and classifying the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
+Artificial neural networks (ANNs), K-mean clustering, and principal component analysis are the other methods to cluster and classifying the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
 
 %ANNs
-ANNs are very powerful tools to used in data processing and pattern recognitions problems.
-Their information process method were inspired by the way neurons in human brains work.
+ANNs are very powerful tools to use in data processing and pattern recognition problems.
+Their information process method was inspired by the way neurons in human brains work.
 An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
-It uses sets of trainings method to learn about a non-linear and complex relations between input and output data and how to apply it on new sets of data.
-Studies shows that ANNs provides better fitting than minimizing chi square and would be an alternative choice for fitting data \citep[e.g.][]{Marquez91,Moayed09}.
-In cases that both methods show the same correlation, ANNs still are better method of fitting due their faster results in large data bases \citep[][]{Gulati97}.
+It uses set of training methods to learn about a non-linear and complex relations between input and output data and how to apply it to new sets of data.
+Studies show that ANNs provides better fitting than minimizing chi square and would be an alternative choice for fitting data~\citep[e.g.][]{Marquez91,Moayed09}.
+In cases that both methods show the same correlation, ANNs still are a better method of fitting due their faster results in large data bases~\citep[][]{Gulati97}.
 
@@
 \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} were among the first studies in astronomy that used SOM for their studies.
-From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classificationf of light curves, this method have been used in various aspects in astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
-\citet{Geach12} used COSMOS data to demonstrate two of main application of SOMs; object classification and clustering, and photometric redshift estimation. 
-The later one were subject of many studies \citep[e.g.][]{Kind14a}
-\citet{In12} introduced a new clustering tool which is based on SOM method to analysing large data of spectra.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method have been used in various aspects in astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
+%20160509PB: suggest starting a new paragraph here, with an introductory sentence about galaxy spectra.
+%SR20160512: I start new paragraph after the next sentence not here.
+\citet{Geach12} used COSMOS data to demonstrate two of main applications of SOMs; object classification and clustering, and photometric redshift estimation. 
+The later one was subject of many studies \citep[e.g.][]{Kind14a}.
+
+Spectrum of a galaxy is from combination of spectra of million stars and clouds inside the galaxy.
+Therefore, large spectra data sets contain information of billions of stars and other objects inside galaxies, and needs to be studied carefully. %%%EEEHHHH
+\citet{In12} introduced a new clustering tool, which is based on the SOM method for analysing large data of spectra.
 They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09}
 to test their tool, and created very large SOMs to analyse the type of spectra/objects.
-They also generated SOMs from quasar spectra in order to find unusual types of quasars spectra.
+They also generated SOMs from quasars' spectra in order to find unusual types of quasars' spectra.
 Later \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys and found a new class of quasars.
@@
 \citet{Fustes13} produced a package based on SOM to classify spectra from GAIA survey that were previously classified as "unknown" by SDSS pipeline.
-The package recognizes an astronomical object from an artificial errors, and then classifies the object based on its spectra.
+The package recognizes an astronomical object from artificial errors, and then classifies the object based on its spectra.
 
 %What is this paper about
-In order to compare supervised and unsupervised method, in this paper, we used data from K96 template to train unsupervised neural networks. 
-The network clustered the SEDs and mapped those clusters and their relative relations.
-We compared our results with K96 galaxies classification.
-Then we classify the SED of a sample of galaxies using the constructed SOM.
-
 We used SED of a 142 galaxies with 0.5 < $z$ < 1 from~\citet[][hereafter T12]{Hossein12} paper.
@@
 The latter shows that, not a single type of galaxies in K96 template could describe the SED of the 37 galaxies.
-The unsupervised methods on the other hand, have the freedom of classifying object between known classes, which can be used in this data to find a best SED class for the 37 galaxies.
-T12 also showed that there are tight correlations between physical properties of galaxies and this correlations might be different based on the types of the galaxies.
+The unsupervised methods, on the other hand, have the freedom of classifying objects between known classes, which can be used in this data to find the best SED class for the 37 galaxies.
+T12 also showed that there are tight correlations between physical properties of galaxies and these correlations might be different for each type of the galaxies.
+
+In order to compare supervised and unsupervised method, in this paper, we used data from K96 template to train unsupervised neural networks. 
+The network clustered the SEDs and mapped those clusters and their relative relations.
+We compared our results with K96 galaxies classification.
+Then we classify the SED of a sample of galaxies using the constructed SOM.
 

### 2016-05-13 sections0.02/method0.02.tex
Draft 0.02

--- 2016-05-07 sections0.01/method0.01.tex
@@
 
- The SOM is a clustering method which reduces the dimension of data to lower dimensions usually 1 or 2D while preserving topological features of the original data.
- Results of SOM contains nodes (neurons) that arranged in 1D or 2D arrays \citep{Kohonen98}.
+ The SOM is a clustering method which reduces the dimension of data to lower dimensions, usually 1 or 2D, while preserving topological features of the original data.
+ Results of SOM contain nodes (neurons) that arranged in 1D or 2D arrays \citep{Kohonen98}.
 
- Each nodes may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
+ Each node may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
  In the way that similar data are closer together in the array and the further nodes go from each other, the more dissimilarity appears between their samples.
- %Sahar_self_notes: maybe "some" is better instead of one or more
- A weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be change during the process and has a key factor in a position of nodes in the map.
+ A weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be changed during the process and has a key factor in a position of nodes in the map.
 
@@
      We start by creating S1 $\times$ S2 empty neurons. 
-     The initial arrangement of these neurons depends on a map's topology provided by user.
-     In the case of the 1D maps, since each neurons have two immediate neighbours the topology of the map does not have any affect on the final result and we can choose any topology.
-     However, in 2D maps, the shape of the neurons specifies the number of the immediate neighbours for each neurons and it is up to user that which shape is more suitable for their data.
+     The initial arrangement of these neurons depends on a map's topology provided by users.
+     In the case of the 1D maps, since each neuron has two immediate neighbours the topology of the map does not have any effect on the final result and we can choose any topology.
+     However, in 2D maps, the shape of the neurons specifies the number of the immediate neighbours for each neuron and it is up to user that which shape is more suitable for their data.
      In this paper, we chose hexagonal topology which gives each neuron six neighbours, and causes more interactions between neurons.
@@
         \item Chooses a random vector from our data set ($V_i$).
-        \item Calculates the euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
-This neuron is the winner node and is calling Best Matching Unit (BMU).
+        \item Calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
+This neuron is the winner node and is called the Best Matching Unit (BMU).
         \item  Computes the radius of the neighbourhood of the BMU to find nodes within this radius.
@@
         \end{equation}
-        where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$.
+        where $\tau$ is a decay constant and usually set to be the same as the number of iterations, $N$.
 $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively.
-        \item Changes the weight vectors of the BMU and all the nodes within r(t) as:
+        \item Changes the weight vectors of the BMU, and all the nodes within $r^t_{BMU}$ as:
         \begin{equation}
@@
         where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
-$R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
+$R(t)$ determines how the weight of nodes in the neighbourhood of BMU will change.
         \item  Repeats these steps for $N$ times.
@@
 \label{sec: create_som}
-     In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     SOM in {\tiny NNT} can be created by {\tiny newsom} or {\tiny selforgmap} library which both work in two phases. 
+     In order to create SOM, we used {\tiny MATLAB} neural network 
+     toolbox~\citep[NNT,][]{matlabtolbox}.
+     %%Sr160611: Last time I got the following note from the MNRAS editor:
+     %"Please note that computer software/programming lan- guages must be styled in SMALL CAPITAL LETTERS, according to journal style. Please check and correct this paper accordingly."
+     SOM in {\tiny NNT} can be created by {\tiny NEWSOM} or {\tiny SELFORGMAP} library which both work in two phases. 
      Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
-     The ordering phase continues for requested number of iterations.
+     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by the user. 
+     The ordering phase continues for the requested number of iterations.
      During the iterations, the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to tuning phase neighbourhood distance which both of the numbers set by the user.
@@
      This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
-     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. %cite kohenen book?!
-     We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.
+     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning to happen slowly. %cite kohenen book?!
+     We chose the number of epochs the tuning phase to be 3 times more than the number of epochs in the ordering phase.
 
      To show our results, we used two of the {\tiny NNT}'s built-in plots.
-     A Hits map, which shows number of the times each neurons become the winner (hits), and a distances map, which shows the same neurons as the hits map and the distance between them.
+     These plots, which are evolved version of old SOM plots, are designed to show distance between each clusters more clear.
+     A Hits map, which shows the number of the times each neuron become the winner (hits), and a distance map, which shows the same neurons as the hits map and the distance between them.
      In the maps, the purple hexagonal shape areas represent the neurons.
-     The distances in a distance map are showing by the grey cycle colours.
-     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.
+     The distances in a distance map are shown by the grey cycle colours.
+     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is a small distance between neurons.
      In hit maps, neurons with zero hit left empty.
 
-    Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of maps. 
+    Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of the maps. 
     Although \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size, users usually choose the size of grids based on their data set and their usages of the results.
@@
             \caption{SOM of the mock sample.
-In both plots axis shows the position of the neurones.
+In both plots axis shows the position of the neurons.
 Hexagonal shapes represent the neurons.
 The upper plot is a distance map.
-The gray cycle colours shows the differences between weight of each neuron with white is the minimum differences and black has the maximum one.
+The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one.
 The lower plot is a hit plot.
-It represents number of samples in each neurons, while the empty with neurons means zero hit.
+It represents the number of samples in each neuron, while the empty with neurons means zero hit.
 In this sample the 27 galaxies clustered in 4 groups of 8, 7, 6 and 6 galaxies.}
@@
 
- We created  a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analyzed.
- The mock sample contains two information from each galaxy; first type of galaxies: type 1 or type 2, and either they are high or low star forming galaxies. 
- We generated a SOM with size of $10 \times 10$ using the same initial values mentioned in the Section ~\ref{sec: create_som}.
+ We created  a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analysed.
+ The mock sample contains two information from each galaxy; The type of galaxies: type 1 or type 2, and either they are high or low star forming galaxies. 
+ We generated a SOM with the size of $10 \times 10$ using the same initial values mentioned in the Section ~\ref{sec: create_som}.
 
@@
  The lower plot in the Fig.~\ref{fig: sample} shows a hit map.
- In this map similar to the distance map the axis shows the position of the neurons where the hexagonal shapes are neurons.
- The purple neurons with a number on them shows the number of galaxy in that neurons.
+ On this map similar to the distance map the axis shows the position of the neurons where the hexagonal shapes are the neurons.
+ The purple neurons with a number on them shows the number of galaxies in them.
  Colour coverage of neurons is different and depends on the number of the hits on the sample.
@@
 
-Using this method, as we predicted, we were able to divide the mock sample galaxies in 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
+Using this method, as we predicted, we were able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
 The upper plot in the Fig.~\ref{fig: sample}, clearly shows this division.
 In that plot, the upper part belongs to high star forming galaxies, while the lower part belongs to the low star forming galaxies.
-The left part of the plots is where type 1 galaxies belong to and the right side is for type 2 galaxies.
+The left part of the plot, is where type 1 galaxies belong to and the right side is for type 2 galaxies.
 Grey to black colours shows the border between regions.
@@
 8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
-Since the input data are so simple, each entry only could get either 0 or 1 as type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
-%The reason of that there are only 4 filled neurons in the network is the simplicity of the input data, and the fact that each entry only could get either 0 or 1 as for type of galaxy and 0 or 0.5 as an indicator of SFR.
-We can concludes that although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed only in four groups.
-This network is considered as a train network, and if there is any data set with similar entries, we can use this network to cluster the new data set.
+Since the input data are so simple, each entry only could get either 0 or 1 as a type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
+
+We can conclude that although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed only in four groups.
+This network is considered as a train network, and if there are any data set with similar entries, we can use this network to cluster the new data set.
 
 As we show in the following sections, in the real world with the real data, we never have two galaxies with exactly the same information, we have more than 2 dimensions, and more galaxy types. 
-Therefore, if the network has high enough neurons, the input data would eventually separate from each other and cluster into the smaller and smaller groups. 
-However, if the information of the input data are pretty similar to each other, the number of neurons are going to be much higher than number of input samples, to be able to separate the groups from each other.
-In those cases, one can decide that the amount of similarity or dissimilarity between the input samples.
+Therefore, if the network has high enough neurons, the input data would eventually separate from each other and cluster into smaller and smaller groups. 
+However, if the information of the input data is very similar to each other, the number of neurons is going to be much higher than the number of input samples, to be able to separate the groups from each other.
+Therefore, it is up to the users that decide the similarity or dissimilarity between the input data based on number of neurons.

### 2016-05-13 sections0.02/results0.02.tex
Draft 0.02

--- 2016-05-07 sections0.01/results0.01.tex
@@
 
-    %%% should I move this paragraph to method section?!
     In order to find sufficient size for the trained networks, we created maps with sizes from $1\times2$ to $50\times50$.
@@
     For each grid we created different SOMs with different learning factors, neighbourhood distances, and iteration numbers to find the optimum result for our sample.
-    We created the final SOMs with following initial values: number of iterations in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
+    We created the final SOMs with following initial values: number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance to be 1000, 0.9, 0.02, and 1, respectively.
 
@@
         \label{sec: 1Dt}
-            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and star burst.
+            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and starburst.
             In this case, we generated a network with only two neurons.
@@
             Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of training networks.
-            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
-            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance, $D_j$, between the neurons and the darker is the colour the more $D_j$ is between them.
+            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances, $D_j$, from each other.
+            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance between the neurons and the darker is the colour the more relative distance is between them.
             The lower part shows how many galaxies from K96 template places in each neuron. 
@@
 Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map.
-In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts.
-Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
+In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are starbursts.
+Because of their high emission lines, Sc galaxies moved towards the starburst ones.}
                  \label{fig: 1by2T}
@@
 
-            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups.
+            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.
             In the lower part of Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
-            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
-            In this method, the Sc galaxies have been categorized as star burst galaxy due to the relatively higher amount of the disk stellar population relative to the bulge ones. 
+            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
+            In this method, the Sc galaxies have been categorized as starburst galaxy due to the relatively higher amount of the disk stellar population relative to the bulge ones. 
             According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.
@@
             However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
-            These two galaxies, which are separated from group of star burst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
+            These two galaxies, which are separated from group of starburst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
             In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
             The black colour indicates that the left neuron is completely different from the other two groups.
-            While the white colour shows the two neurons are very similar to one another.
+            While the white colour shows the two right neurons are very similar to one another.
 
-            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided into two groups. 
-            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are star burst galaxies and have strong emission lines.
+            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the starburst galaxies are divided into two groups. 
+            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are starburst galaxies and have strong emission lines.
             However, SB5 and SB6 types have the most internal extinctions.
-            The high amount of extinction causes SED become more flat in the lower wavelength regions.
-            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies than other star burst ones.
+            The high amount of extinction causes SED become more flat at shorter wavelength regions.
+            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies than other starburst ones.
             So in the networks, SB5 and SB6 types intend to move more towards the early type galaxies.
@@
                 \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid.
-In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts.
-However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
+In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as starbursts.
+However, this time 2 of galaxies (SB5, and SB6) are separated starbursts groups.}
                  \label{fig: 1by3T}
@@
             If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 at each node).
-            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
+            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and three of them are empty, which shows there were no galaxy in K96 sample that can fill those neurons.
             In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together. 
@@
             It shows that although we separated the galaxies in twelve groups, but they are still divided in two main groups.
-            The closest occupied neurons in the star burst side of the SOM, belongs to the SB6 type. 
-            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other star burst types.
+            The closest occupied neurons in the starburst side of the SOM, belongs to the SB6 type. 
+            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other starburst types.
 
@@
             Therefore, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.
-           % For using SOM method, one should be careful about these small differences and consider that how much details do we need to pay attention to, to consider two groups are separate from each other.
-           %%%% (I'm not sure if it is good to be here or not)
+
         \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
@@
             Upper plot in Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
-            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
+            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to starburst galaxies.
             The lower plot shows the average SED of the galaxies in each node. 
@@
 Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group.
-In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies.
+In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the starburst galaxies.
 Down: Average SED of the SEDs of the galaxies in each group.
-The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the star burst ones).}
+The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the starburst ones).}
                 \label{fig: 1by2V}
@@
             Since in this network galaxies forced to be divided into maximum two groups, for any SED between these two groups the SOM must decide that each galaxy belongs to which group based on strongest features of its SED.
-            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
+            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as starbursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
             Increasing the size of the SOM helps to solve the problem of the galaxies which have features of both groups.
@@
              Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
-             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to star burst galaxies. 
-             29 of the galaxies are more similar to star burst ones, but not with all of their features. 
-             These groups of galaxies have strong emission lines and the ascending slope towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).
+             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to starburst galaxies. 
+             29 of the galaxies are more similar to starburst ones, but not with all of their features. 
+             These groups of galaxies have strong emission lines and rising flux towards the ultraviolet, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).
 
@@
                 \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
-In the average SED of each neuron, we can clearly see the changes from early type galaxies in the star burst ones.
+In the average SED of each neuron, we can clearly see the changes from early type galaxies in the starburst ones.
 4000\AA~ break reduces from left to right and emission lines increase.}
@@
             There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
-            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and star burst galaxies.
+            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
             In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
@@
 
-        \begin{figure*}
+        \begin{figure}
             \centering
-            \includegraphics[width=\textwidth]{../images0.01/1d/props5.png}
-            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
+            \includegraphics[width=0.5\textwidth]{../images0.01/1d/props5.png}
+            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$ (balck circles), $1\times4$ (blue diamond), and $1\times8$ (red triangles) networks.}
             \label{fig: props}
-        \end{figure*}
+        \end{figure}
 
         Fig.~\ref{fig: props} shows the results of the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in $1\times2$, $1\times4$, and $1\times8$ networks.
-        In all the plots $x$-axis shows the number of the neurons divided by the size of the network, and $y$-axis shows one of the mentioned properties.
+        In all the plots horizontal axis shows the number of the neurons divided by the size of the network, and vertical axis shows one of the mentioned properties.
 
-        In Fig.~\ref{fig: props}, from early type galaxies to star burst ones, stellar mass and age decreases while sSFR and $f_\mathrm{burst}$ increases, in all three lines. 
-        These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties.
+        In Fig.~\ref{fig: props}, from early type galaxies to starburst ones, stellar mass and age decreases while sSFR and $f_\mathrm{burst}$ increases, in all three lines. 
+       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties.
+%PB20160510: I would say something more like "the SED categories represent a continuum of physical properties".
+Of course the physical properties were derived from the SEDs, so maybe this isn't so surprising and you could mention that as well.
+        %%%SR20160611: Sorry I am not sure that I understand this comment?
+        Considering results from Fig.~\ref{fig: props}, we can clearly see that separating galaxies based on SED types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs.
 
@@
         Through these models, some of the properties are already known to be correlated with each others, i.e. stellar mass and star formation rate.
-        They, however, studied other relations between properties of a sample of SINGS galaxies which didn't have a direct correlation in the models.
+        They, however, studied other relations between properties, that didn't have any direct correlation in the models, in a sample of SINGS galaxies.
+%%eHMM I will change the previous sentence!
+It doesn't read well
         They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggested that younger stellar population correlate with high SFR.
@@
 The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies.
-The other colours depend on how much they are close to red or blue show that the galaxies are early type or star burst.}
+The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
         \label{fig: props_vs_props}
@@
         The colours show the galaxy types where B type galaxies are shown with red and SB1 ones are shown with blue colours.
-        The redder the colour shows the more similarity with early type galaxies, while the purple to blue colours show more similarity to star burst galaxies.
+        The redder the colour shows the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
         Since in this method we allow galaxies to stay in the classes between the original 12 types of the galaxies, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
@@
 
-        The lower plots in Fig.~\ref{fig: props_vs_props} show the relations between A$_{\rm {FUV}}$ and sSFR, age, and stellar mass.
-        Unlike N09, we found a correlation between A$_{\rm {FUV}}$ and these three parameters.
-        N09 used SINGS galaxies as their test sample and concluded that the attenuation is independent of the star formation, age or stellar mass.
-        They found a very weak correlation between A$_{\rm {FUV}}$ and morphological types of galaxies, which was much weaker than previous studies~\citep[e.g.][]{Dale07}.
-        In Fig.~\ref{fig: props_vs_props}, there is a more clear and stronger correlation between the A$_{\rm {FUV}}$ and the other parameters.
-        The only exception is data from S0 type galaxies.
-        They tend to have a very low A$_{\rm {FUV}}$, which is out of the general trend in all three lower plots of Fig.~\ref{fig: props_vs_props}.
-        However, this value and position is very similar to N09 results.
-        Otherwise, considering the morphology of the galaxies, early type galaxies have more A$_{\rm {FUV}}$.
-        Therefore, we could conclude that the classification of the SED of galaxies using SOM, separates galaxies based on their morphological type and the characteristic of each of these groups are in agreement with the general picture of the galaxy evolution.
+        N09 studied a correlation between A$_{\rm {FUV}}$ and the other properties of galaxies and showed that the attenuation has no dependency to the specific star formation, and age.
+        In contrast to N09, we found a correlation between A$_{\rm {FUV}}$ and these two parameters, which are shown in lower plots in Fig.~\ref{fig: props_vs_props}.
+        The general trend of the correlation, that we see in Fig.~\ref{fig: props_vs_props}, between A$_{\rm {FUV}}$ and sSFR is similar to the trend that have been found by \cite{Dale07}.
+        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measurement of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
+        They found that for early type galaxies L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and in case of spiral galaxies, there is an anticorrelation between  L$_{IR}$/L$_{FUV}$ and sSFR.
+        It should be noted that, by early type galaxies they mostly meant E and S0 and S0/a types of galaxies.
+        Since in our sample we do not have E type galaxies, we cannot show confidently that we see the same correlation between A$_{\rm {FUV}}$ and sSFR in early type galaxies. 
+        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing the sSFR in the S0 and Sa types.
+        The correlation in the other types of galaxies is very similar to the one that had been shown in \cite{Dale07}.
+        Both \cite{Dale07} and N09 have argued that these apparent trends can be a result of the dependence of star formation history to L$_{IR}$/L$_{FUV}$.
+        Whether these dependency is real or not, in this paper we showed that using SOM we can separate SEDs of galaxies on the way that the characteristic of each of these groups are in agreement with the general picture of the galaxy evolution.
 
@@
     In 2D network, each neuron can have more than two immediate neighbours, therefore, they provide more complete pictures of relations between each SED type.
-    As described in the Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the BMU, the weight of the whole map will be changed.
+    As described in the Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
     This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
@@
 
-    In the upper left part of the map in Fig.~\ref{fig: 12by12}, there is a strip of the grey, dark grey and in some cases black colour is distinguishable.
-    This strip is separating early type galaxies with star burst ones.
+    In the upper left part of the map in Fig.~\ref{fig: 12by12}, although galaxies have more space to move on and more can be separated in any way, they were separated in two main groups.
+    There is a distinguishable strip of the grey, dark grey and in some cases black colour in the map.
+    This strip is separating early type galaxies with starburst ones.
     The lower map shows that 5 of the neurons on the left side of the strip are full. 
@@
     The only difference is that here, in this map they have more space to be separated from each other.
-    When we use this network to categorize the SED of galaxies, any galaxy places on the left hand side of the strip is an early type galaxy and anyone placed on the right side of the strip is a star burst one.
-    The decision about what type of early type or star burst galaxy, is based upon its relative position to each type in the SOM.
+    When we use this network to categorize the SED of galaxies, any galaxy places on the left hand side of the strip is an early type galaxy and anyone placed on the right side of the strip is a starburst one.
+    The decision about what type of early type or starburst galaxy, is based upon its relative position to each type in the SOM.
 
-    The border between the early type galaxies and the star burst ones, in the upper right map in Fig.~\ref{fig: 12by12}, is the black strips in the middle of the upper map, which end up with bright grey colour at the bottom of the map in the fifth neuron.
-    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the star burst ones. 
-    In case of the categorizing a new set of SEDs, if the new SEDs are similar to K96 sample all of them will place in the bottom of the map, but if there are different type of the galaxies, they would sit in any other neurons in the map.
+    Same as other map, in the upper right map in Fig.~\ref{fig: 12by12}, galaxies generally are divided into two main groups.
+    The border between the early type galaxies and the starburst ones is the black strips in the middle of the upper map, which end up with bright grey colour at the bottom of the map in the fifth neuron.
+    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
+    When categorizing a new set of SEDs, if the new SEDs are similar to K96 sample all of them will place in the bottom of the map, but if there are different type of the galaxies, they would sit in any other neurons in the map.
+    In large data sets, one can easily used this network to figure out whether there is any new type of SEDs (or any outliers) are in the data sets or not. 
+    Since, the networks are already available, this procedure should be really fast and easy for big data sets.
 
@@
     In both lower maps in Fig.~\ref{fig: 12by12}, most the galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.
+    Note that, from this sample we do not conclude that there are more early type galaxies in higher red-shifts.
+    We simply indicate that in this sample, we have more early type galaxies, and the reason is the selection effect from the fact that those galaxies had more reliable redshift estimation.
+%PB20160510: could also talk about this as it relates to the method used to select the galaxies in the first place (once you find out what that was!)
+    %SR20160512 I need to talk about it.
 

### 2016-05-18 main.tex
Second draft completed

@@
 In this paper, we introduce a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
-Artificial neural networks provide us a reliable method to cluster SEDs of galaxies.
+%Artificial neural networks provide us a reliable method to cluster SEDs of galaxies.
 We use an unsupervised self organizing map(SOM) as a training method to train networks with a sample of galaxies with SEDs between FUV to NIR wavelengths, which their morphological types are known.
-Since information that can be extracted from each network depends on the size and dimension of the trained networks, in this project we train networks with different grids in 1D or 2D.
+Since information that can be extracted from each network depends on the size and dimension of the trained networks, in this project we train networks with different grids in 1D or 2D.%%???
 We visualise each trained network using a new version of SOM plots.
@@
 We plot average SED of SEDs of galaxies in each neurons in 1D networks, to investigate the nature galaxies in new clusters.
-For each network, we visualise the properties of galaxies in each neurons. 
-We compare mean physical properties of the galaxies such as age, specific star formation rate, stellar mass, and FUV extinction, with each other and found a tight correlations between them.
-Comparing our results with clustering results from supervised artificial neural networks, show us using SOM we can classify galaxies in between types of original spectral types.
-As a result we have a power tool to classify morphological type of galaxies based on their SEDs which also can  identify galaxies with a new shape of SEDs.
+For each network, we visualise the properties of galaxies in each neurons. %%%% combine 94 and 93 
+We compare mean physical properties of the galaxies in each neuron such as age, specific star formation rate, stellar mass, and FUV extinction, with each other and found a tight correlations between them.
+Comparing our results with clustering results from supervised artificial neural networks, show us using SOM we can classify galaxies in between types of original spectral types. %%rephrase
+As a result we have a power tool to classify spectral glaxies based on their SEDs which also can  identify galaxies with a new shape of SEDs.
 
 %%%% SR20160512: I do not like it! But I do not know how to fix it. I already wrote at least 4 version of it. I need help with this one:((
+
+%%% what is the problem we are trying to solve in general! why do we want o classify thing in general, and what is wrong in exciting classification scheam
 

### 2016-05-30 main.tex
after grammatical corrections

--- 2016-05-07 main.tex
@@
 
-\begin{abstract} %Most of this abstract is just a filler % PB160426: OK, no comments on it for now.
-In this paper we introduce a new method of clustering high red shift galaxies, based on their SED.
-We use unsupervised self organizing map to train and validate an artificial neural network which can categorize the spectral energy distribution (SED) of galaxies. 
-We utilize the spectral model introduced by Kinney et al. as a training set and a sample of 142 galaxies with 0.5 < $z$ < 1 a validation set.
-We used physical properties of the sample galaxies measured using {\em CIGALE} code to study and compare the properties of each cluster.
-In this paper we used an unsupervised self organizing map (SOM)method, to create a network based in SED models of galaxies and used sample of galaxies to test the networks. 
-We classify galaxies in different groups and studied the correlation between properties of the galaxies.
-we conclude that the SOM is a very useful and accurate method to be used in classifying galaxies base on their morphology.
+\begin{abstract}%% (Must be 250 Words)
+Spectral energy distribution (SED) of a galaxy contains information about the physical properties of it.
+Classifying SEDs using temples helps understand the nature of the source of SEDs.
+However, available SED templates are limited, which makes finding type of SEDs tricky.
+Most of the current classifying methods cannot classify SEDs outside the ones in the template, and will fail in the special cases.
+In this paper, we introduced a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
+SOM is a type of the artificial neural networks, which mostly is used to identify subgroups in a sample.
+We utilized an unsupervised self-organizing map (SOM) as a method to train networks using templates of SEDs ranging from far ultraviolet (FUV) to near infrared (NIR) wavelengths.
+Then, we used the trained networks to cluster a sample of 142 galaxies with 0.5 < $z$ < 1.
+Since, some the SEDs of these galaxies are not exactly the same as the ones in the template, the previous attempts to classifying SEDs of this group of galaxies were not completely successful. 
+By using SOM, we classify those special SEDs and show that they have similarities to two more of the template ones.
+We investigated the vapidity of our results, by studying the SEDs, and some physical properties of the galaxies that are averaged over galaxies in each neuron the SOMs.
 
-%%%%%%From this point it is just repeated%%%%%%%%%
+%%% what is the problem we are trying to solve in general! why do we want o classify thing in general, and what is wrong in exciting classification scheme
 
@@
 
-\import{sections0.01/}{intro0.01.tex}
+\import{sections0.03/}{intro0.03.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.01/}{data0.01.tex}
+\import{sections0.03/}{data0.03.tex}
 
@@
 
-\import{sections0.01/}{method0.01.tex}
+\import{sections0.03/}{method0.03.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.01/}{results0.01.tex}
+\import{sections0.03/}{results0.03.tex}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\section{SUMMARY}
-\label{sec: summary} %PB160427: not so sure I like the numbering of every sentence, or starting almost all of them with "We". But this is a style thing that we can discuss later.
-1) We introduced the self organizing maps to be used to categorizing the SED of galaxies.
-\newline
-2) Using this method we not only can categorized the galaxies with more precision but also we can see the relative similarity or dissimilarity between each type of galaxies.  
-\newline
-3) We show that using SOM, we could recognize the galaxies have similarity to two or more morphological types of galaxies.
-\newline
-4) We trained networks using sample of SEDs and test them with sample of galaxies with SEDs in the similar badpasses.
-\newline
-5) We plot the properties of the galaxies using new classification and see the correlation between age and SSFR and stellar mass of the galaxies.
-\newline
-6) We show that the properties of the galaxies in each groups is in good agreement between their morphological types.
-\newline
-7) We show that SOM can help us to easily identified new type of the galaxies, in large surveys very easy. 
-\newline
-8) This method can be used to find outliers very fast.
-\newline
-%PB160427: Um, I'm not so sure you really demonstrated numbers 7 and 8. Those are interesting and it could be that a little more work on this and addition to the results section would be a good idea.
+\section{SUMMARY AND FUTURE APPLICATIONS}
+\label{sec: summary}
+
+% Self organizing maps can be used to classify celestial objects (i.e. stars, quasars, spectra of galaxies, light curves, etc.).
+% We showed that we can create various networks with different sizes/dimensions based on information we need from the data. 
+% If a broad and general classification is required, networks can have one dimension with few number of neurons.
+% While if we need classifications based on differences in more details, we can use a higher number of neurons.
+% Since the SOM codes does not work with uncertainty of input parameter, sometimes too much attention to details can cause problems in classifications. 
+% Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
+% for using SOM method, one should be careful about these small differences and consider in order to separate two groups from each other, how much details do they need to pay attention to.
+
+% We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
+% By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
+% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
+% We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.
+
+% The sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+% One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
+% The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
+% A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
+% T12  have used a supervised training method, and trained networks with K96 SED template.
+% Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
+% However, they could not classify 37 out of 142 galaxies in the sample.
+% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or between those types. 
+% Therefore, we classified all 142 galaxies of our test sample.
+% We plotted the properties of the galaxies in test sample using new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
+% We also showed he properties of the galaxies in each groups is in good agreement between their morphological types.
+
+Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.).
+We showed that we can create various networks with different sizes/dimensions based on the information we need from the data. 
+If a broad and general classification is required, networks can have one dimension with a few number of neurons.
+If one needs more detailed classifications, a higher number of neurons should be used.
+Since the SOM codes does not include the uncertainty of input parameter, sometimes too much attention to details can cause problems in classifications. 
+Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
+When using SOM method, one should be careful about these small differences and consider them in order to separate two groups from each other.
+
+We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
+By varying the size of the networks, we found the relative similarity or dissimilarity between each type of galaxies.
+Since we needed a 1D network with 22 neurons to be able to separate all 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are very similar to each other.
+We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outliers in large surveys.
+
+A sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
+The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
+The freedom of having in-between types is one of the main differences between supervised and unsupervised ANNs.
+T12 have used a supervised training method, and trained networks with K96 SED template.
+Same as this work, they tried to classify the sample of 142 galaxies using the trained networks.
+However, they could not classify 37 out of 142 galaxies in the sample.
+The unsupervised method, which we have used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or in between those types.
+Therefore, we classified all 142 galaxies of our test sample.
+We plotted the properties of the galaxies in test sample using the new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
+We also showed that the properties of the galaxies in each groups is in good agreement between their morphological types.
 
 \section*{ACKNOWLEDGMENTS}
-S.R.
-and P.B.
-acknowledge research support from the Natural Sciences and Engineering Research Council of Canada.
-This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
+S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
 %----------------------------------------------------------------------------------------

### 2016-05-30 sections0.03/data0.03.tex
after grammatical corrections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{DATA}
\label{sec: data}
We use SED templates from K96 to train neural networks.
To test the trained networks, we use SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
Following the T12 work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare both supervised and unsupervised methods.

 \subsection{Kinney spectral model}
     \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{images/k96.jpg}
        \caption{K96 spectra template for 12 types of galaxies from T12 paper (Fig. 1 in T12). The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies. Starburst galaxies spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic colour extinction.}
        \label{fig: k96}
    \end{figure}

    K96 used UV-optical spectra of 70 star forming and quiescent nearby galaxies to produce a template that contained 12 types of SEDs.
    These templates were widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies\citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
    K96 claims that these templates can also be used to classifying the SED of the high redshift galaxies.

    The 12 types (what 12 types? the SEDs? in that case this sentence does not belong here at all) of spectra are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    Bulge group represents galaxies similar to M31 and M81, which their UV and optical spectroscopy is dominated by the stellar population in their bulges.
    The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As it is clear in the Fig.~\ref{fig: k96}, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.

    K96 spectra spans from $\sim1200$\AA~to $10000$\AA~with a resolution of $\sim 10$\AA.
    However, in this letter we only use data between $\sim1200$\AA ~to $8000$\AA~to train our networks. 
    This wavelength range was chosen due to availability of flux information in those wavelengths for all 12 types of galaxies.
    In early type galaxies' spectra (B to Sb), the spectrum is redder, and strong absorption lines and 4000\AA~break are distinguishable.
    SEDs of starburst galaxies are more flat on the optical and NIR region than those of the the early types and show strong emission lines.
    For more details on each spectral type, we encourage readers to see K96 and references therein.

 \subsection{SED and Properties of the sample galaxies} 
    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field.
    For each galaxy, robust spectroscopic redshift and photometry data from the Good-MUSIC catalogue had been known.
    The 142 galaxies were selected in T12 based on the availability of data from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC for whole galaxies. 
    Data from these instruments were necessary in order to have a complete picture of stellar population and SFR.
    The photometry data contain information of the galaxies in 10 - 13 filters with the wavelength range of $\sim 0.4-24~\mu$m in the observed frame.
    T12 matched the resolution of the photometry data with K96 data and used these photometry data as inputs for Code Investigating GALaxy Enmission ({\em CIGALE} code;~\citep[][hereafter N09]{Noll09}) to generate the best fitted SED for each galaxy.% as well as some of the physical properties of the galaxies.

    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$\AA, for each galaxy.
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of galaxies such as age, and stellar mass.
    Some of these properties are shown in Tab.~\ref{tab: props}.
    In the Sec.~\ref{sec: 1D}, we study these properties for each categorization.
    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.

    \begin{table}
\caption[]{Description of the properties of T12 galaxies; the output result of {\em CIGALE}}     
\label{tab: props}
\centering
\begin{tabular}{l l l}
\hline\hline
\noalign{\smallskip}
Par. & Unit & Description\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
$f_\mathrm{burst}$ & --- & mass fraction of \\
& & young single population (SP) model \\
\noalign{\smallskip}
$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age \\
\noalign{\smallskip}
$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
SFR & M$_\odot$/yr & instantaneous SFR  \\
$A_\mathrm{FUV}$ & mag & attenuation at 1500\,\AA{} \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{table}

    For testing the created networks, we use SEDs that were produced by T12. 
    These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths.
    Since we have used the T12 SEDs to test the trained network, we only used the part of the SEDs that have a same wavelength range as K96 templates.

 %%%%SR160611: The following is the Hossein's answers to the questions that you asked in the data section; Since, we did not used the spectra data here (we only used generated SEDs and information that was derived from SEDs) ,I assumed it is unnecessary to talk a lot about spectroscopy data. But, if you think it would help to understand the subject better, I will add those information to data section.

%  Is the data vector for each object a list of fluxes (flux densities) as a function of (rest) wavelength? I think we discus this question so I skip it.
%  Same wavelengths for every object? Yes
%  What is the spectral resolution? It depends on the type of spectra we use in T12 see
% below for more information.
%  Do the spectra include the whole galaxy or just the central part? For observed 142
% galaxies: whole spectra because they are in high redshift. For K96 they are co-added
% spectra from different parts.
%  Does the resolution match with K96? We match them to K96, see below.
%  What is the coverage of spectra? See below.
%  Do these galaxies have spectroscopic redshifts, or were redshifts derived from
%   photometry?" All 142 galaxies have robust spectroscopic redshift.
% For more clarification about spectra used in T12: We have three sets of spectra.
% 1 – observed spectroscopic spectra. They are used just for extra independent validation; see figure 17 from T12. This validation is nothing to do with network validations. The useful wavelength range (of
% FORS2 spectrometer) is 4800−10 000 Å, the nominal resolution is R = λ/Δλ = 580, which corresponds to
% a spectral resolution of ∼13Å. We use only range [3500-5100] because all the 142 observed spectra have information in this interval (some of them have no spectral information in 8000A, for example). In T12 you can also find this that can help: “The rest-frame spectra of the sample all include spectral information
% ∼3500–5100 Å. This interval brackets the important features such as the 4000Å break and also the strong emission
% lines such as [O ii]λ3727, λHβ 4861, and [O iii] λλ4959, 5007. The spectroscopic data for the sample galaxies contain different spectral types from starbursts (with a flatter continuum and stronger emission lines) to early-type galaxies (with a redder continuum, strong absorption lines, and large 4000Å break.”
% 2- k96 Model spectra which are for training. The spectra cover the interval ∼1200–10000Å and have a resolution of∼10 Å. We use only interval 1200-7500A. because all the 12 K96 spectra have information in
% this interval (some of the spectra have no information in 9000A, for example).
% 3– The Maraston’s models (SEDs): For each galaxy (from 142) we obtain a best Maraston spectrum (SED) by fitting photometric data to the models. Mraston’s models range very extended wavelength interval (from UV to far IR) with different resolution in different part of a given spectrum. For example resolution in IR is 100A and in optical ~3-5A. The best resolution is related to the optical part (3-5A and we convert all to 10A i.e., to resolution of K69). We cut the best 142 spectra in interval [1200-7500] like K96 for ANN validation or test. (If we had spectral information for all K96 spectra in the interval 1200-10000A, for example, then we would cut all 142 SEDs in 1200- 10000A). So if you find a new training set (other than K96 which we talked about that in our skype chat) and if they had information in 1000-15000A, for example, then we would cut the SEDs in this new interval for validation.
% As a summary: as you know (better than me!) we use K96 as training set and 142 SEDs as validation (or test) set. When we obtain the class of each 142 galaxies (in fact 105 galaxies! You are improving this number to 142 in your paper) then we use 105 observed spectra to make figure 17 from T12. The co-added observed spectra in a certain class match with the associated K96 spectra in the same class (i.e., an independent validation).

### 2016-05-30 sections0.03/intro0.03.tex
after grammatical corrections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}
\label{sec: intro}
%General information about SEDs
All information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on the spectral energy distribution (SED) of that galaxy.
We can determine some physical properties of galaxies by properly modeling various features observed in their SEDs, and the general shape of the SEDs can be used as an identifier of the morphological type of the galaxies.
Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical, or spiral.
Each group has its own characteristic features and can in turn be divided into many sub-branches.

%%Creating templates and NIR_UV templates
Several attempts have been made to composite a thorough template for categorizing the spectral type of galaxies using data from nearby galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00,Mannucci01}. 
Based on their usage, these templates are restricted to certain wavelengths.
In near-infrared (NIR) to ultraviolet (UV) domain of wavelengths (the region where output of stars peak), SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, wide range of the stellar population, some information on interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM.

% categorizing galaxies based on their SED

Attaining high-resolution data and detailed SEDs has been made possible due to advances in imaging techniques, and photometry and spectroscopy devices.
Although this has resulted in a more detailed observation of SEDs, it has also made classification of galaxies more complex.
Since no two galaxies, even with the same morphology, have exactly the same properties, classifying the SED of the galaxies using the templates is very challenging.
To overcome this challenge, many fitting methods have been developed and used to find the best template match for each SED, with $\chi^2$ minimizing method being the most commonly used. 
Artificial neural networks (ANNs), K-mean clustering, and principal component analysis are some other methods used to cluster and classify the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.

%ANNs
ANNs, which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data.
Studies have shown that ANNs outperform chi-square minimizing technique and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91,Moayed09}.
Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.

%Training methods for networks
Neural networks can be trained using two methods; supervised and unsupervised.
In supervised method, a neural network would be trained using input data based on a desired outcome.
This method is very useful for classification of data with specific target values.% (e.g. any pattern recognition with known templates).
On the other hand, in unsupervised method there is no prediction of output.
This method classifies data based on their underlying structures and hidden patterns.
The unsupervised method is very helpful to obtain knowledge from the data, or when the underlying structure of data is not well established.% (e.g. producing a template of SED of galaxies).

%SOM
Kohonen Self organizing map (also called self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citep{Kohonen82}.
It shows a simple geometrical relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
%SOM in Astronomy
The utilization of the SOM in astronomy dates back to 1990s, and \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} were among the first to use SOM in their studies.
\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOM: object classification and clustering, and photometric redshift estimation; the later one was the subject of many other studies \citep[e.g.][]{Kind14a}.
From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
%20160509PB: suggest starting a new paragraph here, with an introductory sentence about galaxy spectra.
%SR20160512: I start new paragraph after the next sentence not here.

%SOM in Astronomy continued.
Spectrum of a galaxy contains the spectra of million stars and clouds inside the galaxy.
Therefore, the spectra datasets are typically very large and very complex to study. %%%EEEHHHH
\citet{In12} introduced a new clustering tool, which was based on the SOM method for analyzing these large datasets.
They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
Later \citet{Meusinger16} used these SOMs, and updated data from SDSS and other surveys, and found a new class of quasars.
The other application of SOMs is to find outliers or errors in the data.
\citet{Fustes13} produced a package based on SOM to classify spectra from GAIA survey that were previously classified as ``unknown'' by SDSS pipeline. This package can recognize an astronomical object from artificial errors, and then classifies the objects based on its spectra.

%What T12 did
~\citet[][hereafter T12]{Hossein12} classified SEDs of a sample of 142 galaxies using supervised neural network method, based on the spectral template presented by K96.
With supervised method, they could only classify SED of 105 out of the 142 galaxies.
The SED of the 37 galaxies from their samples could not be matched with any of those in the K96 templates. 
In order to classify the remaining 37 galaxies, they combined spectrum of the K96 templates.
This procedure showed that, not a single type of galaxies in K96 template could describe the SED of any of those 37 galaxies.
Since the SOM have the freedom to classify objects in between the known classes, it could be applied on this data to find the best SED class for the remaining 37 galaxies.
T12 also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxies.

%What we did
In order to compare supervised and unsupervised methods directly, we use exactly the same data as T12.  
First, we train SOMs using data from K96 and compare our classification with K96 galaxies classification.
Then, we use the trained network to classify the SEDs of 142 galaxies with 0.5 < $z$ < 1 from T12 paper.
Same as T12, we also plot the properties of the T12 galaxies based on the new clusters and compare them with previous works.
In Section $\S$~\ref{sec: data}, we present the data that we use to train and test our networks. 
We describe the SOM methods in Section $\S$~\ref{sec: method}. 
The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss the future works in this subject.

### 2016-05-30 sections0.03/method0.03.tex
after grammatical corrections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{METHOD}
\label{sec: method}
 \subsection{Self Organizing Maps}
 \label{sec: som}

 The SOM is a clustering method which reduces the dimension of the data, usually to 1D or 2D, while preserving topological features of the original dataset.
 Results of SOM contain nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
 Each node may contain one or more samples from the input data.
 The distance between the nodes represents similarity or dissimilarity of underlying samples, i.e., similar data are closer together in the array and the longer the distance between two nodes, the more dissimilar are their samples.
 A weight vector ``\boldit{W}" with the same dimension as the input data is associated with each node, which will be varied during the training process.
 This vector is the key factor in determining the position of the nodes in a map.
 \cite{Geach12} presented the application of the SOM and discussed its algorithm in detail.
 In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a  test model which will help interpreting our results.

 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on the map's topology provided by the user.
     In the case of the 1D maps, since each neuron has two immediate neighbours the topology of the map does not have any effect on the final result and any topology can be chosen.
     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
     Then, a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
     The process of creating SOM happens over a series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration, the SOM code:
     \begin{enumerate}
        \item chooses a random vector from the dataset ($V_i$).
        \item calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$"). This neuron is the winner node and is called the Best Matching Unit (BMU). 
        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size. It then decays exponentially over each iteration as
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
     \end{enumerate}
     These steps are then repeated $N$ times.

\subsection{Creating SOM}
\label{sec: create_som}
     In order to create SOM, we use {\tiny MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     %%Sr160611: Last time I got the following note from the MNRAS editor:
     %"Please note that computer software/programming lan- guages must be styled in SMALL CAPITAL LETTERS, according to journal style. Please check and correct this paper accordingly."
     SOM in {\tiny NNT} can be created by {\tiny NEWSOM} or {\tiny SELFORGMAP} library, both of which work in two phases; ``ordering phase" and ``tuning phase". 
     The first phase is called the ``ordering phase". 
     This phase starts with maximum neighbourhood distance, and an initial high learning factor (usually 0.9), which is provided by the user. 
     The ordering phase continues for a requested number of iterations.
     During the iterations, the learning factor decreases to the tuning phase learning factor and the neighbourhood distance reaches that of the tuning phase as well.
     Both the learning factor and the neighbourhood of the tuning phase are set by the user. 
     The amount by which these two factors change in each iteration depends on the number of iterations.

     The second phase is called the ``tuning phase".
     During this phase, the neighbourhood distance is kept at the user-defined minimum.
     The learning factor, however, decreases gradually.
     The gradual change in the leaning factor helps fine tuning the topology results, leading to a more stable SOM. 
     To allow the fine tuning, The number of iterations in this phase must be much larger than the that of the ordering phase. %cite kohenen book?!
     We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.

     To present our results, we use the {\tiny NNT}'s built-in plotting tool.
     This tool, which is the enhanced version of the old SOM plots, are designed to show the distance between each cluster more clearly.
     Specifically, we use two of the plots in this tool: Hits map, which shows the number of times each neuron has won (hits), and distance map, which shows the distance between those neurons.
     In the maps, the purple hexagonal shape areas represent the neurons.
     The distances in a distance map are shown by the grey cycle colours.
     The darker the colour, the larger distance between neurons.
     In the hit maps, neurons with zero hits are left empty.

    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
    However, \cite{Vesanto05} suggested that the total number of $5\sqrt{n}$ neurons is the most sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.

\subsection{Mock sample}

         \begin{figure}
            \begin{subfigure}[b]{0.5\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/sample/sample2_dist.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{images0.01/sample/sample2_hits.png}
            \end{subfigure}
            \caption{SOM of the mock sample. In both plots, the axes show the position of the neurons. Hexagonal shapes represent the neurons. The top plot is a distance map. The grey cycle colours show the differences between the weights of each neuron with white being the minimum differences and black being the maximum one. The lower plot is a ``hits plot". It represents the number of samples in each neuron, where empty means zero hits. In this sample, the 27 galaxies clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
            \label{fig: sample}
        \end{figure}

 To illustrate how SOM works, we create a mock sample of 27 galaxies.
% We create a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analysed.(<- I don't like this sentence)
 The mock sample contains two attributions of each galaxy: the type (type 1 or type 2), and the start formation rate (high or low). 
 We generated a SOM sized $10 \times 10$ using the same initial values mentioned in Section ~\ref{sec: create_som}.

 Fig. ~\ref{fig: sample} shows the SOM of this mock sample. 
 The upper plot is the distance map. 
 The axes show the position of the neurons in the $10 \times 10$ network.
 The lower plot in Fig.~\ref{fig: sample} shows the hit map.
 On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
 The purple neurons with a number on them shows the number of galaxies in them.
 Colour coverage of neurons depends on the number of the hits on the sample.
 The neuron with the maximum number of hits is darkly coloured while the empty neurons are left uncoloured (white).

Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
The upper plot in the Fig.~\ref{fig: sample}, clearly shows this division.
In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to the low star forming galaxies.
The left half of the plot is where type 1 galaxies belong to, and type 2 galaxies reside in the right side.
Different shades of gray show the border between regions.
The lower plot in Fig.~\ref{fig: sample} shows that only 4 neurons (out of 100) are occupied. 
8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
%Since the input data are chosen to not to be complex, each entry only could get either 0 or 1 as a type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
We can conclude that although each galaxy had  the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributions, they remained only in four groups.
This network is considered as a train network and can be used to cluster any new dataset with similar entries.

As we show in the following sections, with data from real galaxies, we see that the number of dimensions are more than two and we never have two galaxies with exactly the same information. 
Therefore, if the network has high enough neurons, the input data would eventually separate from each other and cluster into smaller groups. 
However, if the information of the input data is very similar to each other, the number of neurons is going to be much higher than the number of input samples, to be able to separate the groups from each other. 
Therefore, it is up to the users that decide the similarity or dissimilarity between the input data based on number of neurons.

### 2016-05-30 sections0.03/results0.03.tex
after grammatical corrections

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{RESULTS and DISCUSSION}
\label{sec: result}

    In this section we show the results of the neural networks that are trained using K96 data.
    Training with K96 templates results in networks that have regions with known morphological types. 
    The trained networks can then be used to categorize other galaxies.
    %In following we show how we trained data and used galaxies from T12 to show how the clustering using trained networks works.

    In order to find sufficient size for the trained networks, we create maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying grid size of the maps helps us to monitor whether grouping galaxies in smaller maps is because of their similarities in their SEDs or not having enough space to be separated. %(this sentence is definitely wrong and I don't understand what you are trying to say to fix it.).
    Based on size the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.
    We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.

    We start our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then we increase the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
    We generate 2D networks (Sec.~\ref{sec: 2D}), and once again we start with the smallest number of neuron possible (4 neurons in $2\times2$ map), and then increase them to 144 in a $12\times12$ map.

    For each generated network, we compare the results with K96 categorization.
    We also use these networks to classify the T12 galaxy samples, and compare them with classifications from supervised networks in T12.
    \subsection{1D SOMs}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            To start our clustering, we assume that galaxies can be divided into only two general types; quiescent and starburst.
            In this case, we generate a network with only two neurons.
            We increased the size of the map gradually until the 12 input sample galaxies divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of the training networks.
            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances, $D_j$.
            As it was mentioned in the Sec.~\ref{sec: method}, increase in the darkness of colours between neurons represents the the increase in relative distance between the neurons.
            The lower parts of figurs show the number galaxies from K96 template that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are starbursts. Because of their high emission lines, Sc galaxies moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.%(why do you keep reaping that?)
            In the lower part of Fig.~\ref{fig: 1by2T}, we see that galaxies are divided into two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc galaxies have been categorized as starburst galaxy due to the relatively higher amounts of disk stellar population relative to that of the bulge. 
            According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
            %If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty(this sentence does not make much sense. I kind of think I know what you're trying to say (because once I translate this sentence to farsi word by word, it kind of comes together) but please phrase it more carefully.).
            %[suggested sentence: 
            If the galaxies in Fig.~\ref{fig: 1by2T} were truly belong in two groups, they would be grouped into two groups yet again, even when we try to cluster them into three. 
            However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
            These two galaxies, which are separated from group of starburst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups.
            While the white colour shows the two right neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst galaxies are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are starburst galaxies and have strong emission lines.
            On the other hand, SB5 and SB6 types have the highest internal extinctions; this causes the SED to become more flat at shorter wavelength regions. 
            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies rather than other starbursts.
            Therefore, in the networks, SB5 and SB6 types intend to be grouped close to the early type galaxies.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as starbursts. However, this time 2 of galaxies (SB5, and SB6) are separated starbursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increase the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the program%(program? definitely use something else; like the algorithm?) 
            pays more attention to small differences between each group.
            Increasing the size of maps means that even the smallest differences between galaxies have to be considered.
            If the galaxies from K96 have completely distinct SEDs, then a $1\times12$ sized SOM is expected to show 12 different groups each containing a single galaxy.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two galaxies and three of them are empty.
            It is evident that there were no galaxy in K96 sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types B and E, SB3 and SB4, and SB1 and SB2 are the ones groups together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies, however, remain in the same neuron until the size of map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between galaxies B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.

            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups. 
            5 groups in the left side neurons were separated from 7 groups in the right side of the map with two dark-grey colours between them.
            This shows that even though the galaxies are clustered in twelve groups, there still remains only two main distinct groups.
            The closest occupied neurons in the starburst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other starburst types.

            The fact that the galaxies needs to have at least 22 different neurons to be divided into 12 groups, shows that the differences between SB1 and SB2, and B and E galaxies are very small.
            Because of their similarities, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.

        \subsubsection{CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            Once the networks are trained, as discussed in Sec.~\ref{sec: 1Dt}, we used them to classifying a sample 142 galaxies from T12.
            Upper plot in Fig.~\ref{fig: 1by2V} shows the result of this classification of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            The lower plot shows the average SED of the galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that were classified as an early type galaxy. 
            These galaxies are similar to the ones in the left node in the upper plot in Fig.~\ref{fig: 1by2T}.
            The plots clearly show the 4000\AA~break in the SEDs, which is one of the signatures of early type galaxies.
            The strong emission lines in the figure could be from galaxies with similar SED to Sa galaxies, but with stronger emission lines.
            The right plot in the lower part of Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are indications of high SFR in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in Fig.~\ref{fig: 1by2T}. Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the starburst galaxies. Down: Average SED of the SEDs of the galaxies in each group. The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the starburst ones).}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, what predominantly decides which group the galaxy belongs to is the strongest feature in its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as starbursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.

            Fig.~\ref{fig: 1by3V} presents the result of classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
            In the upper plot of this figure we see that 66 of the galaxies belong to the early type group, and 47 belong to starburst galaxies. 
            29 of the galaxies, however, are similar to starbursts in some, but not all, of their features. 
            These groups of galaxies have strong emission lines and high flux in shorter wavelengths, but they also have a strong 4000\AA~break, which makes them cluster closer to the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the K96 galaxies into 12 different neurons.
            Same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belong in each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies in the starburst ones. 4000\AA~ break reduces from left to right and emission lines increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower plot of the figure presents the average SED of the galaxies in each neuron.
            However, since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, we only have 12.

            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
            If a cluster from T12 galaxies fills the same neurons as the K96 galaxies ones, we can conclude that SEDs of galaxies in the cluster are very similar to those of the K96 galaxies.
            Otherwise, we can conclude that SEDs of galaxies in the cluster are similar to two of those in K96 sample.
            For the later case, the colours establish that galaxies are more similar to which ones in the K96 sample.

            It can be seen that the first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies with specifications similar to that of the type B or E in the T12 sample.
            There are 3 galaxies in the third neuron, which shows these 3 galaxies are similar to the S0 type. 
            18 of the galaxies are on the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
            The far right neurons in the network belongs to galaxies with SED comparable to type SB1 and SB2.

            In general, 56 galaxies correspond exactly to K96 types and the other 86 are placed between the initial 12 suggestions.
            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model was constructed from co-adding 12 spectra of the 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.

            On the other hand, the other methods e.g. $\chi^2$ fitting, trained neural network of fitting SEDs are limited to models, and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.

        \subsubsection{RESULTS PROPERTIES OF CLUSTERED GALAXIES}

        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~is correct, in this section we test the relations between properties of the galaxies in each neuron.

        \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{images0.01/1d/props5.png}
            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$ (balck circles), $1\times4$ (blue diamond), and $1\times8$ (red triangles) networks.}
            \label{fig: props}
        \end{figure}

        Fig.~\ref{fig: props} shows the results of the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network, and vertical axis is one of the aforementioned properties.

        As shown in Fig.~\ref{fig: props}, in all three lines, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst ones. 
       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
        Considering the results from Fig.~\ref{fig: props}, we can clearly see that separating galaxies based on SED types also leads to a separation in properties that derived (via {\em CIGALE}) from the SEDs.

        N09 used various models to derive the properties galaxies.
        Through these models, some of the properties are already known to be correlated with each others, e.g., stellar mass and star formation rate.
        They also studied other relations between properties that didn't have any direct correlation in the models in a sample of SINGS galaxies. %%eHMM I will change the previous sentence! It doesn't read well
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlate with high SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in {\em CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        T12 replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than N09 results.

               \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
        \end{subfigure}
        \caption{From up to down: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the mean values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the mean values. colours shows the type of the galaxies in the new classification. The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies. The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
        \label{fig: props_vs_props}
    \end{figure*}

        In order to compare our classifications with previous works, we produced similar plots to the ones in both N09 and T12 (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, data points are mean values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties. 
        The colours show the galaxy types, where B type galaxies are shown with red and SB1 ones are shown with blue colours.
        The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original 12 types of the galaxies, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        Galaxies with SEDs more similar to type Sc having bright purple colour, but, as expected from the shape of the SED, they are old galaxies with high sSFR.
        Therefore, in all three plots of Fig.~\ref{fig: props_vs_props}, there is a purple point in the middle of the blue points.

        The upper plots in Fig.~\ref{fig: props_vs_props} show the same relations as N09 and T12, but with tighter correlation than those two, in all three plots.
        As mentioned in both N09 and T12, galaxies with smaller mass tend to be younger and more active.
        In Fig.~\ref{fig: props}, we see the same results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        It is clearly noticeable that from older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
        %for more details discussion on these correlations, we encourage readers to read N09 and T12.

        N09 studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependency to the specific star formation, and age.
        In contrast to N09, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, which are shown in lower plots in Fig.~\ref{fig: props_vs_props}.
        The general trend of the correlation that we see between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend that have been found by \cite{Dale07}.
        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measurement of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
        They found that for early type galaxies L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and in case of spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
        It should be noted that, by early type galaxies they mostly meant E and S0 and S0/a types of galaxies.
        Since in our sample we do not have E type galaxies, we cannot show confidently that we see the same correlation between A$_{\rm {FUV}}$ and sSFR in early type galaxies. 
        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing the sSFR in the S0 and Sa types.
        The correlation in the other types of galaxies is very similar to the one that had been shown in \cite{Dale07}.
        Both \cite{Dale07} and N09 have argued that these apparent trends can be a result of the dependence of star formation history to L$_{IR}$/L$_{FUV}$.
        Whether these dependency is real or not, in this paper we showed that using SOM we can separate SEDs of galaxies on the way that the characteristic of each of these groups are in agreement with the general picture of the galaxy evolution.

    \subsection{2D SOMs}
    \label{sec: 2D}
    The 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category.
    However, each neuron in these networks is limited to be connected to one other neuron in each direction.
    In 2D network, each neuron can have more than two immediate neighbours, therefore, they provide more complete pictures of relations between each SED type.
    As described in the Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
    This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
    At first, as we had in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
    In this case, we can categorize SEDs of other galaxies based on those 12 types.

    In the second approach, we trained networks with an assumption of there might be some completely different types of galaxies that we never encountered before.
    This approach can be used to trace and recognize the outliers.
    To be able to execute the second approach, we used {\tiny selforgmap} library in {\tiny MATLAB}.
    Using {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together.
    The latter case, can be used to identify outliers.

    For getting the best result from both of these ways, we should have SOMs with ``high enough"  neurons to give any new sets of galaxies a chance to find their place in the map.
    The  ``high enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information you need from the SOMs. %PB160427: this is a feature of clustering methods in general. Maybe in the methods section where you talk about the size of maps, you could give some examples of what "what kind of information" might mean.
    Since the training data (K96 ones) have 12 galaxies, we assumed a SOM with size of $8\times8$~would be a good start.
    We then increased the size of the SOM to find the highest size suitable for the training sample.
    We noticed that SOMs with size of $12\times12$~are the maximum possible choice.
    That is increasing from $12\times12$~neurons, would not change the SOMs by much.

    \begin{figure*}
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images0.01/2d/dist_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images0.01/2d/dist_12_by_self_org_res12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{images0.01/2d/hit_v_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{images0.01/2d/hit_v_12_by_self_org_res12.png}
        \end{subfigure}
        \caption{$12\times12$~2D SOM results. Up: Trained SOMs using K96. For training 2D SOMs two different approaches were considered; Either only 12 types of galaxies are existed (left) or not (right). Down: classifying the galaxies from T12, using the trained networks above them. From the right side one, we can see that there is no outlier in the galaxies from T12, and we can use the left side map as a final clustering results for the T12 galaxies.}
        \label{fig: 12by12}
    \end{figure*}

    The upper left part of Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
    Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
    Using this network to categorize any set of SEDs forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
    However, all K96 galaxies are in a small side in the upper right map in Fig.~\ref{fig: 12by12}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even if it is way far away from the K96 templates.

    In the upper left part of the map in Fig.~\ref{fig: 12by12}, although galaxies have more ways to be separated, they were separated in two main groups.
    There is a distinguishable strip of the grey, dark grey and in some cases black colour in the map.
    This strip is separating early type galaxies with starburst ones.
    The lower map shows that 5 of the neurons on the left side of the strip are full. 
    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies).
    The only difference is that here, in this map they have more space to be separated from each other.
    When we use this network to categorize the SED of galaxies, any galaxy places on the left hand side of the strip is an early type galaxy and any one placed on the right side of the strip is a starburst one.
    The decision about what type of early type or starburst galaxy, is based upon its relative position to each type in the SOM.

    Same as ther other map, in the upper right map in Fig.~\ref{fig: 12by12}, galaxies generally are divided into two main groups.
    The border between the early type galaxies and the starburst ones is black strips in the middle of the upper map, which end up with bright grey colour at the bottom of the map in the fifth neuron.
    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
    When categorizing a new set of SEDs, if the new SEDs are similar to K96 sample all of them will be placed in the bottom of the map, but if there are different type of the galaxies, they would sit in any other neurons in the map.
    In large datasets, one can easily used this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets or not. 
    Since the networks are already available, this procedure should be really fast and easy for big datasets.

    We use both 2D networks to categorize the T12 galaxies and the results are shown in lower maps in Fig.~\ref{fig: 12by12}.
    Since in the lower right map in Fig.~\ref{fig: 12by12} all galaxies are placed in the bottom part of the map, we can conclude that there are no outliers or very different type of the SEDs from K96 templates in T12 samples.
    The lower left map of Fig.~\ref{fig: 12by12} represents the T12 galaxies categorization based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
    Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see that only 23 galaxies correspond exactly to K96 types.
    Using 2D maps, we categorized galaxies in more intermediate type than 1D ones.
    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.
    Note that, from this sample we do not conclude that there are more early type galaxies in higher red-shifts.
    We simply indicate that in this sample, we have more early type galaxies, and the reason is the selection effect from the fact that those galaxies had more reliable redshift estimation.

    Although for the fluency of the paper, we first talked about 1D networks and continued to 2D networks we suggest, in case of using the SOMs to categorize the SED of the galaxies or to explore any related data, the first step to be checking the data using networks similar to the upper left map in Fig.~\ref{fig: 12by12}.
    In this case, all the outliers or specific cases would be identified and removed from the sample.

    % \subsection{Caveat}
    % There is no established method to find the best SOM initial values. 
    % Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new results.
    % Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
    %no quantitative way to analyse the data?!

### 2016-06-03 main.tex
PB: edit abstract

@@
 \begin{abstract}%% (Must be 250 Words)
-Spectral energy distribution (SED) of a galaxy contains information about the physical properties of it.
-Classifying SEDs using temples helps understand the nature of the source of SEDs.
-However, available SED templates are limited, which makes finding type of SEDs tricky.
-Most of the current classifying methods cannot classify SEDs outside the ones in the template, and will fail in the special cases.
-In this paper, we introduced a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
-SOM is a type of the artificial neural networks, which mostly is used to identify subgroups in a sample.
-We utilized an unsupervised self-organizing map (SOM) as a method to train networks using templates of SEDs ranging from far ultraviolet (FUV) to near infrared (NIR) wavelengths.
-Then, we used the trained networks to cluster a sample of 142 galaxies with 0.5 < $z$ < 1.
-Since, some the SEDs of these galaxies are not exactly the same as the ones in the template, the previous attempts to classifying SEDs of this group of galaxies were not completely successful. 
-By using SOM, we classify those special SEDs and show that they have similarities to two more of the template ones.
-We investigated the vapidity of our results, by studying the SEDs, and some physical properties of the galaxies that are averaged over galaxies in each neuron the SOMs.
+The spectral energy distribution (SED) of a galaxy contains information about its physical properties.
+Classifying SEDs using templates helps elucidate the nature of a galaxy's energy sources.
+However, available templates are limited, which can complicate SED classification.
+Most current classification methods cannot classify SEDs outside the range of templates, and will fail in special cases.
+In this paper, we introduce a new method of classifying the spectral
+energy distributions of high redshift galaxies: the self-organizing map.
+Self-organizing maps are a type of artificial neural network, mostly used to identify subgroups in a sample.
+We trained an unsupervised self-organizing map networks using a set of
+galaxy SED templates covering the wavelength range from far ultraviolet to near infrared.
+The trained networks were used to cluster the SEDs of a sample of 142 galaxies with $0.5 < z < 1$.
+Compared to previous attempts to classify this sample, the
+self-organizing map approach was able to better classify the SEDs with
+similarities to more than one template.
+The averaged SEDs and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
 

### 2016-06-03 main.tex
add PB CPSX affiliation

@@
 \date{\today}
-\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1}$\thanks{E-mail:
-srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1}$\\
+\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
+srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1,3}$\\
 $^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
-$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
+$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
+$^{3}$Center for Planetary Science \& Exploration, Western University}
 \maketitle

### 2016-06-03 main.tex
PB: edit summary

@@
 
-Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.).
-We showed that we can create various networks with different sizes/dimensions based on the information we need from the data. 
-If a broad and general classification is required, networks can have one dimension with a few number of neurons.
+Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.)
+Galaxy spectra can be classified in various networks with different sizes/dimensions based on the information needed from the data. 
+If a broad and general classification is required, networks can have one dimension with a few neurons.
 If one needs more detailed classifications, a higher number of neurons should be used.
-Since the SOM codes does not include the uncertainty of input parameter, sometimes too much attention to details can cause problems in classifications. 
-Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
-When using SOM method, one should be careful about these small differences and consider them in order to separate two groups from each other.
+Since self-organizing maps do not include the uncertainty of input parameters, sometimes too much attention to detail can cause problems in classifications. 
+%Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
+When using the SOM method, one should consider whether small differences between objects are physically meaningful when separating two groups from each other.
 
-We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
-By varying the size of the networks, we found the relative similarity or dissimilarity between each type of galaxies.
-Since we needed a 1D network with 22 neurons to be able to separate all 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are very similar to each other.
-We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outliers in large surveys.
+We used SOMs to classify the template spectra of K96, made from galaxies with known morphological type, and created networks with different uses.
+By varying the size of the networks, we found the relative similarity between the K96 template classes.
+A one-dimensional network with 22 neurons was needed in order to
+separate all 12 K96 spectra; we concluded that K96 types B and E, and types SB1 and SB2, are very similar to each other.
+We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.
 
 A sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
-One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
-The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
-The freedom of having in-between types is one of the main differences between supervised and unsupervised ANNs.
-T12 have used a supervised training method, and trained networks with K96 SED template.
-Same as this work, they tried to classify the sample of 142 galaxies using the trained networks.
-However, they could not classify 37 out of 142 galaxies in the sample.
-The unsupervised method, which we have used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or in between those types.
-Therefore, we classified all 142 galaxies of our test sample.
-We plotted the properties of the galaxies in test sample using the new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
-We also showed that the properties of the galaxies in each groups is in good agreement between their morphological types.
+%One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
+The test results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.% but not exactly the same as one of them.
+The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
+T12 used a supervised training method to train networks with K96 SED templates and classify the same sample of 142 galaxy spectra;
+however, they could not classify 37 out of 142 spectra.
+The unsupervised method used in this project was able to classify  all 142 spectra in the sample
+as belonging to one of the morphological types introduced by K96 or a class in between those types.
+
+The properties of the galaxies in the test sample using the new
+classification were found to more tightly correlate in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies. 
+The properties of the galaxies in each group are in good agreement with their morphological types.
 

### 2016-06-03 main.tex
change ti \citealias for K96 and T12

@@
 
-%\defcitealias{Hossein12}{T12}
+%\defcitealias{Hossein12}{\citealias{Hossein12}}
 
@@
 \defcitealias{Hossein12}{T12}
+\defcitealias{Kinney96}{K96}
 
@@
 
-% We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
+% We used SOMs to classify SEDs of the galaxies with known morphological type from \citealias{Kinney96}, and created networks with different usages.
 % By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
-% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
+% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from \citealias{Kinney96} for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
 % We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.
 
-% The sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+% The sample of 142 high red-shift galaxies from \citealias{Hossein12} was used to test the trained networks.
 % One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
@@
 % A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
-% T12  have used a supervised training method, and trained networks with K96 SED template.
+% \citealias{Hossein12}  have used a supervised training method, and trained networks with \citealias{Kinney96} SED template.
 % Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
 % However, they could not classify 37 out of 142 galaxies in the sample.
-% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or between those types. 
+% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by \citealias{Kinney96} or between those types.
 % Therefore, we classified all 142 galaxies of our test sample.
@@
 
-We used SOMs to classify the template spectra of K96, made from galaxies with known morphological type, and created networks with different uses.
-By varying the size of the networks, we found the relative similarity between the K96 template classes.
+We used SOMs to classify the template spectra of \citealias{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
+By varying the size of the networks, we found the relative similarity between the \citealias{Kinney96} template classes.
 A one-dimensional network with 22 neurons was needed in order to
-separate all 12 K96 spectra; we concluded that K96 types B and E, and types SB1 and SB2, are very similar to each other.
+separate all 12 \citealias{Kinney96} spectra; we concluded that \citealias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
 We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.
 
-A sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+A sample of 142 high red-shift galaxies from \citealias{Hossein12} was used to test the trained networks.
 %One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
@@
 The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-T12 used a supervised training method to train networks with K96 SED templates and classify the same sample of 142 galaxy spectra;
+\citealias{Hossein12} used a supervised training method to train networks with \citealias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
 however, they could not classify 37 out of 142 spectra.
 The unsupervised method used in this project was able to classify  all 142 spectra in the sample
-as belonging to one of the morphological types introduced by K96 or a class in between those types.
+as belonging to one of the morphological types introduced by \citealias{Kinney96} or a class in between those types.
 

### 2016-06-03 sections0.03/intro0.03.tex
PB edited intro

@@
 %General information about SEDs
-All information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on the spectral energy distribution (SED) of that galaxy.
-We can determine some physical properties of galaxies by properly modeling various features observed in their SEDs, and the general shape of the SEDs can be used as an identifier of the morphological type of the galaxies.
-Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical, or spiral.
+Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
+We can determine some physical property of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
+Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral.
 Each group has its own characteristic features and can in turn be divided into many sub-branches.
@@
 %%Creating templates and NIR_UV templates
-Several attempts have been made to composite a thorough template for categorizing the spectral type of galaxies using data from nearby galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00,Mannucci01}.
+Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using data from nearby galaxies~(e.g.\citealt{Kinney93}, \citealt{Kinney96}, hereafter K96, \citealt{Bershady00}, \citealt{Mannucci01}).
 Based on their usage, these templates are restricted to certain wavelengths.
-In near-infrared (NIR) to ultraviolet (UV) domain of wavelengths (the region where output of stars peak), SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, wide range of the stellar population, some information on interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM.
+In near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where energy output of stars peaks), the SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
 
@@
 
-Attaining high-resolution data and detailed SEDs has been made possible due to advances in imaging techniques, and photometry and spectroscopy devices.
-Although this has resulted in a more detailed observation of SEDs, it has also made classification of galaxies more complex.
-Since no two galaxies, even with the same morphology, have exactly the same properties, classifying the SED of the galaxies using the templates is very challenging.
-To overcome this challenge, many fitting methods have been developed and used to find the best template match for each SED, with $\chi^2$ minimizing method being the most commonly used. 
-Artificial neural networks (ANNs), K-mean clustering, and principal component analysis are some other methods used to cluster and classify the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
+Advances in techniques and detectors have resulted in more detailed observations of SEDs and also made classification of galaxies more complex.
+Since no two galaxies, even with the same morphology, have exactly the same properties, classifying SEDs of galaxies using templates is very challenging.
+To overcome this challenge, many fitting methods have been developed and used to find template matches for SEDs, with $\chi^2$ minimization being the most commonly used. 
+Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
 
 %ANNs
-ANNs, which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
+Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
 An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
 It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data.
-Studies have shown that ANNs outperform chi-square minimizing technique and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91,Moayed09}.
+Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91,Moayed09}.
 Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.
@@
 %Training methods for networks
-Neural networks can be trained using two methods; supervised and unsupervised.
+Neural networks can be trained using two methods: supervised and unsupervised.
 In supervised method, a neural network would be trained using input data based on a desired outcome.
@@
 %SOM
-Kohonen Self organizing map (also called self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citep{Kohonen82}.
-It shows a simple geometrical relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
+A Kohonen self-organizing map (also called self-organizing map, or SOM) is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
+It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
 %SOM in Astronomy
-The utilization of the SOM in astronomy dates back to 1990s, and \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} were among the first to use SOM in their studies.
-\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOM: object classification and clustering, and photometric redshift estimation; the later one was the subject of many other studies \citep[e.g.][]{Kind14a}.
+The utilization of the SOM in astronomy dates back to the 1990s, with \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} among the first to use SOMs in their studies.
+\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOMs: object classification and clustering, and photometric redshift estimation.
+The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
 From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
@@
 %SOM in Astronomy continued.
-Spectrum of a galaxy contains the spectra of million stars and clouds inside the galaxy.
-Therefore, the spectra datasets are typically very large and very complex to study. %%%EEEHHHH
-\citet{In12} introduced a new clustering tool, which was based on the SOM method for analyzing these large datasets.
+Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
+These integrated specta combine the light of billions of individual stars and nebulae within a galaxy, and
+finding patterns and common characteristics between galaxies can be a complex task.
+\citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
 They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
 They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
-Later \citet{Meusinger16} used these SOMs, and updated data from SDSS and other surveys, and found a new class of quasars.
+Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
 The other application of SOMs is to find outliers or errors in the data.
-\citet{Fustes13} produced a package based on SOM to classify spectra from GAIA survey that were previously classified as ``unknown'' by SDSS pipeline.
-This package can recognize an astronomical object from artificial errors, and then classifies the objects based on its spectra.
+\citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
+This package can recognize an astronomical object from artificial errors, and then classify the object based on its spectrum.
+%PB20160603: I don't know what you mean by "artificial errors"
 
 %What T12 did
-~\citet[][hereafter T12]{Hossein12} classified SEDs of a sample of 142 galaxies using supervised neural network method, based on the spectral template presented by K96.
-With supervised method, they could only classify SED of 105 out of the 142 galaxies.
+~\citet[][hereafter T12]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by K96.
+With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
 The SED of the 37 galaxies from their samples could not be matched with any of those in the K96 templates. 
 In order to classify the remaining 37 galaxies, they combined spectrum of the K96 templates.
-This procedure showed that, not a single type of galaxies in K96 template could describe the SED of any of those 37 galaxies.
-Since the SOM have the freedom to classify objects in between the known classes, it could be applied on this data to find the best SED class for the remaining 37 galaxies.
-T12 also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxies.
+%This procedure showed that, not a single type of galaxies in K96 template could describe the SED of any of those 37 galaxies. %PB20160603: repeats previous sentence
+T12 also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.
 
 %What we did
-In order to compare supervised and unsupervised methods directly, we use exactly the same data as T12.  
-First, we train SOMs using data from K96 and compare our classification with K96 galaxies classification.
-Then, we use the trained network to classify the SEDs of 142 galaxies with 0.5 < $z$ < 1 from T12 paper.
-Same as T12, we also plot the properties of the T12 galaxies based on the new clusters and compare them with previous works.
+In this paper, we compare supervised and unsupervised methods of galaxy spectral classification directly, using exactly the same data as T12.  
+Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
+to find the best SED class for the 37 galaxies that could not be clasified by the supervised method.
+First, we train self-organizing maps using the K96 spectral templates and compare our classification with the K96 classification.
+Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from T12. 
+As in T12, we examine the averaged properties of the new galaxy groups and compare them with previous work.
 In Section $\S$~\ref{sec: data}, we present the data that we use to train and test our networks. 
@@
 The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
-In Section $\S$~\ref{sec: summary}, we summarize our results and discuss the future works in this subject.
+In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

### 2016-06-03 sections0.03/data0.03.tex
PB edited data section, added important comment

@@
 We use SED templates from K96 to train neural networks.
-To test the trained networks, we use SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
-Following the T12 work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare both supervised and unsupervised methods.
+To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from T12.
+Following the T12 work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.
 
@@
 
-    K96 used UV-optical spectra of 70 star forming and quiescent nearby galaxies to produce a template that contained 12 types of SEDs.
-    These templates were widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies\citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
-    K96 claims that these templates can also be used to classifying the SED of the high redshift galaxies.
+    K96 used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
+    These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies\citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
+    K96 stated that these templates can also be used to classify the SED of high-redshift galaxies.
 
-    The 12 types (what 12 types?
-the SEDs?
-in that case this sentence does not belong here at all) of spectra are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}).
+    The 12 templates are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
     The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
-    Bulge group represents galaxies similar to M31 and M81, which their UV and optical spectroscopy is dominated by the stellar population in their bulges.
+    The bulge group represents galaxies similar to M31 and M81, whose UV and optical spectra are dominated by their bulge stellar populations.
     The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
-    As it is clear in the Fig.~\ref{fig: k96}, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.
-
-    K96 spectra spans from $\sim1200$\AA~to $10000$\AA~with a resolution of $\sim 10$\AA.
-    However, in this letter we only use data between $\sim1200$\AA ~to $8000$\AA~to train our networks. 
-    This wavelength range was chosen due to availability of flux information in those wavelengths for all 12 types of galaxies.
-    In early type galaxies' spectra (B to Sb), the spectrum is redder, and strong absorption lines and 4000\AA~break are distinguishable.
-    SEDs of starburst galaxies are more flat on the optical and NIR region than those of the the early types and show strong emission lines.
+    As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.
+   In the early type (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
+    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
     For more details on each spectral type, we encourage readers to see K96 and references therein. 
+   The K96 spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
+    However, in this work we only use $\sim1200< \lambda < 8000$~\AA to train our networks; 
+    this wavelength range was chosen due to availability of flux information in those wavelengths for all 12 templates.
 
  \subsection{SED and Properties of the sample galaxies} 
-    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field.
-    For each galaxy, robust spectroscopic redshift and photometry data from the Good-MUSIC catalogue had been known.
-    The 142 galaxies were selected in T12 based on the availability of data from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC for whole galaxies. 
-    Data from these instruments were necessary in order to have a complete picture of stellar population and SFR.
-    The photometry data contain information of the galaxies in 10 - 13 filters with the wavelength range of $\sim 0.4-24~\mu$m in the observed frame.
-    T12 matched the resolution of the photometry data with K96 data and used these photometry data as inputs for Code Investigating GALaxy Enmission ({\em CIGALE} code;~\citep[][hereafter N09]{Noll09}) to generate the best fitted SED for each galaxy.% as well as some of the physical properties of the galaxies.
-
-    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
-    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
-    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
-    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$\AA, for each galaxy.
-    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of galaxies such as age, and stellar mass.
+    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field \citep{}. %PB20160603: need citation here.
+    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
+   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
+    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSYC catalogue \citep{} was available. %PB20160603: need citation here.
+   T12 matched the resolution of the photometric data with K96 data %PB20160603: I don't understand what this phrase means
+and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.% as well as some of the physical properties of the galaxies.
+% PB 20160603: commented out following 3 lines as I don't think this fit well here. Could maybe go somewhere else.    
+%    {\em CIGALE} is a valuable tool to investigate the properties of galaxies using ultraviolet to infrared wavebands.
+%    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei optical spectral templates to model the SEDs of galaxies.
+%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
+    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$~\AA, for each galaxy. %PB20160603: 10^9~AA is not a useful unit!
+    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
     Some of these properties are shown in Tab.~\ref{tab: props}.
-    In the Sec.~\ref{sec: 1D}, we study these properties for each categorization.
-    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.
+    In Sec.~\ref{sec: 1D}, we study these properties for each category.
+    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in N09 and T12.
 
@@
     For testing the created networks, we use SEDs that were produced by T12. 
-    These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths.
-    Since we have used the T12 SEDs to test the trained network, we only used the part of the SEDs that have a same wavelength range as K96 templates.
+    These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths. %PB20160603: available where?
+    Since we have used the T12 SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the K96 templates.
+
+%PB20160603: I'm an idiot for not figuring this out sooner, but I think I finally understand what exactly you are doing.
+For each galaxy the photometric data are fitted with Maraston models by CIGALE, and the best-fit SED is determined.
+Those SEDs (and not the observed photometric or spectroscopic data) are what's being classified by the SOM in comparison to the K96 templates.
+% I think we need a clearer justification of why it's a good idea to do it this way - why use the CIGALE-output SEDs rather than the observed data?
+Is it just that we need the continuous wavelnegth overage, or uniform spectral resolution, that the CIGALE-output provides?
+Are we sure that we are learning something about the galaxies rather than about CIGALE?
 

### 2016-06-04 sections0.03/results0.03.tex
PB edited section 4.1.1

@@
 
-    In order to find sufficient size for the trained networks, we create maps with sizes ranging from $1\times2$ to $50\times50$.
-    Varying grid size of the maps helps us to monitor whether grouping galaxies in smaller maps is because of their similarities in their SEDs or not having enough space to be separated.
-%(this sentence is definitely wrong and I don't understand what you are trying to say to fix it.).
-    Based on size the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
+    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
+    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
+   Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
     For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.
@@
 
-    We start our analysis by creating 1D SOMs. 
+    We started our analysis by creating 1D SOMs. 
     First, we created SOMs with only two neurons ($1\times2$ map), and then we increase the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
-    We generate 2D networks (Sec.~\ref{sec: 2D}), and once again we start with the smallest number of neuron possible (4 neurons in $2\times2$ map), and then increase them to 144 in a $12\times12$ map.
+    We generate 2D networks (Sec.~\ref{sec: 2D}), and once again we start with the smallest number of neurons possible (4 neurons in $2\times2$ map), and then increase them to 144 in a $12\times12$ map.
+    For each generated network, we compare the results with K96 categorization.
+    We also use these networks to classify the T12 galaxy sample, and compare this classification with that from the supervised networks in T12.
 
-    For each generated network, we compare the results with K96 categorization.
-    We also use these networks to classify the T12 galaxy samples, and compare them with classifications from supervised networks in T12.
-    \subsection{1D SOMs}
+    \subsection{One-dimensional self-organized maps}
     \label{sec: 1D}
-        \subsubsection{TRAINING THE NETWORKS}
+        \subsubsection{TRAINING THE NETWORKS} %PB note: I've changed 'galaxy' to 'template' pretty much everywhere.
         \label{sec: 1Dt}
-            To start our clustering, we assume that galaxies can be divided into only two general types; quiescent and starburst.
-            In this case, we generate a network with only two neurons.
-            We increased the size of the map gradually until the 12 input sample galaxies divide into the 12 neurons.
+            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
+            This corresponds to a network with only two neurons.
+            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.
 
-            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of the training networks.
-            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances, $D_j$.
-            As it was mentioned in the Sec.~\ref{sec: method}, increase in the darkness of colours between neurons represents the the increase in relative distance between the neurons.
-            The lower parts of figurs show the number galaxies from K96 template that are placed in each neuron. 
+            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
+            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
+            As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
+            The lower panels of the figures show the number of K96 templates that are placed in each neuron. 
             \begin{figure}
@@
                 \caption{Results of training network in $1\times2$~grid.
-Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map.
-In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are starbursts.
-Because of their high emission lines, Sc galaxies moved towards the starburst ones.}
+As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map.
+In this network, 5 of the templates from K96 are categorized as quiescent galaxies and the rest are starbursts.
+Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                  \label{fig: 1by2T}
@@
             In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.%(why do you keep reaping that?)
-            In the lower part of Fig.~\ref{fig: 1by2T}, we see that galaxies are divided into two groups of 5 and 7.
-            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
-            In this method, the Sc galaxies have been categorized as starburst galaxy due to the relatively higher amounts of disk stellar population relative to that of the bulge. 
-            According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.
+            In the lower part of Fig.~\ref{fig: 1by2T}, we see that the templates are divided into two groups of 5 and 7.
+            Although we know from K96 and T12 that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
+            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
+            According to K96, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.
 
@@
             %[suggested sentence: 
-            If the galaxies in Fig.~\ref{fig: 1by2T} were truly belong in two groups, they would be grouped into two groups yet again, even when we try to cluster them into three. 
-            However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
-            These two galaxies, which are separated from group of starburst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
+            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
+            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
+            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
             In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
-            The black colour indicates that the left neuron is completely different from the other two groups.
-            While the white colour shows the two right neurons are very similar to one another.
+            The black colour indicates that the left neuron is completely different from the other two groups,
+            while the white colour shows that the two right neurons are very similar to one another.
 
-            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst galaxies are divided into two groups. 
-            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are starburst galaxies and have strong emission lines.
-            On the other hand, SB5 and SB6 types have the highest internal extinctions; this causes the SED to become more flat at shorter wavelength regions. 
-            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies rather than other starbursts.
-            Therefore, in the networks, SB5 and SB6 types intend to be grouped close to the early type galaxies.
+            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
+            Based on the colours between these two groups, we conclude that they are very similar; both groups are starbursting and have strong emission lines.
+            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the SED to become flatter at shorter wavelengths. 
+            The flatter UV SED makes these two templates more similar to quiescent galaxies than to other starbursts.
+            Therefore, in the networks, SB5 and SB6 types are to be grouped close to the early type galaxy templates.
 
@@
                 \end{subfigure}
-                \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid.
-In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as starbursts.
-However, this time 2 of galaxies (SB5, and SB6) are separated starbursts groups.}
+                \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid.
+In this network again, 5 of the K96 templates are categorized as quiescent and 7 as starbursts.
+However, this time 2  templates (SB5 and SB6) are separated from the starburst groups.}
                  \label{fig: 1by3T}
@@
 
-            We increase the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
-            Since there are more nodes in higher grid SOMs, the program%(program? definitely use something else; like the algorithm?) 
-            pays more attention to small differences between each group.
-            Increasing the size of maps means that even the smallest differences between galaxies have to be considered.
-            If the galaxies from K96 have completely distinct SEDs, then a $1\times12$ sized SOM is expected to show 12 different groups each containing a single galaxy.
-            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two galaxies and three of them are empty.
-            It is evident that there were no galaxy in K96 sample that can fill those empty neurons.
-            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types B and E, SB3 and SB4, and SB1 and SB2 are the ones groups together. 
+            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
+            Since there are more nodes in higher grid SOMs, the  algorithm %program%(program? definitely use something else; like the algorithm?)  - algorithm is better - PB.
+            pays more attention to small differences between groups.
+ %           Increasing the size of maps means that even the smallest differences between galaxies have to be considered.
+            If the templates from K96 had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
+            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
+            It is evident that there was no template in the K96 sample that can fill those empty neurons.
+            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
             The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
-            The SB1 and SB2 galaxies, however, remain in the same neuron until the size of map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
-            The separation between galaxies B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
+            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
+            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
         \begin{figure*}

### 2016-06-04 sections0.03/results0.03.tex
PB finished editing section 4.1.1

@@
 
-            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups. 
-            5 groups in the left side neurons were separated from 7 groups in the right side of the map with two dark-grey colours between them.
-            This shows that even though the galaxies are clustered in twelve groups, there still remains only two main distinct groups.
-            The closest occupied neurons in the starburst side of the SOM, belongs to the SB6 type. 
-            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other starburst types.
+            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups:
+            5 groups in the left-side neurons are separated from 7 groups on the right side of the map with two dark-grey colours between them.
+            This shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
+            The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
+            This template has the most extinction and its SED has more similarity to early type galaxies than other starburst types.
 
-            The fact that the galaxies needs to have at least 22 different neurons to be divided into 12 groups, shows that the differences between SB1 and SB2, and B and E galaxies are very small.
-            Because of their similarities, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.
+            The fact that the templates need to have at least 22 different neurons to be divided into 12 groups shows that the differences between SB1 and SB2, and B and E, templates are very small.
+            Because of their similarities, they tend to stay in the same group until the network becomes big enough to make attention to the smallest particularity.
 

### 2016-06-04 sections0.03/results0.03.tex
PB finished editing sections 4.0 and 4.1.2

@@
 
-    In this section we show the results of the neural networks that are trained using K96 data.
-    Training with K96 templates results in networks that have regions with known morphological types. 
+    In this section we show the results of the neural networks trained using the K96 template spectra.
+    Training with K96 templates results in networks that have regions corresponding to galaxies of known morphological type. 
     The trained networks can then be used to categorize other galaxies.
@@
     We started our analysis by creating 1D SOMs. 
-    First, we created SOMs with only two neurons ($1\times2$ map), and then we increase the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
-    We generate 2D networks (Sec.~\ref{sec: 2D}), and once again we start with the smallest number of neurons possible (4 neurons in $2\times2$ map), and then increase them to 144 in a $12\times12$ map.
-    For each generated network, we compare the results with K96 categorization.
+    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
+    We generate 2D networks (Sec.~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
+    For each generated network, we compare the results with the K96 categorization.
     We also use these networks to classify the T12 galaxy sample, and compare this classification with that from the supervised networks in T12.
@@
 
-        \subsubsection{CLASSIFYING SAMPLE OF GALAXIES}
+        \subsubsection{Classifying the galaxy sample}
          \label{sec: 1Dv}
-            Once the networks are trained, as discussed in Sec.~\ref{sec: 1Dt}, we used them to classifying a sample 142 galaxies from T12.
-            Upper plot in Fig.~\ref{fig: 1by2V} shows the result of this classification of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
-            It shows that 80 of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
-            The lower plot shows the average SED of the galaxies in each node. 
-            The left plot shows the average SED of 80 galaxies that were classified as an early type galaxy. 
-            These galaxies are similar to the ones in the left node in the upper plot in Fig.~\ref{fig: 1by2T}.
-            The plots clearly show the 4000\AA~break in the SEDs, which is one of the signatures of early type galaxies.
-            The strong emission lines in the figure could be from galaxies with similar SED to Sa galaxies, but with stronger emission lines.
-            The right plot in the lower part of Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are indications of high SFR in the galaxies. 
+            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from T12.
+            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
+            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
+            %The lower panels show the average SED of the galaxies in each node. 
+            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
+            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
+            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
+            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
+            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
             \begin{figure}
@@
                 \end{subfigure}
-                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in Fig.~\ref{fig: 1by2T}.
-Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group.
-In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the starburst galaxies.
-Down: Average SED of the SEDs of the galaxies in each group.
-The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the starburst ones).}
+                \caption{Classification of fitted galaxy SEDs from T12 using the $1\times2$~networks trained from the K96 templates (Fig.~\ref{fig: 1by2T}).
+Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
+In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies.
+Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
 
-            Since in this network galaxies were forced to be divided into a maximum of two groups, what predominantly decides which group the galaxy belongs to is the strongest feature in its SED.
-            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as starbursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
+            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's SED predominantly decides which group the galaxy belongs to.
+            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as early type.
             Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.
 
-            Fig.~\ref{fig: 1by3V} presents the result of classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
-            In the upper plot of this figure we see that 66 of the galaxies belong to the early type group, and 47 belong to starburst galaxies. 
-            29 of the galaxies, however, are similar to starbursts in some, but not all, of their features. 
-            These groups of galaxies have strong emission lines and high flux in shorter wavelengths, but they also have a strong 4000\AA~break, which makes them cluster closer to the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).
+            Fig.~\ref{fig: 1by3V} presents the result of classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to the early type group, and 47 belong to the starburst group.
+            However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
+            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the early type galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
 
@@
                 \end{subfigure}
-                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
+                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                 \label{fig: 1by3V}
@@
             In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
-            As mentioned in the Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the K96 galaxies into 12 different neurons.
-            Same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belong in each neuron in the $1\times22$ SOM.
+            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the K96 galaxies into 12 different neurons.
+           As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
             \begin{figure*}
@@
                 \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
-In the average SED of each neuron, we can clearly see the changes from early type galaxies in the starburst ones.
-4000\AA~ break reduces from left to right and emission lines increase.}
+In the average SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones.
+The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
                 \label{fig: 1by22V}
             \end{figure*}
-            The lower plot of the figure presents the average SED of the galaxies in each neuron.
-            However, since galaxies had more space to separate, some of the neurons are left empty.
-            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, we only have 12.
+            The lower panels present the average SED of the galaxies in each neuron.
+            Since galaxies had more space to separate, some of the neurons are left empty.
+            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.
 
-            By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
-            If a cluster from T12 galaxies fills the same neurons as the K96 galaxies ones, we can conclude that SEDs of galaxies in the cluster are very similar to those of the K96 galaxies.
-            Otherwise, we can conclude that SEDs of galaxies in the cluster are similar to two of those in K96 sample.
-            For the later case, the colours establish that galaxies are more similar to which ones in the K96 sample.
+            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
+            If a cluster from the T12 sample fills the same neuron as a K96 template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
+            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the K96 templates.
+            For the latter case, the colours establish which template has greater similarity to the T12 cluster.
 
-            It can be seen that the first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
-            We therefore conclude that there are no galaxies with specifications similar to that of the type B or E in the T12 sample.
-            There are 3 galaxies in the third neuron, which shows these 3 galaxies are similar to the S0 type. 
-            18 of the galaxies are on the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
+            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
+            We therefore conclude that there are no galaxies in the T12 sample with SEDs similar to that of type B or E.
+            There are 3 galaxies in the third neuron, similar to the S0 type. 
+            18 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
             There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
             The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
-            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which shows that these two are very different.
-            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
-            The far right neurons in the network belongs to galaxies with SED comparable to type SB1 and SB2.
+            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
+            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 14 galaxies in the ninth neuron are similar to the SB6 galaxies.
+            The far right neurons in the network belong to galaxies with SED comparable to types SB1 and SB2.
 
-            In general, 56 galaxies correspond exactly to K96 types and the other 86 are placed between the initial 12 suggestions.
-            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model was constructed from co-adding 12 spectra of the 70 galaxies.
+            In general, 56 galaxies correspond exactly to K96 templates and the other 86 are placed between the initial 12 suggestions.
+            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model was constructed from co-adding spectra of 70 galaxies.
             In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.
 
-            On the other hand, the other methods e.g. $\chi^2$ fitting, trained neural network of fitting SEDs are limited to models, and the results are always reported with uncertainties.
+            %PB20160604: is this paragraph really necessary?
+            With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of SEDs is limited to models and the results are always reported with uncertainties.
             However, with SOM, we have the freedom to categorize galaxies in intermediate groups.

### 2016-06-04 sections0.03/results0.03.tex
PB finished editing section 4.1.3

@@
 
-        \subsubsection{RESULTS PROPERTIES OF CLUSTERED GALAXIES}
+        \subsubsection{PROPERTIES OF CLUSTERED GALAXIES}
 
-        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~is correct, in this section we test the relations between properties of the galaxies in each neuron.
+        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
 
@@
             \includegraphics[width=0.5\textwidth]{images0.01/1d/props5.png}
-            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$ (balck circles), $1\times4$ (blue diamond), and $1\times8$ (red triangles) networks.}
+            \caption{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
             \label{fig: props}
@@
 
-        Fig.~\ref{fig: props} shows the results of the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in $1\times2$, $1\times4$, and $1\times8$ networks.
-        In all plots, the horizontal axis is the number of the neurons divided by the size of the network, and vertical axis is one of the aforementioned properties.
+        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
+        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.%, and vertical axis is one of the aforementioned properties.
+%        
+        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
+       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
+        %Considering the results from Fig.~\ref{fig: props}, we can clearly see that s
+Separating galaxies based on SED types also leads to a separation in properties that derived (via {\sc CIGALE}) from the SEDs, as expected since the SED types are also based on {\sc CIGALE} fitting.
 
-        As shown in Fig.~\ref{fig: props}, in all three lines, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst ones. 
-       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
-        Considering the results from Fig.~\ref{fig: props}, we can clearly see that separating galaxies based on SED types also leads to a separation in properties that derived (via {\em CIGALE}) from the SEDs.
-
-        N09 used various models to derive the properties galaxies.
-        Through these models, some of the properties are already known to be correlated with each others, e.g., stellar mass and star formation rate.
-        They also studied other relations between properties that didn't have any direct correlation in the models in a sample of SINGS galaxies.
-%%eHMM I will change the previous sentence!
-It doesn't read well
-        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlate with high SFR.
+%PB20160604: this paragraph needs a topic sentence.
+        N09 used various models to derive the properties of galaxies.
+        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
+        They also studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies. %%eHMM I will change the previous sentence! It doesn't read well
+        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
         They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
-        Since in {\em CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar-mass-related correlation must be astrophysically meaningful. 
+        Since in the {\sc CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar-mass-related correlation must be astrophysically meaningful. 
         They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
@@
         \end{subfigure}
-        \caption{From up to down: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
+        \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
 Points show the mean values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the mean values.
@@
 
-        In order to compare our classifications with previous works, we produced similar plots to the ones in both N09 and T12 (Fig.~\ref{fig: props_vs_props}).
-        In Fig.~\ref{fig: props_vs_props}, data points are mean values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
-        The colours show the galaxy types, where B type galaxies are shown with red and SB1 ones are shown with blue colours.
+        In order to compare our classifications with previous work, we produced similar plots to the ones in both N09 and T12 (Fig.~\ref{fig: props_vs_props}).
+        In Fig.~\ref{fig: props_vs_props}, the data points are mean values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
+% PB20160604: why mean here but median in previous plot?
+        The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
         The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
-        Since in this method we allow galaxies to occupy classes in between the original 12 types of the galaxies, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
-        Galaxies with SEDs more similar to type Sc having bright purple colour, but, as expected from the shape of the SED, they are old galaxies with high sSFR.
-        Therefore, in all three plots of Fig.~\ref{fig: props_vs_props}, there is a purple point in the middle of the blue points.
+        Since in this method we allow galaxies to occupy classes in between the original K96 templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
+        The purple point in the middle of the blue points in  Fig.~\ref{fig: props_vs_props} corresponds to galaxies with SEDs similar to type Sc: the shape of their SED indicates that they are old galaxies with high sSFR.
 
-        The upper plots in Fig.~\ref{fig: props_vs_props} show the same relations as N09 and T12, but with tighter correlation than those two, in all three plots.
+        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as N09 and T12, but with tighter correlation than those two, in all three plots.
         As mentioned in both N09 and T12, galaxies with smaller mass tend to be younger and more active.
-        In Fig.~\ref{fig: props}, we see the same results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
-        It is clearly noticeable that from older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
+        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
+        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
         %for more details discussion on these correlations, we encourage readers to read N09 and T12.
 
-        N09 studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependency to the specific star formation, and age.
-        In contrast to N09, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, which are shown in lower plots in Fig.~\ref{fig: props_vs_props}.
-        The general trend of the correlation that we see between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend that have been found by \cite{Dale07}.
-        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measurement of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
-        They found that for early type galaxies L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and in case of spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
-        It should be noted that, by early type galaxies they mostly meant E and S0 and S0/a types of galaxies.
-        Since in our sample we do not have E type galaxies, we cannot show confidently that we see the same correlation between A$_{\rm {FUV}}$ and sSFR in early type galaxies. 
-        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing the sSFR in the S0 and Sa types.
-        The correlation in the other types of galaxies is very similar to the one that had been shown in \cite{Dale07}.
-        Both \cite{Dale07} and N09 have argued that these apparent trends can be a result of the dependence of star formation history to L$_{IR}$/L$_{FUV}$.
-        Whether these dependency is real or not, in this paper we showed that using SOM we can separate SEDs of galaxies on the way that the characteristic of each of these groups are in agreement with the general picture of the galaxy evolution.
+        N09 studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
+        In contrast to N09, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
+        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
+        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
+        They found that for early type galaxies (E, S0 and S0/a ), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
+       Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
+        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
+        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
+        Both \cite{Dale07} and N09 argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
+        Whether this dependence is real or not, our results here show that using self-organizing maps can separate SEDs of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
 

### 2016-06-04 sections0.03/results0.03.tex
PB finished editing section 4.2

@@
 
-    \subsection{One-dimensional self-organized maps}
+    \subsection{One-dimensional self-organizing maps}
     \label{sec: 1D}
@@
 
-    \subsection{2D SOMs}
+    \subsection{Two-dimensional self-organizing maps}
     \label{sec: 2D}
-    The 1D networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies in each category.
+    The one-dimensional networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies with category.
     However, each neuron in these networks is limited to be connected to one other neuron in each direction.
-    In 2D network, each neuron can have more than two immediate neighbours, therefore, they provide more complete pictures of relations between each SED type.
-    As described in the Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
+    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each SED type.
+    As described in Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
     This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
-    At first, as we had in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
+    At first, as in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
     In this case, we can categorize SEDs of other galaxies based on those 12 types.
+   In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
+    This approach can be used to trace and recognize the outliers.
+    To execute the second approach, we used the {\tiny selforgmap} library in {\tiny MATLAB}.
+    Using the {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
+%    The latter case, can be used to identify outliers.
 
-    In the second approach, we trained networks with an assumption of there might be some completely different types of galaxies that we never encountered before.
-    This approach can be used to trace and recognize the outliers.
-    To be able to execute the second approach, we used {\tiny selforgmap} library in {\tiny MATLAB}.
-    Using {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together.
-    The latter case, can be used to identify outliers.
-
-    For getting the best result from both of these ways, we should have SOMs with ``high enough"  neurons to give any new sets of galaxies a chance to find their place in the map.
-    The  ``high enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information you need from the SOMs.
+    To get the best result from both methods, we should have SOMs with ``enough"  neurons to give any new types of galaxies a chance to find their places in the map.
+    ``Enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
 %PB160427: this is a feature of clustering methods in general.
 Maybe in the methods section where you talk about the size of maps, you could give some examples of what "what kind of information" might mean.
-    Since the training data (K96 ones) have 12 galaxies, we assumed a SOM with size of $8\times8$~would be a good start.
+    Since the training dataset (the K96 templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
     We then increased the size of the SOM to find the highest size suitable for the training sample.
-    We noticed that SOMs with size of $12\times12$~are the maximum possible choice.
-    That is increasing from $12\times12$~neurons, would not change the SOMs by much.
+    We noticed that very few changes occurred after the SOMs were grown to a size greater than $12\times12$, so we used this as the maximum size.
 
@@
         \caption{$12\times12$~2D SOM results.
-Up: Trained SOMs using K96.
-For training 2D SOMs two different approaches were considered; Either only 12 types of galaxies are existed (left) or not (right).
-Down: classifying the galaxies from T12, using the trained networks above them.
-From the right side one, we can see that there is no outlier in the galaxies from T12, and we can use the left side map as a final clustering results for the T12 galaxies.}
+Upper pabel: SOMs trained using the K96 templates.
+For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right).
+Lower panel: classifying the galaxies from T12, using the trained networks shown in the upper panels.
+From the lower right panel, we can see that there are no outliers in the galaxies from T12, and we can use the map in the lower left panel as a final clustering result for the T12 galaxies.}
         \label{fig: 12by12}
@@
 
-    The upper left part of Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
-    Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
-    Using this network to categorize any set of SEDs forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
-    However, all K96 galaxies are in a small side in the upper right map in Fig.~\ref{fig: 12by12}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even if it is way far away from the K96 templates.
+    The upper left panel in Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
+    Since we considered that SEDs of all galaxies can be categorized using the K96 templates, the galaxies were placed all over the map.
+    Using this network to categorize any set of SEDs forced the SEDs to be either in the same neurons as the K96 templates or in the neurons between them.
+    In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the K96 templates are in a small region.
+This provides enough freedom for the SEDs of galaxies to be placed everywhere in the map, even far away from the templates.
 
     In the upper left part of the map in Fig.~\ref{fig: 12by12}, although galaxies have more ways to be separated, they were separated in two main groups.
-    There is a distinguishable strip of the grey, dark grey and in some cases black colour in the map.
-    This strip is separating early type galaxies with starburst ones.
+    There is a distinguishable strip of grey, dark grey and in some cases black colour in the map:
+    this strip separates early type galaxies from starburst ones.
     The lower map shows that 5 of the neurons on the left side of the strip are full. 
-    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies).
-    The only difference is that here, in this map they have more space to be separated from each other.
-    When we use this network to categorize the SED of galaxies, any galaxy places on the left hand side of the strip is an early type galaxy and any one placed on the right side of the strip is a starburst one.
-    The decision about what type of early type or starburst galaxy, is based upon its relative position to each type in the SOM.
+    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies),
+    the only difference being that in this map they have more space to be separated from each other.
+    When we use this network to categorize the SED of galaxies, any galaxy placed on the left hand side of the strip is an early type galaxy and any one placed on the right side of the strip is a starburst one.
+    The decision about what sub-type of early type or starburst galaxy is based upon its relative position to each type in the SOM.
 
-    Same as ther other map, in the upper right map in Fig.~\ref{fig: 12by12}, galaxies generally are divided into two main groups.
-    The border between the early type galaxies and the starburst ones is black strips in the middle of the upper map, which end up with bright grey colour at the bottom of the map in the fifth neuron.
+    As in the other map, in the upper right panel of Fig.~\ref{fig: 12by12}, galaxies are generally divided into two main groups.
+    The border between the early type galaxies and the starburst ones is the black strips in the middle of the map,  ending with the bright grey colour at the bottom of the map in the fifth neuron.
     In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
-    When categorizing a new set of SEDs, if the new SEDs are similar to K96 sample all of them will be placed in the bottom of the map, but if there are different type of the galaxies, they would sit in any other neurons in the map.
-    In large datasets, one can easily used this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets or not. 
-    Since the networks are already available, this procedure should be really fast and easy for big datasets.
+    When categorizing a new set of SEDs, if the new SEDs are similar to the K96 template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
+    In large datasets, one can easily use this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets. 
+    Since the networks are already available, this procedure should be quick and easy for big datasets.
 
-    We use both 2D networks to categorize the T12 galaxies and the results are shown in lower maps in Fig.~\ref{fig: 12by12}.
-    Since in the lower right map in Fig.~\ref{fig: 12by12} all galaxies are placed in the bottom part of the map, we can conclude that there are no outliers or very different type of the SEDs from K96 templates in T12 samples.
-    The lower left map of Fig.~\ref{fig: 12by12} represents the T12 galaxies categorization based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
+    We used both 2D networks to categorize the T12 galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
+    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the T12 sample there are no outliers or SEDs very different from  the K96 templates.
+    The lower left map of Fig.~\ref{fig: 12by12} shows the T12 galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
     Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see that only 23 galaxies correspond exactly to K96 types.
-    Using 2D maps, we categorized galaxies in more intermediate type than 1D ones.
-    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the early type side of the SOM, which was predictable from the results in the Sec.\ref{sec: 1Dv}.
-    Note that, from this sample we do not conclude that there are more early type galaxies in higher red-shifts.
-    We simply indicate that in this sample, we have more early type galaxies, and the reason is the selection effect from the fact that those galaxies had more reliable redshift estimation.
+    Using 2D maps results in categorizing galaxies into more intermediate type than in 1D maps.
+    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the early type side of the SOM, which was predictable from the results in Sec.\ref{sec: 1Dv}.
+This does not imply that in general there are more early type galaxies at higher red-shifts but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.
 
-    Although for the fluency of the paper, we first talked about 1D networks and continued to 2D networks we suggest, in case of using the SOMs to categorize the SED of the galaxies or to explore any related data, the first step to be checking the data using networks similar to the upper left map in Fig.~\ref{fig: 12by12}.
-    In this case, all the outliers or specific cases would be identified and removed from the sample.
+    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy SED classification should use 2D networks first.
+These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
+%    In this case, all the outliers or specific cases would be identified and removed from the sample.
 

### 2016-06-06 main.tex
comment: SED or spectrum? Unsure.
changed K96, T12, N09 to use \citealias
Updates from ShareLaTeX

@@
 \defcitealias{Kinney96}{K96}
+\defcitealias{Noll09}{N09}
 
-\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
-\author{rahmani.sahar }
+\title[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
 \date{\today}
-\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
+\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,3}$\thanks{E-mail:
 srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1,3}$\\
@@
 \begin{abstract}%% (Must be 250 Words)
+%PB20160603: are we really classifying SEDs or spectra? Need to think about this.
 The spectral energy distribution (SED) of a galaxy contains information about its physical properties.
@@
 
-\import{sections0.03/}{intro0.03.tex}
+\import{sections0.04/}{intro0.04.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.03/}{data0.03.tex}
+\import{sections0.04/}{data0.04.tex}
 
@@
 
-\import{sections0.03/}{method0.03.tex}
+\import{sections0.04/}{method0.04.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.03/}{results0.03.tex}
+\import{sections0.04/}{results0.04.tex}
 %----------------------------------------------------------------------------------------

### 2016-06-06 sections0.04/data0.04.tex
Updates from ShareLaTeX

--- 2016-06-03 sections0.03/data0.03.tex
@@
 \label{sec: data}
-We use SED templates from K96 to train neural networks.
-To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from T12.
-Following the T12 work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.
+We use SED templates from \citealias{Kinney96} to train neural networks.
+To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from \citealias{Hossein12}.
+Following the \citealias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.
 
@@
         \includegraphics[width=0.5\textwidth]{images/k96.jpg}
-        \caption{K96 spectra template for 12 types of galaxies from T12 paper (Fig.
-1 in T12).
+        \caption{\citealias{Kinney96} spectra template for 12 types of galaxies from \citealias{Hossein12} paper (Fig.
+1 in \citealias{Hossein12}).
 The type of each template is shown in each frame.
@@
 
-    K96 used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
+    \citealias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
     These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies\citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
-    K96 stated that these templates can also be used to classify the SED of high-redshift galaxies.
+    \citealias{Kinney96} stated that these templates can also be used to classify the SED of high-redshift galaxies.
 
@@
     SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
-    For more details on each spectral type, we encourage readers to see K96 and references therein. 
-   The K96 spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
+    For more details on each spectral type, we encourage readers to see \citealias{Kinney96} and references therein. 
+   The \citealias{Kinney96} spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
     However, in this work we only use $\sim1200< \lambda < 8000$~\AA to train our networks; 
@@
  \subsection{SED and Properties of the sample galaxies} 
-    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field \citep{}. %PB20160603: need citation here.
+    \citealias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field \citep{}. %PB20160603: need citation here.
     The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
@@
     For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSYC catalogue \citep{} was available. %PB20160603: need citation here.
-   T12 matched the resolution of the photometric data with K96 data %PB20160603: I don't understand what this phrase means
+   \citealias{Hossein12} matched the resolution of the photometric data with \citealias{Kinney96} data %PB20160603: I don't understand what this phrase means
 and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.% as well as some of the physical properties of the galaxies.
@@
 %    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei optical spectral templates to model the SEDs of galaxies.
-%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
-    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$~\AA, for each galaxy. %PB20160603: 10^9~AA is not a useful unit!
+%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by \citealias{Noll09}.
+    \citealias{Hossein12} produced the best SED match, with wavelength interval of 910 to $\sim 8\times10^9$~\AA, for each galaxy. %PB20160603: 10^9~AA is not a useful unit!
     Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
@@
     In Sec.~\ref{sec: 1D}, we study these properties for each category.
-    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in N09 and T12.
+    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citealias{Noll09} and \citealias{Hossein12}.
 
     \begin{table}
-\caption[]{Description of the properties of T12 galaxies; the output result of {\em CIGALE}}     
+\caption[]{Description of the properties of \citealias{Hossein12} galaxies; the output result of {\em CIGALE}}     
 \label{tab: props}
@@
 
-    For testing the created networks, we use SEDs that were produced by T12. 
+    For testing the created networks, we use SEDs that were produced by \citealias{Hossein12}. 
     These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths. %PB20160603: available where?
-    Since we have used the T12 SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the K96 templates.
+    Since we have used the \citealias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citealias{Kinney96} templates.
 
@@
 For each galaxy the photometric data are fitted with Maraston models by CIGALE, and the best-fit SED is determined.
-Those SEDs (and not the observed photometric or spectroscopic data) are what's being classified by the SOM in comparison to the K96 templates.
+Those SEDs (and not the observed photometric or spectroscopic data) are what's being classified by the SOM in comparison to the \citealias{Kinney96} templates.
 % I think we need a clearer justification of why it's a good idea to do it this way - why use the CIGALE-output SEDs rather than the observed data?
@@
 %  Same wavelengths for every object? Yes
-%  What is the spectral resolution? It depends on the type of spectra we use in T12 see
+%  What is the spectral resolution? It depends on the type of spectra we use in \citealias{Hossein12} see
 % below for more information.
 %  Do the spectra include the whole galaxy or just the central part? For observed 142
-% galaxies: whole spectra because they are in high redshift. For K96 they are co-added
+% galaxies: whole spectra because they are in high redshift. For \citealias{Kinney96} they are co-added
 % spectra from different parts.
-%  Does the resolution match with K96? We match them to K96, see below.
+%  Does the resolution match with \citealias{Kinney96}? We match them to \citealias{Kinney96}, see below.
 %  What is the coverage of spectra? See below.
@@
 %   photometry?" All 142 galaxies have robust spectroscopic redshift.
-% For more clarification about spectra used in T12: We have three sets of spectra.
+% For more clarification about spectra used in \citealias{Hossein12}: We have three sets of spectra.
 % 1 – observed spectroscopic spectra.
-They are used just for extra independent validation; see figure 17 from T12.
+They are used just for extra independent validation; see figure 17 from \citealias{Hossein12}.
 This validation is nothing to do with network validations.
@@
 We use only range [3500-5100] because all the 142 observed spectra have information in this interval (some of them have no spectral information in 8000A, for example).
-In T12 you can also find this that can help: “The rest-frame spectra of the sample all include spectral information
+In \citealias{Hossein12} you can also find this that can help: “The rest-frame spectra of the sample all include spectral information
 % ∼3500–5100 Å. This interval brackets the important features such as the 4000Å break and also the strong emission
@@
 We use only interval 1200-7500A.
-because all the 12 K96 spectra have information in
+because all the 12 \citealias{Kinney96} spectra have information in
 % this interval (some of the spectra have no information in 9000A, for example).
@@
 The best resolution is related to the optical part (3-5A and we convert all to 10A i.e., to resolution of K69).
-We cut the best 142 spectra in interval [1200-7500] like K96 for ANN validation or test.
-(If we had spectral information for all K96 spectra in the interval 1200-10000A, for example, then we would cut all 142 SEDs in 1200- 10000A).
-So if you find a new training set (other than K96 which we talked about that in our skype chat) and if they had information in 1000-15000A, for example, then we would cut the SEDs in this new interval for validation.
-% As a summary: as you know (better than me!) we use K96 as training set and 142 SEDs as validation (or test) set.
+We cut the best 142 spectra in interval [1200-7500] like \citealias{Kinney96} for ANN validation or test.
+(If we had spectral information for all \citealias{Kinney96} spectra in the interval 1200-10000A, for example, then we would cut all 142 SEDs in 1200- 10000A).
+So if you find a new training set (other than \citealias{Kinney96} which we talked about that in our skype chat) and if they had information in 1000-15000A, for example, then we would cut the SEDs in this new interval for validation.
+% As a summary: as you know (better than me!) we use \citealias{Kinney96} as training set and 142 SEDs as validation (or test) set.
 When we obtain the class of each 142 galaxies (in fact 105 galaxies!
-You are improving this number to 142 in your paper) then we use 105 observed spectra to make figure 17 from T12.
-The co-added observed spectra in a certain class match with the associated K96 spectra in the same class (i.e., an independent validation).
+You are improving this number to 142 in your paper) then we use 105 observed spectra to make figure 17 from \citealias{Hossein12}.
+The co-added observed spectra in a certain class match with the associated \citealias{Kinney96} spectra in the same class (i.e., an independent validation).

### 2016-06-22 main.tex
After Sophia and Aycha's comments.

--- 2016-06-03 main.tex
@@
 \usepackage{amsmath}
-%\usepackage{hyperref}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=True,
+    linkcolor=red,
+    filecolor=magenta,      
+    urlcolor=cyan,
+    citecolor=blue,
+}
 \usepackage{graphicx}
@@
 \usepackage[flushleft]{threeparttable}
+\usepackage{pgffor}
 
@@
 
-%\defcitealias{Hossein12}{T12}
+%\defcitealias{Hossein12}{\citetalias{Hossein12}}
 
@@
 \defcitealias{Hossein12}{T12}
+\defcitealias{Kinney96}{K96}
+\defcitealias{Noll09}{N09}
 
-\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
-\author{rahmani.sahar }
+\title[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+%\author{rahmani.sahar}
 \date{\today}
 \author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
-srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1,3}$\\
+srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, P.~Barmby$^{1,2}$\\
 $^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
-$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
-$^{3}$Center for Planetary Science \& Exploration, Western University}
+$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
+$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
 \maketitle
@@
 
-\begin{abstract}%% (Must be 250 Words)
+\begin{abstract}
 The spectral energy distribution (SED) of a galaxy contains information about its physical properties.
@@
 
-%%% what is the problem we are trying to solve in general! why do we want o classify thing in general, and what is wrong in exciting classification scheme
-
 \end{abstract}
@@
 
-\import{sections0.03/}{intro0.03.tex}
+\import{sections0.05/}{intro0.05.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.03/}{data0.03.tex}
+\import{sections0.05/}{data0.05.tex}
 
@@
 
-\import{sections0.03/}{method0.03.tex}
+\import{sections0.05/}{method0.05.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.03/}{results0.03.tex}
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Discussion
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-
-%\import{sections0.0/}{diss0.0.tex}
-
+\import{sections0.05/}{results0.05.tex}
 %----------------------------------------------------------------------------------------
@@
 
-% We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
+% We used SOMs to classify SEDs of the galaxies with known morphological type from \citetalias{Kinney96}, and created networks with different usages.
 % By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
-% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
+% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from \citetalias{Kinney96} for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
 % We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.
 
-% The sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+% The sample of 142 high red-shift galaxies from \citetalias{Hossein12} was used to test the trained networks.
 % One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
@@
 % A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
-% T12  have used a supervised training method, and trained networks with K96 SED template.
+% \citetalias{Hossein12}  have used a supervised training method, and trained networks with \citetalias{Kinney96} SED template.
 % Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
 % However, they could not classify 37 out of 142 galaxies in the sample.
-% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or between those types. 
+% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by \citetalias{Kinney96} or between those types.
 % Therefore, we classified all 142 galaxies of our test sample.
@@
 
-We used SOMs to classify the template spectra of K96, made from galaxies with known morphological type, and created networks with different uses.
-By varying the size of the networks, we found the relative similarity between the K96 template classes.
+We used SOMs to classify the template spectra of \citetalias{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
+By varying the size of the networks, we found the relative similarity between the \citetalias{Kinney96} template classes.
 A one-dimensional network with 22 neurons was needed in order to
-separate all 12 K96 spectra; we concluded that K96 types B and E, and types SB1 and SB2, are very similar to each other.
+separate all 12 \citetalias{Kinney96} spectra; we concluded that \citetalias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
 We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.
 
-A sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
-%One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
-The test results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.% but not exactly the same as one of them.
+A sample of 142 high red-shift galaxies from \citetalias{Hossein12} was used to be classified by the trained networks.
+The classification results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.
 The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-T12 used a supervised training method to train networks with K96 SED templates and classify the same sample of 142 galaxy spectra;
+\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
 however, they could not classify 37 out of 142 spectra.
 The unsupervised method used in this project was able to classify  all 142 spectra in the sample
-as belonging to one of the morphological types introduced by K96 or a class in between those types.
+as belonging to one of the morphological types introduced by \citetalias{Kinney96} or a class in between those types.
 
-The properties of the galaxies in the test sample using the new
-classification were found to more tightly correlate in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies. 
+The properties of the galaxies in the \citetalias{Hossein12} sample using the new classification were found to more tightly correlate in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
 The properties of the galaxies in each group are in good agreement with their morphological types.
@@
 \section*{ACKNOWLEDGMENTS}
-S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
+S.R. and P.B. thank S. Lianou and A. Tammour for their useful comments. 
+S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\bibliographystyle{mnras}
+\bibliographystyle{apalike}
 \bibliography{ref_mining_h.bib}

### 2016-06-22 sections0.05/data0.05.tex
After Sophia and Aycha's comments.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{DATA}
\label{sec: data}
We use SED templates from \citetalias{Kinney96} to train neural networks. %To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12}.
We classify the SEDs of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12} using the trained networks, and use their physical properties to test the new classifications.
Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.
 %%%Sr220616: again we did not test anything here

 \subsection{Kinney spectral model}
     \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{images/k96.jpg}
        \caption{\citetalias{Kinney96} spectra template for 12 types of galaxies from \citetalias{Hossein12} paper (Fig. 1 in \citetalias{Hossein12}). The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies. Starburst galaxies spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic colour extinction.}
        \label{fig: k96}
    \end{figure}

    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
    These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
    \citetalias{Kinney96} stated that these templates can also be used to classify the SED of high-redshift galaxies.

    The 12 templates are divided based on their morphological types for quiescent galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    The bulge group represents galaxies similar to M31 and M81, whose UV and optical spectra are dominated by their bulge stellar populations.
    The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies. 
    In the early type (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
    For more details on each spectral type, we encourage readers to see \citetalias{Kinney96} and references therein. 
   The \citetalias{Kinney96} spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
    However, in this work we only use $\sim1200< \lambda < 8000$~\AA~to train our networks; 
    this wavelength range was chosen due to availability of flux information in those wavelengths for all 12 templates.

 \subsection{SED and Properties of the sample galaxies} 
    \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
   \citetalias{Hossein12} assumed decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr to find the best-fit SED for each galaxy. %%%Sr220616: moved the last sentence from the next paragraph to here.

    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
    They derived physical properties of the galaxies such as SFR, age and stellar mass from their fitted SEDs. %%%Sr220616: change the previues sentence to matched to the new corrections.
    Some of these properties are shown in Tab.~\ref{tab: props}.
    In Sec.~\ref{sec: 1D}, we study these properties for each category.
    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.

    \begin{table}
\caption{Description of the properties of \citetalias{Hossein12} galaxies; the output result of {\em CIGALE} using a single population (SP) model}     
\label{tab: props}
\centering
\begin{tabular}{l l l}
\hline\hline
\noalign{\smallskip}
Par. & Unit & Description\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
$f_\mathrm{burst}$ & --- & mass fraction of \\
& & young single population (SP) model \\
\noalign{\smallskip}
$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age \\
\noalign{\smallskip}
$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
SFR & M$_\odot$/yr & instantaneous SFR  \\
$A_\mathrm{FUV}$ & mag & attenuation at 1500\,\AA{} \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{table}

    %%%Sr220616: Same as the intro section we did not test any thing here.
    We classify SEDs that were produced by \citetalias{Hossein12} using the created networks.
    %For testing the created networks, we use SEDs that were produced by \citetalias{Hossein12}. 
    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength in a wide range of wavelengths.
    %Since we have used the \citetalias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} templates.  
    Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} templates.

### 2016-06-22 sections0.05/method0.05.tex
After Sophia and Aycha's comments.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{METHOD}
\label{sec: method}
 \subsection{Self Organizing Maps}
 \label{sec: som}

 The self-organizing map is a clustering method which reduces the dimension of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
 The result of an SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
 Each node may contain one or more samples from the input data.
 The distance between the nodes represents similarity or dissimilarity of the underlying samples, i.e., similar data are closer together in the array and the distance between two nodes is related to the dissimilarity of their samples.
 A weight vector ``\boldit{W}" with the same dimension as the input data is associated with each node and will be varied during the training process.
 This vector is the key factor in determining the position of the nodes in a map.
 \cite{Geach12} presented the application of the SOM and discussed its algorithm in detail.
 In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a mock model which will help interpretation of our results. %%%Sr220616: changed a test model to a mock model

 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map.  %%%Sr220616: moved paraghraph regarding to the size here!
     The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.

     We start by creating S1 $\times$ S2 empty neurons. 
     The arrangement of these neurons depends on the map's topology provided by the user. %%%Sr220616: removed initial from here, it is fixed after choosing the topology.
     In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
     The process of creating SOM happens over a series of $N$ iterations, which is set by a user. %%% SR220616: added here that N is set by a user
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration, the SOM code:
     \begin{enumerate}
        \item chooses a random vector from the dataset ($V_i$).
        \item calculates the Euclidean distance in $\in \Re^n$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$"). This neuron is the winner node and is called the Best Matching Unit (BMU). %%%Sr220616: added $\in \Re^n$ space to be more clear on that it is a distance in n-dimension space no neurons!
        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size. It then decays exponentially over each iteration as
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
     \end{enumerate}
     These steps are then repeated $N$ times.

\subsection{Creating self-organizing maps}
\label{sec: create_som}
     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
     The first phase is called the ``ordering phase" and
     starts with maximum neighbourhood distance and an initial high learning factor (usually 0.9) is provided by the user. 
     The ordering phase continues for a requested number of iterations.
     During the iterations, the learning factor decreases to the tuning phase learning factor and the neighbourhood distance reaches that of the tuning phase as well.
     Both the learning factor and the neighbourhood of the tuning phase are set by the user. 
     The amount by which these two factors change in each iteration depends on the number of iterations.

     In the second, or ``tuning'' phase,
     the neighbourhood distance is kept at the user-defined minimum.
     The learning factor, however, decreases gradually.
     The gradual change in the leaning factor helps to fine-tune the topology results, leading to a more stable SOM. 
     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase. %cite kohenen book?!
     We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.

     We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively. %%%Sr220616: moved this sentence from the result part to here!
     To present our results, we use {\sc nnt}'s built-in plotting tool.
%     This tool is designed to show the distance between each cluster more clearly.
     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
     In the maps, the purple hexagonal shapes represent the neurons. 
     The distances in a distance map are shown by the grey cycle colours:
     the darker the colour, the larger the distance between neurons.
     In the hit maps, neurons with zero hits are left empty.

\subsection{Mock sample}

         \begin{figure}
            \begin{subfigure}[b]{0.5\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/sample/sample2_dist.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{images0.01/sample/sample2_hits.png}
            \end{subfigure}
            \caption{SOM of the mock sample. In both plots, the axes show the position of the neurons. Hexagonal shapes represent the neurons. The top plot is a distance map. The grey cycle colours show the differences between the weights of each neuron with white being the minimum difference and black being the maximum one. The lower plot is a ``hits plot". It represents the number of samples in each neuron, where empty means zero hits. In this sample, the 27 galaxies are clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
            \label{fig: sample}
        \end{figure}

 To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
 The mock sample contains two assigned attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). 
 We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Section ~\ref{sec: create_som}.

 Fig. ~\ref{fig: sample} shows the SOM of this mock sample. 
 The upper panel is the distance map. 
 The axes show the position of the neurons in the $10 \times 10$ network.
 The lower panel in Fig.~\ref{fig: sample} shows the hit map.
 On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
 The number on the purple neurons shows the number of galaxies in that neuron.
 Colour coverage of neurons depends on the number of the hits on the sample.
 The neuron with the maximum number of hits is fully coloured while the empty neurons are left uncoloured (white). %%%Sr220616:changed the dark-coloured to fully coloured

Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
The upper panel in the Fig.~\ref{fig: sample} clearly shows this division.
In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
The left half of the plot is where type 1 galaxies belong, and type 2 galaxies reside in the right side.
Different shades of gray show the border between regions.
The lower panel in Fig.~\ref{fig: sample} shows that only 4 neurons (out of 100) are occupied. 
8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR.

%%%Sr220616:added a paragraph here
We can conclude that although each galaxy had the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
This network is considered a training network and can be used to cluster any new dataset with similar entries.
Some neurons were left empty in this network because they never had became a winner for data in the mock sample.
However, their weights have been updated in each iteration, and they could be a winner for data in the new dataset.%%%Sr220616: added the last two sentences to clear out a confusion about empty neurons.

As we show in the following sections, with data from real galaxies there are more than two dimensions and two galaxies never have exactly the same information. 
If the network has enough neurons, the input data points would eventually separate from each other and cluster into smaller groups. 
However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
Therefore, it is up to the users to decide the similarity or dissimilarity between the input data based on number of neurons.

### 2016-06-22 sections0.05/results0.05.tex
After Sophia and Aycha's comments.

--- 2016-06-04 sections0.03/results0.03.tex
@@
 
-    In this section we show the results of the neural networks trained using the K96 template spectra.
-    Training with K96 templates results in networks that have regions corresponding to galaxies of known morphological type. 
+    In this section we show the results of the neural networks trained using the 12 \citetalias{Kinney96} template spectra.
+    Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
     The trained networks can then be used to categorize other galaxies.
-    %In following we show how we trained data and used galaxies from T12 to show how the clustering using trained networks works.
 
@@
     Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
-    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.
-    We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.
+    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the most suitable values for our dataset, which are listed in Section~\ref{sec: create_som}.
+%%%Sr220616: changed the optimum to the most suitable values ...
+.
+moved the initial values to section 3.2
 
@@
     We generate 2D networks (Sec.~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
-    For each generated network, we compare the results with the K96 categorization.
-    We also use these networks to classify the T12 galaxy sample, and compare this classification with that from the supervised networks in T12.
+    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
+    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.
 
@@
     \label{sec: 1D}
-        \subsubsection{TRAINING THE NETWORKS} %PB note: I've changed 'galaxy' to 'template' pretty much everywhere.
+        \subsubsection{TRAINING THE NETWORKS}
         \label{sec: 1Dt}
@@
 
-            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
+            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T}~show the results of the training $1\times2$, $1\times3$, and $1\times22$ networks, respectively (The rest of the networks are shown in Appendix~\ref{app: high_Z_1d_soms}.
             As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
             As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
-            The lower panels of the figures show the number of K96 templates that are placed in each neuron. 
+            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
             \begin{figure}
@@
 As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map.
-In this network, 5 of the templates from K96 are categorized as quiescent galaxies and the rest are starbursts.
+In this network, 5 of the templates from \citetalias{Kinney96} are categorized as quiescent galaxies and the rest are starbursts.
 Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
@@
 
-            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.%(why do you keep reaping that?)
+            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.
             In the lower part of Fig.~\ref{fig: 1by2T}, we see that the templates are divided into two groups of 5 and 7.
-            Although we know from K96 and T12 that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
+            Although we know from \citetalias{Kinney96} and \citetalias{Hossein12} that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
             In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
-            According to K96, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.
+            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.
 
@@
             In these plots we force the galaxies to be categorize in a maximum 3 groups. 
-            %If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty(this sentence does not make much sense.
-I kind of think I know what you're trying to say (because once I translate this sentence to farsi word by word, it kind of comes together) but please phrase it more carefully.).
-            %[suggested sentence: 
             If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
@@
                 \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid.
-In this network again, 5 of the K96 templates are categorized as quiescent and 7 as starbursts.
+In this network again, 5 of the \citetalias{Kinney96} templates are categorized as quiescent and 7 as starbursts.
 However, this time 2  templates (SB5 and SB6) are separated from the starburst groups.}
@@
             We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
-            Since there are more nodes in higher grid SOMs, the  algorithm %program%(program? definitely use something else; like the algorithm?)  - algorithm is better - PB.
+            Since there are more nodes in higher grid SOMs, the  algorithm 
             pays more attention to small differences between groups.
- %           Increasing the size of maps means that even the smallest differences between galaxies have to be considered.
-            If the templates from K96 had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
+            If the templates from \citetalias{Kinney96} had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
             However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
-            It is evident that there was no template in the K96 sample that can fill those empty neurons.
+            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
             In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
@@
          \label{sec: 1Dv}
-            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from T12.
+            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
             The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
@@
                 \end{subfigure}
-                \caption{Classification of fitted galaxy SEDs from T12 using the $1\times2$~networks trained from the K96 templates (Fig.~\ref{fig: 1by2T}).
+                \caption{Classification of fitted galaxy SEDs from \citetalias{Hossein12} using the $1\times2$~networks trained from the \citetalias{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
@@
             In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
-            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the K96 galaxies into 12 different neurons.
+            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
            As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
@@
             Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
-            If a cluster from the T12 sample fills the same neuron as a K96 template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
-            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the K96 templates.
-            For the latter case, the colours establish which template has greater similarity to the T12 cluster.
+            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
+            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the \citetalias{Kinney96} templates.
+            For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.
 
             The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
-            We therefore conclude that there are no galaxies in the T12 sample with SEDs similar to that of type B or E.
+            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with SEDs similar to that of type B or E.
             There are 3 galaxies in the third neuron, similar to the S0 type. 
@@
 
-            In general, 56 galaxies correspond exactly to K96 templates and the other 86 are placed between the initial 12 suggestions.
-            As T12 mentioned, part of the reason we could not classify all the galaxies using the K96 model is that the model was constructed from co-adding spectra of 70 galaxies.
+            In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
+            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies.
             In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.
@@
             %PB20160604: is this paragraph really necessary?
-            With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of SEDs is limited to models and the results are always reported with uncertainties.
-            However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
-            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.
+            %%Sr: I think it clears the point of having regions in middle neurons
+            %%%%%%%Sr220616: I almost completely changed the following paragraph, but I think it makes more sense, now.
+            Other methods for finding the type of galaxies (e.g. $\chi^2$ fitting and supervised neural network) are limited to templates and the outliers are not classified.
+            However, using SOM method we categorized galaxies based on their position on trained SOMs, which can have empty neurons.
+            The empty neurons in a trained SOM show that there must be another type of template there, that is absent from the K96 template spectra.
+            Using the distance of the trained network is the best way to describe the properties of this absent template.
+            Therefore, with SOM, we have the freedom to categorize galaxies in intermediate (new) templates.
+            %%%%%%%Sr220616: in response to Sophia's comment; In SOM we do not fit the data.
+we create a network using our template.
+In the final version of network each neuron has a weight vector.
+When we give a new data to this weight vector, based on distance of the the weight vector and a new input data, the SOM finds a winner neuron.
+If this winner neurons were the same for K96 and T12 samples, we would say the input vector in these two case were similar.
+Since we know type of the galaxies in K96, we could decide about the type of the galaxies in T12.
 
@@
 
-        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
+        In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
+%%%%%%%Sr220616:changed "conclusion" to clustering!
 
@@
 
-%PB20160604: this paragraph needs a topic sentence.
-        N09 used various models to derive the properties of galaxies.
+        %Sr07062016: Is it better?
+        {\sc CIGALE} has various models to derive the properties of galaxies.
         Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
-        They also studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies. %%eHMM I will change the previous sentence! It doesn't read well
+        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
         They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
         They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
-        Since in the {\sc CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar-mass-related correlation must be astrophysically meaningful. 
+        Since in the {\sc CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
         They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
-        T12 replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than N09 results.
+        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.
 
@@
         \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
-Points show the mean values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the mean values.
+Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values.
 colours shows the type of the galaxies in the new classification.
@@
 
-        In order to compare our classifications with previous work, we produced similar plots to the ones in both N09 and T12 (Fig.~\ref{fig: props_vs_props}).
-        In Fig.~\ref{fig: props_vs_props}, the data points are mean values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
-% PB20160604: why mean here but median in previous plot?
+        In order to compare our classifications with previous works, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
+        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
         The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
         The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
-        Since in this method we allow galaxies to occupy classes in between the original K96 templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
+        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
         The purple point in the middle of the blue points in  Fig.~\ref{fig: props_vs_props} corresponds to galaxies with SEDs similar to type Sc: the shape of their SED indicates that they are old galaxies with high sSFR.
 
-        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as N09 and T12, but with tighter correlation than those two, in all three plots.
-        As mentioned in both N09 and T12, galaxies with smaller mass tend to be younger and more active.
+        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with tighter correlation than those two, in all three plots.
+        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
         Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
         From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
-        %for more details discussion on these correlations, we encourage readers to read N09 and T12.
+        %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.
 
-        N09 studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
-        In contrast to N09, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
+        \citetalias{Noll09} studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
+        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
         The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
@@
         The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
-        Both \cite{Dale07} and N09 argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
+        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
         Whether this dependence is real or not, our results here show that using self-organizing maps can separate SEDs of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
@@
     ``Enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
-%PB160427: this is a feature of clustering methods in general.
-Maybe in the methods section where you talk about the size of maps, you could give some examples of what "what kind of information" might mean.
-    Since the training dataset (the K96 templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
+    Since the training dataset (the \citetalias{Kinney96} templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
     We then increased the size of the SOM to find the highest size suitable for the training sample.
@@
         \caption{$12\times12$~2D SOM results.
-Upper pabel: SOMs trained using the K96 templates.
+Upper pabel: SOMs trained using the \citetalias{Kinney96} templates.
 For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right).
-Lower panel: classifying the galaxies from T12, using the trained networks shown in the upper panels.
-From the lower right panel, we can see that there are no outliers in the galaxies from T12, and we can use the map in the lower left panel as a final clustering result for the T12 galaxies.}
+Lower panel: classifying the galaxies from \citetalias{Hossein12}, using the trained networks shown in the upper panels.
+From the lower right panel, we can see that there are no outliers in the galaxies from \citetalias{Hossein12}, and we can use the map in the lower left panel as a final clustering result for the \citetalias{Hossein12} galaxies.}
         \label{fig: 12by12}
@@
     The upper left panel in Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
-    Since we considered that SEDs of all galaxies can be categorized using the K96 templates, the galaxies were placed all over the map.
-    Using this network to categorize any set of SEDs forced the SEDs to be either in the same neurons as the K96 templates or in the neurons between them.
-    In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the K96 templates are in a small region.
+    Since we considered that SEDs of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
+    Using this network to categorize any set of SEDs forced the SEDs to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
+    In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the \citetalias{Kinney96} templates are in a small region.
 This provides enough freedom for the SEDs of galaxies to be placed everywhere in the map, even far away from the templates.
@@
     In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
-    When categorizing a new set of SEDs, if the new SEDs are similar to the K96 template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
+    When categorizing a new set of SEDs, if the new SEDs are similar to the \citetalias{Kinney96} template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
     In large datasets, one can easily use this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets. 
@@
 
-    We used both 2D networks to categorize the T12 galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
-    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the T12 sample there are no outliers or SEDs very different from  the K96 templates.
-    The lower left map of Fig.~\ref{fig: 12by12} shows the T12 galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
-    Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see that only 23 galaxies correspond exactly to K96 types.
+    We used both 2D networks to categorize the \citetalias{Hossein12} galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
+    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or SEDs very different from  the \citetalias{Kinney96} templates.
+    The lower left map of Fig.~\ref{fig: 12by12} shows the \citetalias{Hossein12} galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
+    Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see that only 23 galaxies correspond exactly to \citetalias{Kinney96} types.
     Using 2D maps results in categorizing galaxies into more intermediate type than in 1D maps.

### 2016-06-23 sections0.05/intro0.05.tex

--- 2016-06-03 sections0.03/intro0.03.tex
@@
 %%Creating templates and NIR_UV templates
-Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using data from nearby galaxies~(e.g.\citealt{Kinney93}, \citealt{Kinney96}, hereafter K96, \citealt{Bershady00}, \citealt{Mannucci01}).
+Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using data from nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}).
 Based on their usage, these templates are restricted to certain wavelengths.
@@
 
-Advances in techniques and detectors have resulted in more detailed observations of SEDs and also made classification of galaxies more complex.
+Advances in techniques and detectors have resulted in more detailed wavelenght sampling of SEDs and also made classification of galaxies more complex.
 Since no two galaxies, even with the same morphology, have exactly the same properties, classifying SEDs of galaxies using templates is very challenging.
@@
 An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
-It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data.
-Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91,Moayed09}.
+It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16,Ellison16a, Ellison16b}.
+Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91}.
 Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.
@@
 In supervised method, a neural network would be trained using input data based on a desired outcome.
-This method is very useful for classification of data with specific target values.% (e.g. any pattern recognition with known templates).
+This method is very useful for classification of data with specific target values.
 On the other hand, in unsupervised method there is no prediction of output.
 This method classifies data based on their underlying structures and hidden patterns.
-The unsupervised method is very helpful to obtain knowledge from the data, or when the underlying structure of data is not well established.% (e.g. producing a template of SED of galaxies).
+The unsupervised method is very helpful to obtain knowledge from the data, or when the underlying structure of data is not well established.
 
@@
 The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
-From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
-%20160509PB: suggest starting a new paragraph here, with an introductory sentence about galaxy spectra.
-%SR20160512: I start new paragraph after the next sentence not here.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
 
@@
 Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
-These integrated specta combine the light of billions of individual stars and nebulae within a galaxy, and
+These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
 finding patterns and common characteristics between galaxies can be a complex task.
@@
 \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
-This package can recognize an astronomical object from artificial errors, and then classify the object based on its spectrum.
-%PB20160603: I don't know what you mean by "artificial errors"
+This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
 
-%What T12 did
-~\citet[][hereafter T12]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by K96.
+%What \citetalias{Hossein12} did
+~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
 With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
-The SED of the 37 galaxies from their samples could not be matched with any of those in the K96 templates. 
-In order to classify the remaining 37 galaxies, they combined spectrum of the K96 templates.
-%This procedure showed that, not a single type of galaxies in K96 template could describe the SED of any of those 37 galaxies. %PB20160603: repeats previous sentence
-T12 also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.
+The SED of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
+In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
+\citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.
 
 %What we did
-In this paper, we compare supervised and unsupervised methods of galaxy spectral classification directly, using exactly the same data as T12.  
+In this paper, we compare supervised and unsupervised methods of galaxy spectral classification directly, using exactly the same data as \citetalias{Hossein12}.  
 Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
-to find the best SED class for the 37 galaxies that could not be clasified by the supervised method.
-First, we train self-organizing maps using the K96 spectral templates and compare our classification with the K96 classification.
-Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from T12. 
-As in T12, we examine the averaged properties of the new galaxy groups and compare them with previous work.
-In Section $\S$~\ref{sec: data}, we present the data that we use to train and test our networks. 
+to find the best SED class for the 37 galaxies that could not be classified by the supervised method.
+First, we train self-organizing maps using the \citetalias{Kinney96} spectral templates and compare our classification with the \citetalias{Kinney96} classification.
+Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
+As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
+In Section $\S$~\ref{sec: data}, we present the data that we use to train our networks, and the ones we classified them using the trained networks.
+%%%%%%%Sr220616: change it here from to test and train networks to this new version!
+(We never tested our networks, we trained them, learned about them and used them to classifying other group of galaxies.
+I think, that's why Sophia keep asking about the testing and validating our networks)
 We describe the SOM methods in Section $\S$~\ref{sec: method}. 

### 2016-06-23 main.tex
Update main.tex
changes to title and abstract

@@
 
-\title[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\title[Classifying high-$z$ galaxy spectra]{Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}
 %\author{rahmani.sahar}
@@
 galaxy SED templates covering the wavelength range from far ultraviolet to near infrared.
-The trained networks were used to cluster the SEDs of a sample of 142 galaxies with $0.5 < z < 1$.
+The trained networks were used to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$.
 Compared to previous attempts to classify this sample, the
-self-organizing map approach was able to better classify the SEDs with
-similarities to more than one template.
+self-organizing map approach was able to better classify the SEDs which had
+similarities with more than one template.
 The averaged SEDs and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.

### 2016-06-23 sections0.05/results0.05.tex
Update results0.05.tex
small edits. No new questions.

@@
     In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
-    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
+    Varying the grid size of the maps helped us to monitor whether tighter grouping of galaxies happens due to their similar properties or a lack of map space to separate them.
     Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
@@
         \label{sec: 1Dt}
-            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
+            To start our clustering, we assumed that galaxies can be divided into only two general types: quiescent and starburst.
             This corresponds to a network with only two neurons.
@@
 
-            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T}~show the results of the training $1\times2$, $1\times3$, and $1\times22$ networks, respectively (The rest of the networks are shown in Appendix~\ref{app: high_Z_1d_soms}.
-            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
+            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T}~show the results of the training $1\times2$, $1\times3$, and $1\times22$ networks, respectively (the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
+            As in Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
             As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
@@
             Although we know from \citetalias{Kinney96} and \citetalias{Hossein12} that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
-            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
-            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.
+            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population compared to that of the bulge. 
+            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flatter SED compare to other quiescent galaxies.
 
             Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
-            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
+            In these plots we force the galaxies to be categorized in a maximum of 3 groups. 
             If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
@@
             We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
-            Since there are more nodes in higher grid SOMs, the  algorithm 
+            Since there are more nodes in larger SOMs, the  algorithm 
             pays more attention to small differences between groups.
@@
             The fact that the templates need to have at least 22 different neurons to be divided into 12 groups shows that the differences between SB1 and SB2, and B and E, templates are very small.
-            Because of their similarities, they tend to stay in the same group until the network becomes big enough to make attention to the smallest particularity.
+            Because of their similarities, they tend to stay in the same group until the network becomes big enough to make use of the smallest particularity.
 
@@
             %The lower panels show the average SED of the galaxies in each node. 
-            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
+            The lower left panel shows the average SED of the 80 galaxies that were classified as quiescent. 
             These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
-            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
+            the SEDs clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
             The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
@@
                 \end{subfigure}
-                \caption{Classification of fitted galaxy SEDs from \citetalias{Hossein12} using the $1\times2$~networks trained from the \citetalias{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
+                \caption{Classification of fitted galaxy SEDs from \citetalias{Hossein12} using the $1\times2$~network trained from the \citetalias{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
 In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies.
-Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
+Lower panel: Average SED of the galaxies in each group, quiescent on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
 
-            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's SED predominantly decides which group the galaxy belongs to.
-            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as early type.
-            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.
+            Since in this network galaxies were forced to divide into a maximum of two groups, the strongest feature in a galaxy's SED predominantly decides which group the galaxy belongs to.
+            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
+            Increasing the size of the SOM helps solve the problem of the galaxies which have features common to both groups.
 
@@
             However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
-            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the early type galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
+            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
 
@@
             There are 3 galaxies in the third neuron, similar to the S0 type. 
-            18 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
+            Eighteen of the galaxies are in the fifth neuron and similar to the Sa type, while the 7 galaxies in the fourth neuron have SEDs similar to both S0 and Sa galaxies.
             There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
@@
             %%%%%%%Sr220616: I almost completely changed the following paragraph, but I think it makes more sense, now.
-            Other methods for finding the type of galaxies (e.g. $\chi^2$ fitting and supervised neural network) are limited to templates and the outliers are not classified.
-            However, using SOM method we categorized galaxies based on their position on trained SOMs, which can have empty neurons.
-            The empty neurons in a trained SOM show that there must be another type of template there, that is absent from the K96 template spectra.
-            Using the distance of the trained network is the best way to describe the properties of this absent template.
+            Other methods for finding the type of galaxies (e.g. $\chi^2$ fitting and supervised neural network) are limited to templates: the outliers cannot be classified.
+            However, using the SOM method we categorized galaxies based on their position on trained maps, which can have empty neurons.
+            The empty neurons in a trained SOM show that there must be another type of template that is absent from the \citealias{K96} template spectra.
+            Using the distance within the trained network is the best way to describe the properties of this absent template.
             Therefore, with SOM, we have the freedom to categorize galaxies in intermediate (new) templates.
@@
 
-        In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
+        In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is correct, in this section we examine the relations between median properties of the galaxies in each neuron.
 %%%%%%%Sr220616:changed "conclusion" to clustering!
@@
             \includegraphics[width=0.5\textwidth]{images0.01/1d/props5.png}
-            \caption{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
+            \caption{Median values of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
             \label{fig: props}
@@
 
-        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
+        Fig.~\ref{fig: props} shows the median values of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
         In all plots, the horizontal axis is the number of the neurons divided by the size of the network.%, and vertical axis is one of the aforementioned properties.
@@
         \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
-Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values.
-colours shows the type of the galaxies in the new classification.
-The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies.
-The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
+Points show the median values of these properties of galaxies in the $1\times22$ network and error bars are the standard deviation of the median values.
+Colours show the type of galaxies in the new classification.
+The purest red colour shows E type galaxies and the bluest one indicates the SB1 galaxies.
+The other colours are determined by the galaxy group's relative distance to these two endpoints.}
         \label{fig: props_vs_props}
@@
         The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
-        The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
+        The redder the colour, the more similarity with  quiescent galaxies, while the purple to blue colours show more similarity to starburst galaxies.
         Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
@@
     \label{sec: 2D}
-    The one-dimensional networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies with category.
+    One-dimensional networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies with category.
     However, each neuron in these networks is limited to be connected to one other neuron in each direction.
-    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each SED type.
+    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between SED types.
     As described in Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
@@
     To get the best result from both methods, we should have SOMs with ``enough"  neurons to give any new types of galaxies a chance to find their places in the map.
-    ``Enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
+    ``Enough  neurons" is a vague statement, but as mentioned in Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
     Since the training dataset (the \citetalias{Kinney96} templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
@@
         \caption{$12\times12$~2D SOM results.
-Upper pabel: SOMs trained using the \citetalias{Kinney96} templates.
+Upper panel: SOMs trained using the \citetalias{Kinney96} templates.
 For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right).
@@
     There is a distinguishable strip of grey, dark grey and in some cases black colour in the map:
-    this strip separates early type galaxies from starburst ones.
+    this strip separates quiescent galaxies from starburst ones.
     The lower map shows that 5 of the neurons on the left side of the strip are full. 
-    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies),
+    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T},
     the only difference being that in this map they have more space to be separated from each other.
-    When we use this network to categorize the SED of galaxies, any galaxy placed on the left hand side of the strip is an early type galaxy and any one placed on the right side of the strip is a starburst one.
+    When we use this network to categorize the SED of galaxies, any galaxy placed on the left hand side of the strip is a quiescent galaxy and any one placed on the right side of the strip is a starburst one.
     The decision about what sub-type of early type or starburst galaxy is based upon its relative position to each type in the SOM.
@@
     The border between the early type galaxies and the starburst ones is the black strips in the middle of the map,  ending with the bright grey colour at the bottom of the map in the fifth neuron.
-    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
+    In this network, neurons in the right side of the strip represent the quiescent galaxies and the neurons in the left side represent the starburst ones. 
     When categorizing a new set of SEDs, if the new SEDs are similar to the \citetalias{Kinney96} template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
-    In large datasets, one can easily use this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets. 
-    Since the networks are already available, this procedure should be quick and easy for big datasets.
+    In large datasets, one can easily use this network to determine whether there is any new type of SEDs (or any outliers) in the datasets. 
+    Since the networks are already available, this procedure should be quick and easy for large datasets.
 
@@
     Using 2D maps results in categorizing galaxies into more intermediate type than in 1D maps.
-    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the early type side of the SOM, which was predictable from the results in Sec.\ref{sec: 1Dv}.
-This does not imply that in general there are more early type galaxies at higher red-shifts but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.
+    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the quiescent side of the SOM, which was predictable from the results in Sec.\ref{sec: 1Dv}.
+This does not imply that in general there are more quiescent galaxies at higher red-shifts but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.
 

### 2016-06-23 main.tex
Update main.tex
minor change to acknowledgements

@@
 
-A sample of 142 high red-shift galaxies from \citetalias{Hossein12} was used to be classified by the trained networks.
+A sample of 142 high-redshift galaxy SEDs from \citetalias{Hossein12} was classified by the trained networks.
 The classification results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.
@@
 
-The properties of the galaxies in the \citetalias{Hossein12} sample using the new classification were found to more tightly correlate in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
+The properties of the galaxies in the \citetalias{Hossein12} sample using the new classification were found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
 The properties of the galaxies in each group are in good agreement with their morphological types.
@@
 \section*{ACKNOWLEDGMENTS}
-S.R. and P.B. thank S. Lianou and A. Tammour for their useful comments. 
+The authors thank S. Lianou and A. Tammour for their useful comments. 
 S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 

### 2016-06-23 sections0.05/data0.05.tex

@@
         \includegraphics[width=0.5\textwidth]{images/k96.jpg}
-        \caption{\citetalias{Kinney96} spectra template for 12 types of galaxies from \citetalias{Hossein12} paper (Fig.
-1 in \citetalias{Hossein12}).
+        \caption{\citetalias{Kinney96} spectral templates for 12 types of galaxies from Fig.
+1 of \citetalias{Hossein12}.
 The type of each template is shown in each frame.
-Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies.
-Starburst galaxies spectra are indicated with SB 1 to 6.
-Higher numbers represent more intrinsic colour extinction.}
+Plots B, E, S0, Sa, Sb and SC show spectra that belong to the quiescent types.
+Star-forming galaxy spectra are indicated with SB 1 to 6.
+Higher numbers represent more intrinsic extinction.}
         \label{fig: k96}
@@
 
-    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
-    These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
-    \citetalias{Kinney96} stated that these templates can also be used to classify the SED of high-redshift galaxies.
+    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star-forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
+    These templates have been widely used in many studies to determine morphological types of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
+    \citetalias{Kinney96} stated that these templates can also be used to classify the SEDs of high-redshift galaxies.
 
@@
     As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.
-    In the early type (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
-    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
+    In the quiescent (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
+    The SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the quiescent types and show strong emission lines.
     For more details on each spectral type, we encourage readers to see \citetalias{Kinney96} and references therein. 
@@
     \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
-    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
+    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLT/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
    Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
     For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
-   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
-   \citetalias{Hossein12} assumed decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr to find the best-fit SED for each galaxy.
+   \citetalias{Hossein12} matched the point spread function of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
+%PB20160623: I don't understand what "matched the point spread function of the photometric data with \citetalias{Kinney96} data" means.
+   \citetalias{Hossein12} assumed decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr.% to find the best-fit SED for each galaxy.
 %%%Sr220616: moved the last sentence from the next paragraph to here.
 
-    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
-    They derived physical properties of the galaxies such as SFR, age and stellar mass from their fitted SEDs. %%%Sr220616: change the previues sentence to matched to the new corrections.
+    The fitting performed by \citetalias{Hossein12} produced the best SED match for each galaxy, with wavelength interval of 910~\AA~to $\sim 80$~cm\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
+    \citetalias{Hossein12} derived physical properties of the galaxies such as SFR, age and stellar mass from these fitted SEDs.
+%%%Sr220616: change the previues sentence to matched to the new corrections.
     Some of these properties are shown in Tab.~\ref{tab: props}.
@@
     \begin{table}
-\caption{Description of the properties of \citetalias{Hossein12} galaxies; the output result of {\em CIGALE} using a single population (SP) model}     
+\caption{Properties of \citetalias{Hossein12} galaxies from {\em CIGALE} output }     %PB20160623: please check changes here 
 \label{tab: props}
@@
 \noalign{\smallskip}
-$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
-$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
+$t_{\,\mathrm{oSP}}$ & Gyr & age of old stellar population \\
+$t_{\,\mathrm{ySP}}$ & Gyr & age of young stellar population \\
 $f_\mathrm{burst}$ & --- & mass fraction of \\
-& & young single population (SP) model \\
+& & young single population  \\
 \noalign{\smallskip}
@@
     %For testing the created networks, we use SEDs that were produced by \citetalias{Hossein12}. 
-    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength in a wide range of wavelengths.
+    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength over a wide range of wavelengths.
     %Since we have used the \citetalias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} templates.  

### 2016-10-07 main.tex
adding K-means section

@@
 \newcommand \Herschel {{\it Herschel }}
-\newcommand{\sii}{S~{\textsc II}\ } 
-\newcommand{\oiii}{O~{\textsc III}\ } 
-\newcommand{\hi}{H~{\textsc I}\ }
+\newcommand \sii {[S~\textsc{ii}]} 
+\newcommand \oiii {[O~\textsc{iii}]} 
+\newcommand \hi {H~\textsc{i}}
+\newcommand \hii {H~\textsc{ii} }
 
@@
 \begin{abstract}
-The spectral energy distribution (SED) of a galaxy contains information about its physical properties.
-Classifying SEDs using templates helps elucidate the nature of a galaxy's energy sources.
-However, available templates are limited, which can complicate SED classification.
-Most current classification methods cannot classify SEDs outside the range of templates, and will fail in special cases.
+The \textbf{\textcolor{red}{spectra}} of a galaxy contains information about its physical properties.
+Classifying \textbf{\textcolor{red}{spectra}} using templates helps elucidate the nature of a galaxy's energy sources.
+However, available templates are limited, which can complicate \textbf{\textcolor{red}{spectra}} classification.
+Most current classification methods classify \textbf{\textcolor{red}{spectra}} outside the range of templates \textbf{with low accuracy}, and will fail in special cases.
 In this paper, we introduce a new method of classifying the spectral
@@
 galaxy SED templates covering the wavelength range from far ultraviolet to near infrared.
-The trained networks were used to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$.
+The trained networks were used to classify the \textbf{\textcolor{red}{spectra}} of a sample of 142 galaxies with $0.5 < z < 1$.
 Compared to previous attempts to classify this sample, the
-self-organizing map approach was able to better classify the SEDs which had
+self-organizing map approach was able to better classify the \textbf{\textcolor{red}{spectra}} which had
 similarities with more than one template.
-The averaged SEDs and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
+The \textbf{\textcolor{red}{median spectra}} and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
 
@@
 
-\import{sections0.05/}{intro0.05.tex}
+\import{sections0.07/}{intro0.07.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.05/}{data0.05.tex}
+\import{sections0.07/}{data0.07.tex}
 
@@
 
-\import{sections0.05/}{method0.05.tex}
+\import{sections0.07/}{method0.07.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.05/}{results0.05.tex}
+\import{sections0.07/}{results0.07.tex}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\section{SUMMARY AND FUTURE APPLICATIONS}
-\label{sec: summary}
-
-% Self organizing maps can be used to classify celestial objects (i.e. stars, quasars, spectra of galaxies, light curves, etc.).
-% We showed that we can create various networks with different sizes/dimensions based on information we need from the data. 
-% If a broad and general classification is required, networks can have one dimension with few number of neurons.
-% While if we need classifications based on differences in more details, we can use a higher number of neurons.
-% Since the SOM codes does not work with uncertainty of input parameter, sometimes too much attention to details can cause problems in classifications. 
-% Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
-% for using SOM method, one should be careful about these small differences and consider in order to separate two groups from each other, how much details do they need to pay attention to.
-
-% We used SOMs to classify SEDs of the galaxies with known morphological type from \citetalias{Kinney96}, and created networks with different usages.
-% By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
-% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from \citetalias{Kinney96} for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
-% We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.
-
-% The sample of 142 high red-shift galaxies from \citetalias{Hossein12} was used to test the trained networks.
-% One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
-% The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
-% A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
-% \citetalias{Hossein12}  have used a supervised training method, and trained networks with \citetalias{Kinney96} SED template.
-% Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
-% However, they could not classify 37 out of 142 galaxies in the sample.
-% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by \citetalias{Kinney96} or between those types.
-% Therefore, we classified all 142 galaxies of our test sample.
-% We plotted the properties of the galaxies in test sample using new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
-% We also showed he properties of the galaxies in each groups is in good agreement between their morphological types.
+\\section{Summary and Future Applications}
+\label{sec: summary_SOMZ}
 
@@
 
+Two-dimensional networks can be used to find the relations of the neurons and classifications in more detail.
+The sample galaxies have more freedom to be categorized, and only 23 of them occupy exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
+Additionally, by using two-dimensional networks we showed that we do not have any outliers in the sample galaxies.
+
 \section*{ACKNOWLEDGMENTS}
-The authors thank S. Lianou and A. Tammour for their useful comments. 
+The authors thank S. Lianou and A. Tammour, and A. Sigut for their useful comments. 
 S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
@@
 
-\import{sections0.0/}{apps0.0.tex}
+%\import{sections0.0/}{apps0.0.tex}
+\import{sections0.07/}{apps_0.07.tex}
 \end{document}

### 2016-10-07 sections0.06/method0.06.tex
adding K-means section

--- 2016-06-22 sections0.05/method0.05.tex
@@
  The self-organizing map is a clustering method which reduces the dimension of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
- The result of an SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
+ The result of a SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
  Each node may contain one or more samples from the input data.
@@
  This vector is the key factor in determining the position of the nodes in a map.
- \cite{Geach12} presented the application of the SOM and discussed its algorithm in detail.
+ \cite{Geach12} presented the application of the self-organized map and discussed its algorithm in detail.
  In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a mock model which will help interpretation of our results.
-%%%Sr220616: changed a test model to a mock model
 
@@
  \label{sec: algorithm}
-     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map.  %%%Sr220616: moved paraghraph regarding to the size here!
-     The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
+     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
+     Sizes of SOMs are arbitrary and there are no rules regarding choosing one over the other. 
     \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
@@
      We start by creating S1 $\times$ S2 empty neurons. 
-     The arrangement of these neurons depends on the map's topology provided by the user. %%%Sr220616: removed initial from here, it is fixed after choosing the topology.
+     The arrangement of these neurons depends on the map's topology provided by the user. 
      In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
@@
      Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
-     The process of creating SOM happens over a series of $N$ iterations, which is set by a user. %%% SR220616: added here that N is set by a user
+     The process of creating SOM happens over a series of $N$ iterations, where $N$ is set by the user. 
      During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
@@
 This neuron is the winner node and is called the Best Matching Unit (BMU).
-%%%Sr220616: added $\in \Re^n$ space to be more clear on that it is a distance in n-dimension space no neurons!
         \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius.
@@
 \label{sec: create_som}
-     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
+     In order to create SOMs, we use the {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}. 
+     An SOM in {\sc nnt} can be created by the {\sc newsom} or {\sc selforgmap} libraries, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
      The first phase is called the ``ordering phase" and
@@
      The gradual change in the leaning factor helps to fine-tune the topology results, leading to a more stable SOM. 
-     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase. %cite kohenen book?!
+     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase. 
      We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.
@@
      We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.
-%%%Sr220616: moved this sentence from the result part to here!
      To present our results, we use {\sc nnt}'s built-in plotting tool.
-%     This tool is designed to show the distance between each cluster more clearly.
      Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
@@
  To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
- The mock sample contains two assigned attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). 
+ The mock sample contains two assigned attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). %PB20160623: were you going to change type1/2 to A/B ?
  We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Section ~\ref{sec: create_som}.
@@
  Colour coverage of neurons depends on the number of the hits on the sample.
- The neuron with the maximum number of hits is fully coloured while the empty neurons are left uncoloured (white). %%%Sr220616:changed the dark-coloured to fully coloured
+ The neuron with the maximum number of hits is fully coloured while the empty neurons are left uncoloured (white).
 
@@
 The upper panel in the Fig.~\ref{fig: sample} clearly shows this division.
-In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
+In that plot, the upper half belongs to highly star-forming galaxies, while the lower half belongs to less star forming galaxies.
 The left half of the plot is where type 1 galaxies belong, and type 2 galaxies reside in the right side.
@@
 
-%%%Sr220616:added a paragraph here
 We can conclude that although each galaxy had the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
 This network is considered a training network and can be used to cluster any new dataset with similar entries.
-Some neurons were left empty in this network because they never had became a winner for data in the mock sample.
-However, their weights have been updated in each iteration, and they could be a winner for data in the new dataset.%%%Sr220616: added the last two sentences to clear out a confusion about empty neurons.
+Some neurons were left empty in this network because they never became a winner for data in the mock sample.
+However, their weights have been updated in each iteration, and they could be a winner for data in the new dataset.
 
@@
 However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
-Therefore, it is up to the users to decide the similarity or dissimilarity between the input data based on number of neurons.
+Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.

### 2016-10-07 sections0.06/results0.06.tex
adding K-means section

--- 2016-06-23 sections0.05/results0.05.tex
@@
     For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the most suitable values for our dataset, which are listed in Section~\ref{sec: create_som}.
-%%%Sr220616: changed the optimum to the most suitable values ...
-.
-moved the initial values to section 3.2
 
@@
             Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
-            %The lower panels show the average SED of the galaxies in each node. 
             The lower left panel shows the average SED of the 80 galaxies that were classified as quiescent. 
@@
 
-            %PB20160604: is this paragraph really necessary?
-            %%Sr: I think it clears the point of having regions in middle neurons
-            %%%%%%%Sr220616: I almost completely changed the following paragraph, but I think it makes more sense, now.
             Other methods for finding the type of galaxies (e.g. $\chi^2$ fitting and supervised neural network) are limited to templates: the outliers cannot be classified.
             However, using the SOM method we categorized galaxies based on their position on trained maps, which can have empty neurons.
-            The empty neurons in a trained SOM show that there must be another type of template that is absent from the \citealias{K96} template spectra.
+            The empty neurons in a trained SOM show that there must be another type of template that is absent from the \citetalias{Kinney96} template spectra.
             Using the distance within the trained network is the best way to describe the properties of this absent template.
             Therefore, with SOM, we have the freedom to categorize galaxies in intermediate (new) templates.
-            %%%%%%%Sr220616: in response to Sophia's comment; In SOM we do not fit the data.
-we create a network using our template.
-In the final version of network each neuron has a weight vector.
-When we give a new data to this weight vector, based on distance of the the weight vector and a new input data, the SOM finds a winner neuron.
-If this winner neurons were the same for K96 and T12 samples, we would say the input vector in these two case were similar.
-Since we know type of the galaxies in K96, we could decide about the type of the galaxies in T12.
-
-        \subsubsection{PROPERTIES OF CLUSTERED GALAXIES}
+       . 
+        \subsubsection{PROPERTIES OF THE CLUSTERED GALAXIES}
 
         In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is correct, in this section we examine the relations between median properties of the galaxies in each neuron.
-%%%%%%%Sr220616:changed "conclusion" to clustering!
 
@@
         Fig.~\ref{fig: props} shows the median values of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
-        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.%, and vertical axis is one of the aforementioned properties.
-%        
+        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
         As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
-       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
-        %Considering the results from Fig.~\ref{fig: props}, we can clearly see that s
         Separating galaxies based on SED types also leads to a separation in properties that derived (via {\sc CIGALE}) from the SEDs, as expected since the SED types are also based on {\sc CIGALE} fitting.
 
-        %Sr07062016: Is it better?
         {\sc CIGALE} has various models to derive the properties of galaxies.
@@
         From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
-        %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.
 
@@
     This approach can be used to trace and recognize the outliers.
-    To execute the second approach, we used the {\tiny selforgmap} library in {\tiny MATLAB}.
-    Using the {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
-%    The latter case, can be used to identify outliers.
+    To execute the second approach, we used the {\sc selforgmap} library in {\sc matlab}.
+    Using the {\sc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
 
@@
 These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
-%    In this case, all the outliers or specific cases would be identified and removed from the sample.
-
-    % \subsection{Caveat}
-    % There is no established method to find the best SOM initial values. 
-    % Size of the maps, number of neighbours in each steps, number of iterations could vary and each one give us a new results.
-    % Also, since at the beginning the weights are generated randomly, in each run the results could have small differences.
-    %no quantitative way to analyse the data?!

### 2016-10-07 sections0.07/apps_0.07.tex
adding K-means section

--- 2016-04-19 sections0.0/apps0.0.tex
@@
 \appendix
-\section{Results of the 1D training and validagtion}
+\section{Results of training for one-dimensional self-organizing maps}
+\label{app: high_Z_1d_soms}
+As mentioned in Sec.~\ref{sec: 1D_somz}, we changed the size of the SOM from $1\times2$ to $1\times22$.
+In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.
+
 \label{app: 1d}
@@
     \end{figure}
+
+\newpage
+
+\section{Comparison of the self-organizing maps and K-means methods}
+\label{app: high_Z_1d_k-means}
+
+In this section we present the result of applying  K-means clustering method on the the spectra of 142 galaxies from \citetalias{Hossein12}.
+K-means clustering, alongside of SOMs are two of main unsupervised methods that are being used in astronomical studies \citep[e.g.][]{DAbrusco12, Aycha16}.
+In the K-means methods, the user decides number of cluster, K. 
+The algorithm, randomly chooses K random points to be set as a centroid of the clusters.
+Then, it finds the data points that are closer to the each assumed centroid and cluster them together.
+Mean values of the data points that are assigned to each cluster were calculated and become the new centroid of the cluster. 
+The algorithm finds new clusters based on the new centroids and repeats the procedure until it converges. 
+We used \textsc{matlab} K-means library to perform the K-means clustering.
+
+For analyzing our data using the spectra of 142 sample galaxies, we set the number of clusters from 2 to 22.
+We calculate the median of the spectra in each cluster, and compare the medians with the \citetalias{Kinney96} templates.
+To find the best match between the medians and the templates, we measured the spectral angle distance between them as follow:
+\begin{equation}
+    cos(\theta) = \frac{\sum_{i=1}^{n} s_it_i}{(\sum_{i=1}^{n} s^2_i)^{0.5} (\sum_{i=1}^{n} t^2_i)^{0.5}}
+\end{equation}
+where $s_i$ and $t_i$ are the ith wavelength of sample and template spectra, respectively. 
+$\theta$ is the angle between the spectrum, that the zero value means completely similar and the 180  degree means the completely different spectra.
+Since $cos(\theta)$, changes between -1 and 1, 1-$cos(\theta)$ would be the easier way to measure and report the distance.
+In this case the minimum of 1-$cos(\theta)$ for each set, would be the best match.
+
+% \ref{fig: k-means22} shows the median spectra of the members of the 22 clusters (solid black lines) and the best match from \citetalias{Kinney96} templates (dash-dot red lines).
+% As it clears in the figure, although the K-means clustering method separated the spectra of sample galaxies into 22 different groups, only 7 of template spectra matches the best with these 22 groups and the rest are completely ignored.
+% The other problem, is that in this method, in some cases even the most similar template spectra is not a good fit to the median spectra of the clusters.
+
+\begin{figure*}
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering
+                  \includegraphics[width=.99\textwidth]{k_means_images/classified_group_in_4cluster_142.pdf}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering \includegraphics[width=.99\textwidth]{k_means_images/classified_group_in_4cluster_som.pdf}
+                \end{subfigure}
+                \caption{km}
+                 \label{fig: som_k_means_4}
+\end{figure*}
+
+\begin{figure}
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering
+                  \includegraphics[width=.99\textwidth]{k_means_images/max_cosine2.pdf}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering \includegraphics[width=.99\textwidth]{k_means_images/min_cosine2.pdf}
+                \end{subfigure}
+                \caption{km}
+                 \label{fig: k_means_minmax}
+\end{figure}
+
+\begin{figure}
+                \begin{subfigure}[b]{0.5\textwidth}
+                    \centering
+                  \includegraphics[width=0.99\textwidth]{k_means_images/SB6_comp.pdf}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.5\textwidth}
+                    \centering \includegraphics[width=\textwidth]{k_means_images/Sa_comp.pdf}
+                \end{subfigure}
+                \caption{km}
+                 \label{fig: som_k_means_comp}
+\end{figure}

### 2016-10-07 sections0.07/data0.07.tex
adding K-means section

\section{Data}
\label{sec: data_highZ}
We use \textbf{\textcolor{red}{spectral templates}} from \citetalias{Kinney96} to train neural networks. 
We classify the \textbf{\textcolor{red}{spectra}} of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12} using the trained networks, and use their physical properties to test the new classifications.
Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in \textbf{\textcolor{red}{spectral}} clustering, but also to easily compare supervised and unsupervised methods.

 \subsection{Kinney Spectral Model}
     \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{images/k96.jpg}
        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from Fig. 1 in \citet{Hossein12}. The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to quiescent galaxies. Starburst galaxy spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic extinction. \textbf{\textcolor{red}{Note that the vertical axis label from \citet{Hossein12} is incorrect: the quantity plotted is flux density, not flux.}}}
        \label{fig: k96}
    \end{figure}

    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star-forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of \textbf{\textcolor{red}{spectral templates}}.
    These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
    \citetalias{Kinney96} stated that these templates can also be used to classify the \textbf{\textcolor{red}{spectra}} of high-redshift galaxies.

    The 12 templates are divided based on their morphological types for quiescent galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    The bulge group represents galaxies similar to M31 and M81, whose UV and optical spectra are dominated by their bulge stellar populations.
    The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies. 
    In the quiescent (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
    The SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the quiescent ones and show strong emission lines.
    For more details on each spectral type, we encourage readers to see \citetalias{Kinney96} and references therein. 
   The \citetalias{Kinney96} spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
    However, in this work we only use $\sim1200< \lambda < 8000$~\AA~to train our networks; 
    this wavelength range was chosen due to availability of flux information in those wavelengths for all 12 templates.

 \subsection{SED and Properties of the Sample Galaxies} 
    \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
   \citetalias{Hossein12} \textbf{\textcolor{red}{matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
    Some of these properties are shown in Table~\ref{tab: props}.
    In Section~\ref{sec: 1D_somz}, we study these properties for each category.}}
    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.

\begin{table}
\caption[Description of the properties of \citet{Hossein12} galaxies]{Description of the properties of \citet{Hossein12} galaxies; the output result of {\em CIGALE}}     
\label{tab: props}
\centering
\begin{tabular}{l l l}
\hline\hline
\noalign{\smallskip}
Par. & Unit & Description\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
$f_\mathrm{burst}$ & --- & mass fraction of \\
& & young single population (SP) model \\
\noalign{\smallskip}
$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age \\
\noalign{\smallskip}
$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
SFR & M$_\odot$/yr & instantaneous SFR  \\
$A_\mathrm{FUV}$ & mag & attenuation at 1500\,\AA{} \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{table}

    We classify SEDs that were produced by \citetalias{Hossein12} using the created networks.
    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength over a wide range of wavelengths.
    Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} \textbf{\textcolor{red}{spectral}} templates.

### 2016-10-07 sections0.07/intro0.07.tex
adding K-means section

--- 2016-06-23 sections0.05/intro0.05.tex
@@
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Intro
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
 \section{Introduction}
-\label{sec: intro}
+\label{sec: intro_somz}
 %General information about SEDs
 Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
-We can determine some physical property of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
-Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral.
+We can determine some physical properties of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
+Considering the main features of SEDs, galaxies can be categorized into two main groups: quiescent or star-forming.
 Each group has its own characteristic features and can in turn be divided into many sub-branches.
@@
 %%Creating templates and NIR_UV templates
-Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using data from nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}).
+Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using \textbf{\textcolor{red}{data from}} nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}).
 Based on their usage, these templates are restricted to certain wavelengths.
-In near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where energy output of stars peaks), the SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
+In near-infrared (NIR) to ultraviolet (UV) wavelengths \textbf{\textcolor{red}{(the region where the energy output of stars peaks)}}, the SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
 
@@
 
-Advances in techniques and detectors have resulted in more detailed wavelenght sampling of SEDs and also made classification of galaxies more complex.
+Advances in techniques and detectors have resulted in more detailed \textbf{\textcolor{red}{observations of SEDs}} and also made classification of galaxies more complex.
 Since no two galaxies, even with the same morphology, have exactly the same properties, classifying SEDs of galaxies using templates is very challenging.
 To overcome this challenge, many fitting methods have been developed and used to find template matches for SEDs, with $\chi^2$ minimization being the most commonly used. 
-Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
+Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies \citep[e.g.][]{Allen13,Ordov14,Shi15}.
 
@@
 Neural networks can be trained using two methods: supervised and unsupervised.
-In supervised method, a neural network would be trained using input data based on a desired outcome.
+In the supervised method, a neural network would be trained using input data based on a desired outcome.
 This method is very useful for classification of data with specific target values.
-On the other hand, in unsupervised method there is no prediction of output.
+On the other hand, in the unsupervised method there is no prediction of output.
 This method classifies data based on their underlying structures and hidden patterns.
-The unsupervised method is very helpful to obtain knowledge from the data, or when the underlying structure of data is not well established.
+The unsupervised method is very helpful to obtain knowledge from the data, or when the underlying structure of the data is not well established.
 
 %SOM
-A Kohonen self-organizing map (also called self-organizing map, or SOM) is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
+A Kohonen self-organizing map (also called self-organizing map, or SOM) is an \textbf{(semi)-}unsupervised neural network \textbf{\textcolor{red}{for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.}}
 It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
+\textbf{An SOM can be trained unsupervised, and its results can be used to classify other data.
+Therefore, this method can be considered as (semi)-unsupervised.}
+
 %SOM in Astronomy
@@
 The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
-From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray burst clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
 
@@
 \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
-This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
+This package can \textbf{\textcolor{red}{distinguish an astronomical object from instrumental errors,}} and then classify the object based on its spectrum.
 
 %What \citetalias{Hossein12} did
-~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
-With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
-The SED of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
-In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
+~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified \textbf{\textcolor{red}{spectral types}} of a sample of 142 galaxies using a supervised (Multi-layer feed-forward) neural network method, based on the spectral templates presented by \citetalias{Kinney96}.
+With the supervised method, they could only classify \textbf{\textcolor{red}{spectral types}} of 105 out of the 142 galaxies.
+The \textbf{\textcolor{red}{spectra}} of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
+In order to classify the remaining 37 galaxies, they combined spectra of the \citetalias{Kinney96} templates.
 \citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.
@@
 Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
-to find the best SED class for the 37 galaxies that could not be classified by the supervised method.
+to find the best \textbf{\textcolor{red}{spectral class}} for the 37 galaxies that could not be classified by the supervised method.
 First, we train self-organizing maps using the \citetalias{Kinney96} spectral templates and compare our classification with the \citetalias{Kinney96} classification.
-Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
+Then, we use the trained network to classify \textbf{\textcolor{red}{the spectra}} of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
 As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
-In Section $\S$~\ref{sec: data}, we present the data that we use to train our networks, and the ones we classified them using the trained networks.
-%%%%%%%Sr220616: change it here from to test and train networks to this new version!
-(We never tested our networks, we trained them, learned about them and used them to classifying other group of galaxies.
-I think, that's why Sophia keep asking about the testing and validating our networks)
-We describe the SOM methods in Section $\S$~\ref{sec: method}. 
-The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
-In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
+In Section $\S$~\ref{sec: data_highZ}, we present the data that we used to train our networks and the data classified using the trained networks. 
+We describe the SOM methods in Section $\S$~\ref{sec: method_somz}. 
+The results of the \textbf{\textcolor{red}{spectral classifications}} and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
+In Section $\S$~\ref{sec: summary_SOMZ}, we summarize our results and discuss potential future work in this subject.

### 2016-10-07 sections0.07/method0.07.tex
adding K-means section

--- 2016-10-07 sections0.06/method0.06.tex
@@
 \section{METHOD}
-\label{sec: method}
+\label{sec: method_somz}
  \subsection{Self Organizing Maps}
@@
 
- The self-organizing map is a clustering method which reduces the dimension of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
- The result of a SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
+ The self-organizing map is a clustering method which reduces the dimensionality of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
+ The result of an SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
  Each node may contain one or more samples from the input data.
@@
  \cite{Geach12} presented the application of the self-organized map and discussed its algorithm in detail.
- In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a mock model which will help interpretation of our results.
+ In this section we briefly discuss the algorithm of SOM, how we create our maps.
 
@@
      In the hit maps, neurons with zero hits are left empty.
-
-\subsection{Mock sample}
-
-         \begin{figure}
-            \begin{subfigure}[b]{0.5\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images0.01/sample/sample2_dist.png}
-            \end{subfigure}
-            \hfill
-            \begin{subfigure}[b]{0.5\textwidth}
-                \includegraphics[width=\textwidth]{images0.01/sample/sample2_hits.png}
-            \end{subfigure}
-            \caption{SOM of the mock sample.
-In both plots, the axes show the position of the neurons.
-Hexagonal shapes represent the neurons.
-The top plot is a distance map.
-The grey cycle colours show the differences between the weights of each neuron with white being the minimum difference and black being the maximum one.
-The lower plot is a ``hits plot".
-It represents the number of samples in each neuron, where empty means zero hits.
-In this sample, the 27 galaxies are clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
-            \label{fig: sample}
-        \end{figure}
-
- To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
- The mock sample contains two assigned attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). %PB20160623: were you going to change type1/2 to A/B ?
- We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Section ~\ref{sec: create_som}.
-
- Fig. ~\ref{fig: sample} shows the SOM of this mock sample. 
- The upper panel is the distance map. 
- The axes show the position of the neurons in the $10 \times 10$ network.
- The lower panel in Fig.~\ref{fig: sample} shows the hit map.
- On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
- The number on the purple neurons shows the number of galaxies in that neuron.
- Colour coverage of neurons depends on the number of the hits on the sample.
- The neuron with the maximum number of hits is fully coloured while the empty neurons are left uncoloured (white).
-
-Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
-The upper panel in the Fig.~\ref{fig: sample} clearly shows this division.
-In that plot, the upper half belongs to highly star-forming galaxies, while the lower half belongs to less star forming galaxies.
-The left half of the plot is where type 1 galaxies belong, and type 2 galaxies reside in the right side.
-Different shades of gray show the border between regions.
-The lower panel in Fig.~\ref{fig: sample} shows that only 4 neurons (out of 100) are occupied. 
-8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR.
-
-We can conclude that although each galaxy had the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
-This network is considered a training network and can be used to cluster any new dataset with similar entries.
-Some neurons were left empty in this network because they never became a winner for data in the mock sample.
-However, their weights have been updated in each iteration, and they could be a winner for data in the new dataset.
-
-As we show in the following sections, with data from real galaxies there are more than two dimensions and two galaxies never have exactly the same information. 
-If the network has enough neurons, the input data points would eventually separate from each other and cluster into smaller groups. 
-However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
-Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.

### 2016-10-07 sections0.07/results0.07.tex
adding K-means section

\section{Results and Discussion}
\label{sec: result}

    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra \textbf{\textcolor{red}{(in 10~\AA wavelength bins)}}.
    Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
    The trained networks can then be used to categorize other galaxies.

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
    Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find \textbf{\textcolor{red}{the optimum.
    We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.}}

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
    We generate 2D networks (Section~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.

    \subsection{One-Dimensional Self-Organizing Maps}
    \label{sec: 1D_somz}
        \subsubsection{Training the Networks}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types, quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
            The upper part of the figures shows the neurons and their relative distances \textbf{\textcolor{red}{between weight of neurons}}.
            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                  \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. The upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups is high, and these two groups are distinguishable.
            In the lower part of Fig.~\ref{fig: 1by2T}, we see that the templates are divided into two groups of 5 and 7.
            Although we know from \citetalias{Kinney96} and \citetalias{Hossein12} that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have  flatter spectra compared to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorized in a maximum of three groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are very similar; both groups are starbursting and have strong emission lines.
            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the \textbf{\textcolor{red}{spectra}} to become flatter at shorter wavelengths. 
            The flatter UV \textbf{\textcolor{red}{spectra}} make these two templates more similar to quiescent galaxies than to other starbursts.
            Therefore, in the networks, SB5 and SB6 types \textbf{\textcolor{red}{are grouped close to the quiescent galaxy templates}}.

            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption[Results of training network in $1\times3$~grid]{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid. In this network again, 5 of the \citet{Kinney96} templates are categorized as quiescent and 7 as starbursts. However, this time 2 templates (SB5 and SB6) are separated from the starburst groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct \textbf{\textcolor{red}{spectral types}}, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
            \end{subfigure}
            \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups:
            5 groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
            \textbf{5 groups in the right-side neurons are separated from the rest by a black colour, and Sc and SB6 galaxies are in two separate blocks.
            This figure is a good example of a problem of using one-dimensional SOMs to explore the data.
            Since are the templates are forced to be arrange in an array, the SB6 and Sc groups are isolated and not connected to any other groups.
            However, in a two-dimensional maps due to connection of each neurons to 6 more neurons, template galaxies have more degree of freedom to find their relation with other neurons.
            As a big picture, Fig.~\ref{fig: 1by22T}} shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
            The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
            This template has the most extinction and its \textbf{\textcolor{red}{spectrum}} has more similarity to \textbf{\textcolor{red}{quiescent galaxies}} than other starburst types.

            The fact that the templates need to have at least 22 different neurons to be divided into 12 groups shows that the differences between SB1 and SB2, and B and E, templates are very small.
            Because of their similarities, they tend to stay in the same group until the network becomes big enough to pay attention to the smallest particularity.

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            %%SROCT16: here should be SED ot spectra
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have \textbf{\textcolor{red}{spectral types}} similar to those of the quiescent galaxies and the \textbf{\textcolor{red}{spectral types}} of the rest are similar to the starburst galaxies.
            The lower left panel shows the \textbf{\textcolor{red}{median spectrum}} of the 80 galaxies that were classified as quiescent. 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the \textbf{\textcolor{red}{spectra}} clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar \textbf{\textcolor{red}{spectral types}} to Sa galaxies, but with stronger emission lines.
            The \textbf{\textcolor{red}{median spectrum}} in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2_fluxdensity.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 \textbf{\textcolor{red}{spectra are classified into the quiescent group}} while the 62 of the 142 spectra are categorized as starburst galaxies. Lower panel: \textbf{\textcolor{red}{median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}}}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's \textbf{\textcolor{red}{spectrum}} predominantly decides to which group the galaxy belongs.
            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.

            Fig.~\ref{fig: 1by3V} presents the result of classifying the \textbf{\textcolor{red}{spectra}} of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to \textbf{\textcolor{red}{the quiescent group, and 47 belong to the starburst group}}. 
            However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by3_fluxdensity.png}
                \end{subfigure}
                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times3$~networks]{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
           As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.

            \begin{figure*}
                \begin{subfigure}[b]{\textwidth}
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_22_n.png}
                    \centering
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                \centering
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by22_fluxdensity.png}
                \end{subfigure}
                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times22$~networks]{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the median spectra of each neuron, we can clearly see the changes from quiescent galaxies to the starburst ones. The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
                \label{fig: 1by22V}
            \end{figure*}

            The lower panels present the \textbf{\textcolor{red}{median spectra}} of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 \textbf{\textcolor{red}{median spectral}} plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.

            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that the \textbf{\textcolor{red}{spectra}} of galaxies in the cluster are very similar to those of the template.
            Otherwise, we can conclude that the \textbf{\textcolor{red}{spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates}}.
            For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with \textbf{\textcolor{red}{spectral type}} similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            \textbf{\textcolor{red}{19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.}}
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neuron have similar \textbf{\textcolor{red}{spectra}} to Sb type galaxies, and the \textbf{\textcolor{red}{spectra}} of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with \textbf{\textcolor{red}{spectra}} comparable to types SB1 and SB2.

            In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.

           \textbf{With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
            Therefore, if the spectra of galaxies do not match completely with any of the spectral templates in Fig.~\ref{fig: k96}, they can be categorized as a spectrum with similarity to two or more of the groups.}

        \subsubsection{Properties of the Clustered Galaxies}

       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is correct, in this section we examine the relations between median properties of the galaxies in each neuron.

        \begin{figure}
            \centering
            \includegraphics[width=0.45\textwidth]{images0.01/1d/props5.png}
            \caption[The median of four properties of galaxies in three networks]{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
            \label{fig: props}
        \end{figure}

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from \textbf{\textcolor{red}{quiescent galaxies to starburst.}}
       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the \textbf{\textcolor{red}{spectra}}, as expected since the spectral types are also based on {\em CIGALE} fitting.

        {\em CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.

        \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
        \end{subfigure}
        \caption[Relations between properties of the clustered galaxies]{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values. colours shows the type of the galaxies in the new classification. The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies. The other colours depend on how much they are close to red or blue show that the galaxies are quiescent or starburst.}
        \label{fig: props_vs_props}
    \end{figure*}

        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
        The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
        The redder the colour, the more similarity with quiescent galaxies, while the purple to blue colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The purple point in the middle of the blue points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with \textbf{\textcolor{red}{spectra}} similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with tighter correlation than those two, in all three plots.
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their \textbf{\textcolor{red}{spectral type}}.
        %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.

        \citetalias{Noll09} studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
        They found that for \textbf{\textcolor{red}{quiescent galaxies}} (E, S0 and S0/a ), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
       Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
        Whether this dependence is real or not, our results here show that using self-organizing maps can separate \textbf{\textcolor{red}{spectra}} of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.

    \subsection{Two-Dimensional Self-Organizing Maps}
    \label{sec: 2D}
    The one-dimensional networks are great tools to categorize the \textbf{\textcolor{red}{spectral}} types of galaxies and monitor the changes of properties of galaxies with category.
    However, each neuron in these networks is limited to connecting to one other neuron in each direction.
    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between \textbf{\textcolor{red}{spectral}} types.
    As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
    This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
    At first, as in the 1D SOMs, we assumed that all the galaxies must have \textbf{\textcolor{red}{spectra}} similar to any of the 12 templates in Fig.~\ref{fig: k96}.
    In this case, we can categorize \textbf{\textcolor{red}{spectra}} of other galaxies based on those 12 types.
    In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
    This approach can be used to trace and recognize the outliers, \textbf{\textcolor{red}{which could include galaxy types that are not presented in the \citetalias{Kinney96} templates (e.g. dwarf galaxies, luminous infrared galaxies, or active galactic nuclei).}}
    To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.
    \textbf{Unlike the {\textsc newsom} library in which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameter), in {\textsc selforgmap} we can change this value.}
    Using the {\textsc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.

    To get the best result from both methods, we should have SOMs with ``enough"  neurons to give any new types of galaxies a chance to find their places in the map.
    ``Enough neurons" is a vague statement, but as mentioned in Section~\ref{sec: method_somz} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
    Since the training dataset (the \citetalias{Kinney96} templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
    We then increased the size of the SOM to find the highest size suitable for the training sample.
    We noticed that very few changes occurred after the SOMs were grown to a size greater than $12\times12$, so we used this as the maximum size.

    \begin{figure*}
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images0.01/2d/dist_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images0.01/2d/dist_12_by_self_org_res12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{images0.01/2d/hit_v_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{images0.01/2d/hit_v_12_by_self_org_res12.png}
        \end{subfigure}
        \caption[$12\times12$ two-dimensional self-organizing map results]{$12\times12$~2D SOM results. Upper panel: SOMs trained using the \citet{Kinney96} templates. For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right). Lower panel: classifying the galaxies from \citet{Hossein12}, using the trained networks shown in the upper panels. From the lower right panel, we can see that there are no outliers in the galaxies from \citetalias{Hossein12}, and we can use the map in the lower left panel as a final clustering result for the \citetalias{Hossein12} galaxies.}
        \label{fig: 12by12}
    \end{figure*}

    The upper left panel in Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
    Since we considered that \textbf{\textcolor{red}{spectra}} of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
    Using this network to categorize any set of \textbf{\textcolor{red}{spectra}} forced the \textbf{\textcolor{red}{spectra}} to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
    In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the \citetalias{Kinney96} templates are in a small region. This provides enough freedom for the \textbf{\textcolor{red}{spectra of galaxies}} to be placed everywhere in the map, even far away from the templates.

    In the upper left part of the map in Fig.~\ref{fig: 12by12}, although galaxies have more ways to be separated, they were separated into two main groups.
    There is a distinguishable strip of grey, dark grey and in some cases black colour in the map:
    this strip separates quiescent galaxies from starburst ones.
    The lower map shows that 5 of the neurons on the left side of the strip are full. 
    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} \textbf{\textcolor{red}{(quiescent galaxies),}}
    the only difference being that in this map they have more space to be separated from each other.
    When we use this network to categorize the \textbf{\textcolor{red}{spectra}} of galaxies, any galaxy placed on the left hand side of the strip is a quiescent galaxy and any one placed on the right side of the strip is a starburst one.
    The decision about what sub-type of \textbf{\textcolor{red}{quiescent}} or starburst galaxy is based upon its position relative to each type in the SOM.

    As in the other map, in the upper right panel of Fig.~\ref{fig: 12by12}, galaxies are generally divided into two main groups.
    The border between the \textbf{\textcolor{red}{quiescent}} galaxies and the starburst ones is the black strips in the middle of the map, ending with the bright grey colour at the bottom of the map in the fifth neuron.
    In this network, neurons in the right side of the strip represent the quiescent galaxies and the neurons in the left side represent the starburst ones. 
    When categorizing a new set of \textbf{\textcolor{red}{spectral types}}, if the new \textbf{\textcolor{red}{spectra}} are similar to the \citet{Kinney96} template all of them will be placed in the bottom of the map, but if the \textbf{\textcolor{red}{new spectra represent different types of galaxies,}} they would sit in any other neurons in the map.
    In large datasets, one can easily use this network to figure out whether there is any of new type of \textbf{\textcolor{red}{spectra}} (or any outliers) in the datasets. 
    Since the networks are already available, this procedure should be quick and easy for big datasets. %%%% add more about time

    We used both 2D networks to categorize the \citetalias{Hossein12} galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or \textbf{\textcolor{red}{spectra}} with very different from the \citetalias{Kinney96} templates.
    The lower left map of Fig.~\ref{fig: 12by12} shows the \citetalias{Hossein12} galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
    Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see that only 23 galaxies correspond exactly to \citetalias{Kinney96} types.
    Using 2D maps results in categorizing galaxies into more intermediate types than in 1D maps.
    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the quiescent side of the SOM, which was predictable from the results in Section\ref{sec: 1Dv}. This does not imply that in general there are more quiescent galaxies at higher redshift but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.

    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy \textbf{\textcolor{red}{spectral}} classification should use 2D networks first.These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
    \textbf{After finding and removing outliers in data, using both 1D and 2D maps are complement each other.
    1D maps are great to explore the general behaviour of data, while 2D ones show more complicated picture of the data.}

### 2016-10-12 sections0.07/apps_0.07.tex
Finishing Appendix B

@@
 
-For analyzing our data using the spectra of 142 sample galaxies, we set the number of clusters from 2 to 22.
-We calculate the median of the spectra in each cluster, and compare the medians with the \citetalias{Kinney96} templates.
-To find the best match between the medians and the templates, we measured the spectral angle distance between them as follow:
+The number of clusters in the K-means method is arbitrary and is set by the user.
+We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters and on the \citetalias{Hossein12} 142 sample galaxies using and 22 clusters. 
+In this case we can easily compare the results of K-means clustering with 1D SOMs. 
+To compare the results, we measured the median of spectra for each cluster both in SOM and K-means results.
+To classify the 142 sample galaxies, we calculate the median of the spectra in each cluster, and compare them with the \citetalias{Kinney96} template spectra.
+We measured the spectral angle distance between the medians and the template spectra, to find the best match between them as follow:
 \begin{equation}
@@
 $\theta$ is the angle between the spectrum, that the zero value means completely similar and the 180  degree means the completely different spectra.
-Since $cos(\theta)$, changes between -1 and 1, 1-$cos(\theta)$ would be the easier way to measure and report the distance.
-In this case the minimum of 1-$cos(\theta)$ for each set, would be the best match.
-
-% \ref{fig: k-means22} shows the median spectra of the members of the 22 clusters (solid black lines) and the best match from \citetalias{Kinney96} templates (dash-dot red lines).
-% As it clears in the figure, although the K-means clustering method separated the spectra of sample galaxies into 22 different groups, only 7 of template spectra matches the best with these 22 groups and the rest are completely ignored.
-% The other problem, is that in this method, in some cases even the most similar template spectra is not a good fit to the median spectra of the clusters.
+Since $cos(\theta)$, changes between -1 and 1, 1-$cos(\theta)$ would be the easier way to measure and report the (dis-)similarity between two spectra.
+The spectrum from the the \citetalias{Kinney96} template that has the most similarity with a median of the cluster, would be assigned to the all galaxies in the cluster
 
@@
                     \centering
-                  \includegraphics[width=.99\textwidth]{k_means_images/classified_group_in_4cluster_142.pdf}
+                  \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster.pdf}
                 \end{subfigure}
@@
                 \begin{subfigure}[b]{0.49\textwidth}
-                    \centering \includegraphics[width=.99\textwidth]{k_means_images/classified_group_in_4cluster_som.pdf}
+                    \centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_som.pdf}
                 \end{subfigure}
-                \caption{km}
+                \caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right).
+Note that both methods randomly assign the initial values for their analysis, therefore cluster's number is not meaningful and is just for distinction of the clusters.}
                  \label{fig: som_k_means_4}
 \end{figure*}
+Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra in 4 groups using both K-means and SOMs.
+For K-means method we cannot have any empty cluster, hence we cannot increase the number of clusters more than 12, which is basically the same as Fig.~\ref{fig: k96}.
+Both plots in Fig.~\ref{fig: som_k_means_4}, separated the most starburst and quiescent galaxies in the similar manner.
+However, for spectra types between the extreme cases, they show discrepancy. 
+The other difference, between these two method is that the network created by SOM method can be used to classify the other spectra, while for the K-means clusters they can only be used one set of data.
 
-\begin{figure}
+\begin{figure*}
                 \begin{subfigure}[b]{0.49\textwidth}
                     \centering
-                  \includegraphics[width=.99\textwidth]{k_means_images/max_cosine2.pdf}
+                  \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/max_cosine2.pdf}
                 \end{subfigure}
@@
                 \begin{subfigure}[b]{0.49\textwidth}
-                    \centering \includegraphics[width=.99\textwidth]{k_means_images/min_cosine2.pdf}
+                    \centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/min_cosine2.pdf}
                 \end{subfigure}
-                \caption{km}
+                \caption{Left: the best match of \citetalias{Kinney96} templates for the median spectra of members in the cluster number 11.
+This fit has the maximum 1-$cos(\theta)$ among all 22 clusters.
+Right: the best fit of the \citetalias{Kinney96} templates to the median spectra in the  cluster number 17.
+This the best fitting result for 22 clusters.}
                  \label{fig: k_means_minmax}
-\end{figure}
+\end{figure*}
+For analyzing 142 sample galaxies from \citetalias{Hossein12}, we chose number of clusters for the K-means analysis to be 22.
+The median spectra of the members of each cluster were fitted by a spectrum from the \citetalias{Kinney96} templates.
+Although the K-means clustering method separated the spectra of 142 sample galaxies into 22 different groups, only 7 of template spectra matches the best with these 22 groups (some of the groups are classified as the same spectra type).
+%As it is clear in Fig.~\ref{fig: k_means_minmax}, in some cases even the most similar template spectra is not a good fit to the median spectra of the clusters.
+Fig.~\ref{fig: k_means_minmax}, shows the best and the worst fitting results among the 22 clusters. 
+As we expected from the results of Section~\ref{sec: 1Dv} and \citetalias{Hossein12} paper, we cannot classify all the 142 sample galaxies with exactly 12 templates. 
+Some of the classifications are almost perfect match, and there are group of galaxies that not exactly the same as any of the template spectra, but not completely different from them. 
+The right plot in the Fig.~\ref{fig: k_means_minmax} is an example of group of galaxies that can not be consider as outlier (in the sense that they are not a completely different group of galaxies), but they cannot be matched exactly with any of the template spectra.
 
-\begin{figure}
-                \begin{subfigure}[b]{0.5\textwidth}
+Being limited to the template is one of the disadvantages of the K-means algorithm over the SOM method. 
+As mentioned in Sections~\ref{sec: 1Dv} and\ref{sec: 2D}, by performing SOM method on the template spectra, we create networks of neurons which each neurons either represents one of the spectrum from the template spectra or a spectrum that has (dis-)similarity with any of the template spectra.
+We can say that using SOM, we introduced a new template based on the \citetalias{Kinney96} template spectra, and classified the 142 sample galaxies based on this new template.
+
+We classified 5 out of 22 clusters, 42 galaxies in total, from the K-means clustering as Sa type galaxies and 7 clusters, 28 galaxies in total, as SB1 type galaxies.
+Using SOM method (see Fig.~\ref{fig: 1by22V}, only 19 galaxies were classified as Sa and 19 galaxies were classified as SB1. 
+Fig.~\ref{fig: som_k_means_comp} shows the comparison between the median of the spectra classified by SOM and by K-means clustering. 
+The medians of both spectra from both methods are tracing each other undoubtedly.
+However, the normalized flux in each case is slightly different. 
+For SB1 galaxies, flux at the low wavelength regime is lower for the K-means clusters than the SOM ones, and in the longer wavelengths the flux is higher.
+These differences is reversed for Sa galaxies.
+
+Using K-means clustering, no cluster were classified as Sb or SB2, which have very similar spectra to Sa and SB1, respectively.
+On the other hand, 14 galaxies were recognized to have similar spectra to SB2, and 33 galaxies were recognized to have a spectra similar to Sa or Sb, using SOM method.
+The differences in the classification and ignoring the templates with similar spectra might come from the error in K-means clustering or error in fitting problem.
+In either case we can conclude that SOM method classifies galaxies considering more details than K-means clustering method.
+
+\begin{figure*}
+                \begin{subfigure}[b]{0.49\textwidth}
                     \centering
-                  \includegraphics[width=0.99\textwidth]{k_means_images/SB6_comp.pdf}
+                  \includegraphics[width=0.99\textwidth, height= 7.5cm]{k_means_images/SB1_comp.pdf}
                 \end{subfigure}
                 \hfill
-                \begin{subfigure}[b]{0.5\textwidth}
-                    \centering \includegraphics[width=\textwidth]{k_means_images/Sa_comp.pdf}
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering \includegraphics[width=\textwidth, height= 7.5cm]{k_means_images/Sa_comp.pdf}
                 \end{subfigure}
-                \caption{km}
+                \caption{Comparing median of classified clusters from the K-means (dashed red lines) and SOM (solid black lines) methods.
+Left: the clusters in both method that is classified as SB1.
+Right: he clusters in both method that is classified as Sa.}
                  \label{fig: som_k_means_comp}
-\end{figure}
+\end{figure*}

### 2016-10-12 sections0.07/results0.07.tex
Finishing Appendix B

@@
             In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
-            The black colour indicates that the left neuron is completely different from the other two groups,
+            The black colour indicates that the left neuron \textbf{has the most differences with} the other two groups,
             while the white colour shows that the two right neurons are very similar to one another.

### 2016-10-26 Referee response.tex
Final corrections after referee report.

Response to Referee Report on:"Classifying galaxy spectra at $0.5<z<1$: an unsupervised approac", Sahar Rahmani et al. 
We thank the referee for her/his helpful comments and have addressed them individually below in lines beginning with "-". Changes to the text are highlighted in bold in the manuscript and also appear in quotations after our responses below. To improve clarity, we made some minor changes in the text which were not requested by the referee and these are in red highlighted text.

"Most current classification methods cannot classify SEDs outside the range of templates, and will fail in special cases." (abstract)
Any classification method can generate a classification for any input.  It may be the case that this is of low confidence, or it is incorrect, but there is still some output.  I suggest rephrasing this claim to indicate the actual limitation (low accuracy? low confidence? something else?).
	-We rephrase the sentence as follows:
	"Most current classification methods classify spectra outside the
		range of templates with low accuracy, and will fail in special cases"

In the end, how does one use the output of the SOM classification? Can you evaluate its accuracy in some way?  I understand that SOMs are exploratory and unsupervised, but there should be some demonstrable benefit or value from having done it.
- There is no standard method to measure the accuracy of the SOM classification, however we hope that our description about comparing K-means clustering and SOM sheds light on the usefulness of the SOM method.

The only statement I can see about something learned from the exercise is that the SOM yielded results with higher correlations between non-spectral properties.  But correlation is never quantified; instead plots are shown, leaving the reader's eye to estimate correlation.  To my eye, the plots in the lower row of Figure 10 have low correlation, if any.  What is the R^2 value?  And why does this matter? 
- We added following sentences to the end of section 4.1 and 4.3 and summary to elaborate on usefulness of the SOM method:
	"A key feature of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. The median properties of the spectral groups change on going from one end of the SOM to the other.
	 K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them. "

	 At the 1st paragraph of section 4.3: 
	 "The other key feature of SOMs compared to supervised classification is the avility to both interpolate between and extrapolate outside of training set classes. 
 	 This permits a fuller exploration of dataset properties and detection of outliers."
 	 Also about the correlation,  the main message for Fig. 9 is how the colours spectrum changes within each plots rather than actual correlation between parameters in the plot.

	For summary:
 	"This particular sample of high-redshift galaxies is well-described by the range of the K96 templates, although some of the spectra fall in between template classes. This implies that these galaxies are not hugely different from those found in the local universe. The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation."

In response to major problems:
1.	Motivate the use of 1D versus 2D SOMs (or both).  As currently presented it is not clear what the benefit is of using either one, especially since they give different results.  Which one is better? Since they have different results, what does each one tell us?  At the end of section 4, the paper advises investigators to use the 2D approach first.  Why?  And if so, what additional knowledge is gained by applying the 1D approach? 
	-  We add the following sentences to the end of section 4:"After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary. One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture"
	We also add the following sentences to chapter 4.3 to compare 1D and 2D maps:
	"\citetalias{Hossein12} showed that when they mask emission lines (i.e., when we do not consider more details in the spectra) two types of galaxies, Sb and SB6 have potential to be confused.
    However, this confusion can be removed if we consider more details. 
    In Fig.~\ref{fig: 1by22T}, we can see that SB6 is placed near Sb galaxies. 
    This is because we use a 1D SOM map which is a good method to obtain a big picture of the problem under study, do not consider the small details. 
    However, in he upper right panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated. 
    this shows that more details of spectra are considered by 2D networks, which is one of the advantaged of using 2D maps over 1D ones."

2. Although the paper explains why the SOM has more flexibility/expressivity than the neural network approach in reference T12, it does not compare the SOM to any other method out there.  The obvious candidate for comparison would be to apply k-means clustering (e.g., cluster the 142 spectra and then each clusters to its closest match of the original 12 templates).  But to compare the meaningfully, again you'll need some measure of performance, which currently is lacking.
- We added Section 4.3 to the paper, which shows the result of K-means analysis on the data. 
	We classified 12 template galaxies in 4 groups and compare them with classification from SOM. 
	Also we classified 142 galaxies using K-means clustering and matched them with K96 template using spectral angle distances. We compare the classification results with SOM classification and show their similarity and dissimilarity

In response to minor problems:
The "mock sample" in section 3.3 does not add anything to the paper.  I suggest omitting it.  It raises more questions than it answers.  For example, is this randomly generated data?  Why 27 samples? Apparently there are only two features with only two possible values each, so there are only 4 unique possible samples, so 23 of the 27 must duplicate some other sample, and the data set is strongly over-specified.  Further, the features have values that are categorical rather than numeric (e.g., "high" and "low"), and it is not at all clear how the SOM, which employs Euclidean distance, can handle that kind of data.  Being able to divide a data set with only 4 unique samples into 4 distinct groups seems to be a non-accomplishment.
    - We removed this section. 
I could not understand how the 2D SOM was constrained so that the results in the right-hand side of Figure 11 were obtained.  This network has the same topology as the one on the left yet somehow the K96 templates "are in a small region" (p. 10, line 43, column 2).
-	We used another SOM library to create the second type of SOM network. In the second method, by controlling the number of neighbourhoods, we can squeeze all the K96 templates into a small part of the map. In this case we can check for outliers in the sample galaxies, of which none were present here.

Euclidean distance is not the best way to match spectra; I recommend using spectral angle distance instead.
-	We tried changing the distance method to spectral angle distance in the SOM code, but [!!unless we change the whole MATLAB package, we were"t successful in doing so !!]. However, we used spectral angle distance when finding the best match between K-means clusters and the templates in appendix B.

This isn't a fully unsupervised approach, since the SOM results are "classified" using the 12 template types (supervision).  That's not a weakness, but it means it would be more accurate to refer to the  method as "weakly supervised" or "partially supervised."
-	We add the following sentences to the paragraph that we introduced SOM and introduced as semi-unsupervised instead of unsupervised:"An SOM can be trained unsupervised, and its results can be used to classify other data. Therefore, this method can be considered as (semi)-supervised"

Section 4.1.1 (p. 6, line 37-39, column 2) states that "The black color indicates that the left neuron is completely different from the other two groups" but earlier it was explained that these colors are relative to the range of differences present.  So black and white could be quite close (e.g., 0.1 and 0.2) or they could be large (e.g., 1 and 100000) but there's no way to know from the color.
-	The referee is correct: the differences are relative and not absolute. We change the phrase to"has the most differences wit". 
Section 4.1.1 (p. 7, lines 10-11, column 1) confusingly states that Figure 5 shows that "5 groups on the left-side neurons are separated from 7 groups on the right side of the map with two dark-grey colors between them."  There are indeed 5 groups then 2 dark-grey links then 7 groups, but those 7 are broken into sub groups with even greater contrast (black links).  So it would be more appropriate to say that the galaxies are split as 5 - 1 - 1 - 5 or even 6 - 1 - 6.
-	We changed the lines to the following:"Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them. Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks. This figure is a good example of the problem of using one-dimensional SOMs to explore the data. Since are the templates are forced to be arranged in a linear array, the SB6 and Sc groups are isolated and not connected to any other groups. However, in a two-dimensional map, due to the connection of each neuron to 6 more neurons, template galaxies have more degrees of freedom to find their neighbourhood.

Section 4.1.2 (p. 7, line 9, column 2) says that Figure 8 has 12 plots, but actually it has 14.
-	Changed it to 14.

It is hard for the reader to track K96, T12, and N09 when their definitions are embedded pages before they are referenced.  I suggest including a small table with these labels, what they are, and their full citation so readers can quickly understand what is meant.
-	Unfortunately, we could not find any suitable place to put the suggested table. However, we made sure that all of the K96, T12 and N09 abbreviations are hyperlinked. In the PDF version, the reader can click on them to see the actual citation.

When re-using figures from a previous publication, you may need copyright permission from the journal source (e.g., Figure 1 was published by the Astronomical Journal).
-	Thanks for reminding us about the copyright permission. We checked the policy of the Astronomical Journal and for copyright purposes the permission of the author is enough. The sole author of the T12 paper is a co-author to the current paper and we have his permission to use the figure.

### 2016-10-26 main.tex
Finishing Appendix B
Final corrections after referee report.

@@
 \begin{abstract}
-The \textbf{\textcolor{red}{spectra}} of a galaxy contains information about its physical properties.
+The \textbf{\textcolor{red}{spectrum}} of a galaxy contains information about its physical properties.
 Classifying \textbf{\textcolor{red}{spectra}} using templates helps elucidate the nature of a galaxy's energy sources.
-However, available templates are limited, which can complicate \textbf{\textcolor{red}{spectra}} classification.
+However, available templates are limited, which can complicate \textbf{\textcolor{red}{spectral}} classification.
 Most current classification methods classify \textbf{\textcolor{red}{spectra}} outside the range of templates \textbf{with low accuracy}, and will fail in special cases.
-In this paper, we introduce a new method of classifying the spectral
-energy distributions of high redshift galaxies: the self-organizing map.
+In this paper, we introduce a new method of classifying the \textbf{\textcolor{red}{spectra}}
+of high redshift galaxies: the self-organizing map.
 Self-organizing maps are a type of artificial neural network, mostly used to identify subgroups in a sample.
-We trained an unsupervised self-organizing map networks using a set of
-galaxy SED templates covering the wavelength range from far ultraviolet to near infrared.
+We trained semi-supervised self-organizing map networks using a set of
+templates covering the wavelength range from far ultraviolet to near infrared. 
 The trained networks were used to classify the \textbf{\textcolor{red}{spectra}} of a sample of 142 galaxies with $0.5 < z < 1$.
@@
 \begin{keywords} 
- galaxies: high red shifts, galaxies: spectral energy distribution, methods: observational, methods: statistical, data mining, methods:data analysis
+ galaxies: high-redshift, 
+ galaxies: \textbf{\textcolor{red}{spectra}}, 
+ methods: observational, 
+ methods: statistical, 
+ methods:data analysis
 \end{keywords}
+
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\\section{Summary and Future Applications}
+\section{Summary and Future Applications}
 \label{sec: summary_SOMZ}
@@
 If a broad and general classification is required, networks can have one dimension with a few neurons. 
+\textbf{\textcolor{red}{Other classification methods such as K-means and supervised artificial neural networks can provide a general classifications with similar performance as SOM.}}
 If one needs more detailed classifications, a higher number of neurons should be used.
@@
 By varying the size of the networks, we found the relative similarity between the \citetalias{Kinney96} template classes.
+Two-dimensional networks can be used to find the relations of the neurons and classifications in great detail.
+The sample galaxies have more freedom to be categorized, and only 23 of them occupy exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
+Additionally, by using two-dimensional networks we showed that we do not have any outliers in the sample galaxies.
+
 A one-dimensional network with 22 neurons was needed in order to
@@
 
-A sample of 142 high-redshift galaxy SEDs from \citetalias{Hossein12} was classified by the trained networks.
-The classification results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.
+A sample of 142 high-redshift galaxy \textbf{\textcolor{red}{spectra}} from \citetalias{Hossein12} was classified by the trained networks.
+The classification results showed that using SOMs can allow identification of galaxies with \textbf{\textcolor{red}{spectra}} similar to two or more morphological types.
 The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
-however, they could not classify 37 out of 142 spectra.
-The unsupervised method used in this project was able to classify  all 142 spectra in the sample
+\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} \textbf{\textcolor{red}{spectral}} templates and classify the same sample of 142 galaxy spectra;
+however, \textbf{\textcolor{red}{this method}} could not classify 37 out of 142 spectra.
+The unsupervised artificial neural network method used in this project was able to classify  all 142 spectra in the sample
 as belonging to one of the morphological types introduced by \citetalias{Kinney96} or a class in between those types.
+\textbf{Although, it might seem that the classification spectra using SOMs are an arbitrary classification, we should remind that this classification is emerged form the results of data mining on the previous templates.}
+%The classification based on SOM networks are not arbitrary, because there is an actual relation between each neurons}
 
@@
 The properties of the galaxies in each group are in good agreement with their morphological types.
-
-Two-dimensional networks can be used to find the relations of the neurons and classifications in more detail.
-The sample galaxies have more freedom to be categorized, and only 23 of them occupy exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
-Additionally, by using two-dimensional networks we showed that we do not have any outliers in the sample galaxies.
+\textbf{This particular sample of high-redshift galaxies is well-described by the range of the K96 templates, although some of the spectra fall in between template classes. 
+This implies that these galaxies are not hugely different from those found in the local universe.
+The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation.}
 
 \section*{ACKNOWLEDGMENTS}
-The authors thank S. Lianou and A. Tammour, and A. Sigut for their useful comments. 
+The authors thank the referee for insightful comments which helped us to improve the manuscript.
+The authors thank S. Lianou, A. Tammour, S.C. Gallagher and A. Sigut for their useful comments. 
 S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 

### 2016-10-26 sections0.07/data0.07.tex
Final corrections after referee report.

@@
 \label{sec: data_highZ}
-We use \textbf{\textcolor{red}{spectral templates}} from \citetalias{Kinney96} to train neural networks. 
+We use \textbf{\textcolor{red}{spectral templates}} from \citetalias{Kinney96}  \textbf{\textcolor{red}{(in 10~\AA\ wavelength bins)}} to train neural networks. 
 We classify the \textbf{\textcolor{red}{spectra}} of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12} using the trained networks, and use their physical properties to test the new classifications.
@@
         \includegraphics[width=0.5\textwidth]{images/k96.jpg}
-        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from Fig.
+        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies, from fig.
 1 in \citet{Hossein12}.
 The type of each template is shown in each frame.
-Plots B, E, S0, Sa, Sb and SC show spectra that belong to quiescent galaxies.
-Starburst galaxy spectra are indicated with SB 1 to 6.
+Plots B, E, S0, Sa, Sb and Sc show spectra that belong to quiescent galaxies.
+Starburst galaxy spectra are indicated with SB1 to SB6.
 Higher numbers represent more intrinsic extinction.
-\textbf{\textcolor{red}{Note that the vertical axis label from \citet{Hossein12} is incorrect: the quantity plotted is flux density, not flux.}}}
+\textbf{\textcolor{red}{Note that the vertical axis label from \citet{Hossein12} is incorrect:  the quantity plotted in the vertical axis is flux density, not flux.}}}
         \label{fig: k96}
@@
    The \citetalias{Kinney96} spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
-    However, in this work we only use $\sim1200< \lambda < 8000$~\AA~to train our networks; 
-    this wavelength range was chosen due to availability of flux information in those wavelengths for all 12 templates.
+    However, in this work we only use \textbf{\textcolor{red}{observations in the rest-frame wavelength range}} $\sim1200< \lambda < 8000$~\AA~to train our networks; 
+    this wavelength range was chosen due to the availability of flux information in those wavelengths for all 12 templates.
 
@@
    \citetalias{Hossein12} \textbf{\textcolor{red}{matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
-    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
-    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
+    \citetalias{Hossein12} produced the best SED match, with the wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code.}.
+    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, he derived physical properties of the galaxies such as age and stellar mass.
     Some of these properties are shown in Table~\ref{tab: props}.
@@
     We classify SEDs that were produced by \citetalias{Hossein12} using the created networks.
-    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength over a wide range of wavelengths.
+    These SEDs are publicly available~\footnote{All the SEDs produced by \citetalias{Hossein12}  can be found at this \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}.} in the form of flux per rest frame wavelength over a wide range of wavelengths.
     Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} \textbf{\textcolor{red}{spectral}} templates.

### 2016-10-26 sections0.07/intro0.07.tex
Final corrections after referee report.

@@
 %%Creating templates and NIR_UV templates
-Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using \textbf{\textcolor{red}{data from}} nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}).
+Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using \textbf{\textcolor{red}{observations of}} nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}).
 Based on their usage, these templates are restricted to certain wavelengths.
-In near-infrared (NIR) to ultraviolet (UV) wavelengths \textbf{\textcolor{red}{(the region where the energy output of stars peaks)}}, the SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
+In the near-infrared (NIR) to ultraviolet (UV) wavelengths \textbf{\textcolor{red}{(the region where the energy output of stars peaks)}}, the \textbf{\textcolor{red}{spectrum}}\footnote{\textbf{\textcolor{red}{In the remainder of this paper, we are concerned with a limited range in wavelength, and so we refer to spectra rather than spectral energy distributions.}}} contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
 
@@
 
-Advances in techniques and detectors have resulted in more detailed \textbf{\textcolor{red}{observations of SEDs}} and also made classification of galaxies more complex.
-Since no two galaxies, even with the same morphology, have exactly the same properties, classifying SEDs of galaxies using templates is very challenging.
-To overcome this challenge, many fitting methods have been developed and used to find template matches for SEDs, with $\chi^2$ minimization being the most commonly used. 
+Advances in techniques and detectors have resulted in more detailed \textbf{\textcolor{red}{observations}} and also made classification of galaxies more complex.
+Since no two galaxies, even with the same morphology, have exactly the same properties, classifying \textbf{\textcolor{red}{spectra}} of galaxies using templates is very challenging.
+To overcome this challenge, many fitting methods have been developed and used to find template matches for \textbf{\textcolor{red}{spectra}}, with $\chi^2$ minimization being the most commonly used. 
 Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies \citep[e.g.][]{Allen13,Ordov14,Shi15}.
@@
 %SOM
-A Kohonen self-organizing map (also called self-organizing map, or SOM) is an \textbf{(semi)-}unsupervised neural network \textbf{\textcolor{red}{for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.}}
+A Kohonen self-organizing map (also called self-organizing map, or SOM) is an \textbf{(semi)-}supervised neural network \textbf{\textcolor{red}{for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.}}
 It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
 \textbf{An SOM can be trained unsupervised, and its results can be used to classify other data.
-Therefore, this method can be considered as (semi)-unsupervised.}
+Therefore, this method can be considered as (semi)-supervised.}
 
@@
 \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
-This package can \textbf{\textcolor{red}{distinguish an astronomical object from instrumental errors,}} and then classify the object based on its spectrum.
+This package can \textbf{\textcolor{red}{distinguish an astronomical object from instrumental artifact,}} and then classify the object based on its spectrum.
+
+%K-means vs. SOM
+\textbf{K-means clustering is another unsupervised method that is being used in many astronomical studies \citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
+K-mean clustering divides data into K clusters, in the way that each data belong to the cluster with the nearest mean value.
+In the first order, both SOM and K-means work similarly.
+In fact, SOM is a combination of K-means and considering the effect of the neighbors which can be ``controlled" by the neighborhood functions (i.e., smoothing process). 
+In SOM approach a neighborhood function has an important role in the operation of the SOM. 
+When the radius of the neighbourhood function goes to zero, the algorithm will lose its ordering power and will act as k-means clustering.
+Because of the smoothing process, the SOM can outperform the K-means clustering even in a simple 1D SOM, which can provide a big picture of clustering similar to the result of K-means clustering.}
 
 %What \citetalias{Hossein12} did
-~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified \textbf{\textcolor{red}{spectral types}} of a sample of 142 galaxies using a supervised (Multi-layer feed-forward) neural network method, based on the spectral templates presented by \citetalias{Kinney96}.
-With the supervised method, they could only classify \textbf{\textcolor{red}{spectral types}} of 105 out of the 142 galaxies.
+~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified \textbf{\textcolor{red}{spectral types}} of a sample of 142 galaxies using a supervised (multi-layer feed-forward) neural network method, based on the spectral templates presented by \citetalias{Kinney96}.
+The supervised method could only classify \textbf{\textcolor{red}{spectral types}} of 105 out of the 142 galaxies.
 The \textbf{\textcolor{red}{spectra}} of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
@@
 As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
-In Section $\S$~\ref{sec: data_highZ}, we present the data that we used to train our networks and the data classified using the trained networks. 
-We describe the SOM methods in Section $\S$~\ref{sec: method_somz}. 
-The results of the \textbf{\textcolor{red}{spectral classifications}} and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
-In Section $\S$~\ref{sec: summary_SOMZ}, we summarize our results and discuss potential future work in this subject.
+\textbf{We cluster both \citetalias{Kinney96} templates and \citetalias{Hossein12} data, usign K-means clustering method and compare the results with the results from SOM clustering.}
+In Section~\ref{sec: data_highZ}, we present the data that we used to train our networks and the data classified using the trained networks. 
+We describe the SOM and \textbf{K-means clustering methods} in Section~\ref{sec: method_somz}. 
+The results of the \textbf{\textcolor{red}{spectral classifications}} and a comparison with previous studies are presented in Section~\ref{sec: result}. 
+In Section~\ref{sec: summary_SOMZ}, we summarize our results and discuss potential future work in this subject.

### 2016-10-26 sections0.07/method0.07.tex
Final corrections after referee report.

@@
  \cite{Geach12} presented the application of the self-organized map and discussed its algorithm in detail.
- In this section we briefly discuss the algorithm of SOM, how we create our maps.
+ In this section we briefly discuss the algorithm of SOM and how we create our maps.
 
@@
         \item chooses a random vector from the dataset ($V_i$).
-        \item calculates the Euclidean distance in $\in \Re^n$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
+        \item calculates the Euclidean distance in $\in \Re^n$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_{j_i})^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
 This neuron is the winner node and is called the Best Matching Unit (BMU).
@@
 \label{sec: create_som}
-     In order to create SOMs, we use the {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}. 
+     In order to create SOMs, we use the {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}, written for \textsc{matlab2015b}. 
      An SOM in {\sc nnt} can be created by the {\sc newsom} or {\sc selforgmap} libraries, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
@@
      Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
-     In the maps, the purple hexagonal shapes represent the neurons. 
+     In the maps, the coloured hexagonal shapes represent the neurons. 
      The distances in a distance map are shown by the grey cycle colours:
@@
      In the hit maps, neurons with zero hits are left empty.
+
+\subsection{K-means clustering}
+\label{sec: kmeans_method}     
+\textbf{In the K-means method, the user decides in advance on a number of clusters, $K$, which cannot be greater than the dimension of data. 
+The algorithm randomly chooses $K$ random points to be set as the centroids of the clusters.
+Then it finds the data points that are closest to the each assumed centroid and clusters them together.
+Mean values of the data points assigned to each cluster are calculated and become the new centroid of the cluster. 
+The algorithm finds new clusters based on the new centroids and repeats the procedure until it converges.
+We used \textsc{matlab} K-means library~\citep{Seber84, Spath85}, written for \textsc{matlab2015b}, to perform the K-means clustering.}

### 2016-10-26 sections0.07/results0.07.tex
Final corrections after referee report.

@@
 
-    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra \textbf{\textcolor{red}{(in 10~\AA wavelength bins)}}.
+    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra.
     Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
@@
     Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
-    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find \textbf{\textcolor{red}{the optimum.
-    We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.}}
+    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find \textbf{\textcolor{red}{the optimum.}}
+    %We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.
 
@@
     First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
-    We generate 2D networks (Section~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
+    \textbf{We applied K-means clustering method (Section~\ref{sec: Kmeansvssom}) on both the template and sample galaxies and compared their results with the results of the 1D SOMs.}
+    \textbf{\textcolor{red}{For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network is $12\times12$ and created two types of SOM to show different applications of 2D SOMs.}}
+
     For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
@@
             Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
-            The upper part of the figures shows the neurons and their relative distances \textbf{\textcolor{red}{between weight of neurons}}.
+            The upper part of the figures shows the neurons and the relative distances \textbf{\textcolor{red}{between their weights}}. 
             As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
@@
             Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
-            Based on the colours between these two groups, we conclude that they are very similar; both groups are starbursting and have strong emission lines.
+            Based on the colours between these two groups, we conclude that they are \textbf{more similar to each other than to the ones in the left neurons}; both groups are starbursting and have strong emission lines.
             On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the \textbf{\textcolor{red}{spectra}} to become flatter at shorter wavelengths. 
@@
 
-            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and ~\ref{fig: 1by22T}).
+            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
             Since there are more nodes in higher grid SOMs, the algorithm 
@@
 
-            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups:
-            5 groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
-            \textbf{5 groups in the right-side neurons are separated from the rest by a black colour, and Sc and SB6 galaxies are in two separate blocks.
-            This figure is a good example of a problem of using one-dimensional SOMs to explore the data.
-            Since are the templates are forced to be arrange in an array, the SB6 and Sc groups are isolated and not connected to any other groups.
-            However, in a two-dimensional maps due to connection of each neurons to 6 more neurons, template galaxies have more degree of freedom to find their relation with other neurons.
+            In Fig.~\ref{fig: 1by22T}, we can see twelve distinct groups.
+            Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
+            \textbf{Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks.
+            This figure is a good example of the problem of using one-dimensional SOMs to explore the data.
+            Since are the templates are forced to be arranged in a linear array, the SB6 and Sc groups are isolated and not connected to any other groups.
+            However, in a two-dimensional map, due to the connection of each neuron to 6 more neurons, template galaxies have more degrees of freedom to find their relation with other neurons.
             As a big picture, Fig.~\ref{fig: 1by22T}} shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
             The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
-            This template has the most extinction and its \textbf{\textcolor{red}{spectrum}} has more similarity to \textbf{\textcolor{red}{quiescent galaxies}} than other starburst types.
+            This template has the most extinction and \textbf{\textcolor{red}{ the general shape of its spectrum}} has more similarity to \textbf{\textcolor{red}{quiescent galaxies}} than to other starburst types.
 
             The fact that the templates need to have at least 22 different neurons to be divided into 12 groups shows that the differences between SB1 and SB2, and B and E, templates are very small.
-            Because of their similarities, they tend to stay in the same group until the network becomes big enough to pay attention to the smallest particularity.
+            Because of their similarities, they tend to stay in the same group until the network becomes large enough to pay attention to the smallest particularity.
 
@@
          \label{sec: 1Dv}
-            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
-            %%SROCT16: here should be SED ot spectra
+            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the spectra derived from the fitted SEDs of the 142-galaxy sample from \citetalias{Hossein12}.
             The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
@@
                 \end{subfigure}
-                \caption{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
+                \caption{Classification of fitted galaxy \textbf{\textcolor{red}{spectra}} from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
@@
            As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
+            The lower panels present the \textbf{\textcolor{red}{median spectra}} of the galaxies in each neuron.
+            Since galaxies had more space to separate, some of the neurons are left empty.
+            Thus, instead of having 22 \textbf{\textcolor{red}{median spectra}} in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.
 
@@
 
-            The lower panels present the \textbf{\textcolor{red}{median spectra}} of the galaxies in each neuron.
-            Since galaxies had more space to separate, some of the neurons are left empty.
-            Thus, instead of having 22 \textbf{\textcolor{red}{median spectral}} plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.
-
             Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
@@
             In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
-            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies.
-            In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.
+            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies and have high uncertainties.
+            Using this small sample, it is quite possible that the spectra from the best-fitting SEDs of 142 sample galaxies do not match any of the template ones perfectly.
 
            \textbf{With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
-            However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
-            Therefore, if the spectra of galaxies do not match completely with any of the spectral templates in Fig.~\ref{fig: k96}, they can be categorized as a spectrum with similarity to two or more of the groups.}
+            However, with SOM, we have the freedom to categorize galaxies into intermediate groups.
+            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.}
 
@@
 
-        \begin{figure}
+        \begin{figure*}
             \centering
-            \includegraphics[width=0.45\textwidth]{images0.01/1d/props5.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/props5.png}
             \caption[The median of four properties of galaxies in three networks]{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
             \label{fig: props}
-        \end{figure}
+        \end{figure*}
 
@@
 Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values.
-colours shows the type of the galaxies in the new classification.
-The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies.
-The other colours depend on how much they are close to red or blue show that the galaxies are quiescent or starburst.}
+Colours show the galaxy types in the new classification.
+The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) one indicates the SB1 galaxies.
+The shading of other colours between light grey and black (red and blue in the online version) measures the location of galaxies along the SOM from  quiescent to starburst.}
         \label{fig: props_vs_props}
@@
         In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
-        The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
-        The redder the colour, the more similarity with quiescent galaxies, while the purple to blue colours show more similarity to starburst galaxies.
+        The colours show the galaxy types, where B type galaxies are shown with light grey (red in the online version) and SB1 types are shown with black (blue in the online version).
+        The lighter grey (redder in the online version) the colour, the more similarity with quiescent galaxies, while the medium grey to black (purple to blue in the online version) colours show more similarity to starburst galaxies.
         Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
-        The purple point in the middle of the blue points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with \textbf{\textcolor{red}{spectra}} similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
+        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with \textbf{\textcolor{red}{spectra}} similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
 
-        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with tighter correlation than those two, in all three plots.
+        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with \textbf{more precision} than those two, in all three plots.
         As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
         Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
-        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their \textbf{\textcolor{red}{spectral type}}.
-        %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.
+        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their \textbf{\textcolor{red}{spectral type}}.
 
@@
         They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
-        They found that for \textbf{\textcolor{red}{quiescent galaxies}} (E, S0 and S0/a ), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
+        They found that for \textbf{\textcolor{red}{quiescent galaxies}} (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
         Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
@@
 
+       \textbf{One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
+       Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. 
+       The median properties of the spectral groups change on going from one end of the SOM to the other.
+       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
+       Therefore, by using the SOM method, we not only study galaxies in different clusters, we also can study the trends between them as well.}
+
+    \subsection{Comparison of the self-organizing maps and K-means methods}
+    \label{sec: Kmeansvssom}
+    We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters and on the \citetalias{Hossein12} 142 sample galaxies using 22 clusters.
+    22 clusters were chosen to be able to compare the results of K-means clustering with the 1D SOM in Fig.~\ref{fig: 1by22V}. 
+    We computed the median spectrum for each cluster (in K-means) or neuron (in SOM), to compare the results.
+
+    To classify the 142 sample galaxies, we calculate the median of the spectra in each cluster, and compare them with the \citetalias{Kinney96} template spectra.
+    %A \citetalias{Kinney96} template spectrum that has the most similarity with the median spectrum of a cluster would be assigned to the all galaxies in the cluster.
+%PB: I don't quite understand this sentence.
+    We measured the spectral angle distance, also known as the cosine distance, between the medians and the template spectra to find the best match between them as follows:
+    \begin{equation}
+        \cos(\theta) = \frac{\sum_{i=1}^{n} s_it_i}{(\sum_{i=1}^{n} s^2_i)^{0.5} (\sum_{i=1}^{n} t^2_i)^{0.5}}
+    \end{equation}
+    where $s_i$ and $t_i$ are the $i^{\rm th}$ wavelength of the sample and template spectra, respectively. 
+    $\theta$ is the angle between the spectrum, such that a value of zero means completely similar and a value of $180^{\circ}$ means completely different spectra. 
+    Since $-1<\cos(\theta)<1$, $1-\cos(\theta)$ is an easier way to measure and report the dissimilarity between two spectra.
+    The clusters were classified by finding the \citetalias{Kinney96} template spectrum with the most similarity to the median spectrum.
+
+    For a direct comparison between clustered spectra and the templates one, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as different points in a high dimension space.
+    Using the spectral angle distance, the spectra are treated as connected entities which helps the shapes of the spectra to be recognized. 
+    In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each points.
+    Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time, the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well.
+    Hence, there is no need to use the spectral angle distance in the SOM method.
+
+    \begin{figure*}
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering
+                  \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster.pdf}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_som.pdf}
+                \end{subfigure}
+                \caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right).
+Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
+                 \label{fig: som_k_means_4}
+    \end{figure*}
+    Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra in 4 groups using both K-means and SOMs.
+    In the K-means method empty clusters are not allowed. 
+    Hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
+    Both plots in Fig.~\ref{fig: som_k_means_4} separated the most starburst and quiescent galaxies in a similar manner.
+    However, they show discrepancies for spectral types between the extreme cases. 
+    The other difference between these two methods is that the network created by the SOM method can be used to classify the other spectra, while for the K-means clusters they can only be used for one set of data.
+
+    \begin{figure*}
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering
+                  \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/max_cosine2.pdf}
+                \end{subfigure}
+                \hfill
+                \begin{subfigure}[b]{0.49\textwidth}
+                    \centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/min_cosine2.pdf}
+                \end{subfigure}
+                \caption{Left: the best-matched of the \citetalias{Kinney96} templates for the median spectrum of members in cluster number 9.
+This fit has the maximum $1-\cos(\theta)$ among all 22 clusters.
+Right: the best fit of the \citetalias{Kinney96} templates to the median spectrum of cluster number 22.
+This the best fitting result for 22 clusters.}
+                 \label{fig: k_means_minmax}
+    \end{figure*}
+    For analyzing 142 sample galaxies from \citetalias{Hossein12}, we chose the number of clusters for the K-means analysis to be 22.
+    The median spectra of the members of each cluster were fitted by a spectrum from the \citetalias{Kinney96} templates.
+    Although the K-means clustering method separated the spectra of 142 sample galaxies into 22 different groups, only 7 template were chosen as the best match with these 22 groups (some of the clusters are classified as the same spectral type).
+    Fig.~\ref{fig: k_means_minmax} shows the best and the worst fitting results among the 22 clusters. 
+    As we expected from the results of Section~\ref{sec: 1Dv} and \citetalias{Hossein12} paper, we cannot classify all the 142 sample galaxies with exactly 12 templates. 
+    Some of the classifications are almost perfect matches, however, there are group of galaxies that are not exactly similar to any of the template spectra.
+    The right plot in the Fig.~\ref{fig: k_means_minmax} is an example of group of galaxies that can not be considered as an outlier (in the sense that they are not a completely different type of galaxies), but they cannot be matched exactly with any of the template spectra.
+
+    There are substantial differences between the K-means and SOM-based classification.
+    From the K-means clustering, we classified 5 out of 22 clusters, 42 galaxies in total, as Sa type galaxies; 7 clusters, 28 galaxies in total, were classified as SB1 type galaxies.
+    Using the SOM method (see Fig.~\ref{fig: 1by22V}, only 19 galaxies were classified as Sa and 19 galaxies were classified as SB1. 
+    The comparison between the median of the spectra classified by SOM and by K-means clustering shows that they are clearly tracing each other.
+    However, the normalized flux in each case is slightly different: 
+    the SB1 galaxies are fainter at short wavelengths and brighter at longer wavelengths for the K-means clusters compared to the SOM ones.
+    These differences are reversed for Sa galaxies.
+
+    Using K-means clustering, no clusters were classified as Sb or SB2, which have very similar spectra to Sa and SB1, respectively.
+    On the other hand, using the SOM method, 14 galaxies were recognized as having similar spectra to SB2, and 33 galaxies were recognized to have spectra similar to Sa or Sb.
+    It seems that the K-means clustering method cannot recognize the differences between template spectra that have similar spectrum (i.e.
+SB1 and SB2, or Sa and Sb), which suggests that SOM method considers more details while clustering the spectra.
+    Being limited to the template set is another disadvantage of the K-means algorithm over the SOM method, which is not the case for the SOM method.
+    We can say that SOM has the advantages of creating a new network (template) based on the existent templates, and classified galaxies using this new network.
+
     \subsection{Two-Dimensional Self-Organizing Maps}
@@
     In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between \textbf{\textcolor{red}{spectral}} types.
+    \textbf{One of the other key feature of SOMs compared to supervised classification is the ability to both interpolate between and extrapolate outside of training set classes.
+    This permits a fuller exploration of dataset properties and detection of outliers.}
     As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
     This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
-    At first, as in the 1D SOMs, we assumed that all the galaxies must have \textbf{\textcolor{red}{spectra}} similar to any of the 12 templates in Fig.~\ref{fig: k96}.
+    At first, as in the 1D SOMs, we assumed that all the galaxies must have \textbf{\textcolor{red}{spectra}} similar to any of the 12 templates in Fig.~\ref{fig: k96}~(i.e. no outliers).
     In this case, we can categorize \textbf{\textcolor{red}{spectra}} of other galaxies based on those 12 types.
@@
     In large datasets, one can easily use this network to figure out whether there is any of new type of \textbf{\textcolor{red}{spectra}} (or any outliers) in the datasets. 
-    Since the networks are already available, this procedure should be quick and easy for big datasets. %%%% add more about time
+    Since the networks are already available, this procedure should be quick and easy for big datasets.
+    \textbf{\citetalias{Hossein12} showed that when they mask emission lines (i.e., when we do not consider more details in the spectra) two types of galaxies, Sb and SB6 can be misclassified as one an other.
+    However, this misclassification can be avoided if we consider more details in the shape of spectra. 
+    In Fig.~\ref{fig: 1by22T}, we see that SB6 is placed near Sb galaxies. 
+    This happened as a result of that 1D SOMs, which is a good method to obtain a big picture, ignore the small details for the classification. 
+    However, in the upper right panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated. 
+    This shows that more details of spectra are considered by 2D networks, which is one of the advantaged of using 2D maps over 1D ones.}
 
@@
     Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy \textbf{\textcolor{red}{spectral}} classification should use 2D networks first.These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
-    \textbf{After finding and removing outliers in data, using both 1D and 2D maps are complement each other.
-    1D maps are great to explore the general behaviour of data, while 2D ones show more complicated picture of the data.}
+    \textbf{After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary.
+    One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture.}

### 2017-03-08 Referee response.tex
change intro part on how using K -means and what is the different between K-means and SOM

@@
-Response to Referee Report on:"Classifying galaxy spectra at $0.5<z<1$: an unsupervised approac", Sahar Rahmani et al. 
+Response to Referee Report on:"Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach", Sahar Rahmani et al. 
 We thank the referee for her/his helpful comments and have addressed them individually below in lines beginning with "-".
 Changes to the text are highlighted in bold in the manuscript and also appear in quotations after our responses below.
-To improve clarity, we made some minor changes in the text which were not requested by the referee and these are in red highlighted text.
+To improve clarity, we made some minor changes in the text which were not requested by the referee; these are in red bold highlighted text.
+
+We hope changes made to the paper, makes it more clear why SOMs is useful method for classifying galaxy spectra and how it does not consider as an arbitrary classification.
 
@@
 something else?).
-	-We rephrase the sentence as follows:
+	- We rephrase the sentence as follows:
 	    "Most current classification methods classify spectra outside the
@@
 I understand that SOMs are exploratory and unsupervised, but there should be some demonstrable benefit or value from having done it.
-- There is no standard method to measure the accuracy of the SOM classification, however we hope that our description about comparing K-means clustering and SOM sheds light on the usefulness of the SOM method.
+    - There is no standard method to measure the accuracy of the SOM classification, however we hope that our description about comparing K-means clustering and self-organizing maps (see below and Section 4.3) sheds light on the usefulness of the SOM method.
+We find that, compared to K-means, SOM seems to be better at both discerning differences between similar templates and classifying objects which do not exactly match the templates.
 
@@
 And why does this matter?
-- We added following sentences to the end of section 4.1 and 4.3 and summary to elaborate on usefulness of the SOM method:
-	"A key feature of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification.
+    - We added the following sentences to sections 4.1, 4.3 and 5 to elaborate on the usefulness of the SOM method:
+    Section 4.1:
+	    "One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
        Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. 
        The median properties of the spectral groups change on going from one end of the SOM to the other.
-	 K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them. "
+       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them."
 
-	 At the 1st paragraph of section 4.3: 
-	 "The other key feature of SOMs compared to supervised classification is the avility to both interpolate between and extrapolate outside of training set classes. 
+	    Section 4.3: 
+	    "One of the other key features of SOMs compared to supervised classification is the ability to both interpolate between and extrapolate outside of training set classes.
         This permits a fuller exploration of dataset properties and detection of outliers."
- 	 Also about the correlation,  the main message for Fig. 9 is how the colours spectrum changes within each plots rather than actual correlation between parameters in the plot.
 
-	For summary:
- 	"This particular sample of high-redshift galaxies is well-described by the range of the K96 templates, although some of the spectra fall in between template classes.
-This implies that these galaxies are not hugely different from those found in the local universe.
-The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation."
+	    Section 5:
+        "This particular sample of high-redshift galaxies is well-described by the range of the K96 templates; some of the spectra fall in between template classes.
+This implies that these galaxies are not markedly different from those found in the local universe.
+The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation.
+     Other classification methods such as K-means and supervised artificial neural networks can provide a general classification with similar performance to the SOM.
+The ordered results and intermediate classes produced by self-organizing maps are distinct advantages of this method which can be utilized for other astronomical applications."
+
+        - Regarding the correlation: in Fig.
+9 the main message is how the colour of the points (corresponding to the classification) is ordered within each plot, rather than the actual correlation between parameters in the plot.
 
@@
 	- We add the following sentences to the end of section 4:"After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary.
-One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture"
-	We also add the following sentences to chapter 4.3 to compare 1D and 2D maps:
-	"\citetalias{Hossein12} showed that when they mask emission lines (i.e., when we do not consider more details in the spectra) two types of galaxies, Sb and SB6 have potential to be confused.
-    However, this confusion can be removed if we consider more details. 
-    In Fig.~\ref{fig: 1by22T}, we can see that SB6 is placed near Sb galaxies. 
-    This is because we use a 1D SOM map which is a good method to obtain a big picture of the problem under study, do not consider the small details. 
-    However, in he upper right panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated. 
-    this shows that more details of spectra are considered by 2D networks, which is one of the advantaged of using 2D maps over 1D ones."
+One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture."
+	We also add the following sentences to section 4.3 to compare 1D and 2D maps:
+    	"T12 showed that by masking emission lines (i.e., by ignoring details in spectra) two types of galaxies, Sb and SB6, can be misclassified as one another.
+        As mentioned before, 1D SOMs are a good method to obtain a big picture of the problem under study and do not consider the small details. 
+        Therefore, we can see that the SB6 category is placed near Sb galaxies in the 1D network in Fig.~\ref{fig: 1by22T}.
+        However, in the upper right panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated.
+This shows that more details of spectral shapes are considered by 2D networks, which is one of the main advantages of  using 2D maps over 1D ones."
 
@@
     - We added Section 4.3 to the paper, which shows the result of K-means analysis on the data. 
-	We classified 12 template galaxies in 4 groups and compare them with classification from SOM. 
-	Also we classified 142 galaxies using K-means clustering and matched them with K96 template using spectral angle distances.
-We compare the classification results with SOM classification and show their similarity and dissimilarity
+    We classified 12 template galaxies in 4 groups and compared them with the classification from SOM.
+We also classified 142 galaxies using K-means clustering and matched them with the nearest K96 template using spectral angle distances.
+We compare the classification results with SOM classification and show their similarity and dissimilarity.
 
@@
     - We removed this section.
+
 I could not understand how the 2D SOM was constrained so that the results in the right-hand side of Figure 11 were obtained.
@@
 Euclidean distance is not the best way to match spectra; I recommend using spectral angle distance instead.
--	We tried changing the distance method to spectral angle distance in the SOM code, but [!!unless we change the whole MATLAB package, we were"t successful in doing so !!].
-However, we used spectral angle distance when finding the best match between K-means clusters and the templates in appendix B.
+    - The main advantage of the spectral angle distance over the Euclidean distance for finding differences in spectra is that in the spectral angle distance looks at the general shape of the spectrum.
+Although SOM uses Euclidean distance to find the differences in some layer of classification, it also considers the overall shape of the spectrum.
+    Therefore, we decided to not use the spectral angle distance for SOM method.
+    However, we used spectral angle distance for the K-means clustering and for finding the best match between K-means clusters and the templates in Section 4.2.
 
@@
 That's not a weakness, but it means it would be more accurate to refer to the  method as "weakly supervised" or "partially supervised."
--	We add the following sentences to the paragraph that we introduced SOM and introduced as semi-unsupervised instead of unsupervised:"An SOM can be trained unsupervised, and its results can be used to classify other data.
-Therefore, this method can be considered as (semi)-supervised"
+    - We add the following sentences to Section 1 where we introduced self-organizing maps: "An SOM can be trained without supervision and its results used to classify other data.
+Therefore, this method can be considered as (semi)-supervised."
 
@@
 So black and white could be quite close (e.g., 0.1 and 0.2) or they could be large (e.g., 1 and 100000) but there's no way to know from the color.
--	The referee is correct: the differences are relative and not absolute. We change the phrase to"has the most differences wit". 
+    - The referee is correct: the differences are relative and not absolute. We change the phrase to:
+        "They are more similar to each other than to the ones in the left neurons".
+
 Section 4.1.1 (p.
@@
 So it would be more appropriate to say that the galaxies are split as 5 - 1 - 1 - 5 or even 6 - 1 - 6.
--	We changed the lines to the following:"Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
+    - We changed the lines to the following:
+        "Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
 Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks.
@@
 When re-using figures from a previous publication, you may need copyright permission from the journal source (e.g., Figure 1 was published by the Astronomical Journal).
--	Thanks for reminding us about the copyright permission.
+    - Thank you for reminding us about the copyright permission.
 We checked the policy of the Astronomical Journal and for copyright purposes the permission of the author is enough.

### 2017-03-08 answer_to_second_referee_comments.tex
change intro part on how using K -means and what is the different between K-means and SOM

Reviewer's Comments:

This paper proposes the use of self-organizing maps (1D and 2D) to aid in classifying galaxy spectra.  The revision has addressed several points and improve the clarity of the text.  However, there are several remaining issues.

1. The authors did not address my comment about the significance of the work.  What was learned?  What method is advocated, and what is the evidence for its superiority?

The sentence that was added about 1D vs. 2D maps comes very late in the paper and is quite abstract, stating that the two methods are complementary.  The Introduction should establish the goals of the investigation so the reader understands the purpose of each experiment as well as its significance.
%20170122PB: draft added
-- We have reorganized the last two paragraphs of Section 1 to better describe the goals of the investigation.

The paper claims that "Compared to previous attempts to classify this sample, the self-organizing map approach was able to better classify the spectra which had similarities with more than one template." (abstract), but I cannot find a quantitative comparison with any previous results.  Figure 9 is presented as the result to compare with previous work, but since the previous results are not presented nor summarized, the reader can't tell how they differ.  The paper reports "more precision", but this is not defined; does it mean smaller error bars?  Stronger correlation?  How does this show "better classification"?  To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.
--- should I put the figure from the previous paper, maybe Noll09 one??! 
% I don't think including the figure from Noll09 will be enough. It's the performance metric that's critical here.

I had suggested comparing the results to a simple nearest-neighbor classification baseline, but this was not addressed.
%--- why could not I find anything about it in the 1st report?:(
%20170122PB: it's there but well-hidden - the sentence which includes "what performance does one get simply by assigning each of the 142 spectra to its closest match from the 12 templates"

The comment about how SOMs provide an ordered clustering of the data (with respect to feature values), which k-means does not, is certainly true.  But the paper must then explain why this is important or valuable.
--- % need comment here

2. Perhaps I have missed it somewhere, but I don't think the paper ever states how exactly the classification of new data is done.  As I understand it, the authors train an SOM using template spectra, then classify new spectra by determining which SOM node is the best fit for the new item and classifying it based on the labeled template spectra that also reside in that node -- but this isn't actually stated anywhere.  Please add text explaining the classification step.  This would probably go in the final paragraph of the introduction and/or a new subsection in section 3 ("Method") - this section describes SOMs and k-means but not how to use either model to classify new data. (i.e., the SOM can't classify anything without knowing the labels of its original data set.  So although it builds the SOM in an unsupervised way, it requires the supervision of the template labels to be able to assign a label to a new item).
-- Added the following paragraph  at the end of section 3.2: %20170122PB: edited for grammar, inserted in paper text. Needs a bit more discussion.
    "As mentioned in the introduction, one of the main advantages of the SOM method  is that the resulting networks can be used to cluster new datasets with no additional training required. 
     New data with the same dimensionality as the original input data can be presented to the already trained network: the SOM algorithm finds the best matching unit considering the weight of nodes in the trained network and each vector from the new data set.
     The winner node determines the place of each new vector on the SOM.
     Based on the location of the new vectors on the SOM, they can be compared with the original data set. %20170122PB: unclear what "they" refers to
     Sections~\ref{sec: 1Dv} and ~\ref{sec: 2D} show the results of galaxy spectral classifications using networks trained on template spectra."

On page 2, lines 29-31, the authors added this text: "An SOM can be trained without supervision and its results used to classify other data. Therefore, this method can be considered as (semi)-supervised." As written, the phrase "this method" seems to refer to SOMs (so the statement wouldn't be true - SOMs are fully unsupervised), but I think instead the authors' proposed method (of building an SOM and then applying it to classify new data, using labels on the SOM-grouped data) is what is meant.  Please clarify.
-- Changed to: %20170122PB: edited for grammar, inserted in paper text
    "The training of a self-organizing map is fully unsupervised.
     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method."

3. The inclusion of k-means helps give useful context to this work. Figure 10 shows a head-to-head comparison of k-means and SOM applied to the 12 templates using 4 clusters/nodes.  But I can't tell which one is better.  The text states that they are similar but "show discrepancies for spectra types between the extreme cases".  Which ones?  How can I tell from this figure?
-- % need a comment here

At the bottom of page 10, the paper states: "The other difference between these two methods is that the network created by the SOM method can be used to classify the other spectra, while for the K-means clusters they can only be used for one set of data."  This isn't true.  (The paper itself points out that SOM reduces to k-means if the weight on the neighborhood function goes to 0, so you should be able to use the result in the same way.)  You can (and should, to do a direct comparison) use the clusters just like you used the SOM nodes - for a new data point, assign it to the most similar cluster center, then assign the template label from the original data used to construct the clusters.
--- I do not know how to do that!
% for each spectrum to be classified, compute the distance (in whatever metric we end up using)
% between the spectrum and the K cluster centres. Spectrum is classified as belonging to whatever cluster results in the smallest distance.

To analyze the 142 galaxies, the SOM and k-means experiments used different methodology and so are difficult to compare or understand. It seems that for k-means, the authors clustered the 142 sample galaxies and then classified the mean spectrum in each cluster and reported how well that did.  But for the SOM, the authors constructed the SOM based on the 12 templates from K96 and then assigned classes to individual new spectra (not the nodes).  This doesn't seem comparable.  Please use the same methodology in both cases.
--- again I do not know how to used the clusters classified based on template to classify new data sets.
% this is a fair comment - need to think more about how to compare

Further, k-means and the SOM used different distance functions (Euclidean vs. spectral angle distance) when operating on the same data.  Differences in results could simply be due to this change.  The authors' explanation for this choice does not make sense to me.
--- We have results from the Euclidean distance for the K-means! But I steel think because of the way SOM operates it is better to use SAD! Or maybe describe it better!

The text says that Figure 11 shows "the best and the worst fitting results among the 22 clusters" (for k-means) but instead it seems to show the best-fit for two clusters (9 and 22) which both look pretty good.  The text implies that Fig 11 (right) is a poor match, but it looks very good.  Please explain.
--- We apologize: this was a typo with "right" and "left" switched.

%%%%! I wrote right and left wrong again:( I should be extra careful on this one.

4. If k-means is retained, the way it is presented needs improvement. The description of k-means clustering in section 1 is a nice addition, but the comparison between k-means and SOM is confusing and wordy. K-means optimizes a partition of the data based on distance in the feature space only.  SOMs operate on a combination of distance in feature space and distance in the resulting low-dimensional map.  I am not sure how this achieves "smoothing", nor whether this is an important detail (the paper never mentions it again).  I recommend explaining what is meant here and why a "smooth" solution is better, or omitting this detail.  Explaining how SOM can be reduced to k-means is a good addition.
% PB: I edited this a bit, but not quite done as of 20170123 - need to talk about the smoothing part.

Please a add citation to the original k-means algorithm (e.g., MacQueen, 1967) when it is first mentioned (in addition to citing people who've used the algorithm).
-- Added the proper citation.

Section 3.3 outlines the k-means method that is used in the experiments.  The language here appears to be more informal and less polished than that which describes the SOM method.  To explain k-means with the same level of detail, it would be appropriate to show the objective function that is employed and to explain that it uses an alternating optimization to assign points to centroids and then update the centroids, iterating until... what?  (There are different termination conditions used by different implementations, so it would be useful to indicate here what the matlab method does.)

--- After attending to the #3 %(PB: I'll help with the language part)

### 2017-03-08 main.tex
change intro part on how using K -means and what is the different between K-means and SOM

@@
 \newcommand \sva {SvA}%: Soviet Astronomy
-\newcommand \aap {APP} %:American Academy of Pediatrics
+\newcommand \aap {A\&A} %:Astronomy & Astrophysics
 \newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
@@
 \begin{abstract}
-The \textbf{\textcolor{red}{spectrum}} of a galaxy contains information about its physical properties.
-Classifying \textbf{\textcolor{red}{spectra}} using templates helps elucidate the nature of a galaxy's energy sources.
-However, available templates are limited, which can complicate \textbf{\textcolor{red}{spectral}} classification.
-Most current classification methods classify \textbf{\textcolor{red}{spectra}} outside the range of templates \textbf{with low accuracy}, and will fail in special cases.
-In this paper, we introduce a new method of classifying the \textbf{\textcolor{red}{spectra}}
+    The spectrum of a galaxy contains information about its physical properties.
+    Classifying spectra using templates helps elucidate the nature of a galaxy's energy sources.
+    However, available templates are limited, which can complicate spectral classification.
+    Most current classification methods classify spectra outside the range of templates with low accuracy, and will fail in special cases.
+    In this paper, we introduce a new method of classifying the spectra
     of high redshift galaxies: the self-organizing map.
@@
     templates covering the wavelength range from far ultraviolet to near infrared. 
-The trained networks were used to classify the \textbf{\textcolor{red}{spectra}} of a sample of 142 galaxies with $0.5 < z < 1$.
+    The trained networks were used to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$.
     Compared to previous attempts to classify this sample, the
-self-organizing map approach was able to better classify the \textbf{\textcolor{red}{spectra}} which had
-similarities with more than one template.
-The \textbf{\textcolor{red}{median spectra}} and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
+    self-organizing map approach was able to better classify the spectra which had similarities with more than one template.
+    The median spectra and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
 
@@
  galaxies: high-redshift, 
- galaxies: \textbf{\textcolor{red}{spectra}}, 
+ galaxies: spectra, 
  methods: observational, 
@@
 
-\import{sections0.07/}{intro0.07.tex}
+\import{sections0.08/}{intro0.08.tex}
 %----------------------------------------------------------------------------------------
@@
 
-\import{sections0.07/}{data0.07.tex}
+\import{sections0.08/}{data0.08.tex}
 
@@
 
-\import{sections0.07/}{method0.07.tex}
+\import{sections0.08/}{method0.08.tex}
 
@@
 %----------------------------------------------------------------------------------------
-\import{sections0.07/}{results0.07.tex}
+\import{sections0.08/}{results0.08.tex}
 %----------------------------------------------------------------------------------------
@@
     If a broad and general classification is required, networks can have one dimension with a few neurons. 
-\textbf{\textcolor{red}{Other classification methods such as K-means and supervised artificial neural networks can provide a general classifications with similar performance as SOM.}}
     If one needs more detailed classifications, a higher number of neurons should be used.
     Since self-organizing maps do not include the uncertainty of input parameters, sometimes too much attention to detail can cause problems in classifications. 
-%Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
     When using the SOM method, one should consider whether small differences between objects are physically meaningful when separating two groups from each other.
@@
 
-A sample of 142 high-redshift galaxy \textbf{\textcolor{red}{spectra}} from \citetalias{Hossein12} was classified by the trained networks.
-The classification results showed that using SOMs can allow identification of galaxies with \textbf{\textcolor{red}{spectra}} similar to two or more morphological types.
+    A sample of 142 high-redshift galaxy spectra from \citetalias{Hossein12} was classified by the trained networks.
+    The classification results showed that using SOMs can allow identification of galaxies with spectra similar to two or more morphological types.
     The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} \textbf{\textcolor{red}{spectral}} templates and classify the same sample of 142 galaxy spectra;
-however, \textbf{\textcolor{red}{this method}} could not classify 37 out of 142 spectra.
+    \citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} spectral templates and classify the same sample of 142 galaxy spectra;
+    however, this method could not classify 37 out of 142 spectra.
     The unsupervised artificial neural network method used in this project was able to classify  all 142 spectra in the sample
     as belonging to one of the morphological types introduced by \citetalias{Kinney96} or a class in between those types.
-\textbf{Although, it might seem that the classification spectra using SOMs are an arbitrary classification, we should remind that this classification is emerged form the results of data mining on the previous templates.}
-%The classification based on SOM networks are not arbitrary, because there is an actual relation between each neurons}
+    \textbf{Although it might seem that the classes of spectra using SOMs are arbitrary, we remind the reader that this classification emerges from the results of data mining on the previous templates.}
 
@@
     The properties of the galaxies in each group are in good agreement with their morphological types.
-\textbf{This particular sample of high-redshift galaxies is well-described by the range of the K96 templates, although some of the spectra fall in between template classes. 
-This implies that these galaxies are not hugely different from those found in the local universe.
-The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation.}
+    This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates; some of the spectra fall in between template classes. 
+    This implies that these galaxies are not markedly different from those found in the local universe.
+    The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation.
+     Other classification methods such as K-means and supervised artificial neural networks can provide a general classification with similar performance to the SOM.
+The ordered results and intermediate classes produced by self-organizing maps are distinct advantages of this method which can be utilized for other astronomical applications.
 
@@
 The authors thank the referee for insightful comments which helped us to improve the manuscript.
-The authors thank S. Lianou, A. Tammour, S.C. Gallagher and A. Sigut for their useful comments. 
+The authors thank S. Lianou, A. Tammour, S.C. Gallagher, R.G. Abraham, M. Daley and A. Sigut for their useful comments. 
 S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
@@
 %\import{sections0.0/}{apps0.0.tex}
-\import{sections0.07/}{apps_0.07.tex}
+\import{sections0.08/}{apps_0.08.tex}
 \end{document}

### 2017-03-08 sections0.07/apps_0.07.tex
change intro part on how using K -means and what is the different between K-means and SOM

--- 2016-04-19 sections0.0/apps0.0.tex
@@
+%appendix
 \newpage
 \appendix
-\section{Results of the 1D training and validagtion}
+\section{Results of training for one-dimensional self-organizing maps}
+\label{app: high_Z_1d_soms}
+As mentioned in Sec.~\ref{sec: 1D_somz}, we changed the size of the SOM from $1\times2$ to $1\times22$.
+In that section we show some example of the results; here we show the rest of the maps to monitor the changes in the map over various sizes.
+
 \label{app: 1d}

### 2017-03-08 sections0.07/intro0.07.tex
change intro part on how using K -means and what is the different between K-means and SOM

@@
 An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
-It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16,Ellison16a, Ellison16b}.
+It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16a,Hossein16b,Ellison16a, Ellison16b}.
 Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91}.
@@
 It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
-\textbf{An SOM can be trained unsupervised, and its results can be used to classify other data.
+\textbf{An SOM can be trained without supervision and its results used to classify other data.
 Therefore, this method can be considered as (semi)-supervised.}
@@
 %K-means vs. SOM
-\textbf{K-means clustering is another unsupervised method that is being used in many astronomical studies \citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
-K-mean clustering divides data into K clusters, in the way that each data belong to the cluster with the nearest mean value.
-In the first order, both SOM and K-means work similarly.
+\textbf{K-means clustering is another unsupervised method used in many astronomical studies \citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
+K-means clustering divides data into $K$ clusters, in a way that each data point belongs to the cluster with the nearest mean value.
+To first order, SOM and K-means work similarly.
 In fact, SOM is a combination of K-means and considering the effect of the neighbors which can be ``controlled" by the neighborhood functions (i.e., smoothing process). 
-In SOM approach a neighborhood function has an important role in the operation of the SOM. 
-When the radius of the neighbourhood function goes to zero, the algorithm will lose its ordering power and will act as k-means clustering.
-Because of the smoothing process, the SOM can outperform the K-means clustering even in a simple 1D SOM, which can provide a big picture of clustering similar to the result of K-means clustering.}
+In the SOM approach, a neighborhood function has an important role in the operation of the SOM. 
+When the radius of the neighbourhood function goes to zero, the algorithm will lose its ordering power and will act like K-means clustering.
+Because of the smoothing process, the SOM can outperform K-means clustering even in a simple 1D SOM, which can provide a big picture of clustering similar to the result of K-means.}
 
@@
 As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
-\textbf{We cluster both \citetalias{Kinney96} templates and \citetalias{Hossein12} data, usign K-means clustering method and compare the results with the results from SOM clustering.}
+\textbf{We cluster both \citetalias{Kinney96} templates and \citetalias{Hossein12} data using the K-means clustering method and compare the results with the results from SOM clustering.}
 In Section~\ref{sec: data_highZ}, we present the data that we used to train our networks and the data classified using the trained networks. 

### 2017-03-08 sections0.08/data0.08.tex
change intro part on how using K -means and what is the different between K-means and SOM

--- 2016-10-26 sections0.07/data0.07.tex
@@
 \label{sec: data_highZ}
-We use \textbf{\textcolor{red}{spectral templates}} from \citetalias{Kinney96}  \textbf{\textcolor{red}{(in 10~\AA\ wavelength bins)}} to train neural networks. 
-We classify the \textbf{\textcolor{red}{spectra}} of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12} using the trained networks, and use their physical properties to test the new classifications.
-Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in \textbf{\textcolor{red}{spectral}} clustering, but also to easily compare supervised and unsupervised methods.
+We use spectral templates from \citetalias{Kinney96} (in 10~\AA\ wavelength bins) to train neural networks. 
+We classify the spectra of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12} using the trained networks, and use their physical properties to test the new classifications.
+Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in spectral clustering, but also to easily compare supervised and unsupervised methods.
 
- \subsection{Kinney Spectral Model}
+ \subsection{Kinney Spectral Templates}
      \begin{figure}
@@
 Higher numbers represent more intrinsic extinction.
-\textbf{\textcolor{red}{Note that the vertical axis label from \citet{Hossein12} is incorrect:  the quantity plotted in the vertical axis is flux density, not flux.}}}
+Note that the vertical axis label from \citet{Hossein12} is incorrect:  the quantity plotted in the vertical axis is flux density, not flux.}
         \label{fig: k96}
@@
 
-    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star-forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of \textbf{\textcolor{red}{spectral templates}}.
+    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star-forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of spectral templates.
     These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
-    \citetalias{Kinney96} stated that these templates can also be used to classify the \textbf{\textcolor{red}{spectra}} of high-redshift galaxies.
+    \citetalias{Kinney96} stated that these templates can also be used to classify the spectra of high-redshift galaxies.
 
@@
    The \citetalias{Kinney96} spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
-    However, in this work we only use \textbf{\textcolor{red}{observations in the rest-frame wavelength range}} $\sim1200< \lambda < 8000$~\AA~to train our networks; 
+    However, in this work we only use observations in the rest-frame wavelength range $\sim1200< \lambda < 8000$~\AA~to train our networks; 
     this wavelength range was chosen due to the availability of flux information in those wavelengths for all 12 templates.
@@
    Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
-    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
-   \citetalias{Hossein12} \textbf{\textcolor{red}{matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
+    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} were available.
+%  We have gone back and forth on the following sentence several times.
+The commented-out version (what you had) doesn't make sense to me.
+I replaced it with what I understand was done, based on reading T12.
+%   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data 
+\citetalias{Hossein12} used point-spread-function matched photometry 
+    from \citet{Santini09} as input to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
     \citetalias{Hossein12} produced the best SED match, with the wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code.}.
-    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, he derived physical properties of the galaxies such as age and stellar mass.
+    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and an old stellar population with age of $\sim 10$~Gyr, he derived physical properties of the galaxies such as age and stellar mass.
     Some of these properties are shown in Table~\ref{tab: props}.
-    In Section~\ref{sec: 1D_somz}, we study these properties for each category.}}
+    In Section~\ref{sec: 1D_somz}, we study these properties for each category.
     More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.
@@
     These SEDs are publicly available~\footnote{All the SEDs produced by \citetalias{Hossein12}  can be found at this \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}.} in the form of flux per rest frame wavelength over a wide range of wavelengths.
-    Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} \textbf{\textcolor{red}{spectral}} templates.
+    Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} spectral templates.

### 2017-03-08 sections0.08/intro0.08.tex
change intro part on how using K -means and what is the different between K-means and SOM

\section{Introduction}
\label{sec: intro_somz}
%General information about SEDs
Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
We can determine some physical properties of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
Considering the main features of SEDs, galaxies can be categorized into two main groups: quiescent or star-forming.
Each group has its own characteristic features and can in turn be divided into many sub-branches.

%%Creating templates and NIR_UV templates
Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using observations of nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}). 
Based on their usage, these templates are restricted to certain wavelengths.
In the near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where the energy output of stars peaks), the spectrum\footnote{In the remainder of this paper, we are concerned with a limited range in wavelength, and so we refer to spectra rather than spectral energy distributions.} contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.

% categorizing galaxies based on their SED

Advances in techniques and detectors have resulted in more detailed observations and also made classification of galaxies more complex.
Since no two galaxies, even with the same morphology, have exactly the same properties, classifying spectra of galaxies using templates is very challenging.
To overcome this challenge, many fitting methods have been developed and used to find template matches for spectra, with $\chi^2$ minimization being the most commonly used. 
Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies \citep[e.g.][]{Allen13,Ordov14,Shi15}.

%ANNs
Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16a,Hossein16b,Ellison16a, Ellison16b}.
Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91}.
Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.

%Training methods for networks - some grammar edits 20170122
Neural networks can be trained using two methods: supervised and unsupervised.
In supervised methods, a neural network is trained using input data based on a desired outcome.
These methods are very useful for classification of data with specific target values.
In unsupervised methods there is no prediction of output:
these methods classify data based on their underlying structures and hidden patterns.
Unsupervised methods are very helpful in obtaining knowledge from the data, or when the underlying structure of the data is not well established.

%SOM
A Kohonen self-organizing map (also called self-organizing map, or SOM) is an (semi)-supervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
%%%After_second_Referee_report
\textbf{The training of a self-organizing map is fully unsupervised.
     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method.}

%SOM in Astronomy
The utilization of the SOM in astronomy dates back to the 1990s, with \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} among the first to use SOMs in their studies.
\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOMs: object classification and clustering, and photometric redshift estimation. The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
From classifying quasars' spectra to star/galaxy classifications, from gamma-ray burst clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.

%SOM in Astronomy continued.
Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
finding patterns and common characteristics between galaxies can be a complex task.
\citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
The other application of SOMs is to find outliers or errors in the data.
\citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline. This package can distinguish an astronomical object from instrumental artifact, and then classify the object based on its spectrum.

%K-means vs. SOM
% the comparison between k-means and SOM is confusing and wordy. K-means optimizes a partition of the data based on distance in the feature space only.  SOMs operate on a combination of distance in feature space and distance in the resulting low-dimensional map.  I am not sure how this achieves "smoothing", nor whether this is an important detail (the paper never mentions it again).  I recommend explaining what is meant here and why a "smooth" solution is better, or omitting this detail.  Explaining how SOM can be reduced to k-means is a good addition.
K-means clustering~\citep{Macqueen67} is another unsupervised method used in many astronomical studies~\citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
K-means clustering divides data into $K$ clusters, in such a way that each data point belongs to the cluster with the nearest mean value.
To first order, SOM and K-means work similarly: both algorithms operate on the distances between \boldit{N} $\in \Re^m$ objects defined by the properties under consideration.
The SOM algorithm also considers distances between objects in the low-dimensional map, as  controlled by a neighborhood function. 
When the radius of the neighbourhood function goes to zero, the SOM algorithm loses its ordering power and acts like K-means clustering.
%%%%After second referee report
\textbf{On the other note, in the K-means clustering the centre of each cluster are independent, but in the SOM the winner nodes adjust each other and provide an ordered display of clusters. Therefore, the (dis)-similarity between each cluster becomes more profound.}

%20170122: combined and reorganized last 2 paragraphs of section - DRAFT
%%%%After second referee report
The goal of this work is to compare SOM-based classification of galaxy spectra to two other methods: supervised neural network and (unsupervised) K-means. 
The SOM-based classification involves generating one- and two-dimensional self-organizing maps using the \citetalias{Kinney96} spectral templates. 
These maps are used to classify the spectra of 142 galaxies with $0.5 < z < 1$, the same
sample as analyzed by ~\citet[][hereafter \citetalias{Hossein12}]{Hossein12}.
That work classified spectra using a supervised (multi-layer feed-forward) neural network method and the spectral templates presented by \citetalias{Kinney96}.
The K-means method is used to cluster the \citetalias{Kinney96} and then find distance of each \citetalias{Hossein12} data to centre of clusters to classify them.
 As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
 %HERE IS WHERE WE MENTION OUR METRIC TO SAY WHICH METHOD IS BETTER

% haven't figured out where to put this.
%\citetalias{Hossein12} also 
%showed that there are tight correlations between physical properties of galaxies, and these %correlations might be different for each type of galaxy.
%This method could only match 105 out of the 142 galaxies directly to the \citetalias{Kinney96} templates; classifying the remaining 37 galaxies required combining template spectra.
%Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to these data to find the best spectral class for the 37 galaxies that could not be classified by the supervised method.

%What we did

This paper is organized as follows.
In Section~\ref{sec: data_highZ}, we present the data used to train the networks and the data classified using the trained networks. 
We describe the SOM and K-means clustering methods in Section~\ref{sec: method_somz}. 
The results of the spectral classifications and comparison with previous studies are presented in Section~\ref{sec: result}. 
In Section~\ref{sec: summary_SOMZ}, we summarize our results and discuss potential future work in this subject.

### 2017-03-08 sections0.08/method0.08.tex
change intro part on how using K -means and what is the different between K-means and SOM

--- 2016-10-26 sections0.07/method0.07.tex
@@
 
+     %%%After_second_referee_report
+     \textbf{As mentioned in the introduction, one of the main advantages of the SOM method  is that the resulting networks can be used to cluster new datasets with no additional training required.
+     New data with the same dimensionality as the original input data can be presented to the already trained network: the SOM algorithm finds the best matching unit considering the weight of nodes in the trained network and each vector from the new data set.
+     The winner node determines the place of each new vector on the SOM.
+     Based on the location of the new vectors on the SOM, they can be compared with the original data set. %20170122PB: unclear what "they" refers to
+     Sections~\ref{sec: 1Dv} and ~\ref{sec: 2D} show the results of galaxy spectral classifications using networks trained on template spectra.}
+
 \subsection{K-means clustering}
 \label{sec: kmeans_method}     
-\textbf{In the K-means method, the user decides in advance on a number of clusters, $K$, which cannot be greater than the dimension of data. 
-The algorithm randomly chooses $K$ random points to be set as the centroids of the clusters.
-Then it finds the data points that are closest to the each assumed centroid and clusters them together.
-Mean values of the data points assigned to each cluster are calculated and become the new centroid of the cluster. 
+In the K-means method, the user decides in advance on a number of clusters, $K$, which cannot be greater than the number of data points. 
+The algorithm randomly chooses $K$ random points to be the centroids of the clusters.
+Then it finds the data points that are closest to each assumed centroid and clusters them together.
+The mean values of the data points assigned to each cluster are calculated and become the new centroid of the cluster. 
 The algorithm finds new clusters based on the new centroids and repeats the procedure until it converges.
-We used \textsc{matlab} K-means library~\citep{Seber84, Spath85}, written for \textsc{matlab2015b}, to perform the K-means clustering.}
+We used \textsc{matlab} K-means library~\citep{Seber84, Spath85}, written for \textsc{matlab2015b}, to perform the K-means clustering.

### 2017-03-08 sections0.08/results0.08.tex
change intro part on how using K -means and what is the different between K-means and SOM

--- 2016-10-26 sections0.07/results0.07.tex
@@
     Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
-    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find \textbf{\textcolor{red}{the optimum.}}
-    %We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.
+    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.
 
@@
     First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
-    \textbf{We applied K-means clustering method (Section~\ref{sec: Kmeansvssom}) on both the template and sample galaxies and compared their results with the results of the 1D SOMs.}
-    \textbf{\textcolor{red}{For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network is $12\times12$ and created two types of SOM to show different applications of 2D SOMs.}}
+    We also applied the K-means clustering method (Section~\ref{sec: Kmeansvssom}) to both the template and sample galaxies and compared the results with the results of the 1D SOMs.
+    For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network to be $12\times12$ and created two types of SOM to show different applications of 2D SOMs.
 
@@
 
-            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
-            The upper part of the figures shows the neurons and the relative distances \textbf{\textcolor{red}{between their weights}}. 
+            Figs.~\ref{fig: 1by2T} --~\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
+            The upper part of the figures shows the neurons and the relative distances between their weights. 
             As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
@@
             In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
-            The black colour indicates that the left neuron \textbf{has the most differences with} the other two groups,
+            The black colour indicates that the left neuron has the most differences with the other two groups,
             while the white colour shows that the two right neurons are very similar to one another.
@@
             Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
-            Based on the colours between these two groups, we conclude that they are \textbf{more similar to each other than to the ones in the left neurons}; both groups are starbursting and have strong emission lines.
-            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the \textbf{\textcolor{red}{spectra}} to become flatter at shorter wavelengths. 
-            The flatter UV \textbf{\textcolor{red}{spectra}} make these two templates more similar to quiescent galaxies than to other starbursts.
-            Therefore, in the networks, SB5 and SB6 types \textbf{\textcolor{red}{are grouped close to the quiescent galaxy templates}}.
+            Based on the colours between these two groups, we conclude that they are more similar to each other than to the ones in the left neurons; both groups are starbursting and have strong emission lines.
+            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the spectra to become flatter at shorter wavelengths. 
+            The flatter UV spectra make these two templates more similar to quiescent galaxies than to other starbursts.
+            Therefore, in the networks, SB5 and SB6 types are grouped close to the quiescent galaxy templates.
 
@@
             pays more attention to small differences between groups.
-            If the templates from \citetalias{Kinney96} had completely distinct \textbf{\textcolor{red}{spectral types}}, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
+            If the templates from \citetalias{Kinney96} had completely distinct spectral types, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
             However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
@@
             Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
-            \textbf{Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks.
+            Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks.
             This figure is a good example of the problem of using one-dimensional SOMs to explore the data.
@@
             However, in a two-dimensional map, due to the connection of each neuron to 6 more neurons, template galaxies have more degrees of freedom to find their relation with other neurons.
-            As a big picture, Fig.~\ref{fig: 1by22T}} shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
+            As a big picture, Fig.~\ref{fig: 1by22T} shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
             The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
-            This template has the most extinction and \textbf{\textcolor{red}{ the general shape of its spectrum}} has more similarity to \textbf{\textcolor{red}{quiescent galaxies}} than to other starburst types.
+            This template has the most extinction and  the general shape of its spectrum has more similarity to quiescent galaxies than to other starburst types.
 
@@
             The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
-            Eighty of the galaxies have \textbf{\textcolor{red}{spectral types}} similar to those of the quiescent galaxies and the \textbf{\textcolor{red}{spectral types}} of the rest are similar to the starburst galaxies.
-            The lower left panel shows the \textbf{\textcolor{red}{median spectrum}} of the 80 galaxies that were classified as quiescent. 
+            Eighty of the galaxies have spectral types similar to those of the quiescent galaxies and the spectral types of the rest are similar to the starburst galaxies.
+            The lower left panel shows the median spectrum of the 80 galaxies that were classified as quiescent. 
             These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
-            the \textbf{\textcolor{red}{spectra}} clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
-            The H$\alpha$ emission in the spectrum could be from galaxies with similar \textbf{\textcolor{red}{spectral types}} to Sa galaxies, but with stronger emission lines.
-            The \textbf{\textcolor{red}{median spectrum}} in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
+            the spectra clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
+            The H$\alpha$ emission in the spectrum could be from galaxies with similar spectral types to Sa galaxies, but with stronger emission lines.
+            The median spectrum in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
             \begin{figure}
@@
                 \end{subfigure}
-                \caption{Classification of fitted galaxy \textbf{\textcolor{red}{spectra}} from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
+                \caption{Classification of fitted galaxy spectra from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
-In this case 80 means that 80 of the 142 \textbf{\textcolor{red}{spectra are classified into the quiescent group}} while the 62 of the 142 spectra are categorized as starburst galaxies.
-Lower panel: \textbf{\textcolor{red}{median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}}}
+In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies.
+Lower panel: median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
 
-            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's \textbf{\textcolor{red}{spectrum}} predominantly decides to which group the galaxy belongs.
+            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decides to which group the galaxy belongs.
             Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
@@
 
-            Fig.~\ref{fig: 1by3V} presents the result of classifying the \textbf{\textcolor{red}{spectra}} of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to \textbf{\textcolor{red}{the quiescent group, and 47 belong to the starburst group}}.
+            Fig.~\ref{fig: 1by3V} presents the result of classifying the spectra of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to the quiescent group, and 47 belong to the starburst group.
             However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
@@
             As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
-            The lower panels present the \textbf{\textcolor{red}{median spectra}} of the galaxies in each neuron.
+            The lower panels present the median spectra of the galaxies in each neuron.
             Since galaxies had more space to separate, some of the neurons are left empty.
-            Thus, instead of having 22 \textbf{\textcolor{red}{median spectra}} in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.
+            Thus, instead of having 22 median spectra in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.
 
@@
             Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
-            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that the \textbf{\textcolor{red}{spectra}} of galaxies in the cluster are very similar to those of the template.
-            Otherwise, we can conclude that the \textbf{\textcolor{red}{spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates}}.
+            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that the spectra of galaxies in the cluster are very similar to those of the template.
+            Otherwise, we can conclude that the spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates.
             For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.
@@
             The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
-            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with \textbf{\textcolor{red}{spectral type}} similar to that of type B or E.
+            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with spectral type similar to that of type B or E.
             There are 3 galaxies in the third neuron, similar to the S0 type. 
-            \textbf{\textcolor{red}{19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
+            19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
             There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
-            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.}}
+            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.
             In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
-            Therefore, 24 galaxies in the eighth neuron have similar \textbf{\textcolor{red}{spectra}} to Sb type galaxies, and the \textbf{\textcolor{red}{spectra}} of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
-            The far right neurons in the network belong to galaxies with \textbf{\textcolor{red}{spectra}} comparable to types SB1 and SB2.
+            Therefore, 24 galaxies in the eighth neuron have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
+            The far right neurons in the network belong to galaxies with spectra comparable to types SB1 and SB2.
 
@@
 
-           \textbf{With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
+           With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
             However, with SOM, we have the freedom to categorize galaxies into intermediate groups.
-            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.}
+            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.
 
@@
         In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
-        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from \textbf{\textcolor{red}{quiescent galaxies to starburst.}}
-       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the \textbf{\textcolor{red}{spectra}}, as expected since the spectral types are also based on {\em CIGALE} fitting.
+        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst.
+       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs, as expected since the spectral types are also based on {\em CIGALE} fitting.
 
@@
         Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
-        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with \textbf{\textcolor{red}{spectra}} similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
+        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
 
-        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with \textbf{more precision} than those two, in all three plots.
+        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with more precision than those two, in all three plots.
         As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
         Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
-        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their \textbf{\textcolor{red}{spectral type}}.
+        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their spectral type.
 
@@
         They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
-        They found that for \textbf{\textcolor{red}{quiescent galaxies}} (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
+        They found that for quiescent galaxies (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
         Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
@@
         Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
-        Whether this dependence is real or not, our results here show that using self-organizing maps can separate \textbf{\textcolor{red}{spectra}} of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
+        Whether this dependence is real or not, our results here show that using self-organizing maps can separate spectra of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
 
-       \textbf{One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
+       One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
        Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. 
@@
        K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
-       Therefore, by using the SOM method, we not only study galaxies in different clusters, we also can study the trends between them as well.}
+       Therefore, by using the SOM method, we not only study galaxies in different clusters, we also can study the trends between them as well.
 
@@
     \label{sec: Kmeansvssom}
+
         We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters and on the \citetalias{Hossein12} 142 sample galaxies using 22 clusters.
         22 clusters were chosen to be able to compare the results of K-means clustering with the 1D SOM in Fig.~\ref{fig: 1by22V}. 
-    We computed the median spectrum for each cluster (in K-means) or neuron (in SOM), to compare the results.
+        We computed the median spectrum for each cluster (in K-means) or neuron (in SOM) to compare the results.
 
         To classify the 142 sample galaxies, we calculate the median of the spectra in each cluster, and compare them with the \citetalias{Kinney96} template spectra.
-    %A \citetalias{Kinney96} template spectrum that has the most similarity with the median spectrum of a cluster would be assigned to the all galaxies in the cluster.
-%PB: I don't quite understand this sentence.
         We measured the spectral angle distance, also known as the cosine distance, between the medians and the template spectra to find the best match between them as follows:
@@
         where $s_i$ and $t_i$ are the $i^{\rm th}$ wavelength of the sample and template spectra, respectively. 
-    $\theta$ is the angle between the spectrum, such that a value of zero means completely similar and a value of $180^{\circ}$ means completely different spectra. 
+        $\theta$ is the angle between the spectra, such that a value of zero means completely similar and a value of $180^{\circ}$ means completely different spectra. 
         Since $-1<\cos(\theta)<1$, $1-\cos(\theta)$ is an easier way to measure and report the dissimilarity between two spectra.
@@
 
-    For a direct comparison between clustered spectra and the templates one, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as different points in a high dimension space.
-    Using the spectral angle distance, the spectra are treated as connected entities which helps the shapes of the spectra to be recognized. 
-    In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each points.
-    Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time, the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well.
-    Hence, there is no need to use the spectral angle distance in the SOM method.
+        For a direct comparison between clustered spectra and templates, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as unrelated points in a high dimensional space.
+        Using the spectral angle distance, the spectra are treated as connected entities, which helps the shapes of the spectra to be recognized. 
+        In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each point.
+        (Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well.
+        Hence, there is no need to use the spectral angle distance in the SOM method.)
 
@@
         The median spectra of the members of each cluster were fitted by a spectrum from the \citetalias{Kinney96} templates.
-    Although the K-means clustering method separated the spectra of 142 sample galaxies into 22 different groups, only 7 template were chosen as the best match with these 22 groups (some of the clusters are classified as the same spectral type).
+        Although the K-means clustering method separated the spectra of 142 sample galaxies into 22 different groups, only 7 templates were chosen as the best match with these 22 groups; some of the clusters are classified as the same spectral type.
         Fig.~\ref{fig: k_means_minmax} shows the best and the worst fitting results among the 22 clusters. 
         As we expected from the results of Section~\ref{sec: 1Dv} and \citetalias{Hossein12} paper, we cannot classify all the 142 sample galaxies with exactly 12 templates. 
-    Some of the classifications are almost perfect matches, however, there are group of galaxies that are not exactly similar to any of the template spectra.
-    The right plot in the Fig.~\ref{fig: k_means_minmax} is an example of group of galaxies that can not be considered as an outlier (in the sense that they are not a completely different type of galaxies), but they cannot be matched exactly with any of the template spectra.
+        Some of the classifications are almost perfect matches, however, there are groups of galaxies that are not exactly similar to any of the template spectra.
+        The left plot in the Fig.~\ref{fig: k_means_minmax} is an example of a group of galaxies that can not be considered as an outlier (in the sense that they are not a completely different type of galaxies), but they cannot be matched exactly with any of the template spectra.
 
@@
         Using K-means clustering, no clusters were classified as Sb or SB2, which have very similar spectra to Sa and SB1, respectively.
-    On the other hand, using the SOM method, 14 galaxies were recognized as having similar spectra to SB2, and 33 galaxies were recognized to have spectra similar to Sa or Sb.
-    It seems that the K-means clustering method cannot recognize the differences between template spectra that have similar spectrum (i.e.
-SB1 and SB2, or Sa and Sb), which suggests that SOM method considers more details while clustering the spectra.
-    Being limited to the template set is another disadvantage of the K-means algorithm over the SOM method, which is not the case for the SOM method.
-    We can say that SOM has the advantages of creating a new network (template) based on the existent templates, and classified galaxies using this new network.
+        On the other hand, using the SOM method, 14 galaxies were recognized as having similar spectra to SB2, and 33 galaxies were recognized as having spectra similar to Sa or Sb.
+        It seems that the K-means clustering method cannot recognize the differences between template spectra that have similar spectra (i.e.
+SB1 and SB2, or Sa and Sb), which suggests that the SOM method considers more details while clustering the spectra.
+        Being limited to the template set is another disadvantage of the K-means algorithm over the SOM method.
+        We can say that SOM has the advantages of creating a new network (template) based on the existing templates, and classifying galaxies using this new network.
 
@@
     \label{sec: 2D}
-    The one-dimensional networks are great tools to categorize the \textbf{\textcolor{red}{spectral}} types of galaxies and monitor the changes of properties of galaxies with category.
+        The one-dimensional networks are great tools to categorize the spectral types of galaxies and monitor the changes of properties of galaxies with category.
         However, each neuron in these networks is limited to connecting to one other neuron in each direction.
-    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between \textbf{\textcolor{red}{spectral}} types.
-    \textbf{One of the other key feature of SOMs compared to supervised classification is the ability to both interpolate between and extrapolate outside of training set classes.
-    This permits a fuller exploration of dataset properties and detection of outliers.}
+        In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between spectral types.
+        One of the other key features of SOMs compared to supervised classification is the ability to both interpolate between and extrapolate outside of training set classes.
+        This permits a fuller exploration of dataset properties and detection of outliers.
         As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole     map will be changed.
         This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
-    At first, as in the 1D SOMs, we assumed that all the galaxies must have \textbf{\textcolor{red}{spectra}} similar to any of the 12 templates in Fig.~\ref{fig: k96}~(i.e. no outliers).
-    In this case, we can categorize \textbf{\textcolor{red}{spectra}} of other galaxies based on those 12 types.
+        At first, as in the 1D SOMs, we assumed that all the galaxies must have spectra similar to any of the 12 templates in Fig.~\ref{fig: k96}~(i.e. no outliers).
+        In this case, we can categorize spectra of other galaxies based on those 12 types.
         In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
-    This approach can be used to trace and recognize the outliers, \textbf{\textcolor{red}{which could include galaxy types that are not presented in the \citetalias{Kinney96} templates (e.g.
-dwarf galaxies, luminous infrared galaxies, or active galactic nuclei).}}
+        This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates (e.g.
+dwarf galaxies, luminous infrared galaxies, or active galactic nuclei).
         To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.
-    \textbf{Unlike the {\textsc newsom} library in which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameter), in {\textsc selforgmap} we can change this value.}
+        Unlike the {\textsc newsom} library in which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameter), in {\textsc selforgmap} we can change this value.
         Using the {\textsc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
@@
         The upper left panel in Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
-    Since we considered that \textbf{\textcolor{red}{spectra}} of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
-    Using this network to categorize any set of \textbf{\textcolor{red}{spectra}} forced the \textbf{\textcolor{red}{spectra}} to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
+        Since we considered that spectra of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
+        Using this network to categorize any set of spectra forced the spectra to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
         In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the \citetalias{Kinney96} templates are in a small region.
-This provides enough freedom for the \textbf{\textcolor{red}{spectra of galaxies}} to be placed everywhere in the map, even far away from the templates.
+This provides enough freedom for the spectra of galaxies to be placed everywhere in the map, even far away from the templates.
 
@@
         The lower map shows that 5 of the neurons on the left side of the strip are full. 
-    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} \textbf{\textcolor{red}{(quiescent galaxies),}}
+        These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (quiescent galaxies),
         the only difference being that in this map they have more space to be separated from each other.
-    When we use this network to categorize the \textbf{\textcolor{red}{spectra}} of galaxies, any galaxy placed on the left hand side of the strip is a quiescent galaxy and any one placed on the right side of the strip is a starburst one.
-    The decision about what sub-type of \textbf{\textcolor{red}{quiescent}} or starburst galaxy is based upon its position relative to each type in the SOM.
+        When we use this network to categorize the spectra of galaxies, any galaxy placed on the left hand side of the strip is a quiescent galaxy and any one placed on the right side of the strip is a starburst one.
+        The decision about what sub-type of quiescent or starburst galaxy is based upon its position relative to each type in the SOM.
 
         As in the other map, in the upper right panel of Fig.~\ref{fig: 12by12}, galaxies are generally divided into two main groups.
-    The border between the \textbf{\textcolor{red}{quiescent}} galaxies and the starburst ones is the black strips in the middle of the map, ending with the bright grey colour at the bottom of the map in the fifth neuron.
+        The border between the quiescent galaxies and the starburst ones is the black strips in the middle of the map, ending with the bright grey colour at the bottom of the map in the fifth neuron.
         In this network, neurons in the right side of the strip represent the quiescent galaxies and the neurons in the left side represent the starburst ones. 
-    When categorizing a new set of \textbf{\textcolor{red}{spectral types}}, if the new \textbf{\textcolor{red}{spectra}} are similar to the \citet{Kinney96} template all of them will be placed in the bottom of the map, but if the \textbf{\textcolor{red}{new spectra represent different types of galaxies,}} they would sit in any other neurons in the map.
-    In large datasets, one can easily use this network to figure out whether there is any of new type of \textbf{\textcolor{red}{spectra}} (or any outliers) in the datasets. 
-    Since the networks are already available, this procedure should be quick and easy for big datasets.
-    \textbf{\citetalias{Hossein12} showed that when they mask emission lines (i.e., when we do not consider more details in the spectra) two types of galaxies, Sb and SB6 can be misclassified as one an other.
-    However, this misclassification can be avoided if we consider more details in the shape of spectra. 
-    In Fig.~\ref{fig: 1by22T}, we see that SB6 is placed near Sb galaxies. 
-    This happened as a result of that 1D SOMs, which is a good method to obtain a big picture, ignore the small details for the classification. 
+        When categorizing a new set of spectral types, if the new spectra are similar to the \citet{Kinney96} template all of them will be placed in the bottom of the map, but if the new spectra represent different types of galaxies, they would sit in any other neurons in the map.
+        In large datasets, one can easily use this network to figure out whether there is any of new type of spectra (or any outliers) in the datasets. 
+        Since the networks are already available, this procedure should be quick (from few seconds to few minutes) and easy for big datasets.
+        \citetalias{Hossein12} showed that by masking emission lines (i.e., by ignoring details in spectra) two types of galaxies, Sb and SB6, can be misclassified as one another.
+        As mentioned before, 1D SOMs are a good method to obtain a big picture of the problem under study and do not consider the small details. 
+        Therefore, we can see that the SB6 category is placed near Sb galaxies in the 1D network in Fig.~\ref{fig: 1by22T}.
         However, in the upper right panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated.
-    This shows that more details of spectra are considered by 2D networks, which is one of the advantaged of using 2D maps over 1D ones.}
+This shows that more details of spectral shapes are considered by 2D networks, which is one of the main advantages of  using 2D maps over 1D ones.
 
         We used both 2D networks to categorize the \citetalias{Hossein12} galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
-    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or \textbf{\textcolor{red}{spectra}} with very different from the \citetalias{Kinney96} templates.
+        In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or spectra with very different from the \citetalias{Kinney96} templates.
         The lower left map of Fig.~\ref{fig: 12by12} shows the \citetalias{Hossein12} galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
@@
 
-    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy \textbf{\textcolor{red}{spectral}} classification should use 2D networks first.These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
-    \textbf{After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary.
-    One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture.}
+        Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy spectral classification should use 2D networks first.These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
+        After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary.
+        One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture.

### 2017-05-21 answer_to_second_referee_comments.tex
Pualine'e edits on version 8

@@
+We thank the reviewer for his/her helpful comments and apologize for the delay in returning a revised version of the manuscript.
+Changed text in the manuscript appears in bold.
+Our responses to individual comments are in the text below, beginning with ---
+
+%TBD: make sure to delete comments in this file before submitting!
+
 Reviewer's Comments:
@@
 The Introduction should establish the goals of the investigation so the reader understands the purpose of each experiment as well as its significance.
-%20170122PB: draft added
--- We have reorganized the last two paragraphs of Section 1 to better describe the goals of the investigation.
+
+--- We have reorganized the last two paragraphs of Section 1 to better describe the goals of the investigation. 
+%TBD: 
+We have also added some text to Section 5 discussing the significance.
 
@@
 To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.
---- should I put the figure from the previous paper, maybe Noll09 one??! 
+%--- should I put the figure from the previous paper, maybe Noll09 one??! 
 % I don't think including the figure from Noll09 will be enough. It's the performance metric that's critical here.
@@
 %20170122PB: it's there but well-hidden - the sentence which includes "what performance does one get simply by assigning each of the 142 spectra to its closest match from the 12 templates"
+--- We apologize for missing this suggestion in the previous version. We have now included this in the analysis and the results are reported in Section XX.
 
@@
 But the paper must then explain why this is important or valuable.
---- % need comment here
+--- We have added text to the end of both Section 4.1 and Section 5 explaining the utility of an ordered clustering.
 
@@
 So although it builds the SOM in an unsupervised way, it requires the supervision of the template labels to be able to assign a label to a new item).
--- Added the following paragraph  at the end of section 3.2: %20170122PB: edited for grammar, inserted in paper text. Needs a bit more discussion.
+-- Added the following paragraph  at the end of section 3.2: 
     "As mentioned in the introduction, one of the main advantages of the SOM method  is that the resulting networks can be used to cluster new datasets with no additional training required. 
@@
      The winner node determines the place of each new vector on the SOM.
-     Based on the location of the new vectors on the SOM, they can be compared with the original data set. %20170122PB: unclear what "they" refers to
+     The location of the new vectors on the SOM allows them to be compared with the original data set. 
      Sections~\ref{sec: 1Dv} and ~\ref{sec: 2D} show the results of galaxy spectral classifications using networks trained on template spectra."
@@
 Please clarify.
--- Changed to: %20170122PB: edited for grammar, inserted in paper text
+--- Changed to: 
     "The training of a self-organizing map is fully unsupervised.
@@
 How can I tell from this figure?
--- % need a comment here
+--- % need a comment here
 
@@
 (The paper itself points out that SOM reduces to k-means if the weight on the neighborhood function goes to 0, so you should be able to use the result in the same way.)  You can (and should, to do a direct comparison) use the clusters just like you used the SOM nodes - for a new data point, assign it to the most similar cluster center, then assign the template label from the original data used to construct the clusters.
---- I do not know how to do that!
+%--- I do not know how to do that!
 % for each spectrum to be classified, compute the distance (in whatever metric we end up using)
@@
 Please use the same methodology in both cases.
---- again I do not know how to used the clusters classified based on template to classify new data sets.
-% this is a fair comment - need to think more about how to compare
+--- This is a reasonable criticism and we have ...
 
@@
 The authors' explanation for this choice does not make sense to me.
---- We have results from the Euclidean distance for the K-means! But I steel think because of the way SOM operates it is better to use SAD! Or maybe describe it better!
+
+%TBD: --- We have results from the Euclidean distance for the K-means! But I steel think because of the way SOM operates it is better to use SAD! Or maybe describe it better!
 
@@
 Please explain.
---- We apologize: this was a typo with "right" and "left" switched.
-
-%%%%! I wrote right and left wrong again:( I should be extra careful on this one.
+--- We apologize for the confusion: this was a typo with "right" and "left" switched.
 
@@
 Explaining how SOM can be reduced to k-means is a good addition.
-% PB: I edited this a bit, but not quite done as of 20170123 - need to talk about the smoothing part.
+--- We have rewritten this paragraph (third to last of Section 1) and omitted the discussion of smoothing.
 
 Please a add citation to the original k-means algorithm (e.g., MacQueen, 1967) when it is first mentioned (in addition to citing people who've used the algorithm).
--- Added the proper citation.
+--- Added the proper citation.
 
@@
 
---- After attending to the #3 %(PB: I'll help with the language part)
+--- We have reorganized Section 3 to discuss K-means first, followed by SOM. The former section 3.3 (now 3.1) has been rewritten, giving the objective function and using more formal language.

### 2017-05-21 main.tex
Pualine'e edits on version 8

@@
 $^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
-$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
+$^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
 $^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
@@
 The ordered results and intermediate classes produced by self-organizing maps are distinct advantages of this method which can be utilized for other astronomical applications.
+%TBD: add some text here explainng why ordering is important
 

### 2017-05-21 sections0.08/intro0.08.tex
Pualine'e edits on version 8

@@
 
-%K-means vs. SOM
-% the comparison between k-means and SOM is confusing and wordy.
-K-means optimizes a partition of the data based on distance in the feature space only.
-SOMs operate on a combination of distance in feature space and distance in the resulting low-dimensional map.
-I am not sure how this achieves "smoothing", nor whether this is an important detail (the paper never mentions it again).
-I recommend explaining what is meant here and why a "smooth" solution is better, or omitting this detail.
-Explaining how SOM can be reduced to k-means is a good addition.
 K-means clustering~\citep{Macqueen67} is another unsupervised method used in many astronomical studies~\citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
@@
 When the radius of the neighbourhood function goes to zero, the SOM algorithm loses its ordering power and acts like K-means clustering.
-%%%%After second referee report
-\textbf{On the other note, in the K-means clustering the centre of each cluster are independent, but in the SOM the winner nodes adjust each other and provide an ordered display of clusters.
-Therefore, the (dis)-similarity between each cluster becomes more profound.}
 
@@
 %%%%After second referee report
-The goal of this work is to compare SOM-based classification of galaxy spectra to two other methods: supervised neural network and (unsupervised) K-means. 
-The SOM-based classification involves generating one- and two-dimensional self-organizing maps using the \citetalias{Kinney96} spectral templates. 
-These maps are used to classify the spectra of 142 galaxies with $0.5 < z < 1$, the same
-sample as analyzed by ~\citet[][hereafter \citetalias{Hossein12}]{Hossein12}.
-That work classified spectra using a supervised (multi-layer feed-forward) neural network method and the spectral templates presented by \citetalias{Kinney96}.
-The K-means method is used to cluster the \citetalias{Kinney96} and then find distance of each \citetalias{Hossein12} data to centre of clusters to classify them.
- As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
- %HERE IS WHERE WE MENTION OUR METRIC TO SAY WHICH METHOD IS BETTER
-
-% haven't figured out where to put this.
+The goal of this work is to compare SOM-based classification of galaxy spectra to two other methods: supervised neural network and (unsupervised) K-means clustering.
+The questions we want to answer are: (1) do galaxy spectra form a continuous distribution or can they be separated into discrete groups as represented by the \citetalias{Kinney96} templates?
+(2) if the distribution is continuous, how do galaxy properties vary along the spectral distribution.
+We analyze the same sample of 142 galaxies with $0.5 < z < 1$ as 
+\citet[][hereafter \citetalias{Hossein12}]{Hossein12}, who classified the spectra using a supervised (multi-layer feed-forward) neural network method with the \citetalias{Kinney96} templates.
+This method could only match 105 out of the 142 galaxies directly to the \citetalias{Kinney96} templates; classifying the remaining 37 galaxies required combining template spectra.
+%not sure if we want this sentence or not
+%Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to these data to find the best spectral class for the 37 galaxies that could not be classified by the supervised method.
+% also not sure if we want these sentences.
+% As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
 %\citetalias{Hossein12} also 
 %showed that there are tight correlations between physical properties of galaxies, and these %correlations might be different for each type of galaxy.
-%This method could only match 105 out of the 142 galaxies directly to the \citetalias{Kinney96} templates; classifying the remaining 37 galaxies required combining template spectra.
-%Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to these data to find the best spectral class for the 37 galaxies that could not be classified by the supervised method.
-
-%What we did
+ %HERE IS WHERE WE MENTION OUR METRIC TO SAY WHICH METHOD IS BETTER
 

### 2017-05-21 sections0.08/method0.08.tex
Pualine'e edits on version 8

@@
 \label{sec: method_somz}
+
+\textbf{In this section we describe the algorithms for both self-organizing maps and K-means clustering.
+As K-means is both simpler and more well-known, we introduce it briefly first before discussing SOM in detail.}
+
+%Sahar: note that I changed the notation a little bit here, for both K-means and SOM. Where you had $n$ in the SOM description I changed it to $d$.
+
+\subsection{K-means clustering}
+\label{sec: kmeans_method}
+
+\textbf{
+The K-means method partitions a data set $x_i$, having $n$ points in $d$-dimensional feature space, into $K$ clusters.
+The number of clusters $K<n$ must be decided by the user in advance, and the cluster centroids in feature space are located at positions $\mu_k$.
+The goal of the algorithm is to minimize the sum
+\begin{equation}
+\label{eq:km_sos}
+J = \sum_{i=1}^n \sum_{k=1}^K \min \big( \norm{x_i - \mu_k}^2 \big)
+\end{equation}
+where $\norm{z}$ indicates the distance measurement in $d$-dimensional space. In this work the Euclidean distance is is used, but other metrics are also possible.
+The algorithm is initialized by randomly choosing $K$ random points as cluster centroids.
+Each data point is assigned to the cluster with the closest centroid, and the centroids are re-calculated.
+The steps of re-assigning cluster membership and re-calculating the cluster centroids are repeated until a stopping criterion is reached (a maximum number of iterations or no change in cluster assignments).
+We used the \textsc{matlab} K-means library~\citep{Seber84, Spath85}, written for \textsc{matlab2015b}, to perform  K-means clustering.
+The default maximum number of iterations (100) was used.
+}
+
+%Sahar: Please check that the last sentence is correct.
+Also please check that the K-means version you used was randomly picking the initial centroids - looks like Matlab can also do this in other ways.
+
  \subsection{Self Organizing Maps}
@@
  \label{sec: algorithm}
-     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
+     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^d$, and we want to map them on an S1 by S2 map. 
      Sizes of SOMs are arbitrary and there are no rules regarding choosing one over the other. 
-    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
+    \citet{Vesanto05} suggested that a total number of $5\sqrt{d}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
 
@@
      In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
-     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
+     Initially a random weight vector, \boldit{W} $\in \Re^d$, will be assigned to each node.
      The process of creating SOM happens over a series of $N$ iterations, where $N$ is set by the user. 
@@
         \item chooses a random vector from the dataset ($V_i$).
-        \item calculates the Euclidean distance in $\in \Re^n$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_{j_i})^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
+        \item calculates the Euclidean distance in $\in \Re^d$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=d} (V_i - W_{j_i})^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{\min}}$").
 This neuron is the winner node and is called the Best Matching Unit (BMU).
@@
         \begin{equation}
-            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
+            r^t_{\rm BMU} = r^0_{\rm BMU}e^{(-t/\tau)}
         \end{equation}
         where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$.
-$r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively.
-        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
+$r^0_{BMU}$ and $r^t_{\rm BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively.
+        \item changes the weight vectors of the BMU and all the nodes within $r^t_{\rm BMU}$ as:
         \begin{equation}
@@
         \end{equation}
-        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
+        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{\rm BMU}})$ is the influence rate.
 $R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
@@
      The winner node determines the place of each new vector on the SOM.
-     Based on the location of the new vectors on the SOM, they can be compared with the original data set. %20170122PB: unclear what "they" refers to
+     The location of the new vectors on the SOM allows them to be compared with the original data set. 
      Sections~\ref{sec: 1Dv} and ~\ref{sec: 2D} show the results of galaxy spectral classifications using networks trained on template spectra.}
-
-\subsection{K-means clustering}
-\label{sec: kmeans_method}     
-In the K-means method, the user decides in advance on a number of clusters, $K$, which cannot be greater than the number of data points. 
-The algorithm randomly chooses $K$ random points to be the centroids of the clusters.
-Then it finds the data points that are closest to each assumed centroid and clusters them together.
-The mean values of the data points assigned to each cluster are calculated and become the new centroid of the cluster. 
-The algorithm finds new clusters based on the new centroids and repeats the procedure until it converges.
-We used \textsc{matlab} K-means library~\citep{Seber84, Spath85}, written for \textsc{matlab2015b}, to perform the K-means clustering.

### 2017-05-21 sections0.08/results0.08.tex
Pualine'e edits on version 8

@@
 
-       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is correct, in this section we examine the relations between median properties of the galaxies in each neuron.
+       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is meaningful, in this section we examine the relations between median properties of the galaxies in each neuron.
 
@@
 
-       One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
-       Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. 
+    % This is better but could perhaps still use work    
+       \textbf{One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification.
+K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
+Ordering is important in the case where the physical causes of the differences between classes/clusters are unknown.
+Average properties of objects within clusters (possibly from data not used for classification) can be used to test hypotheses about the physical differences.
+       Figure~\ref{fig: props_vs_props} shows that the SOM ordering also corresponds to the ordering of the physical properties of the galaxy models used to make the classified spectra. 
        The median properties of the spectral groups change on going from one end of the SOM to the other.
-       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
-       Therefore, by using the SOM method, we not only study galaxies in different clusters, we also can study the trends between them as well.
+       Therefore, by using the SOM method, we can study not only how galaxies group into spectral clusters, but the trends between the clusters as well.}
 

### 2017-06-17 answer_to_second_referee_comments.tex
Moving around text, working on ref letter

@@
 
---- We have reorganized the last two paragraphs of Section 1 to better describe the goals of the investigation. 
+--- We have reorganized the last two paragraphs of Section 1 and added text to better describe the goal of the investigation: comparing different methods of classifying galaxy spectra against templates, with a focus on self-organizing maps.
+We have added additional text in Sections 4.2 and 5 comparing 1D and 2D SOMs.
 %TBD: 
@@
 To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.
-%--- should I put the figure from the previous paper, maybe Noll09 one??! 
-% I don't think including the figure from Noll09 will be enough. It's the performance metric that's critical here.
+--- We selected several performance metrics.
+Two of them (an agreement score and the Fleiss kappa score) measure the degree to which the classifications agree.
+As a measure of the classification performance, we calculate the dispersion in properties of the galaxies in each class and compare these values between methods.
+The results of this analysis are discussed in Section 4.4.
 
 I had suggested comparing the results to a simple nearest-neighbor classification baseline, but this was not addressed.
-%--- why could not I find anything about it in the 1st report?:(
-%20170122PB: it's there but well-hidden - the sentence which includes "what performance does one get simply by assigning each of the 142 spectra to its closest match from the 12 templates"
---- We apologize for missing this suggestion in the previous version. We have now included this in the analysis and the results are reported in Section XX.
+--- We apologize for missing this helpful suggestion in the previous version. This is now part of the analysis described in the paragraph above; the results appear in Section 4.4.
 
@@
 But the paper must then explain why this is important or valuable.
---- We have added text to the end of both Section 4.1 and Section 5 explaining the utility of an ordered clustering.
+--- We have added text to the end of both Section 4.2 (formerly section 4.1) and Section 5 explaining the utility of an ordered clustering.
 
@@
 How can I tell from this figure?
---- % need a comment here
+--- The text describing the differences between the K-means and SOM classification of the templates (in particular, which templates are grouped together by the two methods) has been rewritten and moved to Section 4.1 (newly added in this revision).
 
@@
 --- This is a reasonable criticism and we have ... 
+%TBD: need to finish this
 

### 2017-06-17 main.tex
Moving around text, working on ref letter

@@
 \usepackage{pgffor}
+\usepackage{commath}	% Extra maths symbols
 
@@
 \author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
-srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, P.~Barmby$^{1,2}$\\
+srahma49@uwo.ca}, H.~Teimoorinia$^{3,4}$, P.~Barmby$^{1,2}$\\
 $^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
 $^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
-$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
+$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
+$^{4}$NRC Herzberg Astronomy and Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7, Canada }
 \maketitle

### 2017-06-17 main_all_together.tex
Moving around text, working on ref letter

--- 2016-05-13 sections0.02/results0.02.tex
@@
+\documentclass[useAMS,usenatbib]{mn2e}
+\bibliographystyle{mn2e}
+
+\usepackage{amsmath}
+\usepackage{commath}
+\usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{times}
+\usepackage{float}
+%\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{multirow}
+\usepackage{color,soul}
+\usepackage{import}
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+\usepackage{pdflscape}	% Landscape pages
+%\usepackage{booktabs,fixltx2e}
+\usepackage[flushleft]{threeparttable}
+
+\newcommand \Spitzer {{\it Spitzer }}
+\newcommand{\boldit}[1]{\textbf{\mathversion{bold}#1}}
+
+\newcommand \aaj {A\&A}
+\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
+\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
+\newcommand \afz {Afz}%: Astrofizika
+\newcommand \aj {AJ}%: Astronomical Journal (the)
+\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
+\newcommand \apj {ApJ}
+\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
+\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
+\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
+\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
+\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
+\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
+\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
+\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
+%\newcommand {Nature}%(do not abbreviate)
+\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
+\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
+\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
+\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
+%\newcommand {Science }%}%(do not abbreviate)
+\newcommand \sva {SvA}%: Soviet Astronomy
+\newcommand \aap {APP} %:American Academy of Pediatrics
+\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
+
+%\defcitealias{Hossein12}{T12}
+
+\begin{document}
+% TITLE
+\defcitealias{Hossein12}{T12}
+
+\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
+\author{rahmani.sahar }
+\date{\today}
+\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1}$\thanks{E-mail:
+srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1}$\\
+$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
+$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
+\maketitle
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%abstract
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+
+\begin{abstract}%% (Must be 250 Words)
+% In this paper, we introduce a new method of clustering of high red-shift galaxies, based on their spectral energy distributions (SED)s.
+We use unsupervised self organizing map(SOM) to train an artificial neural network to categorize SEDs of galaxies.
+We utilize as spectral template as a training set, and trained networks to be able to clustered galaxies based on the template.
+We cluster a sample of 142 galaxies with 0.5< z <1 using the trained network.
+We train networks with various sizes and properties to investigate the nature of the 142 sample galaxies.
+For each network, we cluster the sample of 142 galaxies and visualise their properties.
+In order to test new classifications,we compare physical properties of the galaxies in each cluster.
+We compare our results with  clustering  results  from  other  artificial  neural  networks,  and  with  the  original template classification.
+We conclude that SOM is a very useful method to be used in classifying galaxies based on their SEDs.
+It can be used to find morphology of the high red-shift galaxies, and find a new class of SEDs.
+In this paper, we introduce a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
+%Artificial neural networks provide us a reliable method to cluster SEDs of galaxies.
+We use an unsupervised self organizing map(SOM) as a training method to train networks with a sample of galaxies with SEDs between FUV to NIR wavelengths, which their morphological types are known.
+Since information that can be extracted from each network depends on the size and dimension of the trained networks, in this project we train networks with different grids in 1D or 2D.%%???
+We visualise each trained network using a new version of SOM plots.
+To test trained networks, we cluster a sample of 142 galaxies with 0.5 < $z$ < 1 using each of the trained networks.
+We plot average SED of SEDs of galaxies in each neuron in 1D networks, to investigate the nature of galaxies in new clusters.
+For each network, we visualise the properties of galaxies in each neurons. %%%% combine 94 and 93 
+We compare mean physical properties of the galaxies in each neuron such as age, specific star formation rate, stellar mass, and FUV extinction, with each other and found a tight correlations between them.
+Comparing our results with clustering results from supervised artificial neural networks, show us using SOM we can classify galaxies in between types of original spectral types. %%rephrase
+As a result we have a power tool to classify spectra of galaxies based on their SEDs which also can  identify galaxies with a new shape of SEDs.
+
+%%%% SR20160512: I do not like it! But I do not know how to fix it. I already wrote at least 4 version of it. I need help with this one:((
+
+%%% what is the problem we are trying to solve in general! why do we want o classify thing in general, and what is wrong in exciting classification scheme
+
+\end{abstract}
+\begin{keywords} 
+ galaxies: high red shifts, galaxies: spectral energy distribution, methods: observational, methods: statistical, data mining, methods:data analysis
+\end{keywords}
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%Intro
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+\section{Introduction}
+\label{sec: intro}
+%General information about SEDs
+All information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on the spectral energy distribution (SED) of that galaxy.
+We can determine some physical properties of galaxies by properly modeling various features observed in their SEDs.
+The general shape of the SEDs can be used as an identifier of the morphological type of the galaxies.
+Considering the main features of the SEDs galaxies can be categorized in two main groups: elliptical, or spiral.
+Each group has its own characteristic features and can be divided into many sub-branches.
+
+%%Creating templates and NIR_UV templates
+Several attempts have been made to composite a thorough template for categorizing the spectral type of galaxies using data from nearby galaxies~\citep[e.g.][]{Kinney93}~\citep[][hereafter K96]{Kinney96}~\citep[][]{Bershady00,Mannucci01}.
+Based on their usage, these templates are restricted to certain wavelengths.
+In near-infrared (NIR) to ultraviolet (UV) domain of wavelengths (the region where output of stars peaks), SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, wide range of the stellar population, some information on interstellar medium (ISM)'s absorption and emission lines, and extinction from ISM of the galaxies.
+
+% categorizing galaxies based on their SED
+
+Attaining high-resolution data and detailed SEDs has been made possible due to advances in imaging techniques, and photometry and spectroscopy devices.
+This has helped to see the more detailed SEDs, which made classification of galaxies more complex.
+Since no two galaxies, even with the same morphology, have exactly the same properties, classifying the SED of the galaxies using the templates are a challenge.
+Many fitting methods are developed and used to find the best matches of template for each SED.
+$\chi^2$ minimizing method is the most commonly used method to do so. 
+Artificial neural networks (ANNs), K-mean clustering, and principal component analysis are the other methods to cluster and classifying the morphological type of the galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
+
+%ANNs
+ANNs are very powerful tools to use in data processing and pattern recognition problems.
+Their information processing method was inspired by the way neurons in human brains work.
+An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
+It uses a set of training methods to learn about a non-linear and complex relations between input and output data and how to apply it to new sets of data.
+Studies show that ANNs provide better fitting than minimizing chi-squared and would be an alternative choice for fitting data~\citep[e.g.][]{Marquez91,Moayed09}.
+In cases that both methods show the same correlation, ANNs still are a better method of fitting due to their faster results on large databases \citep[][]{Gulati97}.
+
+%Training methods for networks
+Neural networks can be trained using two methods; supervised and unsupervised.
+In supervised method, a neural network would be trained using input data based on desired outcome.
+This method is very useful for classification of data with specific target values (e.g. any pattern recognition with known templates).
+On the other hand, in unsupervised method there is no prediction of output data.
+This method classifies data based on their underlying structures and hidden variables.
+The unsupervised method is a very helpful method to knowledge discovery of your data, or when the underlying structure of data is not well established (e.g. producing a template of SED of galaxies).
+
+%SOM
+Kohonen Self organizing map (or self organizing map, SOM) is an unsupervised neural network for mapping and visualizing a complex and non-linear high dimension data introduced by~\citep{Kohonen82}.
+The SOM is a technique that shows a simple geometry relationship of a non-linear high dimension data on a map \citep{Kohonen98}.
+%SOM in Astronomy
+The utilization of the SOM in astronomy dates back to 1990s. 
+\citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} were among the first studies in astronomy that used SOM for their studies.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method have been used in various aspects in astronomy \citep[e.g.][]{Maehoenen95, Miller96,Andreon00,Balastegui01,Rajaniemi02,Brett04,Scaringi09}.
+%20160509PB: suggest starting a new paragraph here, with an introductory sentence about galaxy spectra.
+%SR20160512: I start new paragraph after the next sentence not here.
+\citet{Geach12} used COSMOS data to demonstrate two of main applications of SOMs; object classification and clustering, and photometric redshift estimation. 
+The later one was subject of many studies \citep[e.g.][]{Kind14a}.
+
+%SOM in Astronomy continued.
+Spectrum of a galaxy is a combination of spectra of million stars and clouds inside the galaxy.
+Therefore, large spectra data sets contain information of billions of stars and other objects inside galaxies, and needs to be studied carefully. %%%EEEHHHH
+\citet{In12} introduced a new clustering tool, which is based on the SOM method for analysing large data of spectra.
+They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09}
+to test their tool, and created very large SOMs to analyse the type of spectra/objects.
+They also generated SOMs from quasars' spectra in order to find unusual types of quasars' spectra.
+Later \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys and found a new class of quasars.
+The other application of the SOM is to find outliers or errors in the data.
+\citet{Fustes13} produced a package based on SOM to classify spectra from GAIA survey that were previously classified as "unknown" by SDSS pipeline.
+The package recognizes an astronomical object from artificial errors, and then classifies the object based on its spectra.
+
+%What T12 did
+~\citet[][hereafter T12]{Hossein12} classified SEDs of this sample of galaxies using supervised neural network method, based on the spectral template presented by K96.
+With supervised method, they could only classify SED of the 105 out of 142 galaxies.
+The SED of the 37 galaxies from their samples could not be matched with any of those in the K96 templates. 
+In order to classify the remaining 37 galaxies, they combined spectrum of the K96 templates.
+This procedure showed that, not a single type of galaxies in K96 template could describe the SED of any of those 37 galaxies.
+Since the SOM have the freedom of classifying objects in between the known classes, it be applied on this data to find the best SED class for the 37 galaxies.
+T12 also showed that there are tight correlations between physical properties of galaxies and these correlations might be different for each type of the galaxies.
+
+%What we did
+In order to compare supervised and unsupervised methods directly, we used exactly the same data as T12 used.  
+First, we trained SOMs using data from K96 and compared our classification with K96 galaxies classification.
+Then, we used the trained network to classify the SEDs of 142 galaxies with 0.5 < $z$ < 1 from T12 paper.
+Same as T12, We also plotted the properties of the T12 galaxies based on the new clusters and compared them with previuse works.
+In Section $\S$~\ref{sec: data}, we present the data that we used to train and test our networks.
+We describe the SOM methos in Section $\S$~\ref{sec: method}.
+The results of the SED classifications and comparing them with previous studies are shown in Section $\S$~\ref{sec: result}.
+In Section $\S$~\ref{sec: summary}, we present the summary of our results and the future works in this subject.
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%DATA
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+
+\section{DATA}
+\label{sec: data}
+We used SED templates from K96, to train neural networks.
+To test the trained networks, we used SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
+Following of T12 work, we chose these two sets of data to not only show the application of SOMs in SED clustering, but also to easily compare both supervised and unsupervised methods.
+
+ \subsection{Kinney spectral model}
+     \begin{figure}
+        \centering
+        \includegraphics[width=0.5\textwidth]{images/k96.jpg}
+        \caption{K96 spectra template for 12 types of galaxies from T12 paper (Fig.
+1 in T12).Type of each template is shown in each frame.
+Plots B, E, S0, Sa, Sb and SC show spectra that belongs to early type galaxies.
+Starburst galaxies spectra are indicated with SB 1 to 6.
+Higher numbers represent more intrinsic colour extinction.}
+        \label{fig: k96}
+    \end{figure}
+
+    K96 used UV-optical spectra of 70 star forming and quiescent nearby galaxies to produce a template that contains 12 types of SEDs.
+    These templates are widely used in many studies to determine morphological type of galaxies, or find properties of specific types of galaxies in many studies \citep[e.g.][]{Shakouri16,Paiano16,Laporte16,Holden16}.
+    K96 mentioned that one of the usage of these templates can be classifying the SED of the high redshift galaxies. 
+    The 12 types of spectra are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}).
+
+    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
+    Bulge group represents galaxies similar to M31 and M81, which their UV and optical spectroscopy dominated by the stellar population in their bulges.
+
+    The starburst galaxies are divided into six groups (SB1 - SB6) based on their intrinsic extinctions ($E(B-V)$). 
+    As it is clear in the Fig.~\ref{fig: k96}, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.
+
+    K96 spectra spans from $\sim1200-10000$\AA with resolution of $\sim 10$\AA~.
+    However, we only used data between $\sim1200-8000$\AA~to train our networks. 
+    This wavelength range was chosen due to availability of flux information in those wavelengths for all 12 types of galaxies.
+    In early type galaxies' spectra (B to Sb), the spectrum is redder and strong absorption lines, and 4000\AA~break is distinguishable. 
+    While SEDs of starburst galaxies are more flat on the optical and NIR part than early type one and show strong emission lines.
+    For more details on each spectral type, we encourage readers to see K96 and references therein.
+
+ \subsection{SED and Properties of the sample galaxies} 
+    T12 selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field.
+    For each galaxy, robust spectroscopic redshift and photometry data from the Good-MUSIC catalogue had been known.
+    The 142 galaxies had been selected in T12 due to availability of data from HST/ACS; VLA/ISAAC; and \Spitzer/MIPS and IRAC for whole galaxies. 
+    Data from these instruments were necessary in order to have a complete picture of stellar population and SFR.
+    The photometry data contain information of the galaxies in 10 - 13 filters with the wavelength range of $\sim 0.4-24 \mu$m in the observed frame.
+    T12 matched the resolution of the photometry data with K96 data and used these photometry data as inputs for Code Investigating GALaxy Enmission ({\em CIGALE} code;~\citep[][hereafter N09]{Noll09}) to generate the best fitted SED for each galaxy.% as well as some of the physical properties of the galaxies.
+
+    {\em CIGALE} is a valuable tool to investigate the properties of the galaxy using UV to IR wavebands.
+    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei's optical spectral templates to model SED of the galaxies.
+    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by N09.
+    T12 produced the best SED match, with wavelength interval of 910 to $\sim 8E9$\AA~, for each galaxy.
+    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55} and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of galaxies such as age, and stellar mass.
+    Some of these properties are shown in Tab~\ref{tab: props}.
+    In the Sec.~\ref{sec: 1D}, we studied these properties for each categorization.
+    More details on creating SEDs and extracting information about galaxies properties using {\em CIGALE} can be found in N09 and T12.
+
+    \begin{table}
+\caption[]{Description of the properties of T12 galaxies; the output result of {\em CIGALE}}     
+\label{tab: props}
+\centering
+\begin{tabular}{l l l}
+\hline\hline
+\noalign{\smallskip}
+Par. & Unit & Description\\
+\noalign{\smallskip}
+\hline
+\noalign{\smallskip}
+$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
+$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
+$f_\mathrm{burst}$ & --- & mass fraction of \\
+& & young single population (SP) model \\
+\noalign{\smallskip}
+$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age \\
+\noalign{\smallskip}
+$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
+SFR & M$_\odot$/yr & instantaneous SFR  \\
+$A_\mathrm{FUV}$ & mag & attenuation at 1500\,\AA{} \\
+\noalign{\smallskip}
+\hline
+\end{tabular}
+\end{table}
+
+    For testing the created networks, we used SEDs that were produced by T12. 
+    These SEDs are publicly available in the form of flux per rest frame wavelength in a wide range of wavelengths.
+    Since we have used the T12 SEDs to test trained network, we only used the part of the SEDs that have a same wavelength range as K96 templates.
+
+ %%%%SR160611: The following is the Hossein's answers to the questions that you asked in the data section; Since, we did not used the spectra data here (we only used generated SEDs and information that was derived from SEDs) ,I assumed it is unnecessary to talk a lot about spectroscopy data.
+But, if you think it would help to understand the subject better, I will add those information to data section.
+
+%  Is the data vector for each object a list of fluxes (flux densities) as a function of (rest) wavelength? I think we discus this question so I skip it.
+%  Same wavelengths for every object? Yes
+%  What is the spectral resolution? It depends on the type of spectra we use in T12 see
+% below for more information.
+%  Do the spectra include the whole galaxy or just the central part? For observed 142
+% galaxies: whole spectra because they are in high redshift. For K96 they are co-added
+% spectra from different parts.
+%  Does the resolution match with K96? We match them to K96, see below.
+%  What is the coverage of spectra? See below.
+%  Do these galaxies have spectroscopic redshifts, or were redshifts derived from
+%   photometry?" All 142 galaxies have robust spectroscopic redshift.
+% For more clarification about spectra used in T12: We have three sets of spectra.
+% 1 – observed spectroscopic spectra.
+They are used just for extra independent validation; see figure 17 from T12.
+This validation is nothing to do with network validations.
+The useful wavelength range (of
+% FORS2 spectrometer) is 4800−10 000 Å, the nominal resolution is R = λ/Δλ = 580, which corresponds to
+% a spectral resolution of ∼13Å.
+We use only range [3500-5100] because all the 142 observed spectra have information in this interval (some of them have no spectral information in 8000A, for example).
+In T12 you can also find this that can help: “The rest-frame spectra of the sample all include spectral information
+% ∼3500–5100 Å. This interval brackets the important features such as the 4000Å break and also the strong emission
+% lines such as [O ii]λ3727, λHβ 4861, and [O iii] λλ4959, 5007.
+The spectroscopic data for the sample galaxies contain different spectral types from starbursts (with a flatter continuum and stronger emission lines) to early-type galaxies (with a redder continuum, strong absorption lines, and large 4000Å break.”
+% 2- k96 Model spectra which are for training.
+The spectra cover the interval ∼1200–10000Å and have a resolution of∼10 Å.
+We use only interval 1200-7500A.
+because all the 12 K96 spectra have information in
+% this interval (some of the spectra have no information in 9000A, for example).
+% 3– The Maraston’s models (SEDs): For each galaxy (from 142) we obtain a best Maraston spectrum (SED) by fitting photometric data to the models.
+Mraston’s models range very extended wavelength interval (from UV to far IR) with different resolution in different part of a given spectrum.
+For example resolution in IR is 100A and in optical ~3-5A.
+The best resolution is related to the optical part (3-5A and we convert all to 10A i.e., to resolution of K69).
+We cut the best 142 spectra in interval [1200-7500] like K96 for ANN validation or test.
+(If we had spectral information for all K96 spectra in the interval 1200-10000A, for example, then we would cut all 142 SEDs in 1200- 10000A).
+So if you find a new training set (other than K96 which we talked about that in our skype chat) and if they had information in 1000-15000A, for example, then we would cut the SEDs in this new interval for validation.
+% As a summary: as you know (better than me!) we use K96 as training set and 142 SEDs as validation (or test) set.
+When we obtain the class of each 142 galaxies (in fact 105 galaxies!
+You are improving this number to 142 in your paper) then we use 105 observed spectra to make figure 17 from T12.
+The co-added observed spectra in a certain class match with the associated K96 spectra in the same class (i.e., an independent validation).
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%Method
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+
+\section{METHOD}
+\label{sec: method}
+ \subsection{Self Organizing Maps}
+ \label{sec: som}
+
+ The SOM is a clustering method which reduces the dimension of data to lower dimensions, usually 1 or 2D, while preserving topological features of the original data.
+ Results of SOM contain nodes (neurons) that arranged in 1D or 2D arrays \citep{Kohonen98}.
+
+ Each node may contain one or more samples from input data and distance between nodes represents similarity or dissimilarity of underlying samples. 
+ In the way that similar data are closer together in the array and the further nodes go from each other, the more dissimilarity appears between their samples.
+ A weight vector ``\boldit{W}" with same dimension of the input data associates with each node which will be changed during the process and has a key factor in a position of nodes in the map.
+
+ \cite{Geach12} presented the application of the SOM and demonstrate the algorithm of the SOM in detail.
+In this section we are going to talk briefly about the algorithm of the SOM, how we create our maps and a test model which will help to interpret our results.
+ \subsubsection{Algorithm of SOM} 
+ \label{sec: algorithm}
+     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on S1 by S2 map. 
+     We start by creating S1 $\times$ S2 empty neurons. 
+     The initial arrangement of these neurons depends on a map's topology provided by users.
+     In the case of the 1D maps, since each neuron has two immediate neighbours the topology of the map does not have any effect on the final result and we can choose any topology.
+     However, in 2D maps, the shape of the neurons specifies the number of the immediate neighbours for each neuron and it is up to user that which shape is more suitable for their data.
+     In this paper, we chose hexagonal topology which gives each neuron six neighbours, and causes more interactions between neurons.
+     Then, a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
+     The process of creating SOM, happens over series of $N$ iterations. 
+     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+      In each iteration SOM code:
+     \begin{enumerate}
+        \item Chooses a random vector from our data set ($V_i$).
+        \item Calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
+This neuron is the winner node and is called the Best Matching Unit (BMU).
+        \item  Computes the radius of the neighbourhood of the BMU to find nodes within this radius.
+The weight vectors of these nodes will be affected in the next steps.
+This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
+        \begin{equation}
+            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
+        \end{equation}
+        where $\tau$ is a decay constant and usually set to be the same as the number of iterations, $N$.
+$r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively.
+        \item Changes the weight vectors of the BMU, and all the nodes within $r^t_{BMU}$ as:
+        \begin{equation}
+            \label{equ: weight adj}
+            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
+        \end{equation}
+        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
+$R(t)$ determines how the weight of nodes in the neighbourhood of BMU will change.
+        \item  Repeats these steps for $N$ times.
+     \end{enumerate}
+
+\subsection{Creating SOM}
+\label{sec: create_som}
+     In order to create SOM, we used {\tiny MATLAB} neural network 
+     toolbox~\citep[NNT,][]{matlabtolbox}.
+     %%Sr160611: Last time I got the following note from the MNRAS editor:
+     %"Please note that computer software/programming lan- guages must be styled in SMALL CAPITAL LETTERS, according to journal style. Please check and correct this paper accordingly."
+     SOM in {\tiny NNT} can be created by {\tiny NEWSOM} or {\tiny SELFORGMAP} library which both work in two phases. 
+     Phase one is the ``ordering phase". 
+     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by the user. 
+     The ordering phase continues for the requested number of iterations.
+     During the iterations, the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to tuning phase neighbourhood distance which both of the numbers set by the user.
+     In the ordering phase, the changes in the learning factor and the neighbourhood distance adjust with the number of the iterations, in the way that at the last iteration, these two values reach to the initial values for the second phase.
+
+     The second phase is the ``tuning phase".
+     In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
+     This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
+     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning to happen slowly. %cite kohenen book?!
+     We chose the number of epochs the tuning phase to be 3 times more than the number of epochs in the ordering phase.
+
+     To show our results, we used two of the {\tiny NNT}'s built-in plots.
+     These plots, which are evolved version of old SOM plots, are designed to show distance between each clusters more clear.
+     A Hits map, which shows the number of the times each neuron become the winner (hits), and a distance map, which shows the same neurons as the hits map and the distance between them.
+     In the maps, the purple hexagonal shape areas represent the neurons.
+     The distances in a distance map are shown by the grey cycle colours.
+     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is a small distance between neurons.
+     In hit maps, neurons with zero hit left empty.
+
+    Size of SOM maps is arbitrary and there is no rules or restrictions on choosing the size of the maps. 
+    Although \cite{Vesanto05} suggested that the total number of  $5\sqrt{n}$ neurons provides the most sufficient size, users usually choose the size of grids based on their data set and their usages of the results.
+
+\subsection{Mock sample}
+
+         \begin{figure}
+            \begin{subfigure}[b]{0.5\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images0.01/sample/sample2_dist.png}
+            \end{subfigure}
+            \hfill
+            \begin{subfigure}[b]{0.5\textwidth}
+                \includegraphics[width=\textwidth]{images0.01/sample/sample2_hits.png}
+            \end{subfigure}
+            \caption{SOM of the mock sample.
+In both plots, the axes show the position of the neurons.
+Hexagonal shapes represent the neurons.
+The upper plot is a distance map.
+The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one.
+The lower plot is a hit plot.
+It represents the number of samples in each neuron, while the empty with neurons means zero hit.
+In this sample the 27 galaxies clustered in 4 groups of 8, 7, 6 and 6 galaxies.}
+            \label{fig: sample}
+        \end{figure}
+
+ We created  a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analysed.
+ The mock sample contains two information from each galaxy; The type of galaxies: type 1 or type 2, and either they are high or low star forming galaxies. 
+ We generated a SOM with the size of $10 \times 10$ using the same initial values mentioned in the Section ~\ref{sec: create_som}.
+
+ Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
+ The upper plot is a distance map. 
+ The axes show the position of the neurons in a $10 \times 10$ network.
+ The lower plot in the Fig.~\ref{fig: sample} shows a hit map.
+ On this map similar to the distance map the axes show the position of the neurons where the hexagonal shapes are the neurons.
+ The purple neurons with a number on them shows the number of galaxies in them.
+ Colour coverage of neurons is different and depends on the number of the hits on the sample.
+ The neuron with the maximum number of hits is completely coloured while the empty neurons are white.
+
+Using this method, as we predicted, we were able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
+The upper plot in the Fig.~\ref{fig: sample}, clearly shows this division.
+In that plot, the upper part belongs to high star forming galaxies, while the lower part belongs to the low star forming galaxies.
+The left part of the plot, is where type 1 galaxies belong to and the right side is for type 2 galaxies.
+Grey to black colours shows the border between regions.
+The lower plot in Fig.~\ref{fig: sample} shows only 4 neurons out of 100 were occupied. 
+8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
+Since the input data are so simple, each entry only could get either 0 or 1 as a type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
+
+We can conclude that although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed only in four groups.
+This network is considered as a train network, and if there are any data set with similar entries, we can use this network to cluster the new data set.
+
+As we show in the following sections, in the real world with the real data, we never have two galaxies with exactly the same information, we have more than 2 dimensions, and more galaxy types. 
+Therefore, if the network has high enough neurons, the input data would eventually separate from each other and cluster into smaller and smaller groups. 
+However, if the information of the input data is very similar to each other, the number of neurons is going to be much higher than the number of input samples, to be able to separate the groups from each other.
+Therefore, it is up to the users that decide the similarity or dissimilarity between the input data based on number of neurons.
+
 %----------------------------------------------------------------------------------------
@@
         \label{sec: 1Dt}
-            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and starburst.
+            To start our clustering, we assumed that galaxies can be divided only in two general types; quiescent and starburst.
             In this case, we generated a network with only two neurons.
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
+                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                 \end{subfigure}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
+                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                 \end{subfigure}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
+                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_3.png}
                 \end{subfigure}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
+                     \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_3.png}
                 \end{subfigure}
@@
                 \centering
-                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
+                \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
             %\caption{$1\times22$ weight map}
@@
             \begin{subfigure}[b]{\textwidth}
-                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
+                \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
              %\caption{$1\times22$ hits map}
@@
             The fact that the galaxies had to have 22 different neurons till be divided into 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
-            These small differences might be very small.
+            %These small differences might be very small.
             Therefore, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
+                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                     %\caption{$1\times2$ weight map}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by2.png}
+                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2.png}
                      %\caption{$1\times2$ hits map}
@@
             Since in this network galaxies forced to be divided into maximum two groups, for any SED between these two groups the SOM must decide that each galaxy belongs to which group based on strongest features of its SED.
-            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as starbursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
+            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as starbursts while galaxies with strong 4000\AA~break, but no emission lines categorized as the early type.
             Increasing the size of the SOM helps to solve the problem of the galaxies which have features of both groups.
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_3.png}
+                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_3.png}
                     %\caption{$1\times2$ weight map}
@@
                 \begin{subfigure}[b]{0.5\textwidth}
-                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by3.png}
+                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by3.png}
                      %\caption{$1\times2$ hits map}
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22_n.png}
+                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_22_n.png}
                     %\caption{$1\times2$ weight map}
@@
                 \begin{subfigure}[b]{0.9\textwidth}
-                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
+                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by22.png}
                      %\caption{$1\times2$ hits map}
@@
             By comparing the upper part of Fig.~\ref{fig: 1by22V} with the lower part of Fig.~\ref{fig: 1by22T}, we can see that the occupied neurons are not necessarily the same.
-            If a group of the T12 galaxies fills the same neurons as the K96 galaxies, we can conclude that these galaxies have SEDs very similar to the SED of one of K96 galaxies.
-            Whereas, we can conclude that a group of the galaxies has properties between the two groups if they fill a neuron which is empty and places between two categories of galaxies in Fig.~\ref{fig: 1by22T}.
+            If a group of T12 galaxies fills the same neurons as the K96 galaxies, we can conclude that these galaxies have SEDs very similar to the SED of one of K96 galaxies.
+            Whereas, we can conclude that a group of galaxies has properties between the two groups if they fill a neuron which is empty and is placed between two categories of galaxies in Fig.~\ref{fig: 1by22T}.
             However, the colours between these neurons in the upper side of Fig.~\ref{fig: 1by22T}, establishes that those galaxies are more similar to which group.
@@
             \centering
-            \includegraphics[width=0.5\textwidth]{../images0.01/1d/props5.png}
+            \includegraphics[width=0.5\textwidth]{images0.01/1d/props5.png}
             \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$ (balck circles), $1\times4$ (blue diamond), and $1\times8$ (red triangles) networks.}
@@
        % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
-%PB20160510: I would say something more like "the SED categories represent a continuum of physical properties".
-Of course the physical properties were derived from the SEDs, so maybe this isn't so surprising and you could mention that as well.
-        %%%SR20160611: Sorry I am not sure that I understand this comment?
         Considering results from Fig.~\ref{fig: props}, we can clearly see that separating galaxies based on SED types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs.
@@
         \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/1d/f1.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/1d/f2.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/1d/f3.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/1d/f4.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/1d/f5.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/1d/f6.png}
+            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
         \end{subfigure}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_12.png}
+            \includegraphics[width=\textwidth]{images0.01/2d/dist_12_by_12.png}
         \end{subfigure}
@@
             \centering
-            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_self_org_res12.png}
+            \includegraphics[width=\textwidth]{images0.01/2d/dist_12_by_self_org_res12.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_12.png}
+            \includegraphics[width=\textwidth]{images0.01/2d/hit_v_12_by_12.png}
         \end{subfigure}
@@
         \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_self_org_res12.png}
+            \includegraphics[width=\textwidth]{images0.01/2d/hit_v_12_by_self_org_res12.png}
         \end{subfigure}
@@
     %no quantitative way to analyse the data?!
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%Summery
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+\section{SUMMARY AND FUTURE APPLICATIONS}
+\label{sec: summary}
+
+Self organizing maps can be used to classify celestial objects (i.e. stars, quasars, spectra of galaxies, light curves, etc.).
+We showed that we can create various networks with different sizes/dimensions based on information we need from the data. 
+If a broad and general classification is required, networks can have one dimension with few number of neurons.
+While if we need classifications based on differences in more details, we can use a higher number of neurons.
+Since the SOM codes does not work with uncertainty of input parameter, sometimes too much attention to details can cause problems in classifications. 
+Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
+for using SOM method, one should be careful about these small differences and consider in order to separate two groups from each other, how much details do they need to pay attention to.
+
+We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
+By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
+since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
+We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.
+
+The sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
+One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
+The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
+A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
+T12  have used a supervised training method, and trained networks with K96 SED template.
+Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
+However, they could not classify 37 out of 142 galaxies in the sample.
+The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or between those types. 
+Therefore, we classified all 142 galaxies of our test sample.
+We plotted the properties of the galaxies in test sample using new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
+We also showed he properties of the galaxies in each groups is in good agreement between their morphological types.
+
+\section*{ACKNOWLEDGMENTS}
+S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. 
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%biblio
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+\bibliographystyle{mnras}
+\bibliography{ref_mining_h.bib}
+
+\import{sections0.0/}{apps0.0.tex}
+\end{document}

### 2017-06-17 sections0.08/intro0.08.tex
Moving around text, working on ref letter

@@
 In the near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where the energy output of stars peaks), the spectrum\footnote{In the remainder of this paper, we are concerned with a limited range in wavelength, and so we refer to spectra rather than spectral energy distributions.} contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
+\textbf{TEXT HERE RE: WHY WE CARE ABOUT CLASSIFYING
+(1) do galaxy spectra form a continuous distribution or can they be separated into discrete groups as represented by the \citetalias{Kinney96} templates?
+(2) if the distribution is continuous, how do galaxy properties vary along the spectral distribution?
+}
 
@@
 %SOM
-A Kohonen self-organizing map (also called self-organizing map, or SOM) is an (semi)-supervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
+A Kohonen self-organizing map (also called self-organizing map, or SOM) is a (semi)-supervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
 It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
-%%%After_second_Referee_report
 \textbf{The training of a self-organizing map is fully unsupervised.
@@
 %%%%After second referee report
-The goal of this work is to compare SOM-based classification of galaxy spectra to two other methods: supervised neural network and (unsupervised) K-means clustering.
-The questions we want to answer are: (1) do galaxy spectra form a continuous distribution or can they be separated into discrete groups as represented by the \citetalias{Kinney96} templates?
-(2) if the distribution is continuous, how do galaxy properties vary along the spectral distribution.
+\textbf{
+The goal of this work is to compare different methods of classifying galaxy spectra against templates, with a particular focus on self-organizing maps. 
+The questions we want to answer are: 
+(1) What is the degree of agreement between $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
+(2) Are certain spectral types more (or less) consistently classified by the different methods? 
+(3) To what extent do the average properties of galaxy classes represent a continuous distribution of physical properties?
 We analyze the same sample of 142 galaxies with $0.5 < z < 1$ as 
 \citet[][hereafter \citetalias{Hossein12}]{Hossein12}, who classified the spectra using a supervised (multi-layer feed-forward) neural network method with the \citetalias{Kinney96} templates.
-This method could only match 105 out of the 142 galaxies directly to the \citetalias{Kinney96} templates; classifying the remaining 37 galaxies required combining template spectra.
+For each of the 142 galaxies, we find the best chi-squared fit among the 12 templates  to have a base for comparing the methods' performance.
+We also use the Fleiss Kappa index \citet{Fleiss71} to test interrater reliability  
+between the three methods.
+}
+
 %not sure if we want this sentence or not

### 2017-06-17 sections0.08/results0.08.tex
Moving around text, working on ref letter

@@
 \label{sec: result}
+
+% Sahar: might have to move some of this text around
 
@@
     We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.
+
+\subsection{One-dimensional self-organizing maps and K-means clustering: templates}
+
+\begin{figure*}
+\begin{subfigure}[b]{0.49\textwidth}
+\centering
+\includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_kinney.pdf}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.49\textwidth}
+\centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_som.pdf}
+\end{subfigure}
+\caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right).
+Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
+\label{fig: som_k_means_4}
+\end{figure*}
+
+        We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters \textbf{and then assigned each of the 142 galaxies in the \citetalias{Hossein12}  sample to the cluster with the closest centroid.}
+        %We measured distance between the centroid of each cluster and spectra of each galaxy to classify galaxies using K-means method.
+
+       % For a direct comparison between clustered spectra and templates, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as unrelated points in a high dimensional space.
+        %Using the spectral angle distance, the spectra are treated as connected entities, which helps the shapes of the spectra to be recognized. 
+        %In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each point.
+        %(Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well.
+        %Hence, there is no need to use the spectral angle distance in the SOM method.)
+    Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra in 4 groups using both K-means and SOMs.
+        In the K-means method empty clusters are not allowed. 
+        Hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
+        Both methods shown in Fig.~\ref{fig: som_k_means_4} separated the most starburst-like and quiescent galaxies in a similar manner.
+        However, they show discrepancies for spectral types between the extreme cases.
+
+%Sahar: here is where we discuss which of the templates is in each group for the 2 methods. Possibly also introduce the performance metric here.
 
@@
 
-    \subsection{Comparison of the self-organizing maps and K-means methods}
-    \label{sec: Kmeansvssom}
-
-        We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters and on the \citetalias{Hossein12} 142 sample galaxies using 22 clusters.
-        22 clusters were chosen to be able to compare the results of K-means clustering with the 1D SOM in Fig.~\ref{fig: 1by22V}. 
-        We computed the median spectrum for each cluster (in K-means) or neuron (in SOM) to compare the results.
-
-        To classify the 142 sample galaxies, we calculate the median of the spectra in each cluster, and compare them with the \citetalias{Kinney96} template spectra.
-        We measured the spectral angle distance, also known as the cosine distance, between the medians and the template spectra to find the best match between them as follows:
-        \begin{equation}
-            \cos(\theta) = \frac{\sum_{i=1}^{n} s_it_i}{(\sum_{i=1}^{n} s^2_i)^{0.5} (\sum_{i=1}^{n} t^2_i)^{0.5}}
-        \end{equation}
-        where $s_i$ and $t_i$ are the $i^{\rm th}$ wavelength of the sample and template spectra, respectively. 
-        $\theta$ is the angle between the spectra, such that a value of zero means completely similar and a value of $180^{\circ}$ means completely different spectra. 
-        Since $-1<\cos(\theta)<1$, $1-\cos(\theta)$ is an easier way to measure and report the dissimilarity between two spectra.
-        The clusters were classified by finding the \citetalias{Kinney96} template spectrum with the most similarity to the median spectrum.
-
-        For a direct comparison between clustered spectra and templates, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as unrelated points in a high dimensional space.
-        Using the spectral angle distance, the spectra are treated as connected entities, which helps the shapes of the spectra to be recognized. 
-        In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each point.
-        (Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well.
-        Hence, there is no need to use the spectral angle distance in the SOM method.)
-
-        \begin{figure*}
-            \begin{subfigure}[b]{0.49\textwidth}
-                \centering
-                \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster.pdf}
-            \end{subfigure}
-                \hfill
-            \begin{subfigure}[b]{0.49\textwidth}
-                \centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_som.pdf}
-            \end{subfigure}
-            \caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right).
-Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
-            \label{fig: som_k_means_4}
-        \end{figure*}
-        Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra in 4 groups using both K-means and SOMs.
-        In the K-means method empty clusters are not allowed. 
-        Hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
-        Both plots in Fig.~\ref{fig: som_k_means_4} separated the most starburst and quiescent galaxies in a similar manner.
-        However, they show discrepancies for spectral types between the extreme cases. 
-        The other difference between these two methods is that the network created by the SOM method can be used to classify the other spectra, while for the K-means clusters they can only be used for one set of data.
-
-        \begin{figure*}
-            \begin{subfigure}[b]{0.49\textwidth}
-                \centering
-                \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/max_cosine2.pdf}
-            \end{subfigure}
-            \hfill
-            \begin{subfigure}[b]{0.49\textwidth}
-                \centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/min_cosine2.pdf}
-            \end{subfigure}
-            \caption{Left: the best-matched of the \citetalias{Kinney96} templates for the median spectrum of members in cluster number 9.
-This fit has the maximum $1-\cos(\theta)$ among all 22 clusters.
-Right: the best fit of the \citetalias{Kinney96} templates to the median spectrum of cluster number 22.
-This the best fitting result for 22 clusters.}
-            \label{fig: k_means_minmax}
-        \end{figure*}
-        For analyzing 142 sample galaxies from \citetalias{Hossein12}, we chose the number of clusters for the K-means analysis to be 22.
-        The median spectra of the members of each cluster were fitted by a spectrum from the \citetalias{Kinney96} templates.
-        Although the K-means clustering method separated the spectra of 142 sample galaxies into 22 different groups, only 7 templates were chosen as the best match with these 22 groups; some of the clusters are classified as the same spectral type.
-        Fig.~\ref{fig: k_means_minmax} shows the best and the worst fitting results among the 22 clusters. 
-        As we expected from the results of Section~\ref{sec: 1Dv} and \citetalias{Hossein12} paper, we cannot classify all the 142 sample galaxies with exactly 12 templates. 
-        Some of the classifications are almost perfect matches, however, there are groups of galaxies that are not exactly similar to any of the template spectra.
-        The left plot in the Fig.~\ref{fig: k_means_minmax} is an example of a group of galaxies that can not be considered as an outlier (in the sense that they are not a completely different type of galaxies), but they cannot be matched exactly with any of the template spectra.
-
-        There are substantial differences between the K-means and SOM-based classification.
-        From the K-means clustering, we classified 5 out of 22 clusters, 42 galaxies in total, as Sa type galaxies; 7 clusters, 28 galaxies in total, were classified as SB1 type galaxies.
-        Using the SOM method (see Fig.~\ref{fig: 1by22V}, only 19 galaxies were classified as Sa and 19 galaxies were classified as SB1. 
-        The comparison between the median of the spectra classified by SOM and by K-means clustering shows that they are clearly tracing each other.
-        However, the normalized flux in each case is slightly different: 
-        the SB1 galaxies are fainter at short wavelengths and brighter at longer wavelengths for the K-means clusters compared to the SOM ones.
-        These differences are reversed for Sa galaxies.
-
-        Using K-means clustering, no clusters were classified as Sb or SB2, which have very similar spectra to Sa and SB1, respectively.
-        On the other hand, using the SOM method, 14 galaxies were recognized as having similar spectra to SB2, and 33 galaxies were recognized as having spectra similar to Sa or Sb.
-        It seems that the K-means clustering method cannot recognize the differences between template spectra that have similar spectra (i.e.
-SB1 and SB2, or Sa and Sb), which suggests that the SOM method considers more details while clustering the spectra.
-        Being limited to the template set is another disadvantage of the K-means algorithm over the SOM method.
-        We can say that SOM has the advantages of creating a new network (template) based on the existing templates, and classifying galaxies using this new network.
-
     \subsection{Two-Dimensional Self-Organizing Maps}
@@
 
-        Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy spectral classification should use 2D networks first.These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
+    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy spectral classification should use 2D networks first.
+         These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
         After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary.
         One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture.
+        % Sahar: can we say anything more quantitative here about the difference betwen 1D and 2D?
+
+\subsection{Comparison of the self-organizing map, K-means, and supervised ANN methods}
+    \label{sec: Kmeansvssom}
+    %Sahar: I moved some of this here from the introduction. May need a little more work or to be moved elsewhere.
+    The one and two-dimensional self-organizing map classifications are compared briefly above. 
+    The 2-D maps allow galaxies to be members of more intermediate classes, and this is a general advantage of SOMs compared to the artificial neural network method used by \citetalias{Hossein12}: in the SOM method galaxies do not need to exactly match template spectra.
+    \citetalias{Hossein12} found that the ANN method could only match 105 out of the 142 galaxies directly to the \citetalias{Kinney96} templates; classifying the remaining 37 galaxies required combining template spectra.
+
+        \textbf{In order to compare results from SOM, K-means, and unsupervised ANN, we used two different methods.
+        We measured the best fit between \citetalias{Kinney96} template spectra and the \citetalias{Hossein12} 142 galaxies spectra, using minimum chi-square.
+        We scored K-means, SOM 4 nodes, SOM 12 nodes SOM 22 nodes and unsupervised ANN using the following system:
+        If the galaxy in each cluster/node was classified the same as the minimum chi-square class, this scored 1 point. 
+        If it was between two nodes (in case of SOM12 and SOM22) this scored 0.5 point. 
+        Otherwise, the classification score was zero points. 
+        Therefore, if the total score of a galaxy from 142 galaxies is 5, it means that all techniques classified the galaxy to the same group.
+        If it is 4.5, it means that either in the SOM with 12 nodes or the SOM with 22 nodes, that galaxy belonged to the in-between area and so on.
+        Comparing the scores, only 12 per cent of galaxies scored 5, 4 per cent had a score of 4.5 and 20 per cent had a score of 4.
+        In total 37 per cent of galaxies had a score greater than 4 which means that these methods are in fair agreement.
+        To see which methods gave the most similar results to the minimum chi-square fitting method, we added up the scores for each of the methods and found K-means 124, SOM-4 103, SOM-12 111.5, SOM-22 79, and unsupervised ANN 52.
+        This shows that the K-means method and SOM-12 nodes have the most similarity with minimum chi-square fitting.}
+
+        \textbf{To check the degree of agreement between different methods, we measured the Fleiss kappa index. 
+        The Fleiss Kappa index is a measure of agreement between three or more raters that are classifying a specific number of objects (i.e. 142 galaxies) to number of classes (i.e. 12 templates).
+        To differentiate between different SOMs we measured two different Fleiss kappa.
+First, we measured agreement between K-means, SOM-12 nodes, and unsupervised ANN, and then we measured agreement between K-means, SOM-22 nodes, and unsupervised ANN.
+        The resulting values of Fleiss kappa were $\sim 27$ per cent and $\sim 21$ per cent, respectively.
+        According to \citep{landis77}, the interpretation of a Fliess kappa measure in the range of 21--40 per cent is that the raters are in fair agreement.
+        }
+
+   %     \begin{figure*}
+    %        \begin{subfigure}[b]{0.49\textwidth}
+   %             \centering
+   %             \includegraphics[width=.99\textwidth, height= %7.5cm]{k_means_images/max_cosine2.pdf}
+   %         \end{subfigure}
+   %         \hfill
+   %         \begin{subfigure}[b]{0.49\textwidth}
+   %             \centering \includegraphics[width=.99\textwidth, height= %7.5cm]{k_means_images/min_cosine2.pdf}
+   %         \end{subfigure}
+   %         \caption{Left: the best-matched of the \citetalias{Kinney96} templates for the median spectrum of members in cluster number 9.
+This fit has the maximum $1-\cos(\theta)$ among all 22 clusters.
+Right: the best fit of the \citetalias{Kinney96} templates to the median spectrum of cluster number 22.
+This the best fitting result for 22 clusters.}
+   %         \label{fig: k_means_minmax}
+   %     \end{figure*}
+   %     For analyzing 142 sample galaxies from \citetalias{Hossein12}, we chose the number of clusters for the K-means analysis to be 22.
+   %     The median spectra of the members of each cluster were fitted by a spectrum from the \citetalias{Kinney96} templates.
+   %     Although the K-means clustering method separated the spectra of 142 %sample galaxies into 22 different groups, only 7 templates were chosen as the best match with these 22 groups; some of the clusters are classified as the same spectral type.
+   %     Fig.~\ref{fig: k_means_minmax} shows the best and the worst fitting results among the 22 clusters. 
+   %     As we expected from the results of Section~\ref{sec: 1Dv} and \citetalias{Hossein12} paper, we cannot classify all the 142 sample %galaxies with exactly 12 templates. 
+  %      Some of the classifications are almost perfect matches, however, there %are groups of galaxies that are not exactly similar to any of the template spectra.
+   %     The left plot in the Fig.~\ref{fig: k_means_minmax} is an example of a group of galaxies that can not be considered as an outlier (in the sense that they are not a completely different type of galaxies), but they cannot be matched exactly with any of the template spectra.
+
+   %     There are substantial differences between the K-means and SOM-based classification.
+   %     From the K-means clustering, we classified 5 out of 22 clusters, 42 %galaxies in total, as Sa type galaxies; 7 clusters, 28 galaxies in total, %were classified as SB1 type galaxies.
+   %     Using the SOM method (see Fig.~\ref{fig: 1by22V}, only 19 galaxies were classified as Sa and 19 galaxies were classified as SB1. 
+   %     The comparison between the median of the spectra classified by SOM and by K-means clustering shows that they are clearly tracing each other.
+   %     However, the normalized flux in each case is slightly different: 
+   %     the SB1 galaxies are fainter at short wavelengths and brighter at longer wavelengths for the K-means clusters compared to the SOM ones.
+   %     These differences are reversed for Sa galaxies.
+   % 
+   %     Using K-means clustering, no clusters were classified as Sb or SB2, which have very similar spectra to Sa and SB1, respectively.
+   %     On the other hand, using the SOM method, 14 galaxies were recognized as having similar spectra to SB2, and 33 galaxies were recognized as having spectra similar to Sa or Sb.
+  %      It seems that the K-means clustering method cannot recognize the differences between template spectra that have similar spectra (i.e.
+SB1 and SB2, or Sa and Sb), which suggests that the SOM method considers more %details while clustering the spectra.
+  %      Being limited to the template set is another disadvantage of the K-means algorithm over the SOM method.
+   %     We can say that SOM has the advantages of creating a new network (template) based on the existing templates, and classifying galaxies using this new network.

### 2017-06-24 answer_to_second_referee_comments.tex
PB edits

@@
 We thank the reviewer for his/her helpful comments and apologize for the delay in returning a revised version of the manuscript.
-Changed text in the manuscript appears in bold.
+Large blocks of changed text in the manuscript appear in bold (we have also made minor grammatical and style changes which are not marked).
 Our responses to individual comments are in the text below, beginning with ---
@@
 --- We have reorganized the last two paragraphs of Section 1 and added text to better describe the goal of the investigation: comparing different methods of classifying galaxy spectra against templates, with a focus on self-organizing maps.
-We have added additional text in Sections 4.2 and 5 comparing 1D and 2D SOMs.
-%TBD: 
-We have also added some text to Section 5 discussing the significance.
+We have added additional text to Sections 4.2 and 5 comparing 1D and 2D SOMs.
+We have also added some text to Section 5 discussing the significance of the work.
 
@@
 To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.
---- We selected several performance metrics.
-Two of them (an agreement score and the Fleiss kappa score) measure the degree to which the classifications agree.
+--- We selected several performance metrics. Two of them (an agreement score and the Fleiss kappa score) measure the degree to which the classifications agree. 
+% TBD: have not done the following yet
 As a measure of the classification performance, we calculate the dispersion in properties of the galaxies in each class and compare these values between methods.
@@
      The winner node determines the place of each new vector on the SOM.
-     The location of the new vectors on the SOM allows them to be compared with the original data set. 
-     Sections~\ref{sec: 1Dv} and ~\ref{sec: 2D} show the results of galaxy spectral classifications using networks trained on template spectra."
+     The location of the new vectors on the SOM allows them to be compared with the original data set."
 
@@
 (The paper itself points out that SOM reduces to k-means if the weight on the neighborhood function goes to 0, so you should be able to use the result in the same way.)  You can (and should, to do a direct comparison) use the clusters just like you used the SOM nodes - for a new data point, assign it to the most similar cluster center, then assign the template label from the original data used to construct the clusters.
-%--- I do not know how to do that!
-% for each spectrum to be classified, compute the distance (in whatever metric we end up using)
-% between the spectrum and the K cluster centres. Spectrum is classified as belonging to whatever cluster results in the smallest distance.
+--- We thank the referee for this helpful suggestion and have implemented it in our use of K-means. The text has been changed to remove this incorrect statement.
 
@@
 Please use the same methodology in both cases.
---- This is a reasonable criticism and we have ... 
-%TBD: need to finish this
+--- This is a reasonable criticism and we have changed our methodology to match between methods.
+We now use the templates to generate the initial classification in both cases, and then apply that classification to the 142 sample galaxies.
+%TBD: Sahar please check.
 
@@
 The authors' explanation for this choice does not make sense to me.
-
-%TBD: --- We have results from the Euclidean distance for the K-means! But I steel think because of the way SOM operates it is better to use SAD! Or maybe describe it better!
+--- We have changed to using the Euclidean distance in both cases.
+%TBD: Sahar please check.
 
@@
 Please explain.
---- We apologize for the confusion: this was a typo with "right" and "left" switched.
+--- We apologize for the confusion. As we have substantially changed the comparison between K-means and SOM results, this figure is no longer relevant and has been removed.
 
@@
 
---- We have reorganized Section 3 to discuss K-means first, followed by SOM. The former section 3.3 (now 3.1) has been rewritten, giving the objective function and using more formal language.
+--- We have reorganized Section 3 to discuss K-means first, followed by SOM.
+The former section 3.3 (now 3.1) has been rewritten, giving the objective function and using more formal language.
+The termination condition is indicated in the text.

### 2017-06-24 main.tex
PB edits

@@
     Classifying spectra using templates helps elucidate the nature of a galaxy's energy sources.
-    However, available templates are limited, which can complicate spectral classification.
-    Most current classification methods classify spectra outside the range of templates with low accuracy, and will fail in special cases.
     In this paper, we introduce a new method of classifying the spectra
-    of high redshift galaxies: the self-organizing map.
+    of galaxies: the self-organizing map.
     Self-organizing maps are a type of artificial neural network, mostly used to identify subgroups in a sample.
@@
     The trained networks were used to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$.
+    %following sentences still need work.
     Compared to previous attempts to classify this sample, the
@@
 
-    Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.)
-    Galaxy spectra can be classified in various networks with different sizes/dimensions based on the information needed from the data. 
+    Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.).
+    {\bf In this work we present a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
+    Based on our experience we suggest some general guidelines for use of SOM in galaxy spectral classification.}
     If a broad and general classification is required, networks can have one dimension with a few neurons. 
@@
     We used SOMs to classify the template spectra of \citetalias{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
-    By varying the size of the networks, we found the relative similarity between the \citetalias{Kinney96} template classes.
-    Two-dimensional networks can be used to find the relations of the neurons and classifications in great detail.
-    The sample galaxies have more freedom to be categorized, and only 23 of them occupy exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
-    Additionally, by using two-dimensional networks we showed that we do not have any outliers in the sample galaxies.
-
+    By varying the size of the networks, we found the relative similarity between the \citetalias{Kinney96} template classes, which can be roughly ordered in one dimension by their amount of star formation.
      A one-dimensional network with 22 neurons was needed in order to
     separate all 12 \citetalias{Kinney96} spectra; we concluded that \citetalias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
-    We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.
+    \textbf{Two-dimensional networks allow more freedom in the galaxy spectral classification.
+    Training $12\times 12$ neurons with the \citetalias{Kinney96} spectra, we found that the two dimensions of the resulting self-organized maps corresponded roughly to amounts of star formation and extinction.}
+
+    In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
+    Additionally, by using two-dimensional networks we showed that there are no outliers in the sample galaxies.
 
@@
     however, this method could not classify 37 out of 142 spectra.
-    The unsupervised artificial neural network method used in this project was able to classify  all 142 spectra in the sample
+    The self-organizing map (unsupervised artificial neural network) method used in the present work was able to classify  all 142 spectra in the sample
     as belonging to one of the morphological types introduced by \citetalias{Kinney96} or a class in between those types.
-    \textbf{Although it might seem that the classes of spectra using SOMs are arbitrary, we remind the reader that this classification emerges from the results of data mining on the previous templates.}
+    \textbf{Although it might seem that the classes of spectra using SOMs are arbitrary, we remind the reader that this classification emerges from the results of data mining on the previous templates.
+    Compared to other classification methods, we found that self-organizing maps show similar levels of agreement with a baseline chi-squared template matching method.}
 
     The properties of the galaxies in the \citetalias{Hossein12} sample using the new classification were found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
+    % QUANTIFY IN ABOVE SENTENCE. BELOW SENTENCE: DO WE ACTUALLY SHOW THIS? 
     The properties of the galaxies in each group are in good agreement with their morphological types.
-    This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates; some of the spectra fall in between template classes. 
+    This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates although some of the spectra fall in between template classes.
     This implies that these galaxies are not markedly different from those found in the local universe.
-    The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relation.
-     Other classification methods such as K-means and supervised artificial neural networks can provide a general classification with similar performance to the SOM.
-The ordered results and intermediate classes produced by self-organizing maps are distinct advantages of this method which can be utilized for other astronomical applications.
-%TBD: add some text here explainng why ordering is important
+    The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relations.
+    Such an ordered classification does not naturally arise from other classification methods such as K-means and supervised artificial neural networks, and can be used to investigate underlying physical causes of changes in properties between classification groups.
 
 \section*{ACKNOWLEDGMENTS}
-The authors thank the referee for insightful comments which helped us to improve the manuscript.
+The authors thank the referee for insightful comments which helped us to improve the work.
 The authors thank S. Lianou, A. Tammour, S.C. Gallagher, R.G. Abraham, M. Daley and A. Sigut for their useful comments. 

### 2017-06-24 sections0.08/data0.08.tex
PB edits

@@
-\section{Data}
+\section{DATA}
 \label{sec: data_highZ}
@@
 
- \subsection{Kinney Spectral Templates}
+ \subsection{Kinney spectral templates}
      \begin{figure}
         \centering
-        \includegraphics[width=0.5\textwidth]{images/k96.jpg}
-        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies, from fig.
+        \includegraphics[width=0.47\textwidth]{images/k96.jpg}
+        \caption {\citet{Kinney96} spectral templates for 12 types of galaxies, from fig.
 1 in \citet{Hossein12}.
@@
     For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} were available.
-%  We have gone back and forth on the following sentence several times.
-The commented-out version (what you had) doesn't make sense to me.
-I replaced it with what I understand was done, based on reading T12.
-%   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data 
 \citetalias{Hossein12} used point-spread-function matched photometry 
@@
     We classify SEDs that were produced by \citetalias{Hossein12} using the created networks.
-    These SEDs are publicly available~\footnote{All the SEDs produced by \citetalias{Hossein12}  can be found at this \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}.} in the form of flux per rest frame wavelength over a wide range of wavelengths.
+    These SEDs are publicly available\footnote{All the SEDs produced by \citetalias{Hossein12}  can be found at this \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}.} in the form of flux per rest frame wavelength over a wide range of wavelengths.
     Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} spectral templates.

### 2017-06-24 sections0.08/intro0.08.tex
PB edits

@@
 \label{sec: intro_somz}
-%General information about SEDs
+
 Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
@@
 
-%%Creating templates and NIR_UV templates
 Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using observations of nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}).
@@
 In the near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where the energy output of stars peaks), the spectrum\footnote{In the remainder of this paper, we are concerned with a limited range in wavelength, and so we refer to spectra rather than spectral energy distributions.} contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
-\textbf{TEXT HERE RE: WHY WE CARE ABOUT CLASSIFYING
-(1) do galaxy spectra form a continuous distribution or can they be separated into discrete groups as represented by the \citetalias{Kinney96} templates?
-(2) if the distribution is continuous, how do galaxy properties vary along the spectral distribution?
+\textbf{
+Using templates to classify galaxy spectra can help to answer the question of whether galaxy spectra form a continuous distribution or can  be separated into discrete groups.
+Templates are also helpful in computing $K$-corrections and discovering new classes of objects as outliers \citep{Folkes96}.
 }
-
-% categorizing galaxies based on their SED
 
@@
 
-%ANNs
 Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
@@
 
-%Training methods for networks - some grammar edits 20170122
 Neural networks can be trained using two methods: supervised and unsupervised.
@@
 
-%SOM
 A Kohonen self-organizing map (also called self-organizing map, or SOM) is a (semi)-supervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
@@
 
-%SOM in Astronomy
 The utilization of the SOM in astronomy dates back to the 1990s, with \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} among the first to use SOMs in their studies.
@@
 
-%SOM in Astronomy continued.
 Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
@@
 
-%20170122: combined and reorganized last 2 paragraphs of section - DRAFT
-%%%%After second referee report
 \textbf{
-The goal of this work is to compare different methods of classifying galaxy spectra against templates, with a particular focus on self-organizing maps. 
+The goal of this work is to investigate the use of self-organizing maps in classifying galaxy spectra against templates, and compare them to other methods. 
 The questions we want to answer are: 
@@
 between the three methods.
+% HAVE NOT YET DONE THE FOLLOWING. MAY WANT TO INCLUDE COMMENTED SENTENCES.
+We calculate the dispersion in properties between galaxies classified in the same groups in order to measure how well each classification method groups similar objects together.
 }
 
-%not sure if we want this sentence or not
-%Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to these data to find the best spectral class for the 37 galaxies that could not be classified by the supervised method.
-% also not sure if we want these sentences.
 % As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
@@
 %showed that there are tight correlations between physical properties of galaxies, and these %correlations might be different for each type of galaxy.
- %HERE IS WHERE WE MENTION OUR METRIC TO SAY WHICH METHOD IS BETTER
 

### 2017-06-24 sections0.08/method0.08.tex
Moving around text, working on ref letter
PB edits

@@
 As K-means is both simpler and more well-known, we introduce it briefly first before discussing SOM in detail.}
-
-%Sahar: note that I changed the notation a little bit here, for both K-means and SOM. Where you had $n$ in the SOM description I changed it to $d$.
 
@@
 
-%Sahar: Please check that the last sentence is correct.
-Also please check that the K-means version you used was randomly picking the initial centroids - looks like Matlab can also do this in other ways.
-
- \subsection{Self Organizing Maps}
+ \subsection{Self-organizing maps}
  \label{sec: som}
@@
         \item chooses a random vector from the dataset ($V_i$).
-        \item calculates the Euclidean distance in $\in \Re^d$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=d} (V_i - W_{j_i})^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{\min}}$").
+        \item calculates the Euclidean distance in $\Re^d$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=d} (V_i - W_{j_i})^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{\min}}$").
 This neuron is the winner node and is called the Best Matching Unit (BMU).
@@
         \item changes the weight vectors of the BMU and all the nodes within $r^t_{\rm BMU}$ as:
+        %Sahar: should w and v in the equation below be W and V (to match the text)?
         \begin{equation}
@@
 
-     %%%After_second_referee_report
      \textbf{As mentioned in the introduction, one of the main advantages of the SOM method is that the resulting networks can be used to cluster new datasets with no additional training required.
@@
      The winner node determines the place of each new vector on the SOM.
-     The location of the new vectors on the SOM allows them to be compared with the original data set. 
-     Sections~\ref{sec: 1Dv} and ~\ref{sec: 2D} show the results of galaxy spectral classifications using networks trained on template spectra.}
+     The location of the new vectors on the SOM allows them to be compared with the original data set. }

### 2017-06-24 sections0.08/results0.08.tex
PB edits

@@
-\section{Results and Discussion}
+\section{RESULTS AND DISCUSSION}
 \label{sec: result}
 
-% Sahar: might have to move some of this text around
+    In this section we show the results of the neural networks and K-means clustering trained using the \citetalias{Kinney96} template spectra.
+    Training with \citetalias{Kinney96} templates results in networks/clusters that have regions corresponding to galaxies of known morphological type. 
+    The trained networks/clusters can then be used to categorize other galaxies.
 
-    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra.
-    Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
-    The trained networks can then be used to categorize other galaxies.
-
-    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
+    The first step in categorizing galaxies is choosing the number of classes.
+    In the K-means method empty clusters are not allowed; 
+    hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
+    We did not want to have too dense or too sparse clusters.
+    Therefore we chose the number of clusters in the K-means clustering method to be $K=4$.
+    Since empty neurons are allowed in SOMs, finding an optimal number of neurons for SOM networks is more subtle than just specifying a number of clusters. 
+    In order to find a sufficient size for the trained neural networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
     Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
@@
 
-    We started our analysis by creating 1D SOMs. 
-    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
-    We also applied the K-means clustering method (Section~\ref{sec: Kmeansvssom}) to both the template and sample galaxies and compared the results with the results of the 1D SOMs.
+    We started our analysis by creating 1D SOMs and K-means clustering. 
+    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time (Section~\ref{sec: 1Dt}).
+    We performed K-means clustering on the \citetalias{Kinney96} templates (Section~\ref{sec: Kmeansvssom}) and compared 
+   the results with the results of the $1\times4$-sized 1D SOMs (Section~\ref{sec: Kmeansvssom}).
     For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network to be $12\times12$ and created two types of SOM to show different applications of 2D SOMs.
+    In Section~\ref{sec: Kmeansvssomvsann} we compare the results of the different classification in several ways. 
+    For each generated neural network, we compare the results with the \citetalias{Kinney96} categorization.
+    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12} and with K-means clustering.
 
-    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
-    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.
-
-\subsection{One-dimensional self-organizing maps and K-means clustering: templates}
-
-\begin{figure*}
-\begin{subfigure}[b]{0.49\textwidth}
-\centering
-\includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_kinney.pdf}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.49\textwidth}
-\centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_som.pdf}
-\end{subfigure}
-\caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right).
-Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
-\label{fig: som_k_means_4}
-\end{figure*}
-
-        We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters \textbf{and then assigned each of the 142 galaxies in the \citetalias{Hossein12}  sample to the cluster with the closest centroid.}
-        %We measured distance between the centroid of each cluster and spectra of each galaxy to classify galaxies using K-means method.
-
-       % For a direct comparison between clustered spectra and templates, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as unrelated points in a high dimensional space.
-        %Using the spectral angle distance, the spectra are treated as connected entities, which helps the shapes of the spectra to be recognized. 
-        %In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each point.
-        %(Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well.
-        %Hence, there is no need to use the spectral angle distance in the SOM method.)
-    Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra in 4 groups using both K-means and SOMs.
-        In the K-means method empty clusters are not allowed. 
-        Hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
-        Both methods shown in Fig.~\ref{fig: som_k_means_4} separated the most starburst-like and quiescent galaxies in a similar manner.
-        However, they show discrepancies for spectral types between the extreme cases.
-
-%Sahar: here is where we discuss which of the templates is in each group for the 2 methods. Possibly also introduce the performance metric here.
-
-    \subsection{One-Dimensional Self-Organizing Maps}
+    \subsection{One-dimensional self-organizing maps}
     \label{sec: 1D_somz}
-        \subsubsection{Training the Networks}
+        \subsubsection{Training the networks}
         \label{sec: 1Dt}
-            To start our clustering, we assumed that galaxies can be divided into only two general types, quiescent and starburst.
+            To start our classification, we assumed that galaxies can be divided into only two general types, quiescent and starburst.
             This corresponds to a network with only two neurons.
@@
 
-            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
+            We increased the size of the maps gradually until the templates were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
             Since there are more nodes in higher grid SOMs, the algorithm 
@@
 
-        \subsubsection{Classifying the Galaxy Sample}
+          \subsubsection{One-dimensional self-organizing maps and K-means clustering: templates}
+          \label{sec: Kmeansvssom}
+
+    \begin{figure*}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \centering
+        \includegraphics[width=.99\textwidth, height=         7.5cm]{k_means_images/classified_group_in_4cluster_kinney.png}
+    \end{subfigure}
+    \hfill
+        \begin{subfigure}[b]{0.49\textwidth}
+        \centering \includegraphics[width=.99\textwidth, height=         7.5cm]{k_means_images/classified_group_in_4cluster_som.png}
+    \end{subfigure}
+    \caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering     (left) and SOM (right).
+Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
+    \label{fig: som_k_means_4}
+    \end{figure*}
+
+    We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters.
+    \textbf{
+    Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra into 4 groups using both K-means and SOMs.
+    Both methods separated the most starburst-like and quiescent galaxies in a similar manner.
+    However, they show discrepancies for spectral types between these extreme cases.
+    Table~\ref{tab:kmeans_som4} shows the group assignments of the \citetalias{Kinney96} templates in the two methods.
+    Templates B, E, S0 and Sa are grouped in the same cluster/neuron in both K-means and $1\times4$-sized SOM. 
+    K-means grouped the Sb template with the above templates, but the SOM network classified it as a separate group.
+    The K-means method clustered the Sc template as a separate group, while the SOM network grouped it with SB5 and SB6. 
+    Another noticeable difference is that K-means clustered the SB1 and SB2 templates in one group and SB3 to SB6 in another while
+    the SOM network grouped the SB1 to SB4 templates in one neuron and SB5 and SB6 in another.
+    As Fig.~\ref{fig: som_k_means_4} shows, K-means clustering of the templates produced groups more similar to each other, while SOM emphasizes the templates' differences.
+    }
+
+    \begin{table}
+    \centering
+    \begin{tabular}{||l|c|c||}
+    \hline
+    \hline
+    \citetalias{Kinney96} template & K-means group & SOM group \\
+    \hline
+    B                                & 3               & 1                         \\
+    E                                & 3               & 1                         \\
+    S0                               & 3               & 1                         \\
+    Sa                               & 3               & 1                         \\
+    Sb                               & 3               & 2                         \\
+    Sc                               & 4               & 3                         \\
+    SB1                              & 2               & 4                         \\
+    SB2                              & 2               & 4                         \\
+    SB3                              & 1               & 4                         \\
+    SB4                              & 1               & 4                         \\
+    SB5                              & 1               & 3                         \\
+    SB6                              & 1               & 3                        \\
+    \hline
+    \end{tabular}
+    \caption{Group assignments for \citetalias{Kinney96} template galaxies, using K-means and $1\times4$-sized SOM methods}
+    \label{tab:kmeans_som4}
+    \end{table}
+
+%Sahar: here is where we discuss which of the templates is in each group for the 2 methods. Possibly also introduce the performance metric here.
+
+        \subsubsection{Classifying the galaxy sample}
          \label{sec: 1Dv}
-            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the spectra derived from the fitted SEDs of the 142-galaxy sample from \citetalias{Hossein12}.
+
+         \textbf{After training with the templates, we used both K-means and self-organizing maps to classify the 142 galaxies in the \citetalias{Hossein12} sample.
+         K-means classification was performed by assigned each galaxy to the K-means cluster with the closest centroid and the results are discussed in Section~\ref{sec: Kmeansvssomvsann}.
+        This section examines the results of one-dimensional SOM-based classification in detail.
+         }
+
             The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
@@
 
-            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decides to which group the galaxy belongs.
-            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
-            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.
+            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decided to which group the galaxy belonged.
+            Galaxies with a weak 4000\AA~break, strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
+            Increasing the size of the SOM helps solve the problem of galaxies which have features that are common in both groups.
 
@@
             In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
-            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
+            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} templates into 12 different neurons.
             As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
@@
             19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
-            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
+            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb.
             The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.
@@
 
-            In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
-            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies and have high uncertainties.
-            Using this small sample, it is quite possible that the spectra from the best-fitting SEDs of 142 sample galaxies do not match any of the template ones perfectly.
-
-           With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
-            However, with SOM, we have the freedom to categorize galaxies into intermediate groups.
-            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.
-
-    \subsubsection{Properties of the Clustered Galaxies}
-
-       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is meaningful, in this section we examine the relations between median properties of the galaxies in each neuron.
+    \subsubsection{Properties of the spectral groups}
 
@@
 
+       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is meaningful, in this section we examine the relations between median properties of the galaxies in each group. 
           Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
@@
         They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
-        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.
+        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than in the \citetalias{Noll09} results.
 
@@
         \end{subfigure}
-        \caption[Relations between properties of the clustered galaxies]{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
-Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values.
-Colours show the galaxy types in the new classification.
-The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) one indicates the SB1 galaxies.
+        \caption{From top to bottom: relations between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
+Square points show the median values of these properties of galaxies in the $1\times22$ SOM network and error bars are the standard deviation of the median values.
+Circles show the median value of properties inside each K-means cluster (using $K=4$) and asterisks show results from \citetalias{Hossein12}.
+Colours show the galaxy types in the SOM classification.
+The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) indicates the SB1 galaxies.
 The shading of other colours between light grey and black (red and blue in the online version) measures the location of galaxies along the SOM from  quiescent to starburst.}
@@
         In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
-        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
-        The colours show the galaxy types, where B type galaxies are shown with light grey (red in the online version) and SB1 types are shown with black (blue in the online version).
-        The lighter grey (redder in the online version) the colour, the more similarity with quiescent galaxies, while the medium grey to black (purple to blue in the online version) colours show more similarity to starburst galaxies.
-        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
+        In Fig.~\ref{fig: props_vs_props}, the point represent the median values of the properties of the galaxies in each group, with different symbol types representing classification method and error bars indicating the standard deviation of those properties.
+       The colour scale represents neuron number in the SOM method, shading from quiescent to starburst. 
+        Since in the $1\times22$-size SOM shown in Fig.~\ref{fig: 1by22V} we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, there are more than 12 colours in Fig.~\ref{fig: props_vs_props}.
         The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
@@
         The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with more precision than those two, in all three plots.
+        % *** MORE PRECISION - NEED TO CLARIFY
         As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
-        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
+        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have lower stellar mass and higher f$_{\rm {burst}}$.
         From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their spectral type.
 
-        \citetalias{Noll09} studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
+        \citetalias{Noll09} studied relations between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
         In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
@@
 
-    % This is better but could perhaps still use work    
        \textbf{One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification.
@@
 Average properties of objects within clusters (possibly from data not used for classification) can be used to test hypotheses about the physical differences.
-       Figure~\ref{fig: props_vs_props} shows that the SOM ordering also corresponds to the ordering of the physical properties of the galaxy models used to make the classified spectra. 
+       Figures~\ref{fig: props} and~\ref{fig: props_vs_props} show that the SOM ordering also corresponds to the ordering of the physical properties of the galaxy models used to make the classified spectra.
        The median properties of the spectral groups change on going from one end of the SOM to the other.
@@
 
-    \subsection{Two-Dimensional Self-Organizing Maps}
+    \subsection{Two-dimensional self-organizing maps}
     \label{sec: 2D}
@@
         However, each neuron in these networks is limited to connecting to one other neuron in each direction.
-        In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between spectral types.
+        In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete picture of relations between spectral types.
         One of the other key features of SOMs compared to supervised classification is the ability to both interpolate between and extrapolate outside of training set classes.
         This permits a fuller exploration of dataset properties and detection of outliers.
+
         As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
@@
         In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
-        This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates (e.g.
+        This approach can be used to trace and recognize the outliers, which could include galaxy types that are not present in the \citetalias{Kinney96} templates (e.g.
 dwarf galaxies, luminous infrared galaxies, or active galactic nuclei).
-        To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.
-        Unlike the {\textsc newsom} library in which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameter), in {\textsc selforgmap} we can change this value.
-        Using the {\textsc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
+        To execute the second approach, we used the \textsc{ selforgmap} library in \textsc{matlab}.
+        Unlike the \textsc{newsom} library in which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameter), in \textsc{selforgmap} we can change this value.
+        Using the \textsc{selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
 
@@
         The decision about what sub-type of quiescent or starburst galaxy is based upon its position relative to each type in the SOM.
+        \citetalias{Hossein12} showed that by masking emission lines (i.e., by ignoring details in spectra) two types of galaxies, Sb and SB6, can be misclassified as one another.
+        As mentioned before, few-node, one-dimensional SOMs are a good method to obtain a big picture of the problem under study with less emphasis on fine detail. 
+        For example, the SB6 category is placed near Sb galaxies in the 1D network in Fig.~\ref{fig: 1by22T}.
+        However, in the upper left panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated. 
+        This shows that more details of spectral shapes are considered by 2D networks, which is one of the main advantages of  using 2D maps over 1D ones.
+        \textbf{In this case, the two dimensions of the self-organizing map correspond approximately to quiescent versus star-forming (left to right) and less to more extinction (bottom to top).}
 
@@
         In this network, neurons in the right side of the strip represent the quiescent galaxies and the neurons in the left side represent the starburst ones. 
-        When categorizing a new set of spectral types, if the new spectra are similar to the \citet{Kinney96} template all of them will be placed in the bottom of the map, but if the new spectra represent different types of galaxies, they would sit in any other neurons in the map.
+        When categorizing a new set of spectral types, if the new spectra are similar to the \citetalias{Kinney96} templates all of them will be placed in the bottom of the map, but if the new spectra represent different types of galaxies, they would sit in any other neurons in the map.
         In large datasets, one can easily use this network to figure out whether there is any of new type of spectra (or any outliers) in the datasets. 
-        Since the networks are already available, this procedure should be quick (from few seconds to few minutes) and easy for big datasets.
-        \citetalias{Hossein12} showed that by masking emission lines (i.e., by ignoring details in spectra) two types of galaxies, Sb and SB6, can be misclassified as one another.
-        As mentioned before, 1D SOMs are a good method to obtain a big picture of the problem under study and do not consider the small details. 
-        Therefore, we can see that the SB6 category is placed near Sb galaxies in the 1D network in Fig.~\ref{fig: 1by22T}.
-        However, in the upper right panel of Fig.~\ref{fig: 12by12}, we can see that the Sb and SB galaxies are completely separated.
-This shows that more details of spectral shapes are considered by 2D networks, which is one of the main advantages of  using 2D maps over 1D ones.
+        Since the networks are already available, this procedure should be quick (from a few seconds to a few minutes) and easy for big datasets.
 
@@
         Using 2D maps results in categorizing galaxies into more intermediate types than in 1D maps.
-        In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the quiescent side of the SOM, which was predictable from the results in Section\ref{sec: 1Dv}. 
-        This does not imply that in general there are more quiescent galaxies at higher redshift but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.
+        In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the quiescent side of the SOM, which was predictable from the results in Section~\ref{sec: 1Dv}.
+        This does not \textbf{necessarily} imply that in general there are more quiescent galaxies at higher redshift but could be a selection effect for galaxies that had more reliable redshift estimates.
 
@@
 \subsection{Comparison of the self-organizing map, K-means, and supervised ANN methods}
-    \label{sec: Kmeansvssom}
-    %Sahar: I moved some of this here from the introduction. May need a little more work or to be moved elsewhere.
+    \label{sec: Kmeansvssomvsann}
+
     The one and two-dimensional self-organizing map classifications are compared briefly above. 
@@
 
+%From introduction:     
+%The questions we want to answer are: 
+%(1) What is the degree of agreement between $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
+%(2) Are certain spectral types more (or less) consistently classified by the different methods? 
+%(3) To what extent do the average properties of galaxy classes represent a continuous distribution of physical properties?
+
         \textbf{In order to compare results from SOM, K-means, and unsupervised ANN, we used two different methods.
-        We measured the best fit between \citetalias{Kinney96} template spectra and the \citetalias{Hossein12} 142 galaxies spectra, using minimum chi-square.
-        We scored K-means, SOM 4 nodes, SOM 12 nodes SOM 22 nodes and unsupervised ANN using the following system:
-        If the galaxy in each cluster/node was classified the same as the minimum chi-square class, this scored 1 point. 
-        If it was between two nodes (in case of SOM12 and SOM22) this scored 0.5 point. 
+        We assigned the 142 galaxies in the sample to the best fit \citetalias{Kinney96} template using minimum chi-square.
+        We scored the classifications by K-means, $1\times4$-sized SOM, $1\times12$-sized SOM $1\times22$-sized SOM and unsupervised ANN using the following system.
+        %Sahar: I rewrote this to make it clearer, but I'm not sure it's correct!!!
+        If a galaxy's minimum chi-square template was classified into the same cluster/neuron, this scored 1 point. 
+        If the galaxy was classified between two nodes (in the case of $1\times12$-sized SOM and $1\times22$-sized SOM) this scored 0.5 point. 
         Otherwise, the classification score was zero points. 
-        Therefore, if the total score of a galaxy from 142 galaxies is 5, it means that all techniques classified the galaxy to the same group.
-        If it is 4.5, it means that either in the SOM with 12 nodes or the SOM with 22 nodes, that galaxy belonged to the in-between area and so on.
-        Comparing the scores, only 12 per cent of galaxies scored 5, 4 per cent had a score of 4.5 and 20 per cent had a score of 4.
-        In total 37 per cent of galaxies had a score greater than 4 which means that these methods are in fair agreement.
-        To see which methods gave the most similar results to the minimum chi-square fitting method, we added up the scores for each of the methods and found K-means 124, SOM-4 103, SOM-12 111.5, SOM-22 79, and unsupervised ANN 52.
-        This shows that the K-means method and SOM-12 nodes have the most similarity with minimum chi-square fitting.}
+        Therefore, if the total score of a galaxy is 5, it means that all techniques classified the galaxy into the same group.
+        If it is 4.5, it means that either in the 12-node SOM  or the 22-node SOM, that galaxy belonged to the in-between area and so on.
+        Comparing the scores, we found that 12 per cent of galaxies scored 5, 4 per cent had a score of 4.5 and 20 per cent had a score of 4.
+        In total, 36 per cent of galaxies had a score greater than 4 and 56 per cent had a total score of 3 or more.
+        The score$=5$ galaxies classified similarly by all methods were primarily (60 per cent) in the Sa template group. %; the rest belonged to the Sb, SB1, SB4 and SB6 template groups.
+        The score $>=3$ galaxies were predominantly SB1, Sa, and Sb type (32, 28, 18 per cent, respectively).
+        The different methods show the most agreement for galaxies similar to the SB1 and Sa templates, with less agreement on the high-extinction and quiescent types (SB5, SB6).
+        }
+
+        \textbf{To see which methods gave the most similar results to the minimum chi-square fitting method, we summed the scores over all galaxies for each of the methods and found totals of K-means 124, $1\times4$-sized SOM 103, $1\times12$-sized SOM 111.5, $1\times22$-sized SOM 79, and unsupervised ANN 52.
+        This shows that the K-means method and $1\times12$-sized SOM have the most similarity with minimum chi-square fitting.
+        However, none of the methods produced results that were extremely similar to chi-squared
+        }
 
         \textbf{To check the degree of agreement between different methods, we measured the Fleiss kappa index. 
-        The Fleiss Kappa index is a measure of agreement between three or more raters that are classifying a specific number of objects (i.e. 142 galaxies) to number of classes (i.e. 12 templates).
-        To differentiate between different SOMs we measured two different Fleiss kappa.
-First, we measured agreement between K-means, SOM-12 nodes, and unsupervised ANN, and then we measured agreement between K-means, SOM-22 nodes, and unsupervised ANN.
-        The resulting values of Fleiss kappa were $\sim 27$ per cent and $\sim 21$ per cent, respectively.
-        According to \citep{landis77}, the interpretation of a Fliess kappa measure in the range of 21--40 per cent is that the raters are in fair agreement.
-        }
-
-   %     \begin{figure*}
-    %        \begin{subfigure}[b]{0.49\textwidth}
-   %             \centering
-   %             \includegraphics[width=.99\textwidth, height= %7.5cm]{k_means_images/max_cosine2.pdf}
-   %         \end{subfigure}
-   %         \hfill
-   %         \begin{subfigure}[b]{0.49\textwidth}
-   %             \centering \includegraphics[width=.99\textwidth, height= %7.5cm]{k_means_images/min_cosine2.pdf}
-   %         \end{subfigure}
-   %         \caption{Left: the best-matched of the \citetalias{Kinney96} templates for the median spectrum of members in cluster number 9.
-This fit has the maximum $1-\cos(\theta)$ among all 22 clusters.
-Right: the best fit of the \citetalias{Kinney96} templates to the median spectrum of cluster number 22.
-This the best fitting result for 22 clusters.}
-   %         \label{fig: k_means_minmax}
-   %     \end{figure*}
-   %     For analyzing 142 sample galaxies from \citetalias{Hossein12}, we chose the number of clusters for the K-means analysis to be 22.
-   %     The median spectra of the members of each cluster were fitted by a spectrum from the \citetalias{Kinney96} templates.
-   %     Although the K-means clustering method separated the spectra of 142 %sample galaxies into 22 different groups, only 7 templates were chosen as the best match with these 22 groups; some of the clusters are classified as the same spectral type.
-   %     Fig.~\ref{fig: k_means_minmax} shows the best and the worst fitting results among the 22 clusters. 
-   %     As we expected from the results of Section~\ref{sec: 1Dv} and \citetalias{Hossein12} paper, we cannot classify all the 142 sample %galaxies with exactly 12 templates. 
-  %      Some of the classifications are almost perfect matches, however, there %are groups of galaxies that are not exactly similar to any of the template spectra.
-   %     The left plot in the Fig.~\ref{fig: k_means_minmax} is an example of a group of galaxies that can not be considered as an outlier (in the sense that they are not a completely different type of galaxies), but they cannot be matched exactly with any of the template spectra.
-
-   %     There are substantial differences between the K-means and SOM-based classification.
-   %     From the K-means clustering, we classified 5 out of 22 clusters, 42 %galaxies in total, as Sa type galaxies; 7 clusters, 28 galaxies in total, %were classified as SB1 type galaxies.
-   %     Using the SOM method (see Fig.~\ref{fig: 1by22V}, only 19 galaxies were classified as Sa and 19 galaxies were classified as SB1. 
-   %     The comparison between the median of the spectra classified by SOM and by K-means clustering shows that they are clearly tracing each other.
-   %     However, the normalized flux in each case is slightly different: 
-   %     the SB1 galaxies are fainter at short wavelengths and brighter at longer wavelengths for the K-means clusters compared to the SOM ones.
-   %     These differences are reversed for Sa galaxies.
-   % 
-   %     Using K-means clustering, no clusters were classified as Sb or SB2, which have very similar spectra to Sa and SB1, respectively.
-   %     On the other hand, using the SOM method, 14 galaxies were recognized as having similar spectra to SB2, and 33 galaxies were recognized as having spectra similar to Sa or Sb.
-  %      It seems that the K-means clustering method cannot recognize the differences between template spectra that have similar spectra (i.e.
-SB1 and SB2, or Sa and Sb), which suggests that the SOM method considers more %details while clustering the spectra.
-  %      Being limited to the template set is another disadvantage of the K-means algorithm over the SOM method.
-   %     We can say that SOM has the advantages of creating a new network (template) based on the existing templates, and classifying galaxies using this new network.
+        The Fleiss Kappa index is a measure of agreement between three or more raters that are classifying a specific number of objects (i.e. 142 galaxies) to a number of classes (i.e. 12 templates).
+        We computed two different values of Fleiss kappa, between  K-means, unsupervised ANN, and either 
+         $1\times12$-sized or $1\times22$-sized SOMs.
+        The resulting values were $\sim 27$ per cent and $\sim 21$ per cent, respectively.
+        According to \citet{landis77}, the interpretation of a Fliess kappa measure in the range 21--40 per cent is that the raters are in fair agreement.
+    %NEXT 2 SENTENCES NEED WORK
+        In Fig.~\ref{fig: props_vs_props}, it is clear that the median of properties of classified galaxies using different methods are in agreement. 
+        However, since with SOM methods we can have more than 12 groups, the results are more detailed than the other methods.}

### 2017-08-11 sections0.08_for_editor/intro0.08.tex
re-submitted version

--- 2017-06-24 sections0.08/intro0.08.tex
@@
 In the near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where the energy output of stars peaks), the spectrum\footnote{In the remainder of this paper, we are concerned with a limited range in wavelength, and so we refer to spectra rather than spectral energy distributions.} contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
-\textbf{
+
 Using templates to classify galaxy spectra can help to answer the question of whether galaxy spectra form a continuous distribution or can  be separated into discrete groups.
 Templates are also helpful in computing $K$-corrections and discovering new classes of objects as outliers \citep{Folkes96}.
-}
 
@@
 It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
-\textbf{The training of a self-organizing map is fully unsupervised.
-     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method.}
+The training of a self-organizing map is fully unsupervised.
+     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method.
 
@@
 
-\textbf{
 The goal of this work is to investigate the use of self-organizing maps in classifying galaxy spectra against templates, and compare them to other methods. 
 The questions we want to answer are: 
-(1) What is the degree of agreement between $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
+(1) What is the degree of agreement between classifications produced $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
 (2) Are certain spectral types more (or less) consistently classified by the different methods? 
-(3) To what extent do the average properties of galaxy classes represent a continuous distribution of physical properties?
+(3) Which classification methods produce classes with the highest internal similarity ?
 We analyze the same sample of 142 galaxies with $0.5 < z < 1$ as 
 \citet[][hereafter \citetalias{Hossein12}]{Hossein12}, who classified the spectra using a supervised (multi-layer feed-forward) neural network method with the \citetalias{Kinney96} templates.
-For each of the 142 galaxies, we find the best chi-squared fit among the 12 templates  to have a base for comparing the methods' performance.
-We also use the Fleiss Kappa index \citet{Fleiss71} to test interrater reliability 
-between the three methods.
-% HAVE NOT YET DONE THE FOLLOWING. MAY WANT TO INCLUDE COMMENTED SENTENCES.
-We calculate the dispersion in properties between galaxies classified in the same groups in order to measure how well each classification method groups similar objects together.
-}
-
-% As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
-%\citetalias{Hossein12} also 
-%showed that there are tight correlations between physical properties of galaxies, and these %correlations might be different for each type of galaxy.
+For each of the 142 galaxies, we find the best chi-squared fit among the 12 templates to use as a base for comparing the methods' performance.
+We compute an agreement score for each method and also use the Fleiss Kappa index \citet{Fleiss71} to test interrater reliability 
+between the methods.
+To measure how well each classification method groups similar objects together, we
+calculate the silhouette scores and dispersions in properties between galaxies classified in the same groups.
 

### 2017-08-11 sections0.08_for_editor/method0.08.tex
re-submitted version

--- 2017-06-24 sections0.08/method0.08.tex
@@
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Method
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-
 \section{METHOD}
@@
 
-\textbf{In this section we describe the algorithms for both self-organizing maps and K-means clustering.
-As K-means is both simpler and more well-known, we introduce it briefly first before discussing SOM in detail.}
+In this section we describe the algorithms for both self-organizing maps and K-means clustering.
+As K-means is both simpler and more well-known, we introduce it briefly first before discussing SOM in detail.
 
@@
 
-\textbf{
 The K-means method partitions a data set $x_i$, having $n$ points in $d$-dimensional feature space, into $K$ clusters.
@@
 The default maximum number of iterations (100) was used.
-}
 
@@
         \item changes the weight vectors of the BMU and all the nodes within $r^t_{\rm BMU}$ as:
-        %Sahar: should w and v in the equation below be W and V (to match the text)?
         \begin{equation}
@@
 
-     \textbf{As mentioned in the introduction, one of the main advantages of the SOM method is that the resulting networks can be used to cluster new datasets with no additional training required.
+     As mentioned in the introduction, one of the main advantages of the SOM method is that the resulting networks can be used to cluster new datasets with no additional training required.
      New data with the same dimensionality as the original input data can be presented to the already trained network: the SOM algorithm finds the best matching unit considering the weight of nodes in the trained network and each vector from the new data set.
      The winner node determines the place of each new vector on the SOM.
-     The location of the new vectors on the SOM allows them to be compared with the original data set. }
+     The location of the new vectors on the SOM allows them to be compared with the original data set.
+
+     \subsection{Classification and clustering metrics}
+     \label{sec:metrics}
+
+     We use several metrics to measure the degree of agreement between classification methods. 
+     As a baseline method for assigning galaxy spectra to template classes, we compute the value of chi-squared between each galaxy and each template and assign the galaxy to the template class with lowest chi-squared value.
+     A metric of agreement with this classification is an agreement score, computed as follows.
+    If a method sorted a galaxy into the same cluster or neuron as its best-fit chi-square template, this was considered a match and scored 1 point. 
+    For the larger-sized self-organized maps, if a galaxy was classified between two nodes, one of which contained its best-fit chi-square template, this scored 0.5 point. 
+    Otherwise, the classification score was zero points.     
+     Another method to check the degree of agreement between different methods is the Fleiss kappa index \citet{landis77}. 
+    This index measures agreement between three or more raters that are classifying a specific number of objects to a number of classes and was calculated using the R software package.
+
+        Classification and clustering are related techniques, and we make
+        another comparison between the classification methods with a clustering metric, the silhouette score  \citep{rousseeuw87}.        
+This score is a metric used to describe cluster compactness and isolation, given by:
+\begin{equation}
+S = \frac{1}{n} \sum{\frac{b - a}{\max\big(a, b\big)}}
+\end{equation}
+where $a$ is the mean distance between a point and the other points in its cluster, and $b$ is the mean distance between a point and the nearest cluster of which that point is not a member.
+A higher silhouette score corresponds to a partition with better defined clusters.
+For a given dataset, the score generally declines with the number of clusters and is sometime used to determine the optimal cluster number.
+In this work we use the silhouette score to compare classifications with a comparable number of classes, as a measure of similarity within the classes.
+Mean values for each classification were calculated using the \textsc{scikit-learn} Python package \citep{sklearn}.

### 2017-08-11 sections0.08_for_editor/results0.08.tex
re-submitted version

--- 2017-06-24 sections0.08/results0.08.tex
@@
     In this section we show the results of the neural networks and K-means clustering trained using the \citetalias{Kinney96} template spectra.
-    Training with \citetalias{Kinney96} templates results in networks/clusters that have regions corresponding to galaxies of known morphological type. 
-    The trained networks/clusters can then be used to categorize other galaxies.
+    Training with \citetalias{Kinney96} templates results in networks or clusters that have regions corresponding to galaxies of known morphological type. 
+    The trained networks or clusters can then be used to categorize other galaxies.
 
@@
 
-            Figs.~\ref{fig: 1by2T} --~\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
+            Figs.~\ref{fig: 1by2T} --~\ref{fig: 1by22T} show the results of the training networks.  
             The upper part of the figures shows the neurons and the relative distances between their weights. 
@@
     We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters.
-    \textbf{
+
     Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra into 4 groups using both K-means and SOMs.
@@
     As Fig.~\ref{fig: som_k_means_4} shows, K-means clustering of the templates produced groups more similar to each other, while SOM emphasizes the templates' differences.
-    }
 
@@
 
-%Sahar: here is where we discuss which of the templates is in each group for the 2 methods. Possibly also introduce the performance metric here.
-
         \subsubsection{Classifying the galaxy sample}
@@
 
-         \textbf{After training with the templates, we used both K-means and self-organizing maps to classify the 142 galaxies in the \citetalias{Hossein12} sample.
+         After training with the templates, we used both K-means and self-organizing maps to classify the 142 galaxies in the \citetalias{Hossein12} sample.
          K-means classification was performed by assigned each galaxy to the K-means cluster with the closest centroid and the results are discussed in Section~\ref{sec: Kmeansvssomvsann}.
         This section examines the results of one-dimensional SOM-based classification in detail.
-         }
 
@@
             Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decided to which group the galaxy belonged.
-            Galaxies with a weak 4000\AA~break, strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
+            Galaxies with a weak 4000~\AA~break, strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000~\AA~break are categorized as quiescent.
             Increasing the size of the SOM helps solve the problem of galaxies which have features that are common in both groups.
@@
             However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
-            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
+            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000~\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
 
@@
 
-    \subsubsection{Properties of the spectral groups}
-
-       \begin{figure*}
-            \centering
-            \includegraphics[width=\textwidth]{images0.01/1d/props5.png}
-            \caption[The median of four properties of galaxies in three networks]{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
-            \label{fig: props}
-        \end{figure*}
-
-       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is meaningful, in this section we examine the relations between median properties of the galaxies in each group. 
-          Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
-        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
-        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst.
-       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs, as expected since the spectral types are also based on {\em CIGALE} fitting.
-
-        {\em CIGALE} has various models to derive the properties of galaxies.
-        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
-        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
-        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
-        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
-        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
-        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
-        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than in the \citetalias{Noll09} results.
-
-        \begin{figure*}
-        \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
-        \end{subfigure}
-       \hfill
-        \begin{subfigure}[b]{0.3\textwidth}
-            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
-        \end{subfigure}
-        \caption{From top to bottom: relations between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
-Square points show the median values of these properties of galaxies in the $1\times22$ SOM network and error bars are the standard deviation of the median values.
-Circles show the median value of properties inside each K-means cluster (using $K=4$) and asterisks show results from \citetalias{Hossein12}.
-Colours show the galaxy types in the SOM classification.
-The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) indicates the SB1 galaxies.
-The shading of other colours between light grey and black (red and blue in the online version) measures the location of galaxies along the SOM from  quiescent to starburst.}
-        \label{fig: props_vs_props}
-        \end{figure*}
-
-        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
-        In Fig.~\ref{fig: props_vs_props}, the point represent the median values of the properties of the galaxies in each group, with different symbol types representing classification method and error bars indicating the standard deviation of those properties.
-       The colour scale represents neuron number in the SOM method, shading from quiescent to starburst. 
-        Since in the $1\times22$-size SOM shown in Fig.~\ref{fig: 1by22V} we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, there are more than 12 colours in Fig.~\ref{fig: props_vs_props}.
-        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
-
-        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with more precision than those two, in all three plots.
-        % *** MORE PRECISION - NEED TO CLARIFY
-        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
-        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have lower stellar mass and higher f$_{\rm {burst}}$.
-        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their spectral type.
-
-        \citetalias{Noll09} studied relations between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
-        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
-        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
-        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
-        They found that for quiescent galaxies (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
-        Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
-        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
-        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
-        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
-        Whether this dependence is real or not, our results here show that using self-organizing maps can separate spectra of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
-
-       \textbf{One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification.
-       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
-Ordering is important in the case where the physical causes of the differences between classes/clusters are unknown.
-Average properties of objects within clusters (possibly from data not used for classification) can be used to test hypotheses about the physical differences.
-       Figures~\ref{fig: props} and~\ref{fig: props_vs_props} show that the SOM ordering also corresponds to the ordering of the physical properties of the galaxy models used to make the classified spectra.
-       The median properties of the spectral groups change on going from one end of the SOM to the other.
-       Therefore, by using the SOM method, we can study not only how galaxies group into spectral clusters, but the trends between the clusters as well.}
-
     \subsection{Two-dimensional self-organizing maps}
@@
 dwarf galaxies, luminous infrared galaxies, or active galactic nuclei).
-        To execute the second approach, we used the \textsc{ selforgmap} library in \textsc{matlab}.
+        To execute the second approach, we used the \textsc{selforgmap} library in \textsc{matlab}.
         Unlike the \textsc{newsom} library in which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameter), in \textsc{selforgmap} we can change this value.
@@
         This shows that more details of spectral shapes are considered by 2D networks, which is one of the main advantages of  using 2D maps over 1D ones.
-        \textbf{In this case, the two dimensions of the self-organizing map correspond approximately to quiescent versus star-forming (left to right) and less to more extinction (bottom to top).}
+       In this case, the two dimensions of the self-organizing map correspond approximately to quiescent versus star-forming (left to right) and less to more extinction (bottom to top).
 
@@
         In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the quiescent side of the SOM, which was predictable from the results in Section~\ref{sec: 1Dv}.
-        This does not \textbf{necessarily} imply that in general there are more quiescent galaxies at higher redshift but could be a selection effect for galaxies that had more reliable redshift estimates.
+        This does not necessarily imply that in general there are more quiescent galaxies at higher redshift but could be a selection effect for galaxies that had more reliable redshift estimates.
 
@@
         After finding and removing outliers in the input data, the use of 1D and 2D maps is complementary.
-        One-dimensional maps are helpful for exploring the general behaviour of the data, while 2D maps show a more detailed picture.
-        % Sahar: can we say anything more quantitative here about the difference betwen 1D and 2D?
+        One-dimensional maps are helpful for exploring the general and ordered behaviour of the data, while 2D maps can show a more detailed picture.
 
-\subsection{Comparison of the self-organizing map, K-means, and supervised ANN methods}
+\subsection{Comparing classification methods}
     \label{sec: Kmeansvssomvsann}
@@
     \citetalias{Hossein12} found that the ANN method could only match 105 out of the 142 galaxies directly to the \citetalias{Kinney96} templates; classifying the remaining 37 galaxies required combining template spectra.
+    Below we compare various other classification methods with the results of the 1-D self-organizing maps using the metrics described in Section~\ref{sec:metrics}.
+    Because the 2-D SOMs subdivide the sample into a larger number of groups, each containing a small number of objects, they are not directly comparable to the other methods and are not included here.
 
-%From introduction:     
-%The questions we want to answer are: 
-%(1) What is the degree of agreement between $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
-%(2) Are certain spectral types more (or less) consistently classified by the different methods? 
-%(3) To what extent do the average properties of galaxy classes represent a continuous distribution of physical properties?
+       To compare results from SOM, K-means, and unsupervised ANN, we first consider how well these methods matched a simple chi-squared fitting classification. 
+        Matching galaxy spectra to templates using chi-squared, we found that not all of the templates had matches among the galaxy sample: no galaxy spectra were best-matched to the B, E, or Sc templates.
+        This is consistent with the results from the self-organized maps.
+        Summing the classification score over all galaxies in the sample allows us to compare how well each technique matched the results of chi-squared fitting.
+        The totals were K-means 124, $1\times4$-sized SOM 103, $1\times12$-sized SOM 111.5, $1\times22$-sized SOM 79, and unsupervised ANN 52.
+        This shows that the K-means method and $1\times12$-sized SOM have the most similarity with minimum chi-square fitting.
+        Summing the classification score over all methods for a single galaxy shows how well the methods agree for a particular spectrum.
+        For example, if the total score of a galaxy is 5, it means that all techniques classified the galaxy into the same group.
+        Comparing the scores, we found that 12 per cent of galaxies scored 5, 36 per cent of galaxies had a score greater than 4, and 56 per cent had a total score of 3 or more.
+        The score-5 galaxies classified similarly by all methods were primarily (60 per cent) in the Sa template group. 
+        The score $>=3$ galaxies were predominantly SB1, Sa, and Sb type (32, 28, 18 per cent, respectively).
+        The different methods show the most agreement for galaxies similar to the SB1 and Sa templates, with less agreement on the high-extinction starburst types (SB5, SB6).
 
-        \textbf{In order to compare results from SOM, K-means, and unsupervised ANN, we used two different methods.
-        We assigned the 142 galaxies in the sample to the best fit \citetalias{Kinney96} template using minimum chi-square.
-        We scored the classifications by K-means, $1\times4$-sized SOM, $1\times12$-sized SOM $1\times22$-sized SOM and unsupervised ANN using the following system.
-        %Sahar: I rewrote this to make it clearer, but I'm not sure it's correct!!!
-        If a galaxy's minimum chi-square template was classified into the same cluster/neuron, this scored 1 point. 
-        If the galaxy was classified between two nodes (in the case of $1\times12$-sized SOM and $1\times22$-sized SOM) this scored 0.5 point. 
-        Otherwise, the classification score was zero points. 
-        Therefore, if the total score of a galaxy is 5, it means that all techniques classified the galaxy into the same group.
-        If it is 4.5, it means that either in the 12-node SOM  or the 22-node SOM, that galaxy belonged to the in-between area and so on.
-        Comparing the scores, we found that 12 per cent of galaxies scored 5, 4 per cent had a score of 4.5 and 20 per cent had a score of 4.
-        In total, 36 per cent of galaxies had a score greater than 4 and 56 per cent had a total score of 3 or more.
-        The score$=5$ galaxies classified similarly by all methods were primarily (60 per cent) in the Sa template group. %; the rest belonged to the Sb, SB1, SB4 and SB6 template groups.
-        The score $>=3$ galaxies were predominantly SB1, Sa, and Sb type (32, 28, 18 per cent, respectively).
-        The different methods show the most agreement for galaxies similar to the SB1 and Sa templates, with less agreement on the high-extinction and quiescent types (SB5, SB6).
-        }
-
-        \textbf{To see which methods gave the most similar results to the minimum chi-square fitting method, we summed the scores over all galaxies for each of the methods and found totals of K-means 124, $1\times4$-sized SOM 103, $1\times12$-sized SOM 111.5, $1\times22$-sized SOM 79, and unsupervised ANN 52.
-        This shows that the K-means method and $1\times12$-sized SOM have the most similarity with minimum chi-square fitting.
-        However, none of the methods produced results that were extremely similar to chi-squared
-        }
-
-        \textbf{To check the degree of agreement between different methods, we measured the Fleiss kappa index. 
-        The Fleiss Kappa index is a measure of agreement between three or more raters that are classifying a specific number of objects (i.e. 142 galaxies) to a number of classes (i.e. 12 templates).
+       We also used the Fleiss kappa index \citet{landis77} to 
+        measure the agreement between methods. 
+        Here the `raters' are the different methods classifying a specific number of objects (i.e. 142 galaxies) to a number of classes (i.e. 12 templates).
         We computed two different values of Fleiss kappa, between  K-means, unsupervised ANN, and either 
@@
         The resulting values were $\sim 27$ per cent and $\sim 21$ per cent, respectively.
-        According to \citet{landis77}, the interpretation of a Fliess kappa measure in the range 21--40 per cent is that the raters are in fair agreement.
-    %NEXT 2 SENTENCES NEED WORK
-        In Fig.~\ref{fig: props_vs_props}, it is clear that the median of properties of classified galaxies using different methods are in agreement. 
-        However, since with SOM methods we can have more than 12 groups, the results are more detailed than the other methods.}
+        According to \citet{landis77}, the interpretation of a Fleiss kappa measure in the range 21--40 per cent is that the raters are in fair agreement, consistent with the results above.
+
+A final comparison between the classification methods is 
+made with the silhouette score  \citep{rousseeuw87}.
+The highest score among our classification was for K-means (0.549), followed by $1\times4$-sized SOM (0.371), $1\times12$-sized SOM (0.302) and $1\times22$-sized SOM (0.249).
+The chi-squared fitting resulted in a score of 0.221 and the supervised neural network 0.142.
+As discussed in Section~\ref{sec:metrics}, the silhouette score usually declines as the number of groups increases, so we cannot conclude from these values that K-means is the superior method. 
+However, the $1\times12$-sized SOM, chi-squared fitting, and supervised neural network all have either 8 or 9 classes.
+In this case we can compare scores directly and conclude that the self-organized map yields groups with more internal similarity.
+This is in contrast to the comparison between K-means and self-organized maps for the templates alone (see Section\ref{sec: Kmeansvssom}) where K-means clustering  produced groups more similar to each other, and emphasizes that the exact data used in a clustering process can strongly affect the outcome.
+
+ \subsection{Properties of spectral groups}
+
+       \begin{figure*}
+            \centering
+            \includegraphics[width=\textwidth]{images0.01/1d/props5.png}
+            \caption[The median of four properties of galaxies in three networks]{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
+            \label{fig: props}
+        \end{figure*}
+
+       To check whether the classifications described above are meaningful, in this section we examine the relations between median properties of the galaxies in each group. 
+          Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ self-organized map networks.
+        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
+        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst.
+       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs, as expected since the spectral types are also based on {\em CIGALE} fitting.
+
+        {\em CIGALE} has various models to derive the properties of galaxies.
+        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
+        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
+        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
+        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
+        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
+        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
+        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than in the \citetalias{Noll09} results.
+
+        \begin{figure*}
+\includegraphics[width=\textwidth]{images0.01/1d/fig11_new_bw.png}
+        \caption{
+        From top to bottom: relations between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
+        Circles, pentagons, and squares show the median values of these properties of galaxies in the $1\times22$, $1\times 12$ and $1\times4$ SOM networks; 
+        triangles show the median value of properties for each K-means cluster (using $K=4$) and stars show median values for groups from \citetalias{Hossein12}.
+        Error bars show standard deviations of the group properties.
+        Colours show the galaxy types in the SOM classification. 
+        The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) indicates the SB1 galaxies. 
+        The shading of other colours between light grey and black (red and blue in the online version) measures the location of galaxies along the SOM from  quiescent to starburst.}
+        \label{fig: props_vs_props}
+        \end{figure*}
+
+        To compare our classifications with previous work, Fig.~\ref{fig: props_vs_props} shows plots similar to those shown by both \citetalias{Noll09} and \citetalias{Hossein12}.
+        The points represent the median values of the properties of the galaxies in each group, with different symbol types representing classification method and error bars indicating the standard deviation of those properties.
+       The colour scale represents neuron number in the SOM method, shading from quiescent to starburst. 
+        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
+
+        Overall, Fig.~\ref{fig: props} and the upper panels in Fig.~\ref{fig: props_vs_props} show the same trends as noted by \citetalias{Noll09} and \citetalias{Hossein12}:
+        galaxies with lower mass tend to be younger and more active.
+        The median group properties as derived by all of the methods show high Pearson correlation coefficients ($r^2\gtrsim 0.9$) between the quantities shown.
+        The ordering of groups in the SOM maps also corresponds to an ordering in age:    
+        from older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version).
+
+        \citetalias{Noll09} studied relations between A$_{\rm {FUV}}$ and other properties of galaxies and found that the attenuation had no dependence on the specific star formation or age.
+        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
+        Although weaker then the correlations above, Pearson correlation coefficients are higher for the SOM groups than for other methods, particularly for the $1x12$-sized SOM. 
+        The slightly different distribution of this particular classification (see Fig.~\ref{fig: 1by12T}) classifies the most quiescent objects as similar to slightly more active galaxies, lessening the turnover in properties as A$_{\rm {FUV}}$ increases.
+
+        The general sense of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
+        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
+        They found that for quiescent galaxies (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
+        Since our sample has no E-type galaxies, we cannot confidently claim the same relation between A$_{\rm {FUV}}$ and sSFR. 
+        However, Fig.~\ref{fig: props_vs_props} does indicate an increase in A$_{\rm {FUV}}$ with increasing sSFR for the quiescient types and a decrease with increasing sSFR for the starburst types.
+        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
+        Whether this dependence is real or not, our results here show that using self-organizing maps can separate spectra of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of galaxy evolution.
+
+       One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification.
+       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
+Ordering is important in the case where the physical causes of the differences between classes/clusters are unknown.
+Average properties of objects within clusters (possibly from data not used for classification) can be used to test hypotheses about the physical differences.
+       Figures~\ref{fig: props} and~\ref{fig: props_vs_props} show that the SOM ordering also corresponds to the ordering of the physical properties of the galaxy models used to make the classified spectra.
+       The median properties of the spectral groups change on going from one end of the SOM to the other.
+       Therefore, by using the SOM method, we can study not only how galaxies group into spectral clusters, but the trends between the clusters as well.

### 2017-08-11 main0.09.tex
Created new version, made minor typo and wording changes as in 3rd ref report, inserted comments from report in relevant places in manuscript.

--- 2017-06-24 main.tex
@@
 \usepackage{float}
-%\usepackage{caption}
 \usepackage{subcaption}
@@
 \usepackage{multicol}        % Multi-column entries in tables
-\usepackage{bm}		% Bold maths symbols, including upright Greek
-\usepackage{pdflscape}	% Landscape pages
-%\usepackage{booktabs,fixltx2e}
-\usepackage[flushleft]{threeparttable}
 \usepackage{pgffor}
@@
 
-\newcommand \kpc        {\,{\rm kpc}}
-\newcommand \halpha    {H$\alpha $\ }
-\newcommand \um    {$\mu$m\ }
-\newcommand \mice {$\mu$m}
-\newcommand \nprime {N$^\prime$}
 \newcommand \boldit {\textbf{\textit{}}}
-\newcommand \eqnprime {N^\prime}
-\newcommand \Spitzer {{\it Spitzer }}
-\newcommand \GALEX {GALEX }
-\newcommand \Herschel {{\it Herschel }}
-\newcommand \sii {[S~\textsc{ii}]} 
-\newcommand \oiii {[O~\textsc{iii}]} 
-\newcommand \hi {H~\textsc{i}}
-\newcommand \hii {H~\textsc{ii} }
 
@@
 
-%\defcitealias{Hossein12}{\citetalias{Hossein12}}
-
 \begin{document}
@@
 
-\title[Classifying high-$z$ galaxy spectra]{Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\title[Classifying high-$z$ galaxy spectra]{Classifying galaxy spectra at $0.5<z<1$ with self-organizing maps}
 %\author{rahmani.sahar}
@@
 
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%abstract
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-
 \begin{abstract}
@@
     Classifying spectra using templates helps elucidate the nature of a galaxy's energy sources.
-    In this paper, we introduce a new method of classifying the spectra
-    of galaxies: the self-organizing map.
-    Self-organizing maps are a type of artificial neural network, mostly used to identify subgroups in a sample.
+    In this paper, we investigate the use of self-organizing maps in classifying galaxy spectra against templates.
     We trained semi-supervised self-organizing map networks using a set of
     templates covering the wavelength range from far ultraviolet to near infrared. 
-    The trained networks were used to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$.
-    %following sentences still need work.
-    Compared to previous attempts to classify this sample, the
-    self-organizing map approach was able to better classify the spectra which had similarities with more than one template.
-    The median spectra and physical properties of the galaxies in each neuron of the self-organizing maps are consistent with other results on galaxy evolution.
-
+    The trained networks were used to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$ and the results compared to classifications performed using K-means clustering, a supervised neural network, and chi-squared minimization.
+    Spectra corresponding to quiescent galaxies were more likely to be classified similarly by all methods while starburst spectra showed more variability.
+    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
+     The class ordering provided by the one-dimensional self-organizing maps corresponds to an ordering in physical properties, a potentially important feature for the exploration of large datasets.
 \end{abstract}
@@
 
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Intro
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
+\import{sections0.09/}{intro0.09.tex}
 
-\import{sections0.08/}{intro0.08.tex}
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%DATA
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
+\import{sections0.09/}{data0.09.tex}
 
-\import{sections0.08/}{data0.08.tex}
+\import{sections0.09/}{method0.09.tex}
 
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Method
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
+\import{sections0.09/}{results0.09.tex}
 
-\import{sections0.08/}{method0.08.tex}
+%referee: Section 5 has been greatly improved and expanded; it now summarizes key observations that arose from the study and emphasizes its importance in further study of galaxy spectra.
+In particular, the final paragraph (and the end of section 4.4) provides an excellent summary of why the SOM methods can be of unique value.
+It should also include a statement about the results of other assessments (Fleiss kappa and silhouette) to provide a complete summary of the findings.
 
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Results
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-\import{sections0.08/}{results0.08.tex}
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%Summery
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-\section{Summary and Future Applications}
+\section{Summary}
 \label{sec: summary_SOMZ}
@@
     Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.).
-    {\bf In this work we present a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
-    Based on our experience we suggest some general guidelines for use of SOM in galaxy spectral classification.}
+    In this work we presented a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
+    Based on our experience we suggest some general guidelines for use of SOMs in galaxy spectral classification.
     If a broad and general classification is required, networks can have one dimension with a few neurons. 
@@
     separate all 12 \citetalias{Kinney96} spectra; we concluded that \citetalias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
-    \textbf{Two-dimensional networks allow more freedom in the galaxy spectral classification.
-    Training $12\times 12$ neurons with the \citetalias{Kinney96} spectra, we found that the two dimensions of the resulting self-organized maps corresponded roughly to amounts of star formation and extinction.}
-
-    In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
-    Additionally, by using two-dimensional networks we showed that there are no outliers in the sample galaxies.
+    Two-dimensional networks allow more freedom in the galaxy spectral classification.
+    Training $12\times 12$ neurons with the \citetalias{Kinney96} spectra, we found that the two dimensions of the resulting self-organized maps corresponded roughly to strength of star formation and amount of extinction.
+The one-dimensional self-organizing map ordering combined these two properties, with the highest-extinction template SB6 appearing between two less-extincted templates (Sb and Sc).
 
     A sample of 142 high-redshift galaxy spectra from \citetalias{Hossein12} was classified by the trained networks.
-    The classification results showed that using SOMs can allow identification of galaxies with spectra similar to two or more morphological types.
-    The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-    \citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} spectral templates and classify the same sample of 142 galaxy spectra;
-    however, this method could not classify 37 out of 142 spectra.
-    The self-organizing map (unsupervised artificial neural network) method used in the present work was able to classify  all 142 spectra in the sample
-    as belonging to one of the morphological types introduced by \citetalias{Kinney96} or a class in between those types.
-    \textbf{Although it might seem that the classes of spectra using SOMs are arbitrary, we remind the reader that this classification emerges from the results of data mining on the previous templates.
-    Compared to other classification methods, we found that self-organizing maps show similar levels of agreement with a baseline chi-squared template matching method.}
+  This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates although many of the spectra fall in between template classes.
+     In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
+    {\bf The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12}    could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.}
+    Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb).
+Spectra with emission lines or ultraviolet emission showed more variable classification results.
+    Classification produced by self-organized maps showed closer correspondence than the supervised method results to the classification from a chi-squared match.
+    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
 
-    The properties of the galaxies in the \citetalias{Hossein12} sample using the new classification were found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
-    % QUANTIFY IN ABOVE SENTENCE. BELOW SENTENCE: DO WE ACTUALLY SHOW THIS? 
-    The properties of the galaxies in each group are in good agreement with their morphological types.
-    This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates although some of the spectra fall in between template classes.
-    This implies that these galaxies are not markedly different from those found in the local universe.
-    The self-organizing map method can order the spectra in such a way as to also match the order along the age/SFR and SSFR/M* relations.
-    Such an ordered classification does not naturally arise from other classification methods such as K-means and supervised artificial neural networks, and can be used to investigate underlying physical causes of changes in properties between classification groups.
+The relations between group-averaged properties of the sample galaxies using the SOM-based classification were found to be consistent with those from previous studies. 
+    The self-organizing map method can order the spectra in such a way as to also match the order along the age/star formation rate and specific star formation rate-stellar mass relations.
+    Such an ordered classification does not naturally arise from other methods such as K-means clustering and supervised artificial neural networks.
+    Ordered classification can be used to investigate underlying physical causes of changes in properties between groups and for this reason we conclude that self-organized maps can be a highly useful tool in exploratory analysis of astronomical spectra.
 
@@
 S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada.
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%biblio
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
+
 \bibliographystyle{apalike}
@@
 
-%\import{sections0.0/}{apps0.0.tex}
-\import{sections0.08/}{apps_0.08.tex}
+\import{sections0.09/}{apps_0.09.tex}
 \end{document}

### 2017-08-11 sections0.09/apps_0.09.tex
Created new version, made minor typo and wording changes as in 3rd ref report, inserted comments from report in relevant places in manuscript.

--- 2017-03-08 sections0.07/apps_0.07.tex
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_4.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_v_1_by_4.png}
              %\caption{$1\times4$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_5.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_v_1_by_5.png}
              %\caption{$1\times5$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_6.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_v_1_by_6.png}
              %\caption{$1\times6$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_7.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_v_1_by_7.png}
              %\caption{$1\times7$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_8.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_v_1_by_8.png}
              %\caption{$1\times8$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_t_1_by_9.png}
+             \includegraphics[width=\textwidth]{../images0.01/1d/apps/hit_v_1_by_9.png}
              %\caption{$1\times9$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_10.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_v_1_by_10.png}
              %\caption{$1\times10$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_11.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_v_1_by_11.png}
              %\caption{$1\times11$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_12.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_v_1_by_12.png}
              %\caption{$1\times12$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_15.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_v_1_by_15.png}
              %\caption{$1\times15$ hits map}
@@
         \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_t_1_by_20.png}
+             \includegraphics[width=\textwidth,height=2.5cm]{../images0.01/1d/apps/hit_v_1_by_20.png}
              %\caption{$1\times20$ hits map}
@@
     \end{figure}
+
+\newpage

### 2017-08-11 sections0.09/intro0.09.tex
Created new version, made minor typo and wording changes as in 3rd ref report, inserted comments from report in relevant places in manuscript.

--- 2017-08-11 sections0.08_for_editor/intro0.08.tex
@@
 \label{sec: intro_somz}
+
+%Referee: Great list of questions near the end of section 1.
+I recommend moving (or merging) the background information/explanation of the methods that are tested to section 3 so that this important content (the goals of the work) is featured more prominently and early on.
 
@@
 The questions we want to answer are: 
-(1) What is the degree of agreement between classifications produced $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
+(1) What is the degree of agreement between classifications produced by $\chi^2$ fitting, one- and two-dimensional self-organizing maps, K-means clustering and artificial neural networks? 
 (2) Are certain spectral types more (or less) consistently classified by the different methods? 

### 2017-08-11 sections0.09/method0.09.tex
Created new version, made minor typo and wording changes as in 3rd ref report, inserted comments from report in relevant places in manuscript.

--- 2017-08-11 sections0.08_for_editor/method0.08.tex
@@
 
+%Referee: The objective function for k-means (equation 1, page 4) is not quite clear as it does not indicate what the "min" is taken over; I suggest adding a subscript "k" here (assuming that is what was intended).
+
 The K-means method partitions a data set $x_i$, having $n$ points in $d$-dimensional feature space, into $K$ clusters.
-The number of clusters $K<n$ must be decided by the user in advance, and the cluster centroids in feature space are located at positions $\mu_k$.
+The number of clusters $K\leq n$ must be decided by the user in advance, and the cluster centroids in feature space are located at positions $\mu_k$.
 The goal of the algorithm is to minimize the sum
@@
 where $\norm{z}$ indicates the distance measurement in $d$-dimensional space. In this work the Euclidean distance is is used, but other metrics are also possible.
-The algorithm is initialized by randomly choosing $K$ random points as cluster centroids.
+The algorithm is initialized by randomly choosing $K$ points as cluster centroids.
 Each data point is assigned to the cluster with the closest centroid, and the centroids are re-calculated.
@@
 
- \subsubsection{Algorithm of SOM} 
+ \subsubsection{SOM algorithm} 
  \label{sec: algorithm}
@@
         \item calculates the Euclidean distance in $\Re^d$ space for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=d} (V_i - W_{j_i})^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{\min}}$").
-This neuron is the winner node and is called the Best Matching Unit (BMU).
+This neuron is the winning node and is called the Best Matching Unit (BMU).
         \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius.
@@
      To present our results, we use {\sc nnt}'s built-in plotting tool.
-     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
+     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between those neurons.
      In the maps, the coloured hexagonal shapes represent the neurons. 
@@
      New data with the same dimensionality as the original input data can be presented to the already trained network: the SOM algorithm finds the best matching unit considering the weight of nodes in the trained network and each vector from the new data set.
-     The winner node determines the place of each new vector on the SOM.
+     The winning node determines the place of each new vector on the SOM.
      The location of the new vectors on the SOM allows them to be compared with the original data set.

### 2017-09-18 sections0.09/intro0.09.tex
Updates from ShareLaTeX

@@
 I recommend moving (or merging) the background information/explanation of the methods that are tested to section 3 so that this important content (the goals of the work) is featured more prominently and early on.
+% DONE, but needs looked at again to make sure it makes sense.
 
@@
 In the near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where the energy output of stars peaks), the spectrum\footnote{In the remainder of this paper, we are concerned with a limited range in wavelength, and so we refer to spectra rather than spectral energy distributions.} contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.
-
 Using templates to classify galaxy spectra can help to answer the question of whether galaxy spectra form a continuous distribution or can  be separated into discrete groups.
@@
 
-Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
-An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
-It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16a,Hossein16b,Ellison16a, Ellison16b}.
-Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91}.
-Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.
-
 Neural networks can be trained using two methods: supervised and unsupervised.
@@
 Unsupervised methods are very helpful in obtaining knowledge from the data, or when the underlying structure of the data is not well established.
-
-A Kohonen self-organizing map (also called self-organizing map, or SOM) is a (semi)-supervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
-It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
-The training of a self-organizing map is fully unsupervised.
-     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method.
-
-The utilization of the SOM in astronomy dates back to the 1990s, with \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} among the first to use SOMs in their studies.
-\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOMs: object classification and clustering, and photometric redshift estimation.
-The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
-From classifying quasars' spectra to star/galaxy classifications, from gamma-ray burst clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
-
-Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
-These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
-finding patterns and common characteristics between galaxies can be a complex task.
-\citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
-They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
-They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
-Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
-The other application of SOMs is to find outliers or errors in the data.
-\citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
-This package can distinguish an astronomical object from instrumental artifact, and then classify the object based on its spectrum.
-
-K-means clustering~\citep{Macqueen67} is another unsupervised method used in many astronomical studies~\citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
-K-means clustering divides data into $K$ clusters, in such a way that each data point belongs to the cluster with the nearest mean value.
-To first order, SOM and K-means work similarly: both algorithms operate on the distances between \boldit{N} $\in \Re^m$ objects defined by the properties under consideration.
-The SOM algorithm also considers distances between objects in the low-dimensional map, as controlled by a neighborhood function. 
-When the radius of the neighbourhood function goes to zero, the SOM algorithm loses its ordering power and acts like K-means clustering.
+A Kohonen self-organizing map (also called self-organizing map, or SOM) is a (semi)-supervised neural network.
 

### 2017-09-18 sections0.09/method0.09.tex
Updates from ShareLaTeX

@@
 
-In this section we describe the algorithms for both self-organizing maps and K-means clustering.
-As K-means is both simpler and more well-known, we introduce it briefly first before discussing SOM in detail.
+In this section we  briefly review the use of both self-organizing maps and K-means clustering in astronomy and describe their algorithms. 
+As K-means is both simpler and more well-known, we introduce it briefly first before discussing self-organizing maps in detail.
 
@@
 
+K-means clustering~\citep{Macqueen67} is an unsupervised method used in many astronomical studies~\citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
+K-means clustering divides data into $K$ clusters, in such a way that each data point belongs to the cluster with the nearest mean value.
+To first order, SOM and K-means work similarly: both algorithms operate on the distances between \boldit{N} $\in \Re^m$ objects defined by the properties under consideration.
+The SOM algorithm also considers distances between objects in the low-dimensional map, as controlled by a neighborhood function. 
+When the radius of the neighbourhood function goes to zero, the SOM algorithm loses its ordering power and acts like K-means clustering.
+
 %Referee: The objective function for k-means (equation 1, page 4) is not quite clear as it does not indicate what the "min" is taken over; I suggest adding a subscript "k" here (assuming that is what was intended).
+% DONE
 
@@
 \label{eq:km_sos}
-J = \sum_{i=1}^n \sum_{k=1}^K \min \big( \norm{x_i - \mu_k}^2 \big)
+J = \sum_{i=1}^n \sum_{k=1}^K {\min}_k \big( \norm{x_i - \mu_k}^2 \big)
 \end{equation}
@@
  \label{sec: som}
+
+ Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
+An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
+It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16a,Hossein16b,Ellison16a, Ellison16b}.
+Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91}.
+Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.
+
+A Kohonen self-organizing map (also called self-organizing map, or SOM) is a (semi)-supervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
+It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
+The training of a self-organizing map is fully unsupervised.
+     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method.
+The utilization of the SOM in astronomy dates back to the 1990s, with \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} among the first to use SOMs in their studies.
+\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOMs: object classification and clustering, and photometric redshift estimation.
+The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray burst clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
+
+Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
+These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
+finding patterns and common characteristics between galaxies can be a complex task.
+\citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
+They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
+They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
+Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
+The other application of SOMs is to find outliers or errors in the data.
+\citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
+This package can distinguish an astronomical object from instrumental artifact, and then classify the object based on its spectrum.
 

### 2017-09-27 main0.09.tex
marked changed text using \changed command

@@
 \newcommand \boldit {\textbf{\textit{}}}
+\newcommand \changed {\textbf{}}
 
@@
      In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
-    {\bf The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12}    could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.}
+ The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12}    could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.
     Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb).

### 2017-09-27 sections0.09/method0.09.tex
marked changed text using \changed command

@@
 
-In this section we  briefly review the use of both self-organizing maps and K-means clustering in astronomy and describe their algorithms. 
+\changed{In this section we  briefly review the use of both self-organizing maps and K-means clustering in astronomy and describe their algorithms.} 
 As K-means is both simpler and more well-known, we introduce it briefly first before discussing self-organizing maps in detail.
@@
 
+\changed{
 K-means clustering~\citep{Macqueen67} is an unsupervised method used in many astronomical studies~\citep[e.g.][]{DAbrusco12,Ordov14,Boersma14,Aycha16}.
@@
 When the radius of the neighbourhood function goes to zero, the SOM algorithm loses its ordering power and acts like K-means clustering.
-
+}
 %Referee: The objective function for k-means (equation 1, page 4) is not quite clear as it does not indicate what the "min" is taken over; I suggest adding a subscript "k" here (assuming that is what was intended).
@@
 where $\norm{z}$ indicates the distance measurement in $d$-dimensional space. In this work the Euclidean distance is is used, but other metrics are also possible.
-The algorithm is initialized by randomly choosing $K$ points as cluster centroids.
+\changed{The algorithm is initialized by randomly choosing $K$ points as cluster centroids.}
 Each data point is assigned to the cluster with the closest centroid, and the centroids are re-calculated.
@@
 
+\changed{ 
  Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
@@
 This package can distinguish an astronomical object from instrumental artifact, and then classify the object based on its spectrum.
+}
 

### 2018-03-25 sections0.08/answer_to_second_referee_comments.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-06-24 answer_to_second_referee_comments.tex
@@
 Large blocks of changed text in the manuscript appear in bold (we have also made minor grammatical and style changes which are not marked).
+The subsections of Section 4 have been reorganized both to address the referee's comments and make the flow more logical.
 Our responses to individual comments are in the text below, beginning with ---
-
-%TBD: make sure to delete comments in this file before submitting!
 
@@
 To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.
---- We selected several performance metrics. Two of them (an agreement score and the Fleiss kappa score) measure the degree to which the classifications agree. 
-% TBD: have not done the following yet
-As a measure of the classification performance, we calculate the dispersion in properties of the galaxies in each class and compare these values between methods.
-The results of this analysis are discussed in Section 4.4.
+--- We measure performance metrics in two areas: one set of metrics (an agreement score and the Fleiss kappa score) measures the degree to which the different classifications agree.
+The other set (silhouette score and Pearson correlation coefficient) measures the similarity between properties of galaxies assigned to the same class.
+The metrics are described in Section 3.4.
+
+The results of this analysis are described in Sections 4.3 and 4.4. We have rewritten the abstract and summary to reflect the results.
 
 I had suggested comparing the results to a simple nearest-neighbor classification baseline, but this was not addressed.
---- We apologize for missing this helpful suggestion in the previous version. This is now part of the analysis described in the paragraph above; the results appear in Section 4.4.
+--- We apologize for missing this helpful suggestion in the previous version. This is now part of the analysis described in the paragraph above; the results appear in Section 4.3.
 
@@
 But the paper must then explain why this is important or valuable.
---- We have added text to the end of both Section 4.2 (formerly section 4.1) and Section 5 explaining the utility of an ordered clustering.
+--- We have added text to the end of both Section 4.4 (formerly section 4.1) and Section 5 explaining the utility of an ordered clustering.
 
@@
 How can I tell from this figure?
---- The text describing the differences between the K-means and SOM classification of the templates (in particular, which templates are grouped together by the two methods) has been rewritten and moved to Section 4.1 (newly added in this revision).
+--- The text describing the differences between the K-means and SOM classification of the templates (in particular, which templates are grouped together by the two methods) has been rewritten and moved to Section 4.1.2.
 
@@
 We now use the templates to generate the initial classification in both cases, and then apply that classification to the 142 sample galaxies.
-%TBD: Sahar please check.
 
@@
 --- We have changed to using the Euclidean distance in both cases.
-%TBD: Sahar please check.
 

### 2018-03-25 Z_ref_reports_responses/Ref_report_1.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

Reviewer's Comments:

This paper proposes the use of self-organizing maps (1D and 2D) to aid in classifying galaxy spectra.  In contrast to strictly supervised methods, the SOM is able to create its own classes including those that may fall "between" existing template classes, and therefore it can provide a better fit to the data.

This is a very clear, readable, and well written paper.  The careful steps through different network architectures helps the reader understand the different behavior and results.

However, what's missing is a larger sense of significance.  What did this analysis accomplish?  The paper claims value in having "classified" all 142 samples.  But any arbitrary decision rule could classify them (i.e., assign them to a class); what is needed is some statement about the accuracy of that classification, or efficiency, or some other measurable benefit.  Related, it is confusing to claim that

"Most current classification methods cannot classify SEDs outside the range of templates, and will fail in special cases." (abstract)

Any classification method can generate a classification for any input.  It may be the case that this is of low confidence, or it is incorrect, but there is still some output.  I suggest rephrasing this claim to indicate the actual limitation (low accuracy? low confidence? something else?).

In the end, how does one use the output of the SOM classification? Can you evaluate its accuracy in some way?  I understand that SOMs are exploratory and unsupervised, but there should be some demonstrable benefit or value from having done it.

The only statement I can see about something learned from the exercise is that the SOM yielded results with higher correlations between non-spectral properties.  But correlation is never quantified; instead plots are shown, leaving the reader's eye to estimate correlation.  To my eye, the plots in the lower row of Figure 10 have low correlation, if any.  What is the R^2 value?  And why does this matter?

Other major suggestions:

1. Motivate the use of 1D versus 2D SOMs (or both).  As currently presented it is not clear what the benefit is of using either one, especially since they give different results.  Which one is better? Since they have different results, what does each one tell us?  At the end of section 4, the paper advises investigators to use the 2D approach first.  Why?  And if so, what additional knowledge is gained by applying the 1D approach?

2. Although the paper explains why the SOM has more flexibility/expressivity than the neural network approach in reference T12, it does not compare the SOM to any other method out there.  The obvious candidate for comparison would be to apply k-means clustering (e.g., cluster the 142 spectra and then each clusters to its closest match of the original 12 templates).  But to compare the meaningfully, again you'll need some measure of performance, which currently is lacking.

Relatedly, what performance does one get simply by assigning each of the 142 spectra to its closest match from the 12 templates?  This would help us understand whether an SOM is even needed for this problem.

Minor points:

- The "mock sample" in section 3.3 does not add anything to the paper.  I suggest omitting it.  It raises more questions than it answers.  For example, is this randomly generated data?  Why 27 samples? Apparently there are only two features with only two possible values each, so there are only 4 unique possible samples, so 23 of the 27 must duplicate some other sample, and the data set is strongly over-specified.  Further, the features have values that are categorical rather than numeric (e.g., "high" and "low"), and it is not at all clear how the SOM, which employs Euclidean distance, can handle that kind of data.  Being able to divide a data set with only 4 unique samples into 4 distinct groups seems to be a non-accomplishment.

- I could not understand how the 2D SOM was constrained so that the results in the right-hand side of Figure 11 were obtained.  This network has the same topology as the one on the left yet somehow the K96 templates "are in a small region" (p. 10, line 43, column 2).

- Euclidean distance is not the best way to match spectra; I recommend using spectral angle distance instead.

- This isn't a fully unsupervised appraoch, since the SOM results are "classified" using the 12 template types (supervision).  That's not a weakness, but it means it would be more accurate to refer to the  method as "weakly supervised" or "partially supervised."

- Section 4.1.1 (p. 6, line 37-39, column 2) states that "The black color indicates that the left neuron is completely different from the other two groups" but earlier it was explained that these colors are relative to the range of differences present.  So black and white could be quite close (e.g., 0.1 and 0.2) or they could be large (e.g., 1 and 100000) but there's no way to know from the color.

- Section 4.1.1 (p. 7, lines 10-11, column 1) confusingly states that Figure 5 shows that "5 groups on the left-side neurons are separated from 7 groups on the right side of the map with two dark-grey colors between them."  There are indeed 5 groups then 2 dark-grey links then 7 groups, but those 7 are broken into sub groups with even greater contrast (black links).  So it would be more appropriate to say that the galaxies are split as 5 - 1 - 1 - 5 or even 6 - 1 - 6.

- Section 4.1.2 (p. 7, line 9, column 2) says that Figure 8 has 12 plots, but actually it has 14.

- It is hard for the reader to track K96, T12, and N09 when their definitions are embedded pages before they are referenced.  I suggest including a small table with these labels, what they are, and their full citation so readers can quickly understand what is meant.

- When re-using figures from a previous publication, you may need copyright permission from the journal source (e.g., Figure 1 was published by the Astronomical Journal).

### 2018-03-25 Z_ref_reports_responses/Ref_report_2.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

Reviewer's Comments:

This paper proposes the use of self-organizing maps (1D and 2D) to aid in classifying galaxy spectra.  The revision has addressed several points and improve the clarity of the text.  However, there are several remaining issues.

1. The authors did not address my comment about the significance of the work.  What was learned?  What method is advocated, and what is the evidence for its superiority?

The sentence that was added about 1D vs. 2D maps comes very late in the paper and is quite abstract, stating that the two methods are complementary.  The Introduction should establish the goals of the investigation so the reader understands the purpose of each experiment as well as its significance.

The paper claims that "Compared to previous attempts to classify this sample, the self-organizing map approach was able to better classify the spectra which had similarities with more than one template." (abstract), but I cannot find a quantitative comparison with any previous results.  Figure 9 is presented as the result to compare with previous work, but since the previous results are not presented nor summarized, the reader can't tell how they differ.  The paper reports "more precision", but this is not defined; does it mean smaller error bars?  Stronger correlation?  How does this show "better classification"?  To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.

I had suggested comparing the results to a simple nearest-neighbor classification baseline, but this was not addressed.

The comment about how SOMs provide an ordered clustering of the data (with respect to feature values), which k-means does not, is certainly true.  But the paper must then explain why this is important or valuable.

2. Perhaps I have missed it somewhere, but I don't think the paper ever states how exactly the classification of new data is done.  As I understand it, the authors train an SOM using template spectra, then classify new spectra by determining which SOM node is the best fit for the new item and classifying it based on the labeled template spectra that also reside in that node -- but this isn't actually stated anywhere.  Please add text explaining the classification step.  This would probably go in the final paragraph of the introduction and/or a new subsection in section 3 ("Method") - this section describes SOMs and k-means but not how to use either model to classify new data. (i.e., the SOM can't classify anything without knowing the labels of its original data set.  So although it builds the SOM in an unsupervised way, it requires the supervision of the template labels to be able to assign a label to a new item).

On page 2, lines 29-31, the authors added this text: "An SOM can be trained without supervision and its results used to classify other data. Therefore, this method can be considered as (semi)-supervised." As written, the phrase "this method" seems to refer to SOMs (so the statement wouldn't be true - SOMs are fully unsupervised), but I think instead the authors' proposed method (of building an SOM and then applying it to classify new data, using labels on the SOM-grouped data) is what is meant.  Please clarify.

3. The inclusion of k-means helps give useful context to this work. Figure 10 shows a head-to-head comparison of k-means and SOM applied to the 12 templates using 4 clusters/nodes.  But I can't tell which one is better.  The text states that they are similar but "show discrepancies for spectra types between the extreme cases".  Which ones?  How can I tell from this figure?

At the bottom of page 10, the paper states: "The other difference between these two methods is that the network created by the SOM method can be used to classify the other spectra, while for the K-means clusters they can only be used for one set of data."  This isn't true.  (The paper itself points out that SOM reduces to k-means if the weight on the neighborhood function goes to 0, so you should be able to use the result in the same way.)  You can (and should, to do a direct comparison) use the clusters just like you used the SOM nodes - for a new data point, assign it to the most similar cluster center, then assign the template label from the original data used to construct the clusters.

To analyze the 142 galaxies, the SOM and k-means experiments used different methodology and so are difficult to compare or understand. It seems that for k-means, the authors clustered the 142 sample galaxies and then classified the mean spectrum in each cluster and reported how well that did.  But for the SOM, the authors constructed the SOM based on the 12 templates from K96 and then assigned classes to individual new spectra (not the nodes).  This doesn't seem comparable.  Please use the same methodology in both cases.

Further, k-means and the SOM used different distance functions (Euclidean vs. spectral angle distance) when operating on the same data.  Differences in results could simply be due to this change.  The authors' explanation for this choice does not make sense to me.

The text says that Figure 11 shows "the best and the worst fitting results among the 22 clusters" (for k-means) but instead it seems to show the best-fit for two clusters (9 and 22) which both look pretty good.  The text implies that Fig 11 (right) is a poor match, but it looks very good.  Please explain.

4. If k-means is retained, the way it is presented needs improvement. The description of k-means clustering in section 1 is a nice addition, but the comparison between k-means and SOM is confusing and wordy. K-means optimizes a partition of the data based on distance in the feature space only.  SOMs operate on a combination of distance in feature space and distance in the resulting low-dimensional map.  I am not sure how this achieves "smoothing", nor whether this is an important detail (the paper never mentions it again).  I recommend explaining what is meant here and why a "smooth" solution is better, or omitting this detail.  Explaining how SOM can be reduced to k-means is a good addition.

Please a add citation to the original k-means algorithm (e.g., MacQueen, 1967) when it is first mentioned (in addition to citing people who've used the algorithm).

Section 3.3 outlines the k-means method that is used in the experiments.  The language here appears to be more informal and less polished than that which describes the SOM method.  To explain k-means with the same level of detail, it would be appropriate to show the objective function that is employed and to explain that it uses an alternating optimization to assign points to centroids and then update the centroids, iterating until... what?  (There are different termination conditions used by different implementations, so it would be useful to indicate here what the matlab method does.)

### 2018-03-25 Z_ref_reports_responses/ref_clarification_report3.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

"By "compare to an external standard" I mean "compare performance on a labeled sample", i.e., one labeled by humans, to see how well the proposed method (and a simple nearest-neighbors baseline) can predict those classifications.

My suggestion with the 142 galaxies was that, if their types are not previously known, to have a human label them (i.e., assign which of the 12 K96 templates each one should belong to).  That would allow for an assessment of the automated classification quality.  If no human can do this, then (as stated) there is no way to assess classification accuracy of the proposed methods.”"

### 2018-03-25 Z_ref_reports_responses/ref_report_3.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

Reviewer's Comments:

This paper compares self-organizing maps (1D and 2D) to k-means and supervised neural networks on the task of classifying galaxy spectra. The paper has greatly improved in focus and impact in this iteration. In fact, I consider the paper ready for publication with the exception of one item:

I do not understand why the clustering and SOM results are compared to the chi-square classifications.  First, the paper should motivate the use of chi-square to match spectra to templates (i.e., why not Euclidean distance as is used in all other parts of the study?).  If chi-square is retained, then to help clarify (and because there seem to be multiple interpretations out there), please provide the equation that was used to calculate the chi-square distance.

More importantly, I think the comparison of clustering/SOM results to the chi-square classifications may be the result of confusion from my last review.  When I suggested comparing to a nearest-neighbor baseline, I meant to compare to its performance (on an external standard), not to use its classifications as a gold standard (unless the chi-square classifications are considered the most accurate -- but if so, then there seems to be no need to use an SOM or anything else; just use chi-square).

Are the true labels of the 142 galaxies unknown?  If so, could someone examine them to provide the correct template match (perhaps starting with the chi-square fit and correcting any errors) and thereby a reference to compute classification accuracy in an objective way?  If not, there's no way to assess classification accuracy as such and the chi-square part can/should be omitted.

Additional minor comments and suggestions:

1. Great list of questions near the end of section 1.  I recommend moving (or merging) the background information/explanation of the methods that are tested to section 3 so that this important content (the goals of the work) is featured more prominently and early on.

2. The objective function for k-means (equation 1, page 4) is not quite clear as it does not indicate what the "min" is taken over; I suggest adding a subscript "k" here (assuming that is what was intended).

2. Good analysis in section 4.1.2.  Since the cluster labels are arbitrary ("cluster 1" for k-means does not mean the same thing as "cluster 1" for SOM), I suggest using letters for one algorithm (cluster A, B, C...) to make this very obvious.  Or, call the clusters K1, K1, K3... for k-means and S1, S2, S3... for SOM.

3. How do we conclude from Fig 5 that "As Fig. 5 shows, K-means clustering of the templates produced groups more similar to each other, while SOM emphasizes the templates’ differences"?  To my eye, SOM clusters 1 and 2 are very similar to each other, and more so than any pair of k-means clusters.  To support the claims about cluster similarity, one can measure this empirically with, e.g., the pairwise Euclidean distance between cluster (means).  Please update the end of section 4.3 as necessary after performing this analysis.

4. K-means cluster 4, which has only one item in it (Sc), genuinely seems to be different given its peak between 3000-4000 A.  Placing it in SOM cluster 3 obscures this feature.  This is worth mentioning in the discussion.

5. On page 12, I am confused by the Fleiss kappa results.  Since it allows pairwise comparison of two raters, I was anticipating perhaps an upper triangular matrix of all (5 choose 2) pairs of methods compared to each other.  Instead, only two values are reported (27% and 21%) and it is not clear what (which pairs) they characterize.  Please elaborate.

6. Section 5 has been greatly improved and expanded; it now summarizes key observations that arose from the study and emphasizes its importance in further study of galaxy spectra.  In particular, the final paragraph (and the end of section 4.4) provides an excellent summary of why the SOM methods can be of unique value.  It should also include a statement about the results of other assessments (Fleiss kappa and silhouette) to provide a complete summary of the findings.

(By the way, this section doesn't talk about "future applications" so I suggest omitting that from the section title.)

Typos/wording improvements:

- page 2, line 36 (column 2):
"classifications produced χ2 fitting," ->
"classifications produced by χ2 fitting," ?

- page 4, line 32:  In K-means clustering, K can equal n, so consider stating "K <= n" instead of "K < n".

- page 4, line 41-42:
"randomly choosing K random points" ->
"randomly choosing K points" or
"choosing K random points"

- title of sub-section 3.2.1: consider "SOM Algorithm" instead of "Algorithm of SOM".  Or, since there is no 3.2.2, omit this sub-section heading.

- page 5, line 50-51:
"the winner node" ->
"the winning node"

- page 5, line 35:
"is sometime used" ->
"is sometimes used"

- page 14, line 47:
"general guidelines for use of SOM in galaxy spectral classification."
"general guidelines for the use of SOMs in galaxy spectral classification."

- page 15, line 11-13:
"the supervised training method used by T12 with the same templates and galaxy sample could not classify 37 out of 142 spectra"

As I've mentioned, "could not classify" doesn't make sense as all methods will output some prediction no matter the input.  Perhaps "could not classify correctly" was intended.

- page 15, line 25-27:
"The relations between group-averaged properties of the sample galaxies in the using the SOM-based classification" ->
"The relations between group-averaged properties of the sample galaxies using the SOM-based classification" ?

### 2018-03-25 Z_ref_reports_responses/ref_report_4.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

27 February 2018

Scientific Editor's Comments:

Please ensure you fully address all comments from the reviewer.

Reviewer's Comments:

This paper compares self-organizing maps (1D and 2D) to k-means and supervised neural networks on the task of classifying galaxy spectra.

1. The paper has again improved, but the narrative still needs work to explain how the chi-squared method fits in.

1a. The authors state (in their response, but not in the paper) that there is no known correct classification for these galaxies.  Please add this necessary context for the paper.  This positions the work in the world of of (semi-) supervision, since correct labels are not available.

1b. The use of the chi-squared template assignment needs to be clearly explained and justified.  The author response states that this is a common method employed in the research community.  This too should be added to the paper to justify why it was chosen as a reference point (ideally with references to show its common usage by others).

1c. If chi-squared minimization is the current most widely used method, then the paper needs to make a strong case for why to bother using a different method (SOMs) that only imperfectly approximates (i.e., does not have 100% agreement with) the chi-squared method.  I expect that the benefit is obtaining the insights provided from the analysis of the trained SOM structure, which cannot be achieved with the chi-squared method.  Make this explicit (up front, in the Introduction) so the reader understands why they might want to bother using this new method instead of chi-squared.

1d. The authors stated "We have added a footnote to clarify how chi-squared was computed."  I cannot find this footnote.  Please define this method in section 3.

1e. The metrics proposed in section 3.4 are
- agreement of algorithm X's output with that obtained by a chi-squared minimization
- Fleiss kappa
- silhouette score (S) - also referred to as within-cluster similarity

I suggest referring to the first metric as "chi-squared agreement" (here and throughout, including the discussion of results starting in section 4.3) or some other term to capture the fact that it specifically relates an algorithm to the chi-squared results.

I am still confused by the the Fleiss kappa results.  If the chi-squared method is the point of reference to use (as with the proposed agreement metric), why does it not appear here?  What does it tell us to determine that the k-means, supervised ANN, and SOMs are in "fair" agreement? (with each other?)  Is that a goal?  The chi-squared agreement analysis showed higher agreement with the SOM than with the other methods, so I wouldn't expect (nor want) there to be high kappa values between those three.  As currently presented, I don't think this adds anything to the paper, and I suggest omitting it (or rephrasing as a second measure of agreement with chi-squared, and computing values accordingly).

2. The re-organization of the paper is helpful for the Introduction, but the new content needs to be better integrated into sections 3.1 and 3.2.  Currently it reads disjointedly.

2a. Section 3.1: The notation "N \in R^m" does not make sense, especially since m is not defined.  Consider something like "N objects, each represented by m features" or "N objects x \in R^m, where m is the number of features used to represent each object".

Note that the following paragraph uses a lower-case "n" for the number of objects.  Please make these consistent.

2b. Section 3.2:
- The text prior to 3.2.1 is now rather unwieldy and hard to follow.  It jumps back and forth between ANNs and SOMs. I suggest making a new 3.2 that covers "Artificial neural networks" (since the paper treats them as an alternative to SOMs later) and 3.3 can be devoted to SOMs as a specialized (semi-supervised) version of ANNs.  Merge old and new content to make a logical flow.
- Provide a citation for ANNs when first mentioned.
- What is meant by "a set of training methods" (end of page 3, column 2)?  Typically only a single training method (e.g., backpropagation) is used.
- Standard practice is to avoid having a single subsection (3.2.1). Remove the subsection heading, or make two (3.2.1, 3.2.2) on different sub-topics.  For example, section 3.3 could (should) be merged into the SOM section, as a subsection.

Minor comments:

1. Footnote 3: Aiding reproducibility is an excellent goal.  This URL points to the T12 paper, and there are links to relevant surveys, but it is not clear how to obtain the exact subset of 142 galaxies used. Please provide sufficient details so that a researcher could obtain them (e.g., a list of ids or a packaged data set with just the SEDs for those 142 galaxies).

2. The paper now asserts that ANNs outperform chi-square methods (top of page 4, left column) - in what sense?  Accuracy (which as we've discussed may not be measurable)?  Runtime?  Something else?

3. Section 4.3: I suggest putting the numeric results for the chi-squared agreement score (paragraph 2) and silhouette score (paragraph 4) into tables to improve their readability.

4. Section 4.2.1 - typo - space needed between the symbol for "angstroms" and the word following it (e.g., "range", "break" - in the new bolded text).

### 2018-03-25 main0.10.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-08-11 main0.09.tex
@@
 
-\newcommand \boldit {\textbf{\textit{}}}
+% 22Jan2018: following 2 commands now work (they didn't before)
+\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
+% for changed text to be bold: uncomment following line and comment out line after that
+\newcommand{\changed}[1]{\textbf{#1}} 
+% for changed text to be normal: comment out line above this, uncomment line below
+%\newcommand{\changed}[1]{#1}
 
@@
 
-\import{sections0.09/}{intro0.09.tex}
+\import{sections0.10/}{intro0.10.tex}
 
-\import{sections0.09/}{data0.09.tex}
+\import{sections0.10/}{data0.10.tex}
 
-\import{sections0.09/}{method0.09.tex}
+\import{sections0.10/}{method0.10.tex}
 
-\import{sections0.09/}{results0.09.tex}
+\import{sections0.10/}{results0.10.tex}
 
-%referee: Section 5 has been greatly improved and expanded; it now summarizes key observations that arose from the study and emphasizes its importance in further study of galaxy spectra.
-In particular, the final paragraph (and the end of section 4.4) provides an excellent summary of why the SOM methods can be of unique value.
-It should also include a statement about the results of other assessments (Fleiss kappa and silhouette) to provide a complete summary of the findings.
-
-\section{Summary}
-\label{sec: summary_SOMZ}
-
-    Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.).
-    In this work we presented a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
-    Based on our experience we suggest some general guidelines for use of SOMs in galaxy spectral classification.
-    If a broad and general classification is required, networks can have one dimension with a few neurons. 
-    If one needs more detailed classifications, a higher number of neurons should be used.
-    Since self-organizing maps do not include the uncertainty of input parameters, sometimes too much attention to detail can cause problems in classifications. 
-    When using the SOM method, one should consider whether small differences between objects are physically meaningful when separating two groups from each other.
-
-    We used SOMs to classify the template spectra of \citetalias{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
-    By varying the size of the networks, we found the relative similarity between the \citetalias{Kinney96} template classes, which can be roughly ordered in one dimension by their amount of star formation.
-     A one-dimensional network with 22 neurons was needed in order to
-    separate all 12 \citetalias{Kinney96} spectra; we concluded that \citetalias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
-    Two-dimensional networks allow more freedom in the galaxy spectral classification.
-    Training $12\times 12$ neurons with the \citetalias{Kinney96} spectra, we found that the two dimensions of the resulting self-organized maps corresponded roughly to strength of star formation and amount of extinction.
-The one-dimensional self-organizing map ordering combined these two properties, with the highest-extinction template SB6 appearing between two less-extincted templates (Sb and Sc).
-
-    A sample of 142 high-redshift galaxy spectra from \citetalias{Hossein12} was classified by the trained networks.
-  This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates although many of the spectra fall in between template classes.
-     In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
-    {\bf The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12}    could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.}
-    Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb).
-Spectra with emission lines or ultraviolet emission showed more variable classification results.
-    Classification produced by self-organized maps showed closer correspondence than the supervised method results to the classification from a chi-squared match.
-    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
-
-The relations between group-averaged properties of the sample galaxies using the SOM-based classification were found to be consistent with those from previous studies. 
-    The self-organizing map method can order the spectra in such a way as to also match the order along the age/star formation rate and specific star formation rate-stellar mass relations.
-    Such an ordered classification does not naturally arise from other methods such as K-means clustering and supervised artificial neural networks.
-    Ordered classification can be used to investigate underlying physical causes of changes in properties between groups and for this reason we conclude that self-organized maps can be a highly useful tool in exploratory analysis of astronomical spectra.
+\import{sections0.10/}{summary0.10.tex}
 
 \section*{ACKNOWLEDGMENTS}
-The authors thank the referee for insightful comments which helped us to improve the work.
+The authors thank the referee for thorough and insightful comments which helped us to improve the work.
 The authors thank S. Lianou, A. Tammour, S.C. Gallagher, R.G. Abraham, M. Daley and A. Sigut for their useful comments. 
@@
 
-\import{sections0.09/}{apps_0.09.tex}
+\import{sections0.10/}{apps_0.10.tex}
 \end{document}

### 2018-03-25 sections0.08/main0.08.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-09-27 main0.09.tex
@@
 \newcommand \boldit {\textbf{\textit{}}}
-\newcommand \changed {\textbf{}}
 
@@
 
-\import{sections0.09/}{intro0.09.tex}
+\import{sections0.08/}{intro0.08.tex}
 
-\import{sections0.09/}{data0.09.tex}
+\import{sections0.08/}{data0.08.tex}
 
-\import{sections0.09/}{method0.09.tex}
+\import{sections0.08/}{method0.08.tex}
 
-\import{sections0.09/}{results0.09.tex}
+\import{sections0.08/}{results0.08.tex}
 
-%referee: Section 5 has been greatly improved and expanded; it now summarizes key observations that arose from the study and emphasizes its importance in further study of galaxy spectra.
-In particular, the final paragraph (and the end of section 4.4) provides an excellent summary of why the SOM methods can be of unique value.
-It should also include a statement about the results of other assessments (Fleiss kappa and silhouette) to provide a complete summary of the findings.
-
-\section{Summary}
+\section{Summary and Future Applications}
 \label{sec: summary_SOMZ}
@@
     Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.).
-    In this work we presented a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
-    Based on our experience we suggest some general guidelines for use of SOMs in galaxy spectral classification.
+    {\bf In this work we presented a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
+    Based on our experience we suggest some general guidelines for use of SOM in galaxy spectral classification.}
     If a broad and general classification is required, networks can have one dimension with a few neurons. 
@@
     separate all 12 \citetalias{Kinney96} spectra; we concluded that \citetalias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
-    Two-dimensional networks allow more freedom in the galaxy spectral classification.
+    \textbf{Two-dimensional networks allow more freedom in the galaxy spectral classification.
     Training $12\times 12$ neurons with the \citetalias{Kinney96} spectra, we found that the two dimensions of the resulting self-organized maps corresponded roughly to strength of star formation and amount of extinction.
-The one-dimensional self-organizing map ordering combined these two properties, with the highest-extinction template SB6 appearing between two less-extincted templates (Sb and Sc).
+The one-dimensional self-organizing map ordering combined these two properties, with the highest-extinction template SB6 appearing between two less-extincted templates (Sb and Sc).}
 
-    A sample of 142 high-redshift galaxy spectra from \citetalias{Hossein12} was classified by the trained networks.
+    \textbf{A sample of 142 high-redshift galaxy spectra from \citetalias{Hossein12} was classified by the trained networks.
   This particular sample of high-redshift galaxies is well-described by the range of the \citetalias{Kinney96} templates although many of the spectra fall in between template classes.
      In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
- The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12}    could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.
+    The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12} with the same templates and galaxy sample  could not classify 37 out of 142 spectra.
     Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb).
@@
     Classification produced by self-organized maps showed closer correspondence than the supervised method results to the classification from a chi-squared match.
-    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
+    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.}
 
-The relations between group-averaged properties of the sample galaxies using the SOM-based classification were found to be consistent with those from previous studies. 
+\textbf{The relations between group-averaged properties of the sample galaxies in the using the SOM-based classification were found to be consistent with those from previous studies. 
     The self-organizing map method can order the spectra in such a way as to also match the order along the age/star formation rate and specific star formation rate-stellar mass relations.
@@
     Ordered classification can be used to investigate underlying physical causes of changes in properties between groups and for this reason we conclude that self-organized maps can be a highly useful tool in exploratory analysis of astronomical spectra.
+}
 
@@
 
-\import{sections0.09/}{apps_0.09.tex}
+\import{sections0.08/}{apps_0.08.tex}
 \end{document}

### 2018-03-25 sections0.08_for_editor/main0.08_for_editor.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-09-27 main0.09.tex
@@
 
-\import{sections0.09/}{intro0.09.tex}
+\import{sections0.08_for_editor/}{intro0.08.tex}
 
-\import{sections0.09/}{data0.09.tex}
+\import{sections0.08_for_editor/}{data0.08.tex}
 
-\import{sections0.09/}{method0.09.tex}
+\import{sections0.08_for_editor/}{method0.08.tex}
 
-\import{sections0.09/}{results0.09.tex}
+\import{sections0.08_for_editor/}{results0.08.tex}
 
-%referee: Section 5 has been greatly improved and expanded; it now summarizes key observations that arose from the study and emphasizes its importance in further study of galaxy spectra.
-In particular, the final paragraph (and the end of section 4.4) provides an excellent summary of why the SOM methods can be of unique value.
-It should also include a statement about the results of other assessments (Fleiss kappa and silhouette) to provide a complete summary of the findings.
-
-\section{Summary}
+\section{Summary and Future Applications}
 \label{sec: summary_SOMZ}
@@
     In this work we presented a detailed comparison between different types of self-organizing maps and other methods used to classify galaxy spectra.
-    Based on our experience we suggest some general guidelines for use of SOMs in galaxy spectral classification.
+    Based on our experience we suggest some general guidelines for use of SOM in galaxy spectral classification.
     If a broad and general classification is required, networks can have one dimension with a few neurons. 
@@
      In the two-dimensional network, only 23 galaxies occupied exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
- The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12}    could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.
+    The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by   \citetalias{Hossein12} with the same templates and galaxy sample  could not classify 37 out of 142 spectra.
     Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb).
@@
 
-The relations between group-averaged properties of the sample galaxies using the SOM-based classification were found to be consistent with those from previous studies. 
+The relations between group-averaged properties of the sample galaxies in the using the SOM-based classification were found to be consistent with those from previous studies. 
     The self-organizing map method can order the spectra in such a way as to also match the order along the age/star formation rate and specific star formation rate-stellar mass relations.
@@
 
-\import{sections0.09/}{apps_0.09.tex}
+\import{sections0.08_for_editor/}{apps_0.08.tex}
 \end{document}

### 2018-03-25 sections0.09/email_to_editor.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

Dear Mrs Williams,

Thank you for your patience with the revisions for this paper. We are committed to completing the process. To avoid further delays, we would like to ask for clarification from the referee to ensure that we understand the request in his/her most recent report.

The particular part of the report that we are unclear about are the three paragraphs which appear before "Additional minor comments and suggestions". We don't understand what is meant by "compare to its performance (on an external standard)" - as the referee says, it's not obvious why chi-square fitting should be considered the standard.

We are also confused by the final paragraph of these comments. The true labels of the 142 galaxies are unknown, which we understand to mean that there is no external reference for the classification accuracy - but this is the opposite of what the last sentence implies. Is it possible that "true labels.. are unknown" should read "true labels ..are known"?

We would be grateful for any clarification that could be offered. We very much appreciate the referee's careful attention and thoughtful comments.

Editor's Answer:
“By "compare to an external standard" I mean "compare performance on a labeled sample", i.e., one labeled by humans, to see how well the proposed method (and a simple nearest-neighbors baseline) can predict those classifications.

My suggestion with the 142 galaxies was that, if their types are not previously known, to have a human label them (i.e., assign which of the 12 K96 templates each one should belong to).  That would allow for an assessment of the automated classification quality.  If no human can do this, then (as stated) there is no way to assess classification accuracy of the proposed methods.”

### 2018-03-25 sections0.09/summary0.09.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-09-27 main0.09.tex
@@
-\documentclass[useAMS,usenatbib]{mn2e}
-\usepackage{amsmath}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=True,
-    linkcolor=red,
-    filecolor=magenta,      
-    urlcolor=cyan,
-    citecolor=blue,
-}
-\usepackage{graphicx}
-\usepackage{natbib}
-\bibliographystyle{mn2e}
-\usepackage{times}
-\usepackage{float}
-\usepackage{subcaption}
-\usepackage{multirow}
-\usepackage{color,soul}
-\usepackage{import}
-\usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{multicol}        % Multi-column entries in tables
-\usepackage{pgffor}
-\usepackage{commath}	% Extra maths symbols
-
-\newcommand \boldit {\textbf{\textit{}}}
-\newcommand \changed {\textbf{}}
-
-\newcommand \aaj {A\&A}
-\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
-\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
-\newcommand \afz {Afz}%: Astrofizika
-\newcommand \aj {AJ}%: Astronomical Journal (the)
-\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
-\newcommand \apj {ApJ}
-\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
-\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
-\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
-\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
-\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
-\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
-\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
-\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
-%\newcommand {Nature}%(do not abbreviate)
-\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
-\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
-\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
-\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
-%\newcommand {Science }%}%(do not abbreviate)
-\newcommand \sva {SvA}%: Soviet Astronomy
-\newcommand \aap {A\&A} %:Astronomy & Astrophysics
-\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
-
-\begin{document}
-% TITLE
-\defcitealias{Hossein12}{T12}
-\defcitealias{Kinney96}{K96}
-\defcitealias{Noll09}{N09}
-
-\title[Classifying high-$z$ galaxy spectra]{Classifying galaxy spectra at $0.5<z<1$ with self-organizing maps}
-%\author{rahmani.sahar}
-\date{\today}
-\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
-srahma49@uwo.ca}, H.~Teimoorinia$^{3,4}$, P.~Barmby$^{1,2}$\\
-$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
-$^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
-$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
-$^{4}$NRC Herzberg Astronomy and Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7, Canada }
-\maketitle
-
-\begin{abstract}
-    The spectrum of a galaxy contains information about its physical properties.
-    Classifying spectra using templates helps elucidate the nature of a galaxy's energy sources.
-    In this paper, we investigate the use of self-organizing maps in classifying galaxy spectra against templates.
-    We trained semi-supervised self-organizing map networks using a set of
-    templates covering the wavelength range from far ultraviolet to near infrared. 
-    The trained networks were used to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$ and the results compared to classifications performed using K-means clustering, a supervised neural network, and chi-squared minimization.
-    Spectra corresponding to quiescent galaxies were more likely to be classified similarly by all methods while starburst spectra showed more variability.
-    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
-     The class ordering provided by the one-dimensional self-organizing maps corresponds to an ordering in physical properties, a potentially important feature for the exploration of large datasets.
-\end{abstract}
-\begin{keywords} 
- galaxies: high-redshift, 
- galaxies: spectra, 
- methods: observational, 
- methods: statistical, 
- methods:data analysis
-\end{keywords}
-
-\import{sections0.09/}{intro0.09.tex}
-
-\import{sections0.09/}{data0.09.tex}
-
-\import{sections0.09/}{method0.09.tex}
-
-\import{sections0.09/}{results0.09.tex}
-
-%referee: Section 5 has been greatly improved and expanded; it now summarizes key observations that arose from the study and emphasizes its importance in further study of galaxy spectra.
-In particular, the final paragraph (and the end of section 4.4) provides an excellent summary of why the SOM methods can be of unique value.
-It should also include a statement about the results of other assessments (Fleiss kappa and silhouette) to provide a complete summary of the findings.
-
 \section{Summary}
@@
     The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by \citetalias{Hossein12} could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.
+
+    \changed{
     Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb). 
@@
     Classification produced by self-organized maps showed closer correspondence than the supervised method results to the classification from a chi-squared match.
-    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
+    Using the Fleiss kappa index to compare classifications showed that the K-means, supervised ANN and one-dimensional SOM are in fair agreement.
+    One-dimensional self-organized-map based classification resulted in a 
+    higher silhouette score for than classification using chi-squared minimization or the supervised neural network, indicating that the galaxies classed together by the SOM had more similar spectra.}
 
@@
     Ordered classification can be used to investigate underlying physical causes of changes in properties between groups and for this reason we conclude that self-organized maps can be a highly useful tool in exploratory analysis of astronomical spectra.
-
-\section*{ACKNOWLEDGMENTS}
-The authors thank the referee for insightful comments which helped us to improve the work.
-The authors thank S. Lianou, A. Tammour, S.C. Gallagher, R.G. Abraham, M. Daley and A. Sigut for their useful comments. 
-S.R. and P.B. also acknowledge research support from the Natural Sciences and Engineering Research Council of Canada.
-
-\bibliographystyle{apalike}
-\bibliography{ref_mining_h.bib}
-
-\import{sections0.09/}{apps_0.09.tex}
-\end{document}

### 2018-03-25 sections0.10/intro0.10.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-09-18 sections0.09/intro0.09.tex
@@
+% Referee comments:
+%1a.
+The authors state (in their response, but not in the paper) that there is no known correct classification for these galaxies.
+Please add this necessary context for the paper.
+This positions the work in the world of of (semi-) supervision, since correct labels are not available.
+
+%1b.
+The use of the chi-squared template assignment needs to be clearly explained and justified.
+The author response states that this is a common method employed in the research community.
+This too should be added to the paper to justify why it was chosen as a reference point (ideally with references to show its common usage by others).
+
+%1c.
+If chi-squared minimization is the current most widely used method, then the paper needs to make a strong case for why to bother using a different method (SOMs) that only imperfectly approximates (i.e., does not have 100% agreement with) the chi-squared method.
+I expect that the benefit is obtaining the insights provided from the analysis of the trained SOM structure, which cannot be achieved with the chi-squared method.
+Make this explicit (up front, in the Introduction) so the reader understands why they might want to bother using this new method instead of chi-squared.
+
 \section{Introduction}
 \label{sec: intro_somz}
-
-%Referee: Great list of questions near the end of section 1.
-I recommend moving (or merging) the background information/explanation of the methods that are tested to section 3 so that this important content (the goals of the work) is featured more prominently and early on.
-% DONE, but needs looked at again to make sure it makes sense.
 
@@
 For each of the 142 galaxies, we find the best chi-squared fit among the 12 templates to use as a base for comparing the methods' performance.
-We compute an agreement score for each method and also use the Fleiss Kappa index \citet{Fleiss71} to test interrater reliability 
+We compute an agreement score for each method and also use the Fleiss Kappa index \citep{Fleiss71} to test interrater reliability 
 between the methods.

### 2018-03-25 sections0.10/method0.10.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-09-18 sections0.09/method0.09.tex
@@
+%Referee comments
+%1d. The authors stated "We have added a footnote to clarify how chi-squared was computed."  I cannot find this footnote.  Please define this method in section 3.
+
+%1e. The metrics proposed in section 3.4 are
+%- agreement of algorithm X's output with that obtained by a chi-squared minimization
+%- Fleiss kappa
+%- silhouette score (S) - also referred to as within-cluster similarity
+
+%I suggest referring to the first metric as "chi-squared agreement" (here and throughout, including the discussion of results starting in section 4.3) or some other term to capture the fact that it specifically relates an algorithm to the chi-squared results.
+
+%I am still confused by the the Fleiss kappa results.
+If the chi-squared method is the point of reference to use (as with the proposed agreement metric), why does it not appear here?
+What does it tell us to determine that the k-means, supervised ANN, and SOMs are in "fair" agreement?
+(with each other?)  Is that a goal?
+The chi-squared agreement analysis showed higher agreement with the SOM than with the other methods, so I wouldn't expect (nor want) there to be high kappa values between those three.
+As currently presented, I don't think this adds anything to the paper, and I suggest omitting it (or rephrasing as a second measure of agreement with chi-squared, and computing values accordingly).
+
+%2. The re-organization of the paper is helpful for the Introduction, but the new content needs to be better integrated into sections 3.1 and 3.2.  Currently it reads disjointedly.
+
+%2a.
+Section 3.1: The notation "N \in R^m" does not make sense, especially since m is not defined.
+Consider something like "N objects, each represented by m features" or "N objects x \in R^m, where m is the number of features used to represent each object".
+
+%Note that the following paragraph uses a lower-case "n" for the number of objects.  Please make these consistent.
+
+%2b. Section 3.2:
+%- The text prior to 3.2.1 is now rather unwieldy and hard to follow.
+It jumps back and forth between ANNs and SOMs.
+I suggest making a new 3.2 that covers "Artificial neural networks" (since the paper treats them as an alternative to SOMs later) and 3.3 can be devoted to SOMs as a specialized (semi-supervised) version of ANNs.
+Merge old and new content to make a logical flow.
+%- Provide a citation for ANNs when first mentioned.
+%- What is meant by "a set of training methods" (end of page 3, column 2)?  Typically only a single training method (e.g., backpropagation) is used.
+%- Standard practice is to avoid having a single subsection (3.2.1).
+Remove the subsection heading, or make two (3.2.1, 3.2.2) on different sub-topics.
+For example, section 3.3 could (should) be merged into the SOM section, as a subsection.
+
+% from minor ref comments:
+%2. The paper now asserts that ANNs outperform chi-square methods (top of page 4, left column) - in what sense?  Accuracy (which as we've discussed may not be measurable)?  Runtime?  Something else?
+
 \section{METHOD}
@@
 When the radius of the neighbourhood function goes to zero, the SOM algorithm loses its ordering power and acts like K-means clustering.
-
-%Referee: The objective function for k-means (equation 1, page 4) is not quite clear as it does not indicate what the "min" is taken over; I suggest adding a subscript "k" here (assuming that is what was intended).
-% DONE
 
@@
      We use several metrics to measure the degree of agreement between classification methods. 
-     As a baseline method for assigning galaxy spectra to template classes, we compute the value of chi-squared between each galaxy and each template and assign the galaxy to the template class with lowest chi-squared value.
+     As a baseline method for assigning galaxy spectra to template classes, we compute the value of chi-squared between each galaxy and each template%
+\footnote{The \citetalias{Kinney96} template spectra do not have tabulated uncertainties and we assume them to be photon-noise dominated for the purposes of computing $\chi^2$.}
+     and assign the galaxy to the template class with lowest chi-squared value. 
      A metric of agreement with this classification is an agreement score, computed as follows.

### 2018-03-25 sections0.10/results0.10.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-08-11 sections0.08_for_editor/results0.08.tex
@@
+% referee comments (minor)
+%3. Section 4.3: I suggest putting the numeric results for the chi-squared agreement score (paragraph 2) and silhouette score (paragraph 4) into tables to improve their readability.
+
+%4. Section 4.2.1 - typo - space needed between the symbol for "angstroms" and the word following it (e.g., "range", "break" - in the new bolded text).
+
 \section{RESULTS AND DISCUSSION}
@@
         \centering
-        \includegraphics[width=.99\textwidth, height=         7.5cm]{k_means_images/classified_group_in_4cluster_kinney.png}
+        \includegraphics[width=.99\textwidth, height=         7.5cm]{k_means_images/classified_group_in_4cluster_kinney_1.pdf}
     \end{subfigure}
@@
     \caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right).
-Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
+Note that both methods randomly assign the initial values for their analysis, therefore the cluster labels are only used for distinguishing cluster membership.}
     \label{fig: som_k_means_4}
@@
     We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters.
-
     Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra into 4 groups using both K-means and SOMs.
@@
     Templates B, E, S0 and Sa are grouped in the same cluster/neuron in both K-means and $1\times4$-sized SOM. 
-    K-means grouped the Sb template with the above templates, but the SOM network classified it as a separate group.
-    The K-means method clustered the Sc template as a separate group, while the SOM network grouped it with SB5 and SB6. 
-    Another noticeable difference is that K-means clustered the SB1 and SB2 templates in one group and SB3 to SB6 in another while
-    the SOM network grouped the SB1 to SB4 templates in one neuron and SB5 and SB6 in another.
-    As Fig.~\ref{fig: som_k_means_4} shows, K-means clustering of the templates produced groups more similar to each other, while SOM emphasizes the templates' differences.
+    K-means grouped the Sb template with the above templates, but the SOM network classified it as a separate group, possibly because it is much more noisy in the ultraviolet range.
+    The K-means method clustered the Sc template as a separate group, 
+    likely due to its distinct features in the 3000--4000 \AA range, while the SOM network grouped it with SB5 and SB6. 
+    Classifying the Sc template in the group with SB5 and SB6 obscures the peak feature in the Sc template.
+    However, when the number of SOM nodes is increased (e.g. in Fig.~\ref{fig: 1by22T}), the Sc template separates and occupies a single neuron.
+    Another noticeable difference is that K-means clustered the SB1 and SB2 templates in one group and SB3 to SB6 in another, while the SOM network grouped the SB1 to SB4 templates in one neuron and SB5 and SB6 in another.
+    SB1 and S2 have similar strong emission lines in the blue, while SB3--6 show H$\alpha$ emission but only weaker emission lines at shorter wavelengths;
+    the SB5 and SB6 templates are flatter with a less-pronounced 4000 \AA break than the remaining SB templates.
+    By comparing the membership of different clusters in Table~\ref{tab:kmeans_som4} we can see that K-means clustering emphasizes the input templates' similarities, while SOM emphasizes the templates' differences.
 
@@
     \hline
-    B                                & 3               & 1                         \\
-    E                                & 3               & 1                         \\
-    S0                               & 3               & 1                         \\
-    Sa                               & 3               & 1                         \\
-    Sb                               & 3               & 2                         \\
-    Sc                               & 4               & 3                         \\
-    SB1                              & 2               & 4                         \\
-    SB2                              & 2               & 4                         \\
-    SB3                              & 1               & 4                         \\
-    SB4                              & 1               & 4                         \\
-    SB5                              & 1               & 3                         \\
-    SB6                              & 1               & 3                        \\
+    B                                & C               & 1                         \\
+    E                                & C               & 1                         \\
+    S0                               & C               & 1                         \\
+    Sa                               & C               & 1                         \\
+    Sb                               & C               & 2                         \\
+    Sc                               & D               & 3                         \\
+    SB1                              & B               & 4                         \\
+    SB2                              & B               & 4                         \\
+    SB3                              & A               & 4                         \\
+    SB4                              & A               & 4                         \\
+    SB5                              & A               & 3                         \\
+    SB6                              & A               & 3                        \\
     \hline
@@
                     \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
-                    %\caption{$1\times2$ weight map}
-                     %\label{fig: 1by3T}
                 \end{subfigure}
@@
                      \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2_fluxdensity.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by3Thits}
                 \end{subfigure}
@@
 
-       To compare results from SOM, K-means, and unsupervised ANN, we first consider how well these methods matched a simple chi-squared fitting classification. 
+       To compare results from SOM, K-means, and supervised ANN, we first consider how well these methods matched a simple chi-squared fitting classification. 
         Matching galaxy spectra to templates using chi-squared, we found that not all of the templates had matches among the galaxy sample: no galaxy spectra were best-matched to the B, E, or Sc templates.
@@
         Summing the classification score over all galaxies in the sample allows us to compare how well each technique matched the results of chi-squared fitting.
-        The totals were K-means 124, $1\times4$-sized SOM 103, $1\times12$-sized SOM 111.5, $1\times22$-sized SOM 79, and unsupervised ANN 52.
+        The totals were K-means 124, $1\times4$-sized SOM 103, $1\times12$-sized SOM 111.5, $1\times22$-sized SOM 79, and supervised ANN 52.
         This shows that the K-means method and $1\times12$-sized SOM have the most similarity with minimum chi-square fitting.
@@
         The score-5 galaxies classified similarly by all methods were primarily (60 per cent) in the Sa template group. 
-        The score $>=3$ galaxies were predominantly SB1, Sa, and Sb type (32, 28, 18 per cent, respectively).
+        The score $\geq 3$ galaxies were predominantly SB1, Sa, and Sb type (32, 28, 18 per cent, respectively).
         The different methods show the most agreement for galaxies similar to the SB1 and Sa templates, with less agreement on the high-extinction starburst types (SB5, SB6).
 
-       We also used the Fleiss kappa index \citet{landis77} to 
+       We also used the Fleiss kappa index \citep{Fleiss71} to 
         measure the agreement between methods. 
         Here the `raters' are the different methods classifying a specific number of objects (i.e. 142 galaxies) to a number of classes (i.e. 12 templates).
-        We computed two different values of Fleiss kappa, between  K-means, unsupervised ANN, and either 
-         $1\times12$-sized or $1\times22$-sized SOMs.
+        We computed values of Fleiss kappa twice: firstly to compare results from K-means, supervised ANN, and $1\times12$-sized SOM and secondly to compare results from K-means, supervised ANN, and $1\times22$-sized SOM.
         The resulting values were $\sim 27$ per cent and $\sim 21$ per cent, respectively.
@@
 In this case we can compare scores directly and conclude that the self-organized map yields groups with more internal similarity.
-This is in contrast to the comparison between K-means and self-organized maps for the templates alone (see Section\ref{sec: Kmeansvssom}) where K-means clustering  produced groups more similar to each other, and emphasizes that the exact data used in a clustering process can strongly affect the outcome.
+This is in contrast to the comparison between K-means and self-organized maps for the templates alone (see Section~\ref{sec: Kmeansvssom}) where K-means clustering  produced groups more similar to each other, and emphasizes that the exact data used in a clustering process can strongly affect the outcome.
 
@@
         \begin{figure*}
-\includegraphics[width=\textwidth]{images0.01/1d/fig11_new_bw.png}
+\includegraphics[width=\textwidth]{images0.01/1d/fig11_new_col.png}
         \caption{

### 2018-03-25 sections0.10/summary0.10.tex
Made new version to address latest (Feb 2018) ref report. Incorporated ref rept into tex files as comments.

--- 2017-09-27 main0.09.tex
@@
     The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks: the supervised training method used by \citetalias{Hossein12} could not classify 37 out of 142 spectra in galaxy sample as matching one of the same set of templates.
+
     Comparing different classification methods, we found that spectra classified similarly by all methods were well-matched to quiescent templates (\citetalias{Kinney96} Sa and Sb). 
@@
     Classification produced by self-organized maps showed closer correspondence than the supervised method results to the classification from a chi-squared match.
-    Compared to classification using chi-squared minimization or the supervised neural network, the galaxies classed together by the self-organizing map had more similar spectra.
+    Using the Fleiss kappa index to compare classifications showed that the K-means, supervised ANN and one-dimensional SOM are in fair agreement.
+    One-dimensional self-organized-map based classification resulted in a 
+    higher silhouette score for than classification using chi-squared minimization or the supervised neural network, indicating that the galaxies classed together by the SOM had more similar spectra.
 
